### 2018-10-15 meta_RL_analyses.Rmd
loading data

---
title: "Meta RL analyses"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
num_runs = 3
results_dir = "results/results_smd/"
```

```{r}
reward_d = data.frame()
for (run_i in 0:(num_runs-1)) {
  filename = sprintf("%srun%i_%s.csv", results_dir, run_i, "new_rewards")
  if (!file.exists(filename)) {
    next
  }
  this_d = read.csv(filename, header=T) %>%
    mutate(run = run_i)
  reward_d = bind_rows(reward_d, this_d)
}

reward_d = reward_d %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str))
```

### 2018-10-15 meta_learning.py
Better holdouts: hold out all loser variations of a game

@@ -40,7 +40,7 @@ config = {
     "new_init_meta_learning_rate": 1e-6,
 
     "lr_decay": 0.85,
-    "meta_lr_decay": 0.85,
+    "meta_lr_decay": 0.9,
 
     "lr_decays_every": 100,
     "min_learning_rate": 1e-7,
@@ -57,7 +57,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_longer/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_more_heldout_smd/",
     "save_every": 20, 
     "eval_all_hands": True, # whether to save guess probs on each hand & each game
 
@@ -65,8 +65,14 @@ config = {
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
     "new_tasks": [{"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": False}], # will be removed
-                                                                  # from base tasks
+                  "black_valuable": False, "suits_rule": False},
+		  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": False},
+		  {"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": True},
+		  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": True}], # will be removed
+                                                                # from base tasks
 
     "new_meta_tasks": [],
 

### 2018-10-15 meta_RL_analyses.Rmd

@@
 results_dir = "results/results_smd/"
+
+new_game_strs = c("game_straight_flush_l_1_bv_1_sr_0")
 ```
@@
          black_valuable = grepl("bv_1", game_str),
-         suits_rule = grepl("sr_1", game_str))
+         suits_rule = grepl("sr_1", game_str),
+         is_new_game = game_str %in% new_game_strs)
 ```
+
+```{r}
+avg_reward_d = reward_d %>%
+  select(-game_str) %>%
+  filter(epoch == 0) %>%
+  group_by(game_type, is_new_game) %>%
+  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
+            se_reward = sd_reward/sqrt(n()), 
+            ci_lo = avg_reward - 1.96*se_reward, 
+            ci_hi = avg_reward + 1.96*se_reward)
+```
+
+```{r}
+theme_set(theme_bw() + 
+            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
+```
+
+```{r}
+ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
+  geom_bar(stat="identity", position="dodge") +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
+  scale_fill_brewer(palette="Set2")
+```

### 2018-10-15 meta_learning.py
And refresh buffers faster

@@ -40,13 +40,13 @@ config = {
     "new_init_meta_learning_rate": 1e-6,
 
     "lr_decay": 0.85,
-    "meta_lr_decay": 0.9,
+    "meta_lr_decay": 0.85,
 
     "lr_decays_every": 100,
     "min_learning_rate": 1e-7,
 
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
-    "refresh_mem_buffs_every": 1000, # how many epochs between updates to buffers
+    "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
     "max_base_epochs": 40000,
     "max_new_epochs": 1000,

### 2018-10-16 meta_learning.py
Learning w/o hints

@@ -29,6 +29,9 @@ config = {
     "num_output": 3, # bet 0, bet 1, bet 2 
     "num_outcome": (3 + 1) + (5 + 2 + 2 + 2), # 3 possible bets (actions) + reward
                                            # + 5 games + 3 binary options
+    "game_hints_on_examples": False, # if true, provides game labels on input,
+                                     # else replaced with zeros
+
     "num_hidden": 32,
     "num_hidden_hyper": 128,
 
@@ -57,9 +60,9 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_more_heldout_smd/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_no_hints/",
     "save_every": 20, 
-    "eval_all_hands": True, # whether to save guess probs on each hand & each game
+    "eval_all_hands": False, # whether to save guess probs on each hand & each game
 
     "memory_buffer_size": 1024, # How many memories of each task are stored
     "meta_batch_size": 768, # how many meta-learner sees
@@ -180,6 +183,7 @@ class meta_model(object):
         self.num_output = config["num_output"]
         self.num_outcome = config["num_outcome"]
         self.bets = config["bets"]
+        self.game_hints_on_examples = config["game_hints_on_examples"]
 
         base_tasks = config["base_tasks"]
         base_meta_tasks = config["base_meta_tasks"]
@@ -482,6 +486,8 @@ class meta_model(object):
     def encode_game(self, task):
         """Takes a task dict, returns vector appropriate for input to graph."""
         vec = np.zeros(11)
+        if not self.game_hints_on_examples: # no hints for you!
+            return vec
         game_type = t["game"]
         black_valuable = t["black_valuable"]
         suits_rule = t["suits_rule"]

### 2018-10-16 meta_learning.py
Parameter tweaks

@@ -43,7 +43,7 @@ config = {
     "new_init_meta_learning_rate": 1e-6,
 
     "lr_decay": 0.85,
-    "meta_lr_decay": 0.85,
+    "meta_lr_decay": 0.9,
 
     "lr_decays_every": 100,
     "min_learning_rate": 1e-7,

### 2018-10-18 meta_RL_analyses.Rmd
Some refactoring, and meta_true basic analysis

@@
 ```{r}
-num_runs = 3
-results_dir = "results/results_smd/"
+num_runs = 1
+results_dir = "results/results_no_hints_2/"
 
-new_game_strs = c("game_straight_flush_l_1_bv_1_sr_0")
+new_game_strs = c("game_straight_flush_l_1_bv_0_sr_0",
+                  "game_straight_flush_l_1_bv_1_sr_0",
+                  "game_straight_flush_l_1_bv_0_sr_1",
+                  "game_straight_flush_l_1_bv_1_sr_1")
 ```
 
+# utils
+
 ```{r}
-reward_d = data.frame()
+load_d = function(results_dir, num_runs, file_type) {
+  d = data.frame()
   for (run_i in 0:(num_runs-1)) {
-  filename = sprintf("%srun%i_%s.csv", results_dir, run_i, "new_rewards")
+    filename = sprintf("%srun%i_%s.csv", results_dir, run_i, file_type)
     if (!file.exists(filename)) {
@@
       mutate(run = run_i)
-  reward_d = bind_rows(reward_d, this_d)
+    d = bind_rows(d, this_d)
   }
+  return(d)
+}
+```
+
+# meta-learning tests
+
+```{r}
+reward_d = load_d(results_dir, num_runs, "new_rewards")
 
@@
 ```
+
+# meta mapping (true) evaluation
+
+```{r}
+meta_d = load_d(results_dir, num_runs, "new_meta_true_losses")
+
+meta_d = meta_d %>%
+  filter(epoch == 0) %>%
+  gather(map_str, reward, -c(run, epoch)) %>%
+  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
+  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
+```
+
+```{r}
+avg_meta_d = meta_d %>%
+  group_by(run, meta_task, is_new) %>%
+  summarize(avg_reward = mean(reward)) %>%
+  group_by(meta_task, is_new) %>%
+  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward)) %>%
+
+```
+
+```{r}
+ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
+  geom_bar(stat="identity", position="dodge") +
+# geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
+  scale_fill_brewer(palette="Set2")
+```

### 2018-10-18 meta_learning.py
Bugfix in epoch indexing, parameters that work better for no hints regime

@@ -47,6 +47,7 @@ config = {
 
     "lr_decays_every": 100,
     "min_learning_rate": 1e-7,
+    "min_meta_learning_rate": 1e-6,
 
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
@@ -60,7 +61,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_no_hints/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_h128/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
 
@@ -919,7 +920,8 @@ class meta_model(object):
             lr_decay = config["lr_decay"]
             meta_lr_decay = config["meta_lr_decay"]
             min_learning_rate = config["min_learning_rate"]
-            for epoch in range(num_epochs):
+            min_meta_learning_rate = config["min_meta_learning_rate"]
+            for epoch in range(1, num_epochs+1):
                 if epoch % config["refresh_mem_buffs_every"] == 0:
                     self.play_games(num_turns=config["memory_buffer_size"],
                                     include_new=include_new,
@@ -960,7 +962,7 @@ class meta_model(object):
                 if epoch % lr_decays_every == 0 and epoch > 0 and learning_rate > min_learning_rate:
                     learning_rate *= lr_decay
 
-                if epoch % lr_decays_every == 0 and epoch > 0 and meta_learning_rate > min_learning_rate:
+                if epoch % lr_decays_every == 0 and epoch > 0 and meta_learning_rate > min_meta_learning_rate:
                     meta_learning_rate *= meta_lr_decay
 
 

### 2018-10-19 meta_RL_analyses.Rmd
Bugfix and new results

@@
 num_runs = 1
-results_dir = "results/results_no_hints_2/"
+results_dir = "results/results_h128/"
 
@@
   group_by(meta_task, is_new) %>%
-  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward)) %>%
+  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward))
 

### 2018-10-22 meta_RL_analyses.Rmd
Embeddings, etc

@@
 ```{r}
-num_runs = 1
-results_dir = "results/results_h128/"
+num_runs = 5
+results_dir = "results/results_h256/"
 
@@
                   "game_straight_flush_l_1_bv_1_sr_1")
+
+meta_mapping_tasks = c("toggle_losers", "toggle_black_valuable", "toggle_suits_rule")
+meta_classification_tasks = c("is_losers", "is_black_valuable", "is_suits_rule",
+                              "is_high_card", "is_match", "is_straight_flush", "is_pairs_and_high", "is_sum_under")
 ```
@@
   group_by(meta_task, is_new) %>%
-  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward))
+  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
+            se_reward = sd_avg_reward/sqrt(n()), 
+            ci_lo = avg_avg_reward - 1.96*se_reward, 
+            ci_hi = avg_avg_reward + 1.96*se_reward)
 
@@
   geom_bar(stat="identity", position="dodge") +
-# geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
   scale_fill_brewer(palette="Set2")
 ```
+
+# embeddings
+
+```{r}
+for (emb_type in c("guess", "final")) {
+  emb_d = data.frame()
+  for (run_i in 0:(nruns-1)) {
+    filename = sprintf("%sm2l%s_run%i_%s_embeddings.csv", resulst_dir, run_i, emb_type)
+    if (!file.exists(filename)) {
+      next
+    }
+    this_d = read.csv(filename, header=T)
+    this_d$run = run_i
+    emb_d = bind_rows(emb_d, this_d)
+  }
+
+  pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
+  pc_d = data.frame(pcs$rotation)
+  pc_d$task = row.names(pc_d)
+  ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
+    geom_point() +
+    geom_text(aes(label=task)) +
+    guides(color=F)
+  ggsave(sprintf("plots/PCA_full_%s.png", results_dir, emb_type), width=7, height=7)
+}
+```
+
+```{r}
+emb_type = "guess"
+emb_d = data.frame()
+for (meta_task in c("None", meta_mapping_tasks)) {
+  for (run_i in 0:(num_runs-1)) {
+    if (meta_task == "None") {
+      filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
+      if (!file.exists(filename)) {
+#          print(paste("Skipping", filename, sep=" "))
+        next 
+      }
+      this_d = read.csv(filename, header=T)
+    } else {
+      filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
+      if (!file.exists(filename)) {
+#          print(paste("Skipping", filename, sep=" "))
+        next 
+      }
+      this_d = read.csv(filename, header=T)
+    }
+    this_d$run = run_i
+    this_d$meta_task = meta_task
+    emb_d = bind_rows(emb_d, this_d)
+  }
+}
+```
+
+```{r}
+
+```

### 2018-10-23 meta_RL_analyses.Rmd
I swear I already committed these bugfixes??

@@
   emb_d = data.frame()
-  for (run_i in 0:(nruns-1)) {
-    filename = sprintf("%sm2l%s_run%i_%s_embeddings.csv", resulst_dir, run_i, emb_type)
+  for (run_i in 0:(num_runs-1)) {
+    filename = sprintf("%srun%i_%s_embeddings.csv", results_dir, run_i, emb_type)
     if (!file.exists(filename)) {
@@
     guides(color=F)
-  ggsave(sprintf("plots/PCA_full_%s.png", results_dir, emb_type), width=7, height=7)
+  ggsave(sprintf("plots/PCA_full_%s.png", emb_type), width=7, height=7)
 }
@@
 ```{r}
-emb_type = "guess"
-emb_d = data.frame()
-for (meta_task in c("None", meta_mapping_tasks)) {
-  for (run_i in 0:(num_runs-1)) {
-    if (meta_task == "None") {
-      filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
-      if (!file.exists(filename)) {
-#          print(paste("Skipping", filename, sep=" "))
-        next 
-      }
-      this_d = read.csv(filename, header=T)
-    } else {
-      filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
-      if (!file.exists(filename)) {
-#          print(paste("Skipping", filename, sep=" "))
-        next 
-      }
-      this_d = read.csv(filename, header=T)
-    }
-    this_d$run = run_i
-    this_d$meta_task = meta_task
-    emb_d = bind_rows(emb_d, this_d)
-  }
-}
+# emb_type = "guess"
+# emb_d = data.frame()
+# for (meta_task in c("None", meta_mapping_tasks)) {
+#   for (run_i in 0:(num_runs-1)) {
+#     if (meta_task == "None") {
+#       filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
+#       if (!file.exists(filename)) {
+# #          print(paste("Skipping", filename, sep=" "))
+#         next 
+#       }
+#       this_d = read.csv(filename, header=T)
+#     } else {
+#       filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
+#       if (!file.exists(filename)) {
+# #          print(paste("Skipping", filename, sep=" "))
+#         next 
+#       }
+#       this_d = read.csv(filename, header=T)
+#     }
+#     this_d$run = run_i
+#     this_d$meta_task = meta_task
+#     emb_d = bind_rows(emb_d, this_d)
+#   }
+# }
 ```

### 2018-10-24 meta_learning.py
dropout

@@ -56,12 +56,17 @@ config = {
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
+    "train_drop_prob": 0.15, # dropout probability, applied on meta and hyper
+                             # but NOT task or input/output at present. Note
+                             # that because of multiplicative effects and depth
+                             # impact can be dramatic.
+
     "softmax_beta": 5, # 1/temperature on action softmax, sharpens if > 1
     "task_weight_weight_mult": 1., # not a typo, the init range of the final
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_h128/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_h256_f64_dp15/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
 
@@ -185,6 +190,7 @@ class meta_model(object):
         self.num_outcome = config["num_outcome"]
         self.bets = config["bets"]
         self.game_hints_on_examples = config["game_hints_on_examples"]
+        self.tkp = 1. - config["train_drop_prob"] # drop prob -> keep prob
 
         base_tasks = config["base_tasks"]
         base_meta_tasks = config["base_meta_tasks"]
@@ -249,6 +255,7 @@ class meta_model(object):
             tf.float32, shape=[None, output_size])
 
         self.lr_ph = tf.placeholder(tf.float32)
+        self.keep_prob_ph = tf.placeholder(tf.float32) # dropout keep prob
 
         num_hidden = config["num_hidden"] 
         num_hidden_hyper = config["num_hidden_hyper"] 
@@ -320,17 +327,22 @@ class meta_model(object):
                                          embedded_targets], axis=-1)
                 guess_input = tf.boolean_mask(guess_input,
                                               self.guess_input_mask_ph)
+                guess_input = tf.nn.dropout(guess_input, self.keep_prob_ph)
 
                 gh_1 = slim.fully_connected(guess_input, num_hidden_hyper,
                                             activation_fn=internal_nonlinearity) 
+                gh_1 = tf.nn.dropout(gh_1, self.keep_prob_ph)
                 gh_2 = slim.fully_connected(gh_1, num_hidden_hyper,
                                             activation_fn=internal_nonlinearity) 
[…]

### 2018-10-24 meta_learning.py
parameter matchups

@@ -32,8 +32,8 @@ config = {
     "game_hints_on_examples": False, # if true, provides game labels on input,
                                      # else replaced with zeros
 
-    "num_hidden": 32,
-    "num_hidden_hyper": 128,
+    "num_hidden": 64,
+    "num_hidden_hyper": 256,
 
     "epsilon": 0.5,
     "init_learning_rate": 1e-4,

### 2018-10-25 writing/embedded_meta_learning.tex
starting a very rough draft

\documentclass[11pt]{article}

\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{relsize}
\usepackage{natbib}
\usepackage{float}
\usepackage[margin=1in]{geometry}

\floatstyle{boxed}
\restylefloat{figure}

\begin{document}

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2017}. One fundamental reason for this is the siloing of knowledge within deep neural networks -- although deep networks represent knowledge about data (activations) and knowledge about transformations of that data (parameters), they do not represent any relationships between these. By contrast, humans are (or can be) consciously aware of both our representations of input, the transformations we can perform on them, and the relationships between data and functions on the data. This is true for domains from game playing to natural language understanding. \par
One of the abilities that this grants humans is the ability to learn rapidly from relatively few examples. This problem has been partially addressed by meta-learning systems \citep{}. Yet humans can then take this knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction. Deep learning systems at present lack this flexiblity. \par
In this paper, we propose a new class of architectures which essentially take a \emph{functional programming perspective} on meta-learning. By treating both data and transformations on the data as functions, we can conceptually think of both as transformable data. This yields the ability to not just learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands. We suggest that this ability will be key to building more intelligent deep learning systems. \par

\section{Method}

\section{Results}

\section{Discussion}

\end{document}

### 2018-11-01 writing/embedded_meta_learning.tex
Porting over figure and improving

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{tikz}
 
-\floatstyle{boxed}
-\restylefloat{figure}
+\usetikzlibrary{shapes,arrows}
+
+\tikzstyle{block} = [rectangle, draw, thick, align=center, rounded corners]
+\tikzstyle{boundingbox} = [very thick, dotted, gray]
+\tikzstyle{dashblock} = [rectangle, draw, thick, align=center, dashed]
+\tikzstyle{conc} = [ellipse, draw, thick, dashed, align=center]
+\tikzstyle{netnode} = [circle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{relunode} = [rectangle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{line} = [draw, very thick, -latex']
 
@@
 Yet humans can then take this knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction.
+For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance \textbf{without any retraining} (i.e.
+zero-shot).
 Deep learning systems at present lack this flexiblity.
 \par
-In this paper, we propose a new class of architectures which essentially take a \emph{functional programming perspective} on meta-learning.
+In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning.
 By treating both data and transformations on the data as functions, we can conceptually think of both as transformable data.
@@
 \section{Method}
+We take a \textbf{functional} perspective on learning.
+A datum can be represented by a constant function which outputs it.
+(For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
+\par
+We can then interpret most machine learning tasks as a mapping of functions to functions.
+These functions could represent data\footnote{Where ``data'' is a quite flexible term.
+The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, e.g.}, or they could be functions that operate on functions themselves.
+Under this perspective, learning tasks and learning to flexibly map between tasks are the same type of problem.
+\par
+Specificially, we
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[auto]
+
+\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}\textbf{Shared} \\ \textbf{representation}\end{tabular}};
+
+% inputs, outputs
+
+\draw [boundingbox] (-8.5, -5) rectangle (-2.1, 5); 
+\node [text=gray] at (-8, 4.7) {\textbf{I/O}};
+
+\node [conc] at (-6, -4) (perc) {\textbf{Basic Input}};
+\node [conc] at (-6, 4) (act) {\textbf{Basic Output}};
+\node [block, text width=2cm] at (-4, -2) (IE) {\textbf{Input Encoder}};
+\node [block, text width=2cm] at (-3.5, 2.5) (OD) {\textbf{Output Decoder}};
+\node [block, text width=2cm] at (-5.5, 1) (TE) {\textbf{Target Encoder}};
+\path [line] (perc.north) to (IE.south);
+\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
+\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
+\path [line] (OD.north) to (act.south);
+\path [line] (act.south) to (TE.north);
+\path [line] (TE.east) to (rep.north west);
+
+% meta
+\draw [boundingbox] (-1.9, 5) rectangle (6, -5); 
+\node [text=gray] at (-0.3, 4.7) {\textbf{Meta Learning}};
+
+\node [dashblock] at (0, -2) (collection) {
+\(\left\{
+\begin{matrix}
+(\text{in}_0, \text{out}_0),\\
+(\text{in}_1, \text{out}_1),\\
+...  
+\end{matrix}\right\}\)};
+\path [line] (rep.south) to (collection);
+\path [line] ([xshift=-1em]rep.south) to (collection);
+\path [line] ([xshift=1em]rep.south) to (collection);
+
+\node [block] at (4, 0) (meta) {\begin{tabular}{c}\textbf{Meta} \\ \textbf{network}\end{tabular}};
+\path [line] (collection.south) to [out=-90, in=-90] (meta.south);
+\path [line] (meta.west) to (rep.east);
+
+% hyper
+
+\node [block] at (4, 3) (hyper) {\begin{tabular}{c}\textbf{Hyper} \\ \textbf{network}\end{tabular}};
+\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(f: \text{rep} \rightarrow \text{rep}\)};
+
+\path [draw, ->, very thick] (rep.north east) to (hyper.south);
+\path [draw, ->, very thick] (hyper.west) to (transform.north east);
+\path [draw, ->, very thick] ([xshift=-1em]transform.south) to ([xshift=-1em]rep.north);
+\path [draw, ->, very thick] ([xshift=1em]rep.north) to ([xshift=1em]transform.south);
+
+\end{tikzpicture}
+\caption{Schematic of our general architecure.}
+\end{figure}
 

### 2018-11-01 writing/embedded_meta_learning.tex
Some description, figure tweaks

@@
 \usepackage{amsmath}
+\usepackage{bm}
 \usepackage{relsize}
@@
 In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning.
-By treating both data and transformations on the data as functions, we can conceptually think of both as transformable data.
+By treating both data and transformations on the data as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
 This yields the ability to not just learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
@@
 \section{Method}
+\subsection{Architecture}
 We take a \textbf{functional} perspective on learning.
@@
 \par
-Specificially, we
+More specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
+Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
+Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
+Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
+(Targets do not necessarily need to be output-like, e.g.
+in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
+Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets.
+These transformations are performed by a system with the following components:
+\begin{itemize}
+\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
+\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
+\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
+\end{itemize}
+See Fig. \ref{architecture_fig} for a schematic of the architecture. \par
+
+\subsection{Operation}
+A basic forward pass through the system might look as follows.
+\begin{enumerate}
+\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
+Another set of (possibly unlabeled) inputs is provided and embedded.
+\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
+\end{enumerate}
+This system can be trained end-to-end if labels are provided for the second set of inputs. \par
 
@@
 
-\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}\textbf{Shared} \\ \textbf{representation}\end{tabular}};
+\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
 
@@
 \draw [boundingbox] (-8.5, -5) rectangle (-2.1, 5); 
-\node [text=gray] at (-8, 4.7) {\textbf{I/O}};
+\node [text=gray] at (-8, 4.65) {\textbf{I/O}};
 
@@
 \node [conc] at (-6, 4) (act) {\textbf{Basic Output}};
-\node [block, text width=2cm] at (-4, -2) (IE) {\textbf{Input Encoder}};
-\node [block, text width=2cm] at (-3.5, 2.5) (OD) {\textbf{Output Decoder}};
-\node [block, text width=2cm] at (-5.5, 1) (TE) {\textbf{Target Encoder}};
+\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
+\node [block, text width=2.2cm] at (-3.5, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
+\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target Encoder}};
 \path [line] (perc.north) to (IE.south);
@@
 \draw [boundingbox] (-1.9, 5) rectangle (6, -5); 
-\node [text=gray] at (-0.3, 4.7) {\textbf{Meta Learning}};
+\node [text=gray] at (-0.4, 4.7) {\textbf{Meta Learner}};
 
-\node [dashblock] at (0, -2) (collection) {
+\node [dashblock] at (0, -2.5) (collection) {
 \(\left\{
@@
 (\text{in}_1, \text{out}_1),\\
-...  
+$\vdots$
 \end{matrix}\right\}\)};
@@
 
-\node [block] at (4, 0) (meta) {\begin{tabular}{c}\textbf{Meta} \\ \textbf{network}\end{tabular}};
+\node [block] at (4, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
 \path [line] (collection.south) to [out=-90, in=-90] (meta.south);
@@
 
-\node [block] at (4, 3) (hyper) {\begin{tabular}{c}\textbf{Hyper} \\ \textbf{network}\end{tabular}};
+\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
 \node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(f: \text{rep} \rightarrow \text{rep}\)};
@@
 \end{tikzpicture}
-\caption{Schematic of our general architecure.}
+\caption{Schematic of our general architecure.
+Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$.} \label{architecture_fig}
 \end{figure}

### 2018-11-06 writing/embedded_meta_learning.tex
sketching forward
Task descriptions

@@
 zero-shot).
-Deep learning systems at present lack this flexiblity.
+Deep learning systems at present lack this representational flexiblity.
 \par
@@
 
-\section{Results}
+\section{Experiments}
+
+\subsection{A toy demonstration: boolean functions}
+As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
+Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input.
+We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs.
+\par
+We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
+
+\subsection{A reinforcment learning setting: simple card games}
+Our next case study was in the setting of simple card games, played with two suits, and 4 values per suit.
+In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands).
+The agent is dealt a hand, and then has to choose to bet 0, 1, or 2.
+If it wins, it is rewarded the value of the bet, if it loses, it receives the negative of the value.
+This doesn't require long term planning, but is nevertheless an RL rather than a supervised problem, since the feedback is stochastic.
+We considered a variety of games:
+\begin{itemize}
+\item \textbf{High card:} Highest card wins.
+\item \textbf{Pairs and high:} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
+\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
+\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
+\item \textbf{Sum under (blackjack):} The rank increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and rank drops below any smaller sum.
+\end{itemize}
+We also considered three binary options that could be altered to produce variants of these games:
+\begin{itemize}
+\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
+\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
+\item \textbf{Switch suit:} Switches which of the suits is more valuable.
+\end{itemize}
+Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. \par
+In order to switch the system to an RL meta learning system, we made a very simple change.
+Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-style approach to predict rewards for each bet in each state.
+The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
+That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples.
+\par
+We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. \par
 

### 2018-11-07 meta_RL_analyses.Rmd
Updating to analyze multiple types of runs simultaneously for the comparisons we actually want to make

@@
 ```{r}
-num_runs = 5
-results_dir = "results/results_h256/"
+num_runs = 20
+results_dir = "results/paper_results/"
+
+result_subdirs = c("basic", "nometa", "basic_su_heldout")
 
@@
 ```{r}
-load_d = function(results_dir, num_runs, file_type) {
+load_d = function(results_dir, result_subdirs, num_runs, file_type) {
   d = data.frame()
   for (run_i in 0:(num_runs-1)) {
-    filename = sprintf("%srun%i_%s.csv", results_dir, run_i, file_type)
+    for (result_subdir in result_subdirs) {
+      filename = sprintf("%s%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
       if (!file.exists(filename)) {
@@
       this_d = read.csv(filename, header=T) %>%
-      mutate(run = run_i)
+        mutate(run = run_i,
+               run_type=result_subdir)
       d = bind_rows(d, this_d)
+      }
   }
@@
 ```{r}
-reward_d = load_d(results_dir, num_runs, "new_rewards")
+reward_d = load_d(results_dir, result_subdirs, num_runs, "new_rewards")
 
@@
   filter(epoch == 0) %>%
-  group_by(game_type, is_new_game) %>%
+  group_by(run_type, game_type, is_new_game) %>%
   summarize(avg_reward = mean(reward), sd_reward=sd(reward),
@@
   geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
-  scale_fill_brewer(palette="Set2")
+  scale_fill_brewer(palette="Set2") +
+  facet_wrap(. ~ run_type)
+```
+```{r}
+avg_reward_d %>% filter(is_new_game)
+```
+
+```{r}
+ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
+  geom_bar(stat="identity", position="dodge") +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
+  scale_fill_brewer(palette="Set1")
 ```
@@
 ```{r}
-meta_d = load_d(results_dir, num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, c("basic", "basic_su_heldout"), num_runs, "new_meta_true_losses")
 
@@
   filter(epoch == 0) %>%
-  gather(map_str, reward, -c(run, epoch)) %>%
+  gather(map_str, reward, -c(run, run_type, epoch)) %>%
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
@@
 avg_meta_d = meta_d %>%
-  group_by(run, meta_task, is_new) %>%
+  group_by(run_type, run, meta_task, is_new) %>%
   summarize(avg_reward = mean(reward)) %>%
-  group_by(meta_task, is_new) %>%
+  group_by(run_type, meta_task, is_new) %>%
   summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
@@
   geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
-  scale_fill_brewer(palette="Set2")
+  scale_fill_brewer(palette="Set2") +
+  facet_wrap(.~run_type)
 ```
@@
 ```{r}
+for (result_subdir in result_subdirs) {
   for (emb_type in c("guess", "final")) {
@@
     for (run_i in 0:(num_runs-1)) {
-    filename = sprintf("%srun%i_%s_embeddings.csv", results_dir, run_i, emb_type)
+      filename = sprintf("%s%s/run%i_%s_embeddings.csv", results_dir, result_subdir, run_i, emb_type)
       if (!file.exists(filename)) {
@@
       guides(color=F)
-  ggsave(sprintf("plots/PCA_full_%s.png", emb_type), width=7, height=7)
+    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)
+  }
 }

### 2018-11-13 meta_RL_analyses.Rmd
Bugfixes

@@
 
-result_subdirs = c("basic", "nometa", "basic_su_heldout")
+result_subdirs = c("basic", "nometa", "basic_su_heldout", "nometa_su_heldout")
 
@@
                   "game_straight_flush_l_1_bv_1_sr_1")
+
+new_game_strs_su_heldout = c("game_sum_under_l_1_bv_0_sr_0",
+                             "game_sum_under_l_1_bv_1_sr_0",
+                             "game_sum_under_l_1_bv_0_sr_1",
+                             "game_sum_under_l_1_bv_1_sr_1")
 
@@
 reward_d = reward_d %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
   gather(game_str, reward, starts_with("game")) %>%
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = game_str %in% new_game_strs)
+         is_new_game = (!is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout))
 ```
@@
   filter(epoch == 0) %>%
-  gather(map_str, reward, -c(run, run_type, epoch)) %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
+  gather(map_str, reward, -c(run, run_type, is_su_ho, epoch)) %>%
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
+  mutate(is_new = (!is_su_ho & (source %in% new_game_strs | target %in% new_game_strs)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
 ```

### 2018-11-13 meta_learning.py
Sweeping meta batch sizes in eval

@@ -33,7 +33,7 @@ config = {
                                      # else replaced with zeros
 
     "num_hidden": 64,
-    "num_hidden_hyper": 256,
+    "num_hidden_hyper": 512,
 
     "epsilon": 0.5,
     "init_learning_rate": 1e-4,
@@ -46,8 +46,8 @@ config = {
     "meta_lr_decay": 0.9,
 
     "lr_decays_every": 100,
-    "min_learning_rate": 1e-7,
-    "min_meta_learning_rate": 1e-6,
+    "min_learning_rate": 3e-8,
+    "min_meta_learning_rate": 3e-7,
 
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
@@ -56,7 +56,7 @@ config = {
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
-    "train_drop_prob": 0.15, # dropout probability, applied on meta and hyper
+    "train_drop_prob": 0.00, # dropout probability, applied on meta and hyper
                              # but NOT task or input/output at present. Note
                              # that because of multiplicative effects and depth
                              # impact can be dramatic.
@@ -66,9 +66,12 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/results_h256_f64_dp15/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL//",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
+    "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
+                                                                # eval each at
+                                                                # training ends
 
     "memory_buffer_size": 1024, # How many memories of each task are stored
     "meta_batch_size": 768, # how many meta-learner sees
@@ -613,9 +616,11 @@ class meta_model(object):
             buff.insert(encoded_hands, encoded_outcomes)
 
 
-    def _random_guess_mask(self, dataset_length):
+    def _random_guess_mask(self, dataset_length, meta_batch_size=None):
+        if meta_batch_size is None:
+            meta_batch_size = config["meta_batch_size"]
         mask = np.zeros(dataset_length, dtype=np.bool)
[…]

### 2018-11-13 meta_learning.py
Capability of random half holdouts

@@ -66,7 +66,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL//",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/basic_random_holdout/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -76,15 +76,16 @@ config = {
     "memory_buffer_size": 1024, # How many memories of each task are stored
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
-    "new_tasks": [{"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": False},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": False},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": True},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": True}], # will be removed
-                                                                # from base tasks
+    "new_tasks": "random",
+#    "new_tasks": [{"game": "sum_under", "losers": True,
+#                  "black_valuable": False, "suits_rule": False},
+#		  {"game": "sum_under", "losers": True,
+#                  "black_valuable": True, "suits_rule": False},
+#		  {"game": "sum_under", "losers": True,
+#                  "black_valuable": False, "suits_rule": True},
+#		  {"game": "sum_under", "losers": True,
+#                  "black_valuable": True, "suits_rule": True}], # will be removed
+#                                                                # from base tasks
 
     "new_meta_tasks": [],
 
@@ -93,10 +94,16 @@ config = {
 }
 
 
+    
+
+
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
 config["base_meta_mappings"] = ["toggle_" + o for o in config["option_names"]]
 config["base_tasks"] = [{"game": g, "losers": l, "black_valuable": b,
                          "suits_rule": s} for g in config["game_types"] for l in config["losers"] for b in config["black_valuable"] for s in config["suits_rule"]]
[…]

### 2018-11-14 meta_learning.py
Bugfix

@@ -966,7 +966,7 @@ class meta_model(object):
                     fout_sweep.write("epoch, size, " + ", ".join(base_names) + "\n")
                     for i, swept_batch_size in enumerate(config["sweep_meta_batch_sizes"]):
                         swept_rewards = s_epoch + ("%i, " % swept_batch_size) + (reward_format % tuple(sweep_rewards[i]))
-                        fout_reward.write(swept_rewards)
+                        fout_sweep.write(swept_rewards)
 
             learning_rate = config["init_learning_rate"]
             meta_learning_rate = config["init_meta_learning_rate"]
@@ -1033,7 +1033,7 @@ class meta_model(object):
                         include_new=include_new, sweep_meta_batch_sizes=config["sweep_meta_batch_sizes"])
                     for i, swept_batch_size in enumerate(config["sweep_meta_batch_sizes"]):
                         swept_rewards = s_epoch + ("%i, " % swept_batch_size) + (reward_format % tuple(sweep_rewards[i]))
-                        fout_reward.write(swept_rewards)
+                        fout_sweep.write(swept_rewards)
 
 
     def save_embeddings(self, filename, meta_task=None,

### 2018-11-14 meta_learning.py
Better filenames

@@ -932,8 +932,7 @@ class meta_model(object):
         config = self.config
         loss_filename = filename_prefix + "_losses.csv"
         reward_filename = filename_prefix + "_rewards.csv"
-        start_sweep_filename = filename_prefix + "start_sweep_rewards.csv"
-        end_sweep_filename = filename_prefix + "end_sweep_rewards.csv"
+        sweep_filename = filename_prefix + "_sweep_rewards.csv"
         meta_filename = filename_prefix + "_meta_true_losses.csv"
         with open(loss_filename, "w") as fout, open(reward_filename, "w") as fout_reward, open(meta_filename, "w") as fout_meta:
             base_names, base_losses, base_rewards = self.run_base_eval(
@@ -960,7 +959,7 @@ class meta_model(object):
             fout_reward.write(curr_rewards)
             fout_meta.write(curr_meta_true)
             if config["sweep_meta_batch_sizes"] is not None:
-                with open(start_sweep_filename, "w") as fout_sweep:
+                with open(sweep_filename, "w") as fout_sweep:
                     sweep_names, sweep_losses, sweep_rewards = self.run_base_eval(
                         include_new=include_new, sweep_meta_batch_sizes=config["sweep_meta_batch_sizes"])
                     fout_sweep.write("epoch, size, " + ", ".join(base_names) + "\n")
@@ -1028,7 +1027,7 @@ class meta_model(object):
                     meta_learning_rate *= meta_lr_decay
 
             if config["sweep_meta_batch_sizes"] is not None:
-                with open(start_sweep_filename, "a") as fout_sweep:
+                with open(sweep_filename, "a") as fout_sweep:
                     sweep_names, sweep_losses, sweep_rewards = self.run_base_eval(
                         include_new=include_new, sweep_meta_batch_sizes=config["sweep_meta_batch_sizes"])
                     for i, swept_batch_size in enumerate(config["sweep_meta_batch_sizes"]):

### 2018-11-14 meta_RL_analyses.Rmd
plot of swept meta batch sizes

@@
 library(tidyverse)
+library
 ```
@@
 ```{r}
-num_runs = 20
+num_runs = 1
 results_dir = "results/paper_results/"
 
-result_subdirs = c("basic", "nometa", "basic_su_heldout", "nometa_su_heldout")
+result_subdirs = c("nometa")#, "nometa_su_heldout", "nometa_random_holdout",
+                   #"basic", "basic_su_heldout", "basic_random_holdout")
 
@@
                              "game_sum_under_l_1_bv_1_sr_1")
+
+new_game_strs_random_heldout = c('game_match_l_0_bv_0_sr_1', 'game_match_l_0_bv_1_sr_1', 'game_pairs_and_high_l_1_bv_1_sr_0', 'game_high_card_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_0_sr_1', 'game_straight_flush_l_0_bv_0_sr_0', 'game_pairs_and_high_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_0_sr_0', 'game_match_l_1_bv_0_sr_1', 'game_pairs_and_high_l_0_bv_1_sr_0', 'game_pairs_and_high_l_1_bv_0_sr_0', 'game_sum_under_l_1_bv_0_sr_0', 'game_sum_under_l_0_bv_1_sr_0', 'game_high_card_l_1_bv_0_sr_1', 'game_sum_under_l_0_bv_0_sr_0', 'game_pairs_and_high_l_0_bv_0_sr_1', 'game_sum_under_l_1_bv_0_sr_1', 'game_match_l_1_bv_1_sr_1', 'game_sum_under_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_1_sr_1')
 
@@
 reward_d = reward_d %>%
-  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_random_ho=grepl("random", run_type)) %>%
   gather(game_str, reward, starts_with("game")) %>%
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (!is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout))
+         is_new_game = (!is_random_ho & !is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) )
 ```
@@
 
+## sweeping batch sizes
+```{r}
+sweep_d = load_d(results_dir, result_subdirs, num_runs, "new_sweep_rewards")
+
+sweep_d = sweep_d %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_random_ho=grepl("random", run_type)) %>%
+  gather(game_str, reward, starts_with("game")) %>%
+  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+         losers = grepl("l_1", game_str),
+         black_valuable = grepl("bv_1", game_str),
+         suits_rule = grepl("sr_1", game_str),
+         is_new_game = (!is_random_ho & !is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) )
+```
+
+```{r}
+avg_sweep_d = sweep_d %>%
+  select(-game_str) %>%
+  filter(epoch == 0) %>%
+  group_by(run_type, size, game_type, is_new_game) %>%
+  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
+            se_reward = sd_reward/sqrt(n()), 
+            ci_lo = avg_reward - 1.96*se_reward, 
+            ci_hi = avg_reward + 1.96*se_reward)
+```
+
+```{r}
+ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
+  geom_point() +
+  geom_line() +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
+  scale_color_brewer(palette="Set2") +
+  xlab("Meta Set Size") +
+  facet_grid(game_type ~ run_type)
+```
 # meta mapping (true) evaluation

### 2018-11-26 meta_RL_analyses.Rmd
Slightly better comparisons

@@
 library(tidyverse)
-library
 ```
@@
 ```{r}
-num_runs = 1
+num_runs = 7
 results_dir = "results/paper_results/"
 
-result_subdirs = c("nometa")#, "nometa_su_heldout", "nometa_random_holdout",
-                   #"basic", "basic_su_heldout", "basic_random_holdout")
+result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout",
+                   "basic", "basic_su_heldout", "basic_random_holdout")
 
@@
 ```
+
+```{r}
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
+  geom_point() +
+  geom_line() +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
+  scale_color_brewer(palette="Set1") +
+  xlab("Meta Set Size") +
+  facet_grid(game_type ~ is_new_game)
+```
+
 # meta mapping (true) evaluation
@@
 ```{r}
-meta_d = load_d(results_dir, c("basic", "basic_su_heldout"), num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout"), num_runs, "new_meta_true_losses")
 

### 2018-11-28 meta_learning.py
Training longer on the random holdout sets

@@ -52,7 +52,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 40000,
+    "max_base_epochs": 60000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -66,7 +66,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/basic_random_holdout/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/nometa_random_holdout_longer/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -77,13 +77,13 @@ config = {
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
     "new_tasks": "random",
-#    "new_tasks": [{"game": "sum_under", "losers": True,
+#    "new_tasks": [{"game": "straight_flush", "losers": True,
 #                  "black_valuable": False, "suits_rule": False},
-#		  {"game": "sum_under", "losers": True,
+#		  {"game": "straight_flush", "losers": True,
 #                  "black_valuable": True, "suits_rule": False},
-#		  {"game": "sum_under", "losers": True,
+#		  {"game": "straight_flush", "losers": True,
 #                  "black_valuable": False, "suits_rule": True},
-#		  {"game": "sum_under", "losers": True,
+#		  {"game": "straight_flush", "losers": True,
 #                  "black_valuable": True, "suits_rule": True}], # will be removed
 #                                                                # from base tasks
 
@@ -93,12 +93,10 @@ config = {
     "output_nonlinearity": None
 }
 
-
-    
-
-
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
 config["base_meta_mappings"] = ["toggle_" + o for o in config["option_names"]]
+#config["base_meta_tasks"] = []#["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
+#config["base_meta_mappings"] = []#["toggle_" + o for o in config["option_names"]]
[…]

### 2018-12-10 meta_RL_analyses.Rmd
Some tidying of the code, and analyzing only_one results

@@
 ```{r}
-num_runs = 7
+num_runs = 10
 results_dir = "results/paper_results/"
 
-result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout",
-                   "basic", "basic_su_heldout", "basic_random_holdout")
+result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one", 
+                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one")
 
@@
                              "game_sum_under_l_1_bv_1_sr_1")
+
+new_game_strs_only_one = c('game_straight_flush_l_0_bv_1_sr_1', 'game_straight_flush_l_0_bv_1_sr_0', 'game_straight_flush_l_0_bv_0_sr_1', 'game_straight_flush_l_1_bv_0_sr_0', 'game_straight_flush_l_1_bv_1_sr_0', 'game_straight_flush_l_1_bv_0_sr_1', 'game_straight_flush_l_1_bv_1_sr_1')
 
@@
   mutate(is_su_ho=grepl("su_heldout", run_type),
-         is_random_ho=grepl("random", run_type)) %>%
+         is_only_one=grepl("only_one", run_type),
+         is_random_ho=grepl("random", run_type),
+         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
   gather(game_str, reward, starts_with("game")) %>%
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (!is_random_ho & !is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) )
+         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) )
 ```
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one", "nometa_only_one")), aes(x=size, color=run_type, y=avg_reward)) +
   geom_point() +
@@
 ```{r}
-meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout"), num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one"), num_runs, "new_meta_true_losses")
 
@@
   filter(epoch == 0) %>%
-  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
-  gather(map_str, reward, -c(run, run_type, is_su_ho, epoch)) %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_only_one=grepl("only_one", run_type),
+         is_random_ho=grepl("random", run_type),
+         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
+  gather(map_str, reward, -c(run, run_type, epoch), -starts_with("is_")) %>%
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = (!is_su_ho & (source %in% new_game_strs | target %in% new_game_strs)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
+  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
 ```
@@
 ```
-
-```{r}
-
-```

### 2018-12-18 meta_learning.py
One last thing to try -- only holding out a single task

@@ -14,7 +14,7 @@ from orthogonal_matrices import random_orthogonal
 pi = np.pi
 ### Parameters #################################################
 config = {
-    "run_offset": 5,
+    "run_offset": 0,
     "num_runs": 5,
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
@@ -66,7 +66,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/nometa_only_one/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/basic_only_one_ho/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -77,21 +77,9 @@ config = {
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
 #    "new_tasks": "random",
-    "new_tasks": [{"game": "straight_flush", "losers": False,
-                  "black_valuable": True, "suits_rule": True},
-		  {"game": "straight_flush", "losers": False,
-                  "black_valuable": True, "suits_rule": False},
-		  {"game": "straight_flush", "losers": False,
-                  "black_valuable": False, "suits_rule": True},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": False},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": False},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": True},
-		  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": True}], # will be removed
-                                                                # from base tasks
+    "new_tasks": [{"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": False}], # will be removed
+                                                                  # from base tasks
 
     "new_meta_tasks": [],
 
@@ -99,10 +87,10 @@ config = {
     "output_nonlinearity": None
 }
 
[…]

### 2018-12-18 compute_baselines.py
Computing baselines under different policies

@@ -1,0 +1,33 @@
+import numpy as np
+from simple_card_games import card_game, _stringify_game 
+
+game_types = ["high_card", "match", "pairs_and_high", "straight_flush", "sum_under"]
+suits_rule = [True, False]
+losers = [True, False]
+black_valuable = [True, False]
+max_bet = 2.
+
+with open("baseline_data.csv", "w") as fout:
+    fout.write("game, policy, expected_reward\n")
+    for game_type in game_types:
+        for sr in suits_rule:
+            for l in losers:
+                for bv in black_valuable:
+                    g = card_game(game_type, bv, sr, l)
+                    name = _stringify_game(g)
+                    fout.write("%s, %s, %f\n" % (name,
+                                                 "optimal",
+                                                 g.compute_expected_return())) 
+
+                    for sr2 in suits_rule:
+                        for l2 in losers:
+                            for bv2 in black_valuable:
+                                if sr2 == sr and l2 == l and bv2 == bv:
+                                    continue
+                                g2 = card_game(game_type, bv2, sr2, l2)
+                                name2 = _stringify_game(g2)
+                                g2_policy = {hand: max_bet * (g2.hand_to_win_prob[hand] > 0.5) for hand in g2.hands}
+                                fout.write("%s, %s, %f\n" % (
+                                    name,
+                                    name2,
+                                    g.compute_expected_return(policy=g2_policy))) 

### 2018-12-18 simple_card_games.py

@@ -32,6 +32,7 @@ class card_game(object):
     instead lose an equal amount, and vice versa."""
     def __init__(self, game_type, black_valuable=True, suits_rule=False,
                  losers=False):
+        self.game_type = game_type
         self.black_valuable = black_valuable
         self.suits_rule = suits_rule
         suit_mult = 0.5 if not suits_rule else 4
@@ -123,15 +124,29 @@ class card_game(object):
             return -bet
 
 
-    def compute_expected_return(self, max_bet=2.):
+    def compute_expected_return(self, max_bet=2., policy=None):
+        """If policy is None, computes the optimal expected return. If not,
+        policy should be a dictionary indexed by hands that gives bets."""
         r = 0.
-        for hand in self.hands:
-            wp = self.hand_to_win_prob[hand]
-            if wp > 0.5:
-                r += wp*max_bet - (1-wp)*max_bet
+        if policy is None:
+            for hand in self.hands:
+                wp = self.hand_to_win_prob[hand]
+                if wp > 0.5:
+                    r += wp*max_bet - (1-wp)*max_bet
+        else:
+            for hand in self.hands:
+                bet = policy[hand]
+                wp = self.hand_to_win_prob[hand]
+                r += wp*bet - (1-wp)*bet
 
         r /= len(self.hands)
         return r
+
+
+def _stringify_game(t):
+    """Helper for printing, etc."""
+    return "game_%s_l_%i_bv_%i_sr_%i" % (t.game_type, t.losers,
+                                         t.black_valuable, t.suits_rule)
 
         
 ### simple tests

### 2018-12-18 meta_RL_analyses.Rmd
Starting to set up for some nicer plots, including baseliens

@@
 
-# utils
+# utils and setup
 
@@
 }
+```
+
+plot themes
+```{r}
+theme_set(theme_bw() + 
+            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
+```
+
+```{r}
+summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
+  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +
+    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
+    geom_point(stat="summary", fun.y=mean, size=2) +
+    geom_errorbar(stat="summary", 
+                  fun.ymin=function(x) {mean(x) - 1.96*sd(x)/sqrt(length(x))},
+                  fun.ymax=function(x) {mean(x) + 1.96*sd(x)/sqrt(length(x))},
+                  width=0.25) +
+    scale_color_brewer(palette=palette)
+
+  if (!is.null(baseline_data)) {
+    p = p + 
+      annotate("segment",
+               x=(1:5)-0.5, xend=(1:5)+0.5,
+               y=simple_baselines$expected_reward,
+               yend=simple_baselines$expected_reward,
+               linetype=3, alpha=0.5) 
+  }
+
+  return(p)
+}
+```
+
+```{r}
+baseline_data = read_csv("baseline_data.csv") %>%
+  mutate(game_type = str_extract(game, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+         losers = grepl("l_1", game),
+         black_valuable = grepl("bv_1", game),
+         suits_rule = grepl("sr_1", game))
 ```
@@
 ```{r}
-theme_set(theme_bw() + 
-            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
+simple_baselines = baseline_data %>% 
+  filter(policy == "optimal") %>%
+  group_by(game_type) %>%
+  summarize(expected_reward = mean(expected_reward)) %>%
+  ungroup()
+
+summary_plot(reward_d %>%
+               filter(epoch == 0),
+             "game_type", "reward", "is_new_game",
+             simple_baselines) +
+  facet_wrap(. ~ run_type)
 ```
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one", "nometa_only_one")), aes(x=size, color=run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
   geom_point() +
@@
 
+    pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
+    pc_d = data.frame(pcs$rotation)
+    pc_d$task = row.names(pc_d)
+    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
+      geom_point() +
+      geom_text(aes(label=task)) +
+      guides(color=F)
+    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)
+
     pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)

### 2018-12-18 writing/embedded_meta_learning.tex
Some cleaning up and clarifying

@@
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2017}.
-One fundamental reason for this is the siloing of knowledge within deep neural networks -- although deep networks represent knowledge about data (activations) and knowledge about transformations of that data (parameters), they do not represent any relationships between these.
-By contrast, humans are (or can be) consciously aware of both our representations of input, the transformations we can perform on them, and the relationships between data and functions on the data.
+One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these.
+That is, neural networks knowledge about \textbf{what} is being computed is \textbf{inaccessible} by the computations.
+By contrast, humans are frequently consciously aware of both our representations of input, the things we can do with them, and the relationships between data and tasks.
 This is true for domains from game playing to natural language understanding.
 \par
-One of the abilities that this grants humans is the ability to learn rapidly from relatively few examples.
-This problem has been partially addressed by meta-learning systems \citep{}.
-Yet humans can then take this knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction.
+One of the abilities that this grants humans is rapid adaptation of our behavior.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep{}.
+However, humans can take rapidly acquired knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction.
 For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance \textbf{without any retraining} (i.e.
@@
 In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning.
-By treating both data and transformations on the data as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
+By treating both data and tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
 This yields the ability to not just learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
-We suggest that this ability will be key to building more intelligent deep learning systems.
+We suggest that this ability will be key to building more intelligent and flexible deep learning systems.
 \par
@@
 
-\subsection{A toy demonstration: boolean functions}
+\subsection{Boolean functions}
 As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
@@
 \item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
-\item \textbf{Sum under (blackjack):} The rank increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and rank drops below any smaller sum.
+\item \textbf{Sum under:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
 \end{itemize}
-We also considered three binary options that could be altered to produce variants of these games:
+These games are simplified analogs of various card games, including poker and blackjack. We also considered three binary options that could be altered to produce variants of these games:
 \begin{itemize}
@@
 In order to switch the system to an RL meta learning system, we made a very simple change.
-Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-style approach to predict rewards for each bet in each state.
+Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{} to predict rewards for each bet in each state.
 The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.

### 2019-01-07 meta_RL_analyses.Rmd
Similarly null results for only one heldout

@@
 
-result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one", 
-                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one")
+result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
+                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho")
 
@@
 new_game_strs_only_one = c('game_straight_flush_l_0_bv_1_sr_1', 'game_straight_flush_l_0_bv_1_sr_0', 'game_straight_flush_l_0_bv_0_sr_1', 'game_straight_flush_l_1_bv_0_sr_0', 'game_straight_flush_l_1_bv_1_sr_0', 'game_straight_flush_l_1_bv_0_sr_1', 'game_straight_flush_l_1_bv_1_sr_1')
+
+new_game_strs_only_one_ho = c('game_straight_flush_l_1_bv_0_sr_0')
 
@@
                yend=simple_baselines$expected_reward,
-               linetype=3, alpha=0.5) 
+               linetype=1, alpha=0.5) 
   }
@@
   mutate(is_su_ho=grepl("su_heldout", run_type),
-         is_only_one=grepl("only_one", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
          is_random_ho=grepl("random", run_type),
-         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
+         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
   gather(game_str, reward, starts_with("game")) %>%
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) )
+         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
 ```
@@
 sweep_d = sweep_d %>%
+
   mutate(is_su_ho=grepl("su_heldout", run_type),
-         is_only_one=grepl("only_one", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
          is_random_ho=grepl("random", run_type),
-         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
+         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
   gather(game_str, reward, starts_with("game")) %>%
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one_ho", "nometa_only_one_ho")), aes(x=size, color=run_type, y=avg_reward)) +
   geom_point() +
@@
 ```{r}
-meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one"), num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho"), num_runs, "new_meta_true_losses")
 
@@
   mutate(is_su_ho=grepl("su_heldout", run_type),
-         is_only_one=grepl("only_one", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
          is_random_ho=grepl("random", run_type),
@@
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
+  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
 ```

### 2019-01-09 meta_learning.py
Basic language setup

@@ -66,7 +66,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/basic_only_one_ho/",
+    "output_dir": "./temp_results/",#"/mnt/fs2/lampinen/meta_RL/paper_results/language/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -105,6 +105,26 @@ def _stringify_game(t):
     """Helper for printing, etc."""
     return "game_%s_l_%i_bv_%i_sr_%i" % (t["game"], t["losers"],
                                          t["black_valuable"], t["suits_rule"])
+
+def _wordify_task(t):
+    """For input to NLP module"""
+    if type(t) == str:
+        words = ["meta"] + t.split("_", 1)
+    else: # base tasks are dict
+        words = ["base", t["game"]] 
+        if t["losers"]:
+            words.append("losers")
+        else:
+            words.extend(["not", "losers"])
+        if t["black_valuable"]:
+            words.append("black_valuable")
+        else:
+            words.extend(["not", "black_valuable"])
+        if t["suits_rule"]:
+            words.append("suits_rule")
+        else:
+            words.extend(["not", "suits_rule"])
+    return words 
 
 
 def _save_config(filename, config):
@@ -211,6 +231,7 @@ class meta_model(object):
         self.new_task_names = [_stringify_game(t) for t in new_tasks]
 
         self.all_base_tasks = self.base_tasks + self.new_tasks
+
         self.memory_buffers = {_stringify_game(t): memory_buffer(
             self.memory_buffer_size, self.num_input,
             self.num_outcome) for t in self.all_base_tasks}
@@ -232,6 +253,10 @@ class meta_model(object):
         self.all_initial_tasks = self.base_tasks + self.all_base_meta_tasks 
         self.all_new_tasks = self.new_tasks + self.new_meta_tasks
         self.all_tasks = self.all_initial_tasks + self.all_new_tasks
+        self.wordified_tasks = {_stringify_game(t): _wordify_task(t) for t in self.all_base_tasks}
+        self.wordified_tasks.update({t: _wordify_task(t) for t in self.all_meta_tasks})
+        self.vocab = set([x for l in self.wordified_tasks.values() for x in l])
+
[…]

### 2019-01-09 meta_learning.py
Language -> emb -> parameters

@@ -255,7 +255,11 @@ class meta_model(object):
         self.all_tasks = self.all_initial_tasks + self.all_new_tasks
         self.wordified_tasks = {_stringify_game(t): _wordify_task(t) for t in self.all_base_tasks}
         self.wordified_tasks.update({t: _wordify_task(t) for t in self.all_meta_tasks})
-        self.vocab = set([x for l in self.wordified_tasks.values() for x in l])
+        self.max_sentence_len = max([len(l) for l in self.wordified_tasks.values()])
+        self.vocab = list(set([x for l in self.wordified_tasks.values() for x in l])) + ["PAD"]
+        self.vocab_size = len(self.vocab)
+        pad_index = self.vocab.index("PAD")
+        self.intified_tasks = {k: [pad_index]*(self.max_sentence_len - len(v)) + [self.vocab.index(w) for w in v] for k, v in self.wordified_tasks.items()} 
 
         # think that's enough redundant variables?
         self.num_tasks = num_tasks = len(self.all_tasks)
@@ -384,6 +388,40 @@ class meta_model(object):
                                                        self.meta_target_ph)
 
 
+        # language processing: lang -> emb
+        self.language_input_ph = tf.placeholder(
+            tf.int32, shape=[None, self.max_sentence_len])
+        with tf.variable_scope("word_embeddings", reuse=False):
+            self.word_embeddings = tf.get_variable(
+                "embeddings", shape=[self.vocab_size, num_hidden_hyper])
+        self.embedded_language = tf.nn.embedding_lookup(self.word_embeddings,
+                                                        self.language_input_ph)
+
+        def _language_network(embedded_language, reuse=True):
+            """Maps from language to a function embedding"""
+            with tf.variable_scope("language_processing"):
+                cell = tf.contrib.rnn.LSTMCell(num_hidden_hyper)
+                state = cell.zero_state(tf.shape(embedded_language)[0],
+                    dtype=tf.float32)
+
+                for i in range(self.max_sentence_len):
+                    cell_output, state = cell(embedded_language[:, i, :], state)
+
+                language_hidden = slim.fully_connected(
+                    cell_output, num_hidden_hyper,
+                    activation_fn=internal_nonlinearity)
+
+                func_embeddings = slim.fully_connected(language_hidden, 
+                                                       num_hidden_hyper,
+                                                       activation_fn=None)
+            return func_embeddings
+
+        self.language_function_emb = _language_network(self.embedded_language,
[…]

### 2019-01-10 meta_learning.py
Language (base) implementation in tf done

@@ -486,9 +486,6 @@ class meta_model(object):
         self.meta_m_task_params = _hyper_network(self.guess_meta_m_function_emb)
         self.fed_emb_task_params = _hyper_network(self.feed_embedding_ph)
         self.language_task_params = _hyper_network(self.language_function_emb)
-        print(self.base_task_params)
-        print(self.language_task_params)
-        exit()
 
         # task network
         def _task_network(task_params, processed_input):
@@ -519,7 +516,15 @@ class meta_model(object):
         self.meta_t_output = tf.nn.sigmoid(self.meta_t_raw_output)
 
         self.meta_m_output = _task_network(self.meta_m_task_params,
-                                               self.meta_input_ph)
+                                           self.meta_input_ph)
+
+        self.base_raw_output_language = _task_network(self.language_task_params,
+                                                 processed_input)
+        self.base_output_language = _output_mapping(self.base_raw_output_language)
+        self.base_output_softmax_language = tf.nn.softmax(
+            config["softmax_beta"] * self.base_output_language)
+
+        # TODO: language for meta tasks & mappings 
 
         # have to mask base output because can only learn about the action 
         # actually taken
@@ -528,6 +533,8 @@ class meta_model(object):
         masked_base_output = tf.boolean_mask(self.base_output,
                                              self.base_target_mask_ph)
         masked_base_fed_emb_output = tf.boolean_mask(self.base_output_fed_emb,
+                                                     self.base_target_mask_ph)
+        masked_base_language_output = tf.boolean_mask(self.base_output_language,
                                                      self.base_target_mask_ph)
         masked_base_target = tf.boolean_mask(self.base_target_ph,
                                              self.base_target_mask_ph)
@@ -538,6 +545,10 @@ class meta_model(object):
         self.base_fed_emb_loss = tf.square(
             masked_base_fed_emb_output - masked_base_target)
         self.total_base_fed_emb_loss = tf.reduce_mean(self.base_fed_emb_loss)
+
+        self.base_language_loss = tf.square(
+            masked_base_language_output - masked_base_target)
+        self.total_base_language_loss = tf.reduce_mean(self.base_language_loss)
 
         self.meta_t_loss = tf.reduce_sum(
             tf.square(self.meta_t_output - processed_class), axis=1)
@@ -551,6 +562,8 @@ class meta_model(object):
         optimizer = tf.train.RMSPropOptimizer(self.lr_ph)
 
[…]

### 2019-01-22 meta_learning.py
Language dropout

@@ -45,7 +45,7 @@ config = {
     "new_init_meta_learning_rate": 1e-6,
 
     "lr_decay": 0.85,
-    "language_lr_decay": 0.85,
+    "language_lr_decay": 0.8,
     "meta_lr_decay": 0.9,
 
     "lr_decays_every": 100,
@@ -56,8 +56,8 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 60000,
-    "max_new_epochs": 1000,
+    "max_base_epochs": 1,# 60000,
+    "max_new_epochs": 1,#1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
     "train_drop_prob": 0.00, # dropout probability, applied on meta and hyper
@@ -70,7 +70,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
+    "output_dir": "temp_results/",# "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -98,6 +98,8 @@ config = {
     "language_compositional": True, # whether language should be used
                                     # compositionally, which is nice but 
                                     # increases sentence length
+    "lang_drop_prob": 0.5, # dropout on language processing features
+                           # to try to address overfitting
 
     "internal_nonlinearity": tf.nn.leaky_relu,
     "output_nonlinearity": None
@@ -427,6 +429,9 @@ class meta_model(object):
 
         # language processing: lang -> emb
         # TODO: only create these if training language, for memory efficiency 
+
+        self.lang_keep_ph = lang_keep_ph = tf.placeholder(tf.float32)
+        self.lang_keep_prob = 1. - config["lang_drop_prob"] 
         self.language_input_ph = tf.placeholder(
             tf.int32, shape=[1, self.max_sentence_len])
         with tf.variable_scope("word_embeddings", reuse=False):
@@ -442,11 +447,19 @@ class meta_model(object):
                 state = cell.zero_state(1, dtype=tf.float32)
 
                 for i in range(self.max_sentence_len):
[…]

### 2019-01-22 meta_learning.py
Checkpointing

@@ -56,8 +56,8 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 1,# 60000,
-    "max_new_epochs": 1,#1000,
+    "max_base_epochs": 60000,
+    "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
     "train_drop_prob": 0.00, # dropout probability, applied on meta and hyper
@@ -70,7 +70,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "temp_results/",# "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -616,6 +616,9 @@ class meta_model(object):
             self.total_base_language_loss)
         self.meta_t_train = optimizer.minimize(self.total_meta_t_loss)
         self.meta_m_train = optimizer.minimize(self.total_meta_m_loss)
+
+        # Saver
+        self.saver = tf.train.Saver()
 
         # initialize
         sess_config = tf.ConfigProto()
@@ -1361,6 +1364,9 @@ class meta_model(object):
                     fout.write(
                         '"' + hand.__repr__() + '", %f, %f, %f\n' % tuple(act_probs[turn, :]))
 
+
+    def save_parameters(self, filename):
+        self.saver.save(self.sess, filename)
                 
 
 ## running stuff
@@ -1381,6 +1387,7 @@ for run_i in range(config["run_offset"], config["run_offset"]+config["num_runs"]
     model.run_training(filename_prefix=filename_prefix,
                        num_epochs=config["max_base_epochs"],
                        include_new=False)
+    model.save_parameters(filename_prefix + "_guess_checkpoint")
     model.save_embeddings(filename=filename_prefix + "_guess_embeddings.csv",
                           include_new=True)
     model.save_embeddings(filename=filename_prefix + "_guess_language_embeddings.csv",
@@ -1397,6 +1404,7 @@ for run_i in range(config["run_offset"], config["run_offset"]+config["num_runs"]
[…]

### 2019-01-22 meta_RL_analyses.Rmd
Language analyses

@@
 
-result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
-                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho")
+result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
+                   "basic", #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
+                   "language")
 
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one_ho", "nometa_only_one_ho")), aes(x=size, color=run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
   geom_point() +
@@
 
+# language results
+
+```{r}
+language_d = load_d(results_dir, result_subdirs, num_runs, "new_language_rewards")
+
+language_d = language_d %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
+         is_random_ho=grepl("random", run_type),
+         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
+  gather(game_str, reward, starts_with("game")) %>%
+  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+         losers = grepl("l_1", game_str),
+         black_valuable = grepl("bv_1", game_str),
+         suits_rule = grepl("sr_1", game_str),
+         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
+```
+
+```{r}
+avg_language_d = language_d %>%
+  select(-game_str) %>%
+  filter(epoch == 0) %>%
+  group_by(run_type, game_type, is_new_game) %>%
+  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
+            se_reward = sd_reward/sqrt(n()), 
+            ci_lo = avg_reward - 1.96*se_reward, 
+            ci_hi = avg_reward + 1.96*se_reward)
+```
+
+```{r}
+summary_plot(language_d %>%
+               filter(epoch == 0),
+             "game_type", "reward", "is_new_game",
+             simple_baselines) +
+  facet_wrap(. ~ run_type)
+```
+
 # meta mapping (true) evaluation
@@
 ```{r}
-meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho"), num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, c("basic", 
+                               #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
+                               "language"), num_runs, "new_meta_true_losses")
 

### 2019-01-25 meta_learning.py
Bugfix

@@ -15,7 +15,7 @@ pi = np.pi
 ### Parameters #################################################
 config = {
     "run_offset": 0,
-    "num_runs": 3,
+    "num_runs": 5,
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
     "suits_rule": [True, False],
@@ -40,9 +40,9 @@ config = {
     "init_language_learning_rate": 1e-4,
     "init_meta_learning_rate": 1e-4,
 
-    "new_init_learning_rate": 1e-6,
-    "new_init_language_learning_rate": 1e-6,
-    "new_init_meta_learning_rate": 1e-6,
+    "new_init_learning_rate": 1e-5,
+    "new_init_language_learning_rate": 1e-5,
+    "new_init_meta_learning_rate": 1e-5,
 
     "lr_decay": 0.85,
     "language_lr_decay": 0.8,
@@ -56,7 +56,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 60000,
+    "max_base_epochs": 5000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -70,7 +70,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/fast_lang_results/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -1192,14 +1192,16 @@ class meta_model(object):
                         swept_rewards = s_epoch + ("%i, " % swept_batch_size) + (reward_format % tuple(sweep_rewards[i]))
                         fout_sweep.write(swept_rewards)
 
-            learning_rate = config["init_learning_rate"]
-            meta_learning_rate = config["init_meta_learning_rate"]
-            language_learning_rate = config["init_language_learning_rate"]
-
             if include_new:
                 tasks = self.all_tasks
+                learning_rate = config["new_init_learning_rate"]
+                meta_learning_rate = config["new_init_meta_learning_rate"]
[…]

### 2019-01-25 meta_learning.py
hyperparameter tweaks

@@ -14,8 +14,8 @@ from orthogonal_matrices import random_orthogonal
 pi = np.pi
 ### Parameters #################################################
 config = {
-    "run_offset": 0,
-    "num_runs": 5,
+    "run_offset": 6,
+    "num_runs": 4,
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
     "suits_rule": [True, False],
@@ -50,13 +50,13 @@ config = {
 
     "lr_decays_every": 100,
     "min_learning_rate": 3e-8,
-    "min_language_learning_rate": 3e-8,
+    "min_language_learning_rate": 1e-8,
     "min_meta_learning_rate": 3e-7,
 
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 5000,
+    "max_base_epochs": 40000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -70,7 +70,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/fast_lang_results/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -98,7 +98,7 @@ config = {
     "language_compositional": True, # whether language should be used
                                     # compositionally, which is nice but 
                                     # increases sentence length
-    "lang_drop_prob": 0.5, # dropout on language processing features
+    "lang_drop_prob": 0.8, # dropout on language processing features
                            # to try to address overfitting
 
     "internal_nonlinearity": tf.nn.leaky_relu,

### 2019-01-25 meta_learning.py
Language net width as a separate hyperparameter

@@ -14,8 +14,8 @@ from orthogonal_matrices import random_orthogonal
 pi = np.pi
 ### Parameters #################################################
 config = {
-    "run_offset": 6,
-    "num_runs": 4,
+    "run_offset": 0,
+    "num_runs": 5,
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
     "suits_rule": [True, False],
@@ -34,6 +34,7 @@ config = {
 
     "num_hidden": 64,
     "num_hidden_hyper": 512,
+    "num_hidden_language": 128,
 
     "epsilon": 0.5,
     "init_learning_rate": 1e-4,
@@ -70,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_smaller/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -98,7 +99,7 @@ config = {
     "language_compositional": True, # whether language should be used
                                     # compositionally, which is nice but 
                                     # increases sentence length
-    "lang_drop_prob": 0.8, # dropout on language processing features
+    "lang_drop_prob": 0.5, # dropout on language processing features
                            # to try to address overfitting
 
     "internal_nonlinearity": tf.nn.leaky_relu,
@@ -429,6 +430,7 @@ class meta_model(object):
 
         # language processing: lang -> emb
         # TODO: only create these if training language, for memory efficiency 
+        num_hidden_language = config["num_hidden_language"]
 
         self.lang_keep_ph = lang_keep_ph = tf.placeholder(tf.float32)
         self.lang_keep_prob = 1. - config["lang_drop_prob"] 
@@ -436,14 +438,14 @@ class meta_model(object):
             tf.int32, shape=[1, self.max_sentence_len])
         with tf.variable_scope("word_embeddings", reuse=False):
             self.word_embeddings = tf.get_variable(
-                "embeddings", shape=[self.vocab_size, num_hidden_hyper])
+                "embeddings", shape=[self.vocab_size, num_hidden_language])
         self.embedded_language = tf.nn.embedding_lookup(self.word_embeddings,
[…]

### 2019-02-01 meta_RL_analyses.Rmd
A few plots for the ARRR

@@
 ```{r}
+summary_plot(reward_d %>%
+               filter(epoch == 0,
+                      run_type == "basic"),
+             "game_type", "reward", "is_new_game",
+             simple_baselines) 
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
+```
+
+```{r}
 ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
@@
   facet_grid(game_type ~ run_type)
+```
+
+```{r}
+ggplot(avg_sweep_d %>%
+         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
+  geom_point() +
+  geom_line() +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
+  scale_color_brewer(palette="Set2") +
+  xlab("Meta Set Size") +
+  facet_wrap(~ game_type)
+
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_sweeping.png", width=5, height=3)
 ```

### 2019-02-08 writing/embedded_meta_learning.tex
Starting to work on writing again

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{bm}
@@
 By treating both data and tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
-This yields the ability to not just learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
+This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
 We suggest that this ability will be key to building more intelligent and flexible deep learning systems.
 \par
-
+In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space.
+We demonstrate the greater flexibility of this approach.
 \section{Method}
 \subsection{Architecture}
-We take a \textbf{functional} perspective on learning.
-A datum can be represented by a constant function which outputs it.
-(For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
-\par
-We can then interpret most machine learning tasks as a mapping of functions to functions.
-These functions could represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, e.g.}, or they could be functions that operate on functions themselves.
-Under this perspective, learning tasks and learning to flexibly map between tasks are the same type of problem.
-\par
-More specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
-Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
-(Targets do not necessarily need to be output-like, e.g.
-in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
-Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets.
-These transformations are performed by a system with the following components:
-\begin{itemize}
-\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
-\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
-\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
-\end{itemize}
-See Fig. \ref{architecture_fig} for a schematic of the architecture. \par
-
-\subsection{Operation}
-A basic forward pass through the system might look as follows.
-\begin{enumerate}
-\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
-Another set of (possibly unlabeled) inputs is provided and embedded.
-\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
-\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
-\end{enumerate}
-This system can be trained end-to-end if labels are provided for the second set of inputs. \par
-
 \begin{figure}
@@
 
-\draw [boundingbox] (-8.5, -5) rectangle (-2.1, 5); 
-\node [text=gray] at (-8, 4.65) {\textbf{I/O}};
+\draw [boundingbox] (-9, -5) rectangle (-2.1, 5); 
+\node [text=gray] at (-8.5, 4.65) {\textbf{I/O}};
 
 \node [conc] at (-6, -4) (perc) {\textbf{Basic Input}};
+\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
 \node [conc] at (-6, 4) (act) {\textbf{Basic Output}};
 \node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
+\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
 \node [block, text width=2.2cm] at (-3.5, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
@@
 \path [line] (perc.north) to (IE.south);
+\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
 \path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
+\path [line] (LE.east) to (rep.west);
 \path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
@@
 \end{figure}
+We take a \textbf{functional} perspective on learning.
+A datum can be represented by a constant function which outputs it.
+(For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
+\par
+We can then interpret most machine learning tasks as a mapping of functions to functions.
+These functions could represent data\footnote{Where ``data'' is a quite flexible term.
+The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, e.g.}, or they could be functions that operate on functions themselves.
+Under this perspective, learning tasks and learning to flexibly map between tasks are the same type of problem.
+\par
+More specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
+Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
+Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
+Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
+(Targets do not necessarily need to be output-like, e.g.
+in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
+Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets.
+These transformations are performed by a system with the following components:
+\begin{itemize}
+\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
+\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
+\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
+\end{itemize}
+See Fig. \ref{architecture_fig} for a schematic of the architecture. \par
+
+\subsection{Operation}
+A basic forward pass through the system might look as follows.
+\begin{enumerate}
+\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
+Another set of (possibly unlabeled) inputs is provided and embedded.
+\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
+\end{enumerate}
+This system can be trained end-to-end if labels are provided for the second set of inputs.
+In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0^*), ...\}$), and some loss function $\mathcal{L}(y^*, \hat{y})$ defined on a single target output $y^*$ and actual model output $\hat{y}$, for some input $x$.
+We define our total loss computed on some dataset $D_2$ as:
+$$\mathbb{E}_{x\in {D}_2} \left[ \mathcal{L}\left(y^*, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
+where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+$$f_{D_1} = \mathcal{H}\left(\mathcal{M}\left(\right)\right)
 

### 2019-02-08 writing/embedded_meta_learning.tex
Framing

@@
 In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning.
-By treating both data and tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
+By treating tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
@@
 \subsection{Architecture}
+The essential idea of the architecture is that we separate the system into two parts: 
+\begin{enumerate}
+\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$
+\item A meta-learning system which:
+    \begin{enumerate}
+    \item Embeds tasks into the shared embedding space $Z$.
+    \item Learns to perform tasks in accordance with their embeddings.
+    \end{enumerate}
+\end{enumerate}
+The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data.
+In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior).
+This is a step closer to the flexible reasoning humans display.
+\par
+Without training on these mappings, of course, the system will not be able to execute them well.
+However, ideally if it is trained on a set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution.
+For instances that fall outside its data distribution or for optimal performance it may require some retraining.
+This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relateively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow.
+\par
+
 \begin{figure}
@@
 This system can be trained end-to-end if labels are provided for the second set of inputs.
-In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0^*), ...\}$), and some loss function $\mathcal{L}(y^*, \hat{y})$ defined on a single target output $y^*$ and actual model output $\hat{y}$, for some input $x$.
+In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
 We define our total loss computed on some dataset $D_2$ as:
-$$\mathbb{E}_{x\in {D}_2} \left[ \mathcal{L}\left(y^*, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
+$$\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
 where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-$$f_{D_1} = \mathcal{H}\left(\mathcal{M}\left(\right)\right)
+$$f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
+\right\}\right)\right)$$
 

### 2019-02-08 writing/embedded_meta_learning.tex
Some more math

@@
 Without training on these mappings, of course, the system will not be able to execute them well.
-However, ideally if it is trained on a set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution.
+However, ideally if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution.
 For instances that fall outside its data distribution or for optimal performance it may require some retraining.
@@
 \end{figure}
-We take a \textbf{functional} perspective on learning.
+More formally, we take a \textbf{functional} perspective on learning.
 A datum can be represented by a constant function which outputs it.
@@
 These functions could represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, e.g.}, or they could be functions that operate on functions themselves.
-Under this perspective, learning tasks and learning to flexibly map between tasks are the same type of problem.
+The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, or they could be functions that operate on functions themselves.
+Under this perspective, learning tasks and learning to flexibly map between tasks, or learning to map from language to tasks, are all the same type of problem.
 \par
-More specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
+Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
@@
 \end{enumerate}
-This system can be trained end-to-end if labels are provided for the second set of inputs.
-In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
-We define our total loss computed on some dataset $D_2$ as:
-$$\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
+To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$.
+This output would be generated as follows:
+$$\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)$$
 where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
@@
 \right\}\right)\right)$$
+This system can be trained end-to-end if labels are provided for a second set of inputs.
+In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
+We define our total loss computed on some dataset $D_2$ as:
+$$\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
+More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and an embedded dataset $D_Z$ of (embedding, target embedding) pairs $\{(z_{in,0}, z_{out,0})\}$.
+Then we can generate an output $\hat{z}_{out} \in Z$ as:
+$$\hat{z}_{out} = f_{D_Z}(z_{in}) \qquad \text{where } f_{D_Z} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left(D_Z\right)\right)$$
+This output can then be appropriately dispatched depedning on the task at hand.
+For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game.
+We could then evaluate performance by how well the system did at losing.
 
@@
 
-\subsection{A reinforcment learning setting: simple card games}
+\subsection{A stochastic learning setting: simple card games}
 Our next case study was in the setting of simple card games, played with two suits, and 4 values per suit.
@@
 If it wins, it is rewarded the value of the bet, if it loses, it receives the negative of the value.
-This doesn't require long term planning, but is nevertheless an RL rather than a supervised problem, since the feedback is stochastic.
+This doesn't require long term planning, but is nevertheless not precisely a supervised problem, since the feedback is stochastic.
 We considered a variety of games:

### 2019-02-12 meta_RL_analyses.Rmd
Some further exploration of language resulst

@@
 ```{r}
-num_runs = 10
+num_runs = 5
 results_dir = "results/paper_results/"
@@
 result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
-                   "basic", #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
-                   "language")
+                   "basic", #"basic_su_heldout", 
+                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
+                   "language", "language_drop_03", "language_drop_05", "language_noncompositional")
 
@@
 ```{r}
+summary_plot(reward_d %>%
+               filter(epoch == 0,
+                      run_type %in% c("basic", "basic_random_holdout_longer")),
+             "game_type", "reward", "is_new_game",
+             simple_baselines) +
+  facet_wrap(. ~ run_type)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
+```
+
+```{r}
 ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
@@
 ```{r}
-language_d = load_d(results_dir, result_subdirs, num_runs, "new_language_rewards")
+language_d = load_d(results_dir, c("language", "language_drop_03", "language_drop_05", "language_noncompositional"), num_runs, "new_language_rewards")
 
@@
 ```{r}
+ggplot(language_d %>%
+         filter(epoch == 0,
+                is_new_game),
+       aes(x=run_type, y=reward, fill=as.factor(run))) +
+  geom_hline(yintercept=0.,
+             linetype=2,
+             alpha=0.5) +
+  geom_violin(position="dodge") +
+  scale_color_brewer(palette="Set2") 
+```
+
+```{r}
 summary_plot(language_d %>%
@@
   facet_wrap(. ~ run_type)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
 ```
@@
 meta_d = load_d(results_dir, c("basic", 
-                               #"basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho",
-                               "language"), num_runs, "new_meta_true_losses")
+                               #"basic_su_heldout",
+                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
+                               #"language"
+                               ), num_runs, "new_meta_true_losses")
 
@@
   facet_wrap(.~run_type)
+```
+
+```{r}
+summary_plot(meta_d %>%
+               filter(epoch == 0,
+                      run_type %in% c("basic", "basic_random_holdout_longer")),
+             "meta_task", "reward", "is_new") +
+  facet_wrap(. ~ run_type)
+
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3)
 ```

### 2019-02-12 meta_learning.py
Language for meta as well as base

@@ -34,7 +34,7 @@ config = {
 
     "num_hidden": 64,
     "num_hidden_hyper": 512,
-    "num_hidden_language": 128,
+    "num_hidden_language": 512,
 
     "epsilon": 0.5,
     "init_learning_rate": 1e-4,
@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_smaller/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -99,8 +99,8 @@ config = {
     "language_compositional": True, # whether language should be used
                                     # compositionally, which is nice but 
                                     # increases sentence length
-    "lang_drop_prob": 0.5, # dropout on language processing features
-                           # to try to address overfitting
+    "lang_drop_prob": 0.0, # dropout on language processing features
+                            # to try to address overfitting
 
     "internal_nonlinearity": tf.nn.leaky_relu,
     "output_nonlinearity": None
@@ -576,7 +576,12 @@ class meta_model(object):
         self.base_output_softmax_language = tf.nn.softmax(
             config["softmax_beta"] * self.base_output_language)
 
-        # TODO: language for meta tasks & mappings 
+        self.meta_t_raw_output_language = _task_network(self.language_task_params,
+                                                        self.meta_input_ph)
+        self.meta_t_output_language = tf.nn.sigmoid(self.meta_t_raw_output_language)
+
+        self.meta_m_output_language = _task_network(self.language_task_params,
+                                                    self.meta_input_ph)
 
         # have to mask base output because can only learn about the action 
         # actually taken
@@ -610,6 +615,13 @@ class meta_model(object):
             tf.square(self.meta_m_output - self.meta_target_ph), axis=1)
         self.total_meta_m_loss = tf.reduce_mean(self.meta_m_loss)
 
+        self.meta_t_language_loss = tf.reduce_sum(
+            tf.square(self.meta_t_output_language - processed_class), axis=1)
[…]

### 2019-02-12 meta_RL_analyses.Rmd
Better naming of run types for plots

@@
 ```{r}
-num_runs = 5
+num_runs = 10
 results_dir = "results/paper_results/"
@@
                    "language", "language_drop_03", "language_drop_05", "language_noncompositional")
+
+name_run_type = function(run_type) { # names for plotting
+  case_when(run_type == "basic" ~ "Targeted 10% holdout",
+            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
+            T ~ run_type)
+}
 
@@
              simple_baselines) +
-  facet_wrap(. ~ run_type)
+  facet_wrap(. ~ named_run_type)
 ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)

### 2019-02-12 meta_RL_analyses.Rmd
Continuing renaming

@@
   }
+  d = d %>%
+    mutate(named_run_type = name_run_type(run_type))
   return(d)
@@
              simple_baselines) +
-  facet_wrap(. ~ run_type)
+  facet_wrap(. ~ named_run_type)
 ```
@@
 
-```{r}
-ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
-  geom_bar(stat="identity", position="dodge") +
-  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
-  scale_fill_brewer(palette="Set2") +
-  facet_wrap(. ~ run_type)
-```
 ```{r}
@@
   filter(epoch == 0) %>%
-  group_by(run_type, size, game_type, is_new_game) %>%
+  group_by(run_type, named_run_type, size, game_type, is_new_game) %>%
   summarize(avg_reward = mean(reward), sd_reward=sd(reward),
@@
   xlab("Meta Set Size") +
-  facet_grid(game_type ~ run_type)
+  facet_grid(game_type ~ named_run_type)
 ```
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
   geom_point() +
@@
                                #"basic_su_heldout",
-                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
-                               #"language"
+                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
+                               "language", "language_drop_03", "language_drop_05", "language_noncompositional"
                                ), num_runs, "new_meta_true_losses")
@@
          is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
-  gather(map_str, reward, -c(run, run_type, epoch), -starts_with("is_")) %>%
+  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
@@
 avg_meta_d = meta_d %>%
-  group_by(run_type, run, meta_task, is_new) %>%
+  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
   summarize(avg_reward = mean(reward)) %>%
-  group_by(run_type, meta_task, is_new) %>%
+  group_by(run_type, named_run_type, meta_task, is_new) %>%
   summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
@@
   scale_fill_brewer(palette="Set2") +
-  facet_wrap(.~run_type)
+  facet_wrap(. ~ named_run_type)
 ```
@@
              "meta_task", "reward", "is_new") +
-  facet_wrap(. ~ run_type)
+  facet_wrap(. ~ named_run_type)
 

### 2019-02-13 meta_learning.py
A better language?

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_simplified/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -134,16 +134,10 @@ if config["language_compositional"]:
             words = ["base", t["game"]] 
             if t["losers"]:
                 words.append("losers")
-            else:
-                words.extend(["not", "losers"])
             if t["black_valuable"]:
                 words.append("black_valuable")
-            else:
-                words.extend(["not", "black_valuable"])
             if t["suits_rule"]:
                 words.append("suits_rule")
-            else:
-                words.extend(["not", "suits_rule"])
         return words 
 else:
     def _wordify_task(t):

### 2019-02-13 writing/embedded_meta_learning.tex

@@
 \tikzstyle{line} = [draw, very thick, -latex']
+
+\setlength{\parskip}{1em}
+\setlength{\parindent}{0em}
 
@@
 $$\hat{z}_{out} = f_{D_Z}(z_{in}) \qquad \text{where } f_{D_Z} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left(D_Z\right)\right)$$
-This output can then be appropriately dispatched depedning on the task at hand.
+This output can then be appropriately dispatched depending on the task at hand.
 For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game.
-We could then evaluate performance by how well the system did at losing.
+We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy.
+\par
+Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language.
+The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified system.
 
@@
 
+\subsubsection{Results}
+\textbf{Basic meta learning:} First, we show that the  \par
+\textbf{Meta mapping (task $\rightarrow$ task):} \par
+\textbf{Basic language (language $\rightarrow$ task):} \par
+\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} \par
+
 \section{Discussion}

### 2019-02-13 meta_learning.py
Bugfix

@@ -1330,7 +1330,7 @@ class meta_model(object):
                     meta_lang_true_losses))
                 fout_lang.write(curr_lang_losses)
                 fout_lang_reward.write(curr_lang_rewards)
-                fout_meta.write(curr_meta_lang_true)
+                fout_lang_meta.write(curr_meta_lang_true)
 
             if config["sweep_meta_batch_sizes"] is not None:
                 with open(sweep_filename, "w") as fout_sweep:
@@ -1422,9 +1422,7 @@ class meta_model(object):
                             meta_lang_true_losses))
                         fout_lang.write(curr_lang_losses)
                         fout_lang_reward.write(curr_lang_rewards)
-                        fout_meta.write(curr_meta_lang_true)
-                        fout_lang.write(curr_lang_losses)
-                        fout_lang_reward.write(curr_lang_rewards)
+                        fout_lang_meta.write(curr_meta_lang_true)
 			print(curr_losses, curr_lang_losses)
                         if np.all(curr_losses < early_stopping_thresh) and np.all(curr_lang_losses < early_stopping_thresh):
                             print("Early stop!")

### 2019-02-13 meta_RL_analyses.Rmd
Basic + meta mapping card results in the paper

@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
+         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho),
+         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
 ```
@@
              simple_baselines) +
-  facet_wrap(. ~ named_run_type)
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3)
+  facet_wrap(. ~ named_run_type) + 
+  guides(color=guide_legend(title=NULL)) +
+  labs(x="Game type", y="Average reward") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
 ```
@@
                                #"basic_su_heldout",
-                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
-                               "language", "language_drop_03", "language_drop_05", "language_noncompositional"
+                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
+                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                                ), num_runs, "new_meta_true_losses")
@@
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
+  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)),
+         is_new = factor(is_new, labels=c("Trained", "Held out")))
 ```
@@
              "meta_task", "reward", "is_new") +
-  facet_wrap(. ~ named_run_type)
+  facet_wrap(. ~ named_run_type)  +
+  guides(color=guide_legend(title=NULL)) +
+  labs(x="Game type", y="Average reward") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
+ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
 ```

### 2019-02-13 writing/embedded_meta_learning.tex
Basic + meta mapping card results in the paper

@@
 \subsubsection{Results}
-\textbf{Basic meta learning:} First, we show that the  \par
-\textbf{Meta mapping (task $\rightarrow$ task):} \par
+\begin{figure}
+
+\end{figure}
+\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig.
+\ref{cards_basic_results}.
+We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``Losers'' variations of the ``straight flush'' game.
+In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
+It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 tasks leads to good generalization.
+Furthermore, starting from this ``guess'' at the correct strategy, the system can rapidly learn to achieve optimal performance ($< 20$ epochs, figure TODO).
+\par
+\begin{figure}
+\centering
+\includegraphics[width=0.66\textwidth]{figures/basic_meta_learning.png}
+\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.}
+\label{cards_basic_results}
+\end{figure}
+\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
+For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
+In Fig.
+\ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
+This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out).
+Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so it is encouraging to see rewards that are substantially above 0.
+Again, given training the system can learn how to achieve this mapping perfectly.
+\par
+\begin{figure}
+\centering
+\includegraphics[width=0.66\textwidth]{figures/meta_mapping.png}
+\caption{The system generalizes to meta-mapping new tasks.
+The system is trained to do the three meta-mappings shown here, and is able to generalize to tasks it has not been trained to map.
+For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
+When given a game it has not mapped in this way, it is able to map it to the losers variation.
+This plot shows the reward produced by taking the mapped embedding and playing the targeted game.}
+\label{cards_meta_map_results}
+\end{figure}
 \textbf{Basic language (language $\rightarrow$ task):} \par

### 2019-02-19 meta_RL_analyses.Rmd
Analyzing lang meta

@@
                    "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
-                   "language", "language_drop_03", "language_drop_05", "language_noncompositional")
+                   "language", "language_noncompositional", "language_simplified", "language_random_holdout", "language_meta")
 
@@
 ```{r}
-language_d = load_d(results_dir, c("language", "language_drop_03", "language_drop_05", "language_noncompositional"), num_runs, "new_language_rewards")
+language_d = load_d(results_dir, c("language", "language_simplified", "language_random_holdout", "language_meta", "language_noncompositional"), num_runs, "new_language_rewards")
 
@@
                                #"basic_su_heldout",
-                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
+                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                                #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
+                               "language", "language_random_holdout", "language_simplified", "language_meta"
                                ), num_runs, "new_meta_true_losses")
@@
 
+# language-induced meta mapping (true) evaluation
+
+```{r}
+lang_meta_d = load_d(results_dir, c("language_meta", "language_simplified"
+                               ), num_runs, "new_language_meta_true_losses")
+
+lang_meta_d = lang_meta_d %>%
+  filter(epoch == 0) %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
+         is_random_ho=grepl("random", run_type),
+         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
+  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
+  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
+  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)),
+         is_new = factor(is_new, labels=c("Trained", "Held out")))
+```
+
+```{r}
+avg_lang_meta_d = lang_meta_d %>%
+  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
+  summarize(avg_reward = mean(reward)) %>%
+  group_by(run_type, named_run_type, meta_task, is_new) %>%
+  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
+            se_reward = sd_avg_reward/sqrt(n()), 
+            ci_lo = avg_avg_reward - 1.96*se_reward, 
+            ci_hi = avg_avg_reward + 1.96*se_reward)
+
+```
+
+```{r}
+ggplot(avg_lang_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
+  geom_bar(stat="identity", position="dodge") +
+  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
+  scale_fill_brewer(palette="Set2") +
+  facet_wrap(. ~ named_run_type)
+```
+
+```{r}
+summary_plot(lang_meta_d %>%
+               filter(epoch == 0),
+             "meta_task", "reward", "is_new") +
+  facet_wrap(. ~ named_run_type)  +
+  guides(color=guide_legend(title=NULL)) +
+  labs(x="Game type", y="Average reward") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+# 
+# ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
+```
 # embeddings

### 2019-02-19 meta_learning.py
Non-toggling meta tasks

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_simplified/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta_nontoggling/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -107,7 +107,7 @@ config = {
 }
 
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
-config["base_meta_mappings"] = ["toggle_" + o for o in config["option_names"]]
+config["base_meta_mappings"] = ["turnON_" + o for o in config["option_names"]] + ["turnOF_" + o for o in config["option_names"]]
 #config["base_meta_tasks"] = []#["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
 #config["base_meta_mappings"] = []#["toggle_" + o for o in config["option_names"]]
 config["base_tasks"] = [{"game": g, "losers": l, "black_valuable": b,
@@ -177,11 +177,12 @@ def _get_meta_pairings(base_tasks, meta_tasks, meta_mappings):
     all_meta_tasks = meta_tasks + meta_mappings
     meta_pairings = {mt: {"base": [], "meta": []} for mt in all_meta_tasks}
     for mt in all_meta_tasks:
-        if mt[:6] == "toggle":
+        if mt[:4] == "turn":
+            ON_or_OFF = mt[4:6] == "ON"
             to_toggle = mt[7:]
             for task in base_tasks: 
                 other = deepcopy(task) 
-                other[to_toggle] = not other[to_toggle]
+                other[to_toggle] = ON_or_OFF 
                 if other in base_tasks:
                     meta_pairings[mt]["base"].append((_stringify_game(task),
                                                       _stringify_game(other)))

### 2019-02-22 meta_learning.py
Critical bugfix in language meta

@@ -1213,6 +1213,7 @@ class meta_model(object):
         rewards = []
         for meta_task in meta_tasks:
             meta_dataset = self.meta_dataset_cache[meta_task]
+            intified_task = self.intified_tasks[t]
             for task, other in meta_pairings[meta_task]["base"]:
                 task_buffer = self.memory_buffers[task]
                 task_embedding = self.get_base_embedding(task_buffer)
@@ -1220,7 +1221,7 @@ class meta_model(object):
                 other_buffer = self.memory_buffers[other]
                 other_game = self.games[other]
 
-                mapped_embedding = self.get_meta_outputs(
+                mapped_embedding = self.get_meta_language_outputs(
                     meta_dataset, {"x": task_embedding})
 
                 names.append(meta_task + ":" + task + "->" + other)

### 2019-02-22 meta_learning.py
Bugfixing the bugfix

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta_nontoggling/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_nontoggling_random_holdout/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -81,16 +81,16 @@ config = {
     "memory_buffer_size": 1024, # How many memories of each task are stored
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
-#    "new_tasks": "random",
-    "new_tasks": [{"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": False},
-                  {"game": "straight_flush", "losers": True,
-                  "black_valuable": False, "suits_rule": True},
-                  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": False},
-                  {"game": "straight_flush", "losers": True,
-                  "black_valuable": True, "suits_rule": True}], # will be removed
-                                                                # from base tasks
+    "new_tasks": "random",
+#    "new_tasks": [{"game": "straight_flush", "losers": True,
+#                  "black_valuable": False, "suits_rule": False},
+#                  {"game": "straight_flush", "losers": True,
+#                  "black_valuable": False, "suits_rule": True},
+#                  {"game": "straight_flush", "losers": True,
+#                  "black_valuable": True, "suits_rule": False},
+#                  {"game": "straight_flush", "losers": True,
+#                  "black_valuable": True, "suits_rule": True}], # will be removed
+#                                                                # from base tasks
 
     "new_meta_tasks": [],
     
@@ -1213,7 +1213,7 @@ class meta_model(object):
         rewards = []
         for meta_task in meta_tasks:
             meta_dataset = self.meta_dataset_cache[meta_task]
-            intified_task = self.intified_tasks[t]
+            intified_task = self.intified_tasks[meta_task]
             for task, other in meta_pairings[meta_task]["base"]:
                 task_buffer = self.memory_buffers[task]
                 task_embedding = self.get_base_embedding(task_buffer)

### 2019-02-22 meta_learning.py
Bugfixing the bugfix

@@ -1159,10 +1159,10 @@ class meta_model(object):
         }
         if meta_class:
             feed_dict[self.meta_class_ph] = this_y 
-            this_fetch = self.meta_t_language_output 
+            this_fetch = self.meta_t_output_language 
         else:
             feed_dict[self.meta_target_ph] = this_y
-            this_fetch = self.meta_m_language_output 
+            this_fetch = self.meta_m_output_language 
 
         res = self.sess.run(this_fetch, feed_dict=feed_dict)
 
@@ -1222,7 +1222,7 @@ class meta_model(object):
                 other_game = self.games[other]
 
                 mapped_embedding = self.get_meta_language_outputs(
-                    meta_dataset, {"x": task_embedding})
+                    intified_task, meta_dataset, {"x": task_embedding})
 
                 names.append(meta_task + ":" + task + "->" + other)
                 _, this_rewards = self.base_embedding_eval(mapped_embedding, other_game, other_buffer)

### 2019-02-22 meta_learning.py
Ability to toggle toggling

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_nontoggling_random_holdout/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta_nontoggling/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -81,17 +81,18 @@ config = {
     "memory_buffer_size": 1024, # How many memories of each task are stored
     "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
-    "new_tasks": "random",
-#    "new_tasks": [{"game": "straight_flush", "losers": True,
-#                  "black_valuable": False, "suits_rule": False},
-#                  {"game": "straight_flush", "losers": True,
-#                  "black_valuable": False, "suits_rule": True},
-#                  {"game": "straight_flush", "losers": True,
-#                  "black_valuable": True, "suits_rule": False},
-#                  {"game": "straight_flush", "losers": True,
-#                  "black_valuable": True, "suits_rule": True}], # will be removed
-#                                                                # from base tasks
+#    "new_tasks": "random",
+    "new_tasks": [{"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": False},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": True},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": False},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": True}], # will be removed
+                                                                # from base tasks
 
+    "meta_toggling": True, # if false, different tasks for turning ON or OFF
     "new_meta_tasks": [],
     
     "train_language": True, # whether to train language as well (only language
@@ -107,9 +108,15 @@ config = {
 }
 
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
[…]

### 2019-02-26 meta_learning.py
Toggling doesn't actually seem to make things worse, so keep it simple

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_meta_nontoggling/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,

### 2019-02-26 meta_RL_analyses.Rmd
Analysis updates/new results

@@
                    "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
-                   "language", "language_noncompositional", "language_simplified", "language_random_holdout", "language_meta")
+                   "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout")
 
@@
 ```{r}
-language_d = load_d(results_dir, c("language", "language_simplified", "language_random_holdout", "language_meta", "language_noncompositional"), num_runs, "new_language_rewards")
+language_d = load_d(results_dir, c("language", "language_noncompositional", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"), num_runs, "new_language_rewards")
 
@@
                                #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
-                               "language", "language_random_holdout", "language_simplified", "language_meta"
+                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
                                ), num_runs, "new_meta_true_losses")
@@
 ```{r}
-lang_meta_d = load_d(results_dir, c("language_meta", "language_simplified"
+lang_meta_d = load_d(results_dir, c(
+                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
                                ), num_runs, "new_language_meta_true_losses")

### 2019-02-26 meta_learning.py
Removing unnecessary code, new noncompositional run (with meta)

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_noncompositional/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
@@ -97,9 +97,9 @@ config = {
     
     "train_language": True, # whether to train language as well (only language
                             # inputs and only base tasks, for now)
-    "language_compositional": True, # whether language should be used
-                                    # compositionally, which is nice but 
-                                    # increases sentence length
+    "language_compositional": False, # whether language should be used in more
+                                     # complex way, which is nice but makes the
+                                     # network's task harder
     "lang_drop_prob": 0.0, # dropout on language processing features
                             # to try to address overfitting
 
@@ -1184,10 +1184,8 @@ class meta_model(object):
             self.language_input_ph: intified_task
         }
         if meta_class:
-            feed_dict[self.meta_class_ph] = this_y 
             this_fetch = self.meta_t_output_language 
         else:
-            feed_dict[self.meta_target_ph] = this_y
             this_fetch = self.meta_m_output_language 
 
         res = self.sess.run(this_fetch, feed_dict=feed_dict)

### 2019-02-26 meta_RL_analyses.Rmd
Better plots, and getting rid of some redundancies

@@
 
-result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
+result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                    "basic", #"basic_su_heldout", 
                    "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
-                   "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout")
+                   #"language", "language_simplified",
+                   "language_noncompositional_old", "language_simplified_random_holdout")
 
@@
             run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
+            run_type == "language_noncompositional_old" ~ "Old language (targeted 10%)",
+            run_type == "language_simplified" ~ "Old language (targeted 10%)",
+            run_type == "language_simplified_random_holdout" ~ "Language (random 50%)",
             T ~ run_type)
@@
 ```{r}
+name_var = function(var) { # var names for plotting
+  case_when(var %in% c("is_new", "is_new_game") ~ "Held out?",
+            var == "game_type" ~ "Game",
+            var %in% c("run_type", "named_run_type") ~ "Run type",
+#            var == "reward" ~ "Reward",
+            grepl("reward", var) ~ "Average Reward",
+            T ~ var)
+  }
+
 summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
@@
                   width=0.25) +
-    scale_color_brewer(palette=palette)
+    scale_color_brewer(palette=palette) +
+    labs(x=name_var(x_var), y=name_var(y_var)) +
+    guides(color=guide_legend(title=NULL))
 
@@
 
-summary_plot(reward_d %>%
-               filter(epoch == 0),
-             "game_type", "reward", "is_new_game",
-             simple_baselines) +
-  facet_wrap(. ~ named_run_type)
+# summary_plot(reward_d %>%
+#                filter(epoch == 0),
+#              "game_type", "reward", "is_new_game",
+#              simple_baselines) +
+#   facet_wrap(. ~ named_run_type)
 ```
@@
   facet_wrap(. ~ named_run_type) + 
-  guides(color=guide_legend(title=NULL)) +
-  labs(x="Game type", y="Average reward") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
@@
 ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
 ```
@@
 ```{r}
-language_d = load_d(results_dir, c("language", "language_noncompositional", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"), num_runs, "new_language_rewards")
+language_d = load_d(results_dir, c("language_noncompositional_old", 
+                                   #"language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
+                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")
 
@@
 ```{r}
-avg_language_d = language_d %>%
-  select(-game_str) %>%
-  filter(epoch == 0) %>%
-  group_by(run_type, game_type, is_new_game) %>%
-  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
-            se_reward = sd_reward/sqrt(n()), 
-            ci_lo = avg_reward - 1.96*se_reward, 
-            ci_hi = avg_reward + 1.96*se_reward)
-```
-
-```{r}
 ggplot(language_d %>%
@@
                 is_new_game),
-       aes(x=run_type, y=reward, fill=as.factor(run))) +
+       aes(x=named_run_type, y=reward, fill=as.factor(run))) +
   geom_hline(yintercept=0.,
@@
   geom_violin(position="dodge") +
-  scale_color_brewer(palette="Set2") 
+  geom_point(aes(group=as.factor(run)),
+             size=3,
+             stat="summary", fun.y="mean",
+             position=position_dodge(width=0.9)) +
+  scale_color_brewer(palette="Set2") + 
+  ylim(-0.6, 0.6) +
+  labs(x="Run type",
+       y="Reward density") + 
+  guides(fill=guide_legend(title="Run"))
+ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
 ```
@@
              simple_baselines) +
-  facet_wrap(. ~ run_type)
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
+  facet_wrap(. ~ run_type) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+ggsave("writing/figures/language_basic.png", width=5, height=3.5)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
 ```
@@
 lang_meta_d = load_d(results_dir, c(
-                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
+                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
+                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout"
                                ), num_runs, "new_language_meta_true_losses")
@@
 ```{r}
-avg_lang_meta_d = lang_meta_d %>%
-  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
-  summarize(avg_reward = mean(reward)) %>%
-  group_by(run_type, named_run_type, meta_task, is_new) %>%
-  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
-            se_reward = sd_avg_reward/sqrt(n()), 
-            ci_lo = avg_avg_reward - 1.96*se_reward, 
-            ci_hi = avg_avg_reward + 1.96*se_reward)
-
-```
-
-```{r}
-ggplot(avg_lang_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
-  geom_bar(stat="identity", position="dodge") +
-  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
-  scale_fill_brewer(palette="Set2") +
-  facet_wrap(. ~ named_run_type)
-```
-
-```{r}
 summary_plot(lang_meta_d %>%
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-# 
-# ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
+ ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
 ```

### 2019-02-28 meta_RL_analyses.Rmd
Tweaks

@@
              simple_baselines) +
-  facet_wrap(. ~ run_type) + 
+  facet_wrap(. ~ named_run_type) + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
@@
                                #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
-                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
+                               # "language", "language_simplified",
+                               # "language_meta_nontoggling", "language_nontoggling_random_holdout", 
+                               "language_noncompositional_old", "language_simplified_random_holdout"
                                ), num_runs, "new_meta_true_losses")

### 2019-02-28 writing/embedded_meta_learning.tex
Tweaks

@@
 \begin{document}
+\title{Embedded meta-learning}
+\author{Andrew K. Lampinen}
+\date{}
+\maketitle
 
 \section{Introduction}
-Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2017}.
+Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016}.
 One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these.
@@
 One of the abilities that this grants humans is rapid adaptation of our behavior.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep{}.
+The problem of rapid learning has been partially addressed by meta-learning systems.
 However, humans can take rapidly acquired knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction.
@@
 In order to switch the system to an RL meta learning system, we made a very simple change.
-Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{} to predict rewards for each bet in each state.
+Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
 The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
-That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples.
+That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure of the game.
 \par
-We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. \par
+We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
+We can also train the system to map language to games, i.e.
+playing a game based on hearing its name, and then ask whether the system can generalize this to held-out games based on the systematicity of the language.
+For example, if trained to play ``straight flush'' but never ``losers straight flush,'' will it nevertheless be able to generalize to this case based on its experience with other games?
+Finally, we can use language denote meta-mappings.
+\par
 
+\newpage
 \subsubsection{Results}
-\begin{figure}
-
-\end{figure}
 \textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig.
@@
 \par
-\begin{figure}
+\begin{figure}[H]
 \centering
 \includegraphics[width=0.66\textwidth]{figures/basic_meta_learning.png}
-\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.}
+\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
+The dashed line indicates chance performance, while the solid lines are optimal performance.}
 \label{cards_basic_results}
 \end{figure}
+\newpage
 \textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
@@
 Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so it is encouraging to see rewards that are substantially above 0.
-Again, given training the system can learn how to achieve this mapping perfectly.
+Again, given a small amount of additional training on the new games, the system can learn how to achieve this mapping perfectly.
 \par
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 \caption{The system generalizes to meta-mapping new tasks.
-The system is trained to do the three meta-mappings shown here, and is able to generalize to tasks it has not been trained to map.
+The system is trained to do the three meta-mappings shown here, and is able to generalize these mappings to tasks it has not been trained on.
 For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
@@
 \end{figure}
-\textbf{Basic language (language $\rightarrow$ task):} \par
-\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} \par
+\newpage
+\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone.
+The system is significantly better than chance at this task, as shown in Fig.
+\ref{cards_language_basic_results}, but it is substantially less successful at this task than at learning from examples.
+This is perhaps unsurprising, however, since examples contain richer information about the structure of the task.
+(Note that the targeted 10\% was run using an older version of the code.
+Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
+Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out.
+This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network.
+Interestingly, simply applying dropout does not seem to ameliorate this.
+\par
+\begin{figure}[H]
+\begin{subfigure}[t]{0.5\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figures/language_basic.png}
+\caption{Average rewards}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
+\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
+\end{subfigure}
+\caption{The system generalizes to held out tasks based on language alone.
+However, it is substantially less good at this task than generalizing to a held-out task based on examples.
+Furthermore, it shows more run-to-run variability and within-run variability.}
+\label{cards_language_basic_results}
+\end{figure}
+\newpage
+\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples.
+Note that this is in some ways an easier task than the basic language-mapping task.
+\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
+\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
+\label{cards_language_meta_results}
+\end{figure}
 
@@
 
+\bibliographystyle{acm}
+\bibliography{arrr}
+
 \end{document}

### 2019-02-28 meta_RL_analyses.Rmd
Fix

@@
                 is_new_game),
-       aes(x=named_run_type, y=reward, fill=as.factor(run))) +
+       aes(x=run, y=reward, fill=as.factor(run))) +
   geom_hline(yintercept=0.,
@@
   ylim(-0.6, 0.6) +
-  labs(x="Run type",
-       y="Reward density") + 
-  guides(fill=guide_legend(title="Run"))
+  labs(x="Run",
+       y="Reward density on held-out tasks") + 
+  guides(fill=guide_legend(title="Run")) +
+  facet_wrap(~named_run_type)
 ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)

### 2019-03-06 compute_baselines.py
Complete baselines

@@ -19,15 +19,16 @@ with open("baseline_data.csv", "w") as fout:
                                                  "optimal",
                                                  g.compute_expected_return())) 
 
-                    for sr2 in suits_rule:
-                        for l2 in losers:
-                            for bv2 in black_valuable:
-                                if sr2 == sr and l2 == l and bv2 == bv:
-                                    continue
-                                g2 = card_game(game_type, bv2, sr2, l2)
-                                name2 = _stringify_game(g2)
-                                g2_policy = {hand: max_bet * (g2.hand_to_win_prob[hand] > 0.5) for hand in g2.hands}
-                                fout.write("%s, %s, %f\n" % (
-                                    name,
-                                    name2,
-                                    g.compute_expected_return(policy=g2_policy))) 
+                    for game_type_2 in game_types:
+                        for sr2 in suits_rule:
+                            for l2 in losers:
+                                for bv2 in black_valuable:
+                                    if game_type_2 == game_type and sr2 == sr and l2 == l and bv2 == bv:
+                                        continue
+                                    g2 = card_game(game_type_2, bv2, sr2, l2)
+                                    name2 = _stringify_game(g2)
+                                    g2_policy = {hand: max_bet * (g2.hand_to_win_prob[hand] > 0.5) for hand in g2.hands}
+                                    fout.write("%s, %s, %f\n" % (
+                                        name,
+                                        name2,
+                                        g.compute_expected_return(policy=g2_policy))) 

### 2019-03-06 meta_RL_analyses.Rmd
Better baselining

--- 2019-02-28 meta_RL_analyses.Rmd
@@
                    #"language", "language_simplified",
+                   "language_noncompositional", "language_simplified", "language_meta_nontoggling",
                    "language_noncompositional_old", "language_simplified_random_holdout")
@@
 
-summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
+summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2") {
   p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +
@@
 
-  if (!is.null(baseline_data)) {
+  if (!is.null(optimal_baseline_data)) {
     p = p + 
@@
                x=(1:5)-0.5, xend=(1:5)+0.5,
-               y=simple_baselines$expected_reward,
-               yend=simple_baselines$expected_reward,
+               y=optimal_baseline_data$expected_reward,
+               yend=optimal_baseline_data$expected_reward,
                linetype=1, alpha=0.5) 
@@
 
+  if (!is.null(other_baseline_data)) {
+    p = p + 
+      geom_spoke(data=other_baseline_data,
+                 aes(x=game_type, y=expected_reward, angle=0, radius=1),
+                 linetype=2, alpha=0.5,
+                 position=position_nudge(x=-0.5)) 
+  }
+
   return(p)
+}
+```
+
+```{r}
+check_if_new_game = function(run_type, game_str) {
+  case_when(grepl("su_heldout", run_type) ~ game_str %in% new_game_strs_su_heldout,
+            grepl("only_one$", run_type) ~ game_str %in% new_game_strs_only_one,
+            grepl("only_one_ho", run_type) ~ game_str %in% new_game_strs_only_one_ho,
+            grepl("random", run_type) ~ game_str %in% new_game_strs_random_heldout,
+            T ~ game_str %in% new_game_strs)
 }
@@
          suits_rule = grepl("sr_1", game))
+```
+```{r}
+optimal_baselines = baseline_data %>% 
+  filter(policy == "optimal") %>%
+  group_by(game_type) %>%
+  summarize(expected_reward = mean(expected_reward)) %>%
+  ungroup()
+```
+
+And "baselines" which show the performance using strategy from most correlated prior game
+
+```{r}
+most_correlated_baselines = crossing(run_type=result_subdirs, baseline_data) %>%
+  mutate(is_new_game = check_if_new_game(run_type, game)) %>%
+  filter((!is_new_game & policy == "optimal") | (policy != "optimal" & !check_if_new_game(run_type, policy))) %>%
+  group_by(run_type, game, is_new_game, game_type, losers, black_valuable, suits_rule) %>%
+  summarize(optimal_expected_reward = max(expected_reward)) %>%
+  group_by(run_type, game_type, is_new_game) %>%
+  summarize(expected_reward = mean(optimal_expected_reward)) %>%
+  mutate(is_new_game = factor(is_new_game, levels=c(F, T), labels=c("Trained", "Held out")),
+         named_run_type = name_run_type(run_type))
+
 ```
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho),
+         is_new_game = check_if_new_game(run_type, game_str),
          is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
@@
 ```{r}
-simple_baselines = baseline_data %>% 
-  filter(policy == "optimal") %>%
-  group_by(game_type) %>%
-  summarize(expected_reward = mean(expected_reward)) %>%
-  ungroup()
 
@@
 #              "game_type", "reward", "is_new_game",
-#              simple_baselines) +
+#              optimal_baselines) +
 #   facet_wrap(. ~ named_run_type)
@@
              "game_type", "reward", "is_new_game",
-             simple_baselines) 
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
+             optimal_baselines,
+             most_correlated_baselines %>%
+               filter(run_type == "basic",
+                      is_new_game == "Held out")) 
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
 ```
@@
 summary_plot(reward_d %>%
-               filter(epoch == 0,
-                      run_type %in% c("basic", "basic_random_holdout_longer")),
+               filter(epoch == 0),
              "game_type", "reward", "is_new_game",
-             simple_baselines) +
+             optimal_baselines,
+             most_correlated_baselines %>%
+               filter(is_new_game == "Held out")) +
   facet_wrap(. ~ named_run_type) + 
@@
 
-ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
+#ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
+         is_new_game = check_if_new_game(run_type, game_str))
+
 ```
@@
 
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_sweeping.png", width=5, height=3)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_sweeping.png", width=5, height=3)
 ```
@@
 language_d = load_d(results_dir, c("language_noncompositional_old", 
-                                   #"language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
+                                   #"language",  "language_nontoggling_random_holdout", 
+                                   "language_simplified", "language_meta_nontoggling", "language_noncompositional",
                                    "language_simplified_random_holdout"), num_runs, "new_language_rewards")
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
+         is_new_game = check_if_new_game(run_type, game_str))
 ```
@@
   ylim(-0.6, 0.6) +
-  labs(x="Run type",
-       y="Reward density") + 
-  guides(fill=guide_legend(title="Run"))
-ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
+  labs(x="Run",
+       y="Reward density on held-out tasks") + 
+  guides(fill=guide_legend(title="Run")) +
+  facet_wrap(~named_run_type)
+#ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
 ```
@@
              "game_type", "reward", "is_new_game",
-             simple_baselines) +
+             optimal_baselines) +
   facet_wrap(. ~ named_run_type) + 
@@
 ```{r}
-meta_d = load_d(results_dir, c("basic", 
-                               #"basic_su_heldout",
-                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
-                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
-                               # "language", "language_simplified",
-                               # "language_meta_nontoggling", "language_nontoggling_random_holdout", 
-                               "language_noncompositional_old", "language_simplified_random_holdout"
-                               ), num_runs, "new_meta_true_losses")
+meta_d = load_d(results_dir, result_subdirs, num_runs, "new_meta_true_losses")
 
@@
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)),
+  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
          is_new = factor(is_new, labels=c("Trained", "Held out")))
@@
 
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
-ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
+#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
 ```
@@
                               # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
-                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout"
+                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
+                               "language_meta_nontoggling", "language_noncompositional"
                                ), num_runs, "new_language_meta_true_losses")
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
- ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
+ #ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
 ```

### 2019-03-07 meta_learning.py
Joint language + examples training & eval

@@ -57,7 +57,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 40000,
+    "max_base_epochs": 20000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -71,15 +71,15 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/language_noncompositional/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/joint_lnex_mb_256_ne_20/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
-    "sweep_meta_batch_sizes": [10, 20, 50, 100, 200, 400, 800], # if not None,
-                                                                # eval each at
-                                                                # training ends
+    "sweep_meta_batch_sizes": [10, 20, 30, 50, 100, 200, 400, 800], # if not None,
+                                                                    # eval each at
+                                                                    # training ends
 
     "memory_buffer_size": 1024, # How many memories of each task are stored
-    "meta_batch_size": 768, # how many meta-learner sees
+    "meta_batch_size": 256, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
 #    "new_tasks": "random",
     "new_tasks": [{"game": "straight_flush", "losers": True,
@@ -96,10 +96,11 @@ config = {
     "new_meta_tasks": [],
     
     "train_language": True, # whether to train language as well (only language
-                            # inputs and only base tasks, for now)
-    "language_compositional": False, # whether language should be used in more
-                                     # complex way, which is nice but makes the
-                                     # network's task harder
+                            # inputs, for now)
+    "train_joint_lnex": True, # whether to train joint language + examples
+    "language_compositional": True, # whether language should be used in more
+                                    # complex way, which is nice but makes the
+                                    # network's task harder
     "lang_drop_prob": 0.0, # dropout on language processing features
                             # to try to address overfitting
 
[…]

### 2019-03-11 meta_RL_analyses.Rmd
Latest updates

@@
                    "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
+                   "meta_batch_64", "meta_batch_128", "meta_batch_256",
                    #"language", "language_simplified",
                    "language_noncompositional", "language_simplified", "language_meta_nontoggling",
-                   "language_noncompositional_old", "language_simplified_random_holdout")
+                   "language_noncompositional_old", "language_simplified_random_holdout",
+                   "language_mb_128_ne_15","language_mb_128_ne_20")
 
@@
 ggplot(avg_sweep_d %>%
-         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
+         filter(run_type == "basic" | run_type == "meta_batch_256"), aes(x=size, color=is_new_game, y=avg_reward)) +
   geom_point() +
@@
   xlab("Meta Set Size") +
-  facet_wrap(~ game_type)
+  facet_grid(game_type ~ run_type)
 
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "meta_batch_256", "meta_batch_128", "meta_batch_64", "language_mb_128_ne_15"),
+                              size < 200), aes(x=size, color=named_run_type, y=avg_reward)) +
   geom_point() +
@@
                                    "language_simplified", "language_meta_nontoggling", "language_noncompositional",
+                                   "language_mb_128_ne_15","language_mb_128_ne_20",
                                    "language_simplified_random_holdout"), num_runs, "new_language_rewards")
@@
                                "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
+                               "language_mb_128_ne_15","language_mb_128_ne_20",
                                "language_meta_nontoggling", "language_noncompositional"

### 2019-03-12 meta_learning.py
Allowing system to learn joint embedding weight

@@ -57,7 +57,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 20000,
+    "max_base_epochs": 5000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/joint_lnex_mb_256_ne_20/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/joint_lnex_mb_256_ne_5/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 30, 50, 100, 200, 400, 800], # if not None,
@@ -494,7 +494,12 @@ class meta_model(object):
                                                        False)
 
         #print(self.language_function_emb)
-        self.joint_lnex_function_emb = 0.5*(self.guess_base_function_emb + self.language_function_emb)
+#        self.joint_lnex_function_emb = 0.5*(self.guess_base_function_emb + self.language_function_emb)
+        self.lnex_ex_weight = tf.get_variable("lnex_ex_weight", [1],
+                                              initializer=tf.constant(0.5),
+                                              dtype=tf.float32)
+        sig_ex_w = tf.nn.sigmoid(self.lnex_ex_weight)
+        self.joint_lnex_function_emb = sig_ex_w*self.guess_base_function_emb + (1-sig_ex_w)*self.language_function_emb
 
 
         # hyper_network: emb -> (f: emb -> emb) 

### 2019-03-12 meta_learning.py
Bugfix

@@ -57,7 +57,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 5000,
+    "max_base_epochs": 10000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/joint_lnex_mb_256_ne_5/",
+    "output_dir": "/mnt/fs2/lampinen/meta_RL/paper_results/joint_lnex_lw_mb_128_ne_10/",
     "save_every": 20, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": [10, 20, 30, 50, 100, 200, 400, 800], # if not None,
@@ -79,7 +79,7 @@ config = {
                                                                     # training ends
 
     "memory_buffer_size": 1024, # How many memories of each task are stored
-    "meta_batch_size": 256, # how many meta-learner sees
+    "meta_batch_size": 128, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
 #    "new_tasks": "random",
     "new_tasks": [{"game": "straight_flush", "losers": True,
@@ -495,7 +495,7 @@ class meta_model(object):
 
         #print(self.language_function_emb)
 #        self.joint_lnex_function_emb = 0.5*(self.guess_base_function_emb + self.language_function_emb)
-        self.lnex_ex_weight = tf.get_variable("lnex_ex_weight", [1],
+        self.lnex_ex_weight = tf.get_variable("lnex_ex_weight",
                                               initializer=tf.constant(0.5),
                                               dtype=tf.float32)
         sig_ex_w = tf.nn.sigmoid(self.lnex_ex_weight)

### 2019-03-13 meta_RL_analyses.Rmd
Plots for commitee meeting

--- 2019-03-06 meta_RL_analyses.Rmd
@@
                    "basic", #"basic_su_heldout", 
-                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
+                   "basic_random_holdout_longer") # "basic_only_one", "basic_only_one_ho")
+
+language_result_subdirs = c(                  
+  "meta_batch_64", "meta_batch_128", "meta_batch_256",
   #"language", "language_simplified",
-                   "language_noncompositional", "language_simplified", "language_meta_nontoggling",
-                   "language_noncompositional_old", "language_simplified_random_holdout")
+  "language_noncompositional", "language_simplified", # "language_meta_nontoggling",
+  "language_noncompositional_old", "language_simplified_random_holdout",
+  "language_mb_128_ne_15","language_mb_128_ne_20")
+
+joint_result_subdirs = c("joint_lnex_mb_256_ne_20",
+                         "joint_lnex_mb_256_ne_10",
+                         "joint_lnex_mb_256_ne_5",
+                         "joint_lnex_lw_mb_256_ne_10",
+                         "joint_lnex_lw_mb_128_ne_10",
+                         "joint_lnex_lw_mb_128_ne_5")
+
+result_subdirs = c(result_subdirs, language_result_subdirs, joint_result_subdirs)
 
@@
             run_type == "language_simplified" ~ "Old language (targeted 10%)",
+            run_type == "meta_batch_128" ~ "Language (targeted 10%)",
             run_type == "language_simplified_random_holdout" ~ "Language (random 50%)",
@@
                filter(run_type == "basic",
-                      is_new_game == "Held out")) 
+                      is_new_game == "Held out")) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3.5)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
+```
+
+```{r}
+summary_plot(reward_d %>%
+               filter(epoch == 0,
+                      run_type == "basic_random_holdout_longer"),
+             "game_type", "reward", "is_new_game",
+             optimal_baselines,
+             most_correlated_baselines %>%
+               filter(run_type == "basic_random_holdout_longer",
+                      is_new_game == "Held out")) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
 ```
@@
 #ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
-#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
 ```
@@
 ```{r}
-avg_reward_d %>% filter(is_new_game)
+#avg_reward_d %>% filter(is_new_game)
 ```
@@
 ```{r}
-ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
-  geom_bar(stat="identity", position="dodge") +
-  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
-  scale_fill_brewer(palette="Set1")
+# ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
+#   geom_bar(stat="identity", position="dodge") +
+#   geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
+#   scale_fill_brewer(palette="Set1")
 ```
@@
 ggplot(avg_sweep_d %>%
-         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
+         filter(run_type %in% c("basic", "meta_batch_256", "joint_lnex_lw_mb_256_ne_10", "joint_lnex_lw_mb_128_ne_10")), aes(x=size, color=is_new_game, y=avg_reward)) +
   geom_point() +
@@
 ```{r}
-ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
+ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "meta_batch_256", "meta_batch_128", "meta_batch_64", "language_mb_128_ne_15", "joint_lnex_mb_256_ne_5", "joint_lnex_mb_256_ne_10"),
+                              size < 200), aes(x=size, color=named_run_type, y=avg_reward)) +
   geom_point() +
@@
 ```{r}
-language_d = load_d(results_dir, c("language_noncompositional_old", 
-                                   #"language",  "language_nontoggling_random_holdout", 
-                                   "language_simplified", "language_meta_nontoggling", "language_noncompositional",
-                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")
+language_d = load_d(results_dir, c(language_result_subdirs, joint_result_subdirs), num_runs, "new_language_rewards")
 
@@
          suits_rule = grepl("sr_1", game_str),
-         is_new_game = check_if_new_game(run_type, game_str))
+         is_new_game = check_if_new_game(run_type, game_str),
+         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
 ```
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-ggsave("writing/figures/language_basic.png", width=5, height=3.5)
+#ggsave("writing/figures/language_basic.png", width=5, height=3.5)
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
+```
+
+```{r}
+summary_plot(language_d %>%
+               filter(epoch == 0,
+                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
+             "game_type", "reward", "is_new_game",
+             optimal_baselines,
+             most_correlated_baselines %>%
+               filter(run_type %in% c("meta_batch_128", "language_simplified_random_holdout"),
+                      is_new_game == "Held out")) +
+  facet_wrap(. ~ named_run_type) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#ggsave("writing/figures/language_basic.png", width=7, height=3.5)
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_basic.png", width=7, height=3.5)
+```
+# joint language + examples
+
+```{r}
+joint_d = load_d(results_dir, joint_result_subdirs, num_runs, "new_joint_lnex_rewards")
+
+joint_d = joint_d %>%
+  mutate(is_su_ho=grepl("su_heldout", run_type),
+         is_only_one=grepl("only_one$", run_type),
+         is_only_one_ho=grepl("only_one_ho", run_type),
+         is_random_ho=grepl("random", run_type),
+         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
+  gather(game_str, reward, starts_with("game")) %>%
+  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+         losers = grepl("l_1", game_str),
+         black_valuable = grepl("bv_1", game_str),
+         suits_rule = grepl("sr_1", game_str),
+         is_new_game = check_if_new_game(run_type, game_str))
+```
+
+```{r}
+ggplot(joint_d %>%
+         filter(epoch == 0,
+                is_new_game),
+       aes(x=run, y=reward, fill=as.factor(run))) +
+  geom_hline(yintercept=0.,
+             linetype=2,
+             alpha=0.5) +
+  geom_violin(position="dodge") +
+  geom_point(aes(group=as.factor(run)),
+             size=3,
+             stat="summary", fun.y="mean",
+             position=position_dodge(width=0.9)) +
+  scale_color_brewer(palette="Set2") + 
+  ylim(-0.6, 0.6) +
+  labs(x="Run",
+       y="Reward density on held-out tasks") + 
+  guides(fill=guide_legend(title="Run")) +
+  facet_wrap(~named_run_type)
+```
+
+```{r}
+summary_plot(joint_d %>%
+               filter(epoch == 0),
+             "game_type", "reward", "is_new_game",
+             optimal_baselines) +
+  facet_wrap(. ~ named_run_type) + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+#ggsave("writing/figures/joint_lnex.png", width=5, height=3.5)
 ```
@@
 ```{r}
-lang_meta_d = load_d(results_dir, c(
-                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
-                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
-                               "language_meta_nontoggling", "language_noncompositional"
-                               ), num_runs, "new_language_meta_true_losses")
+lang_meta_d = load_d(results_dir, c(language_result_subdirs, joint_result_subdirs), num_runs, "new_language_meta_true_losses")
 
@@
 ```
+
+```{r}
+summary_plot(lang_meta_d %>%
+               filter(epoch == 0,
+                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
+             "meta_task", "reward", "is_new") +
+  facet_wrap(. ~ named_run_type)  +
+  guides(color=guide_legend(title=NULL)) +
+  labs(x="Game type", y="Average reward") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
+#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
+```
+
 # embeddings

### 2019-04-16 writing/embedded_meta_learning.tex
Formatting + tweaks

@@
-\documentclass[11pt]{article}
+\documentclass{article}
+
+\usepackage{neurips_2019}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
 
@@
 \usepackage{float}
-\usepackage[margin=1in]{geometry}
 \usepackage{tikz}
@@
 \par
-In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning.
-By treating tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable.
+In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning and exploit the idea of \textbf{homoiconicity}\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language just as data can.}.
+By treating tasks and data as functions, we can conceptually think of both data \textbf{and} learned behaviors as transformable.
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
@@
 In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space.
-We demonstrate the greater flexibility of this approach.
+We demonstrate the greater flexibility of this approach compared to other approaches.
+\par
 \section{Method}

### 2019-04-16 writing/embedded_meta_learning.tex
Generative model

@@
 
-\subsection{Boolean functions}
-As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
+%\subsection{Boolean functions}
+%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
 Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input.
@@
 \par
-We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
+%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
+%
+\subsection{Learning multivariate polynomials}
+As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e.
+the task was to learn functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$).
+This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables).
+This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
+\par
+%% TODO: appendix
+We randomly sampled the train and test polynomials as follows:
+\begin{enumerate}
+\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
+\item Sample the subset of $k$ variables that are relevant uniformly at random.
+\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random intercept drawn from $\mathcal{N}(0, 2.5)$.
+\end{enumerate}
+The data points were sampled uniformly from $[-1, 1]$ independently for each polynomial. \par
+\subsubsection{Results}
 
@@
 If it wins, it is rewarded the value of the bet, if it loses, it receives the negative of the value.
-This doesn't require long term planning, but is nevertheless not precisely a supervised problem, since the feedback is stochastic.
+This doesn't require long term planning, but does incorporate the stochastic feedback aspect of reinforcement learning.
 We considered a variety of games:
@@
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
-The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
+(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as still a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
 That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure of the game.

### 2019-04-24 writing/embedded_meta_learning.tex
Details

@@
 \end{enumerate}
-The data points were sampled uniformly from $[-1, 1]$ independently for each polynomial. \par
+The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial.
+The datasets were resampled every 50 epochs of training.
+\par
 \subsubsection{Results}

### 2019-04-26 writing/embedded_meta_learning.tex
Continual learning setup

@@
 \par
+
+\subsubsection{Results}
+
+\subsection{Continual learning}
+Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step.
+We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined.
+Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}.
+\par
+A very simple solution to these problems is naturally suggested by our architecture.
+Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
+This also allows the potential to optimize these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task.
+That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
+In this section, we demonstrate the effectiveness of this solution by training on new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
+We show that this yields very good results if the model has been pre-trained on a sufficient distribution of tasks.
+\par
+%% TODO: Baselines and the fact that something interesting is being learned
+
 \subsubsection{Results}

### 2019-04-30 writing/embedded_meta_learning.tex
Tweaks

@@
 One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these.
-That is, neural networks knowledge about \textbf{what} is being computed is \textbf{inaccessible} by the computations.
+That is, neural networks knowledge about what is being computed is inaccessible to those computations.
 By contrast, humans are frequently consciously aware of both our representations of input, the things we can do with them, and the relationships between data and tasks.
@@
 The problem of rapid learning has been partially addressed by meta-learning systems.
-However, humans can take rapidly acquired knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction.
-For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance \textbf{without any retraining} (i.e.
+However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction.
+For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
 zero-shot).
-Deep learning systems at present lack this representational flexiblity.
+Deep learning systems at present generally lack this representational flexiblity.
 \par
-In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning and exploit the idea of \textbf{homoiconicity}\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language just as data can.}.
-By treating tasks and data as functions, we can conceptually think of both data \textbf{and} learned behaviors as transformable.
+In this paper, we propose a new class of architectures which essentially take a functional perspective on meta-learning and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language just as data can.}.
+By treating tasks and data as functions, we can conceptually think of both data \emph{and} learned behaviors as transformable.
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
@@
 In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space.
-We demonstrate the greater flexibility of this approach compared to other approaches.
+We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits such as a useful framework for continual learning.
 \par

### 2019-04-30 writing/embedded_meta_learning.tex
Clarity, clarity, clarity

@@
 \begin{document}
-\title{Embedded meta-learning}
+\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
 \author{Andrew K. Lampinen}
@@
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016}.
-One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these.
-That is, neural networks knowledge about what is being computed is inaccessible to those computations.
-By contrast, humans are frequently consciously aware of both our representations of input, the things we can do with them, and the relationships between data and tasks.
-This is true for domains from game playing to natural language understanding.
+One fundamental reason for this is that humans are aware of what we are trying to compute and why.
+By contrasts, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
+That is, neural networks knowledge about what is being computed is only implicitly accessible to those computations.
 \par
-One of the abilities that this grants humans is rapid adaptation of our behavior.
-The problem of rapid learning has been partially addressed by meta-learning systems.
+There are a number of advantages to representing knowledge about data and tasks.
+In particular, it can grant the ability to rapidly adapt behavior to a new task.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep{?????}.
 However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction.
@@
 \par
-In this paper, we propose a new class of architectures which essentially take a functional perspective on meta-learning and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language just as data can.}.
+In this paper, we propose a new class of architectures which essentially take a functional perspective on meta-learning and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}.
 By treating tasks and data as functions, we can conceptually think of both data \emph{and} learned behaviors as transformable.
@@
 For instances that fall outside its data distribution or for optimal performance it may require some retraining.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relateively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow.
+This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow.
 \par
@@
 \end{figure}
-More formally, we take a \textbf{functional} perspective on learning.
+More formally, we take a \emph{functional} perspective on learning.
 A datum can be represented by a constant function which outputs it.

### 2019-04-30 meta_RL_analyses.Rmd
Aesthetics

@@
     geom_point(stat="summary", fun.y=mean, size=2) +
-    geom_errorbar(stat="summary", 
-                  fun.ymin=function(x) {mean(x) - 1.96*sd(x)/sqrt(length(x))},
-                  fun.ymax=function(x) {mean(x) + 1.96*sd(x)/sqrt(length(x))},
-                  width=0.25) +
-    scale_color_brewer(palette=palette) +
-    labs(x=name_var(x_var), y=name_var(y_var)) +
-    guides(color=guide_legend(title=NULL))
+    scale_color_manual(values=c("#6560a3", "#f37f22"))
 
@@
                yend=optimal_baseline_data$expected_reward,
-               linetype=1, alpha=0.5) 
+               linetype=1, alpha=0.33) 
   }
@@
   }
+
+  p = p + 
+    geom_errorbar(stat="summary", 
+                  fun.data="mean_cl_boot",
+                  width=0.25) +
+#    scale_color_brewer(palette=palette) +
+    labs(x=name_var(x_var), y=name_var(y_var)) +
+    guides(color=guide_legend(title=NULL))
 

### 2019-04-30 meta_RL_analyses.Rmd
Baselining for meta + more aesthetics

@@
             T ~ run_type)
+}
+
+name_game_type = function(game) {
+  case_when(game == "high_card" ~ "High card",
+            game == "straight_flush" ~ "Straight flush",
+            game == "match" ~ "Match",
+            game == "sum_under" ~ "Blackjack",
+            game == "pairs_and_high" ~ "Pairs",
+            T ~ game)
+}
+
+name_meta_task = function(meta_task) {
+  case_when(meta_task == "toggle_losers" ~ "Losers",
+            meta_task == "toggle_suits_rule" ~ "Suits > rank",
+            meta_task == "toggle_black_valuable" ~ "Switch suits",
+            T ~ meta_task)
 }
@@
   case_when(var %in% c("is_new", "is_new_game") ~ "Held out?",
-            var == "game_type" ~ "Game",
+            var %in% c("game_type", "named_game_type") ~ "Game",
             var %in% c("run_type", "named_run_type") ~ "Run type",
@@
 summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2") {
+
   p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +  
@@
     geom_point(stat="summary", fun.y=mean, size=2) +
-    scale_color_manual(values=c("#6560a3", "#f37f22"))
+    scale_color_manual(values=c("#555093", "#f38f22"))
 
@@
   if (!is.null(other_baseline_data)) {
+    # get rid of runs that aren't in data
+    run_types_included = data %>% pull(named_run_type) %>% unique()
+    other_baseline_data = other_baseline_data %>%
+      filter(named_run_type %in% run_types_included)
+
     p = p + 
       geom_spoke(data=other_baseline_data,
-                 aes(x=game_type, y=expected_reward, angle=0, radius=1),
+                 aes_string(x=x_var, y="expected_reward", angle=0, radius=1),
                  linetype=2, alpha=0.5,
@@
   p = p + 
+    geom_point(stat="summary", fun.y=mean, size=2) +
     geom_errorbar(stat="summary", 
                   fun.data="mean_cl_boot",
-                  width=0.25) +
+                  width=0.4) +
 #    scale_color_brewer(palette=palette) +
@@
          black_valuable = grepl("bv_1", game),
-         suits_rule = grepl("sr_1", game))
+         suits_rule = grepl("sr_1", game),
+         named_game_type = name_game_type(game_type))
 ```
@@
   filter(policy == "optimal") %>%
-  group_by(game_type) %>%
+  group_by(game_type, named_game_type) %>%
   summarize(expected_reward = mean(expected_reward)) %>%
-  ungroup()
+  ungroup() %>%
+  arrange(named_game_type)
 ```
@@
   mutate(is_new_game = factor(is_new_game, levels=c(F, T), labels=c("Trained", "Held out")),
-         named_run_type = name_run_type(run_type))
+         named_run_type = name_run_type(run_type),
+         named_game_type = name_game_type(game_type))
 
@@
          is_new_game = check_if_new_game(run_type, game_str),
-         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
+         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")),
+         named_game_type = name_game_type(game_type))
 ```
@@
   filter(epoch == 0) %>%
-  group_by(run_type, game_type, is_new_game) %>%
+  group_by(run_type, game_type, named_game_type, is_new_game) %>%
   summarize(avg_reward = mean(reward), sd_reward=sd(reward),
@@
                       run_type == "basic"),
-             "game_type", "reward", "is_new_game",
+             "named_game_type", "reward", "is_new_game",
              optimal_baselines,
@@
                       run_type == "basic_random_holdout_longer"),
-             "game_type", "reward", "is_new_game",
+             "named_game_type", "reward", "is_new_game",
              optimal_baselines,
@@
 summary_plot(reward_d %>%
-               filter(epoch == 0),
-             "game_type", "reward", "is_new_game",
+               filter(epoch == 0,
+                      run_type %in% c("basic", "basic_random_holdout_longer")),
+             "named_game_type", "reward", "is_new_game",
              optimal_baselines,
@@
 
-#ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
+ggsave("writing/figures/basic_meta_learning.png", width=5, height=3)
 ```
@@
 ```{r}
+meta_tasks = c("toggle_losers", "toggle_suits_rule", "toggle_black_valuable")
+meta_baseline_unmapped_d = crossing(meta_task=meta_tasks,
+                                    run_type=result_subdirs,
+                                    baseline_data) %>%
+  filter(case_when(meta_task == "toggle_losers" ~ game == gsub("l_0", "l_1", policy) | game == gsub("l_1", "l_0", policy), 
+                   meta_task == "toggle_black_valuable" ~ game == gsub("bv_0", "bv_1", policy) | game == gsub("bv_1", "bv_0", policy), 
+                   meta_task == "toggle_suits_rule" ~ game == gsub("sr_0", "sr_1", policy) | game == gsub("sr_1", "sr_0", policy), 
+                   T ~ F)) %>%
+  mutate(named_run_type = name_run_type(run_type),
+         named_meta_task = name_meta_task(meta_task),
+         is_new = check_if_new_game(run_type, game) | check_if_new_game(run_type, policy),
+         is_new = factor(is_new, labels=c("Trained", "Held out"))) %>%
+  group_by(run_type, named_run_type, meta_task, named_meta_task, is_new)  %>%
+  summarize(expected_reward = mean(expected_reward))
+
+```
+
+```{r}
 meta_d = load_d(results_dir, result_subdirs, num_runs, "new_meta_true_losses")
@@
   mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
-         is_new = factor(is_new, labels=c("Trained", "Held out")))
+         is_new = factor(is_new, labels=c("Trained", "Held out")),
+         named_meta_task = name_meta_task(meta_task))
 ```
@@
 avg_meta_d = meta_d %>%
-  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
+  group_by(run_type, named_run_type, run, meta_task, named_meta_task, is_new) %>%
   summarize(avg_reward = mean(reward)) %>%
-  group_by(run_type, named_run_type, meta_task, is_new) %>%
+  group_by(run_type, named_run_type, meta_task, named_meta_task, is_new) %>%
   summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
@@
                filter(epoch == 0,
+                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                       run_type %in% c("basic", "basic_random_holdout_longer")),
-             "meta_task", "reward", "is_new") +
+             "named_meta_task", "reward", "is_new",
+             other_baseline_data = meta_baseline_unmapped_d %>%
+               filter(is_new == "Held out",
+                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
   facet_wrap(. ~ named_run_type)  +

### 2019-04-30 meta_RL_analyses.Rmd
even more aesthetics for the meta figures

@@
   guides(color=guide_legend(title=NULL)) +
-  labs(x="Game type", y="Average reward") +
+  labs(x="Meta task", y="Average reward") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
@@
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
-#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
+ggsave("writing/figures/meta_mapping.png", width=5, height=3)
 ```
@@
   mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
-         is_new = factor(is_new, labels=c("Trained", "Held out")))
+         is_new = factor(is_new, labels=c("Trained", "Held out")),
+         named_meta_task=name_meta_task(meta_task))
 ```
@@
                filter(epoch == 0,
+                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                       run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
-             "meta_task", "reward", "is_new") +
+             "named_meta_task", "reward", "is_new",
+             other_baseline_data = meta_baseline_unmapped_d %>%
+               filter(is_new == "Held out",
+                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
   facet_wrap(. ~ named_run_type)  +
   guides(color=guide_legend(title=NULL)) +
-  labs(x="Game type", y="Average reward") +
+  labs(x="Meta task", y="Average reward") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
-#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
+ggsave("writing/figures/language_meta_mapping.png", width=5, height=3)
+
 ```

### 2019-04-30 meta_RL_analyses.Rmd
Continuing figure + caption tuning

@@
 theme_set(theme_bw() + 
-            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
+            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+                  legend.margin = margin(0, 0, 0, 0), 
+                  legend.box.margin = margin(0, 0, 0, 0)))
 ```
@@
 
-ggsave("writing/figures/basic_meta_learning.png", width=5, height=3)
+ggsave("writing/figures/basic_meta_learning.png", width=4.2, height=3)
 ```
@@
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
-ggsave("writing/figures/meta_mapping.png", width=5, height=3)
+ggsave("writing/figures/meta_mapping.png", width=4.2, height=3)
 ```
@@
                       meta_task %in% c("toggle_losers", "toggle_black_valuable"),
-                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
+                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")) %>%
+               mutate(named_run_type = factor(named_run_type, labels=c("Random 50% holdout", "Targeted 10% holdout"))),
+
              "named_meta_task", "reward", "is_new",
@@
 #ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
-ggsave("writing/figures/language_meta_mapping.png", width=5, height=3)
+ggsave("writing/figures/language_meta_mapping.png", width=4.2, height=3)
 

### 2019-04-30 writing/embedded_meta_learning.tex
Continuing figure + caption tuning

@@
 \par
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.66\textwidth]{figures/basic_meta_learning.png}
+\includegraphics[width=0.5\textwidth]{figures/basic_meta_learning.png}
 \caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The dashed line indicates chance performance, while the solid lines are optimal performance.}
+The gray dashed line indicates chance performance, while the solid lines are optimal performance.
+The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen.
+The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.}
 \label{cards_basic_results}
 \end{figure}
-\newpage
 \textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
@@
 \par
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[width=0.66\textwidth]{figures/meta_mapping.png}
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/meta_mapping.png}
+\caption{From examples of mapping.}
+\label{cards_meta_map_results_examples}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/language_meta_mapping.png}
+\caption{From language input.}
+\label{cards_meta_map_results_language}
+\end{subfigure}
 \caption{The system generalizes to meta-mapping new tasks.
-The system is trained to do the three meta-mappings shown here, and is able to generalize these mappings to tasks it has not been trained on.
+The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
 For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
-When given a game it has not mapped in this way, it is able to map it to the losers variation.
-This plot shows the reward produced by taking the mapped embedding and playing the targeted game.}
+When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
+This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
+The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
+The system generally exceeds these baselines by a wide margin, although the switch-suits baseline is more difficult with the targeted holdout.
+Furthermore, the system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).}
 \label{cards_meta_map_results}
@@
 \newpage
-\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone.
+%\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone.
 The system is significantly better than chance at this task, as shown in Fig.
@@
 Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
-Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out.
+%Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out.
 This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network.
@@
 \par
-\begin{figure}[H]
-\begin{subfigure}[t]{0.5\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figures/language_basic.png}
-\caption{Average rewards}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
-\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
-\end{subfigure}
-\caption{The system generalizes to held out tasks based on language alone.
+%\begin{figure}[H]
+%\begin{subfigure}[t]{0.5\textwidth}
+%\centering
+%\includegraphics[width=\textwidth]{figures/language_basic.png}
+%\caption{Average rewards}
+%\end{subfigure}%
+%\begin{subfigure}[t]{0.5\textwidth}
+%\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
+%\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
+%\end{subfigure}
+%\caption{The system generalizes to held out tasks based on language alone.
 However, it is substantially less good at this task than generalizing to a held-out task based on examples.
 Furthermore, it shows more run-to-run variability and within-run variability.}
-\label{cards_language_basic_results}
-\end{figure}
-\newpage
-\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples.
+%\label{cards_language_basic_results}
+%\end{figure}
+%\newpage
+%\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples.
 Note that this is in some ways an easier task than the basic language-mapping task.
 \par
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
-\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
-\label{cards_language_meta_results}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
+%\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
+%\label{cards_language_meta_results}
+%\end{figure}
 
@@
 
+\newpage
+\appendix
+
+\section{Detailed methods}
+\subsection{Datasets}
+\subsubsection{Polynomials}
+
+\subsubsection{Card games}
+
 \end{document}

### 2019-04-30 writing/embedded_meta_learning.tex
Reorganizing games

@@
 \subsection{A stochastic learning setting: simple card games}
-Our next case study was in the setting of simple card games, played with two suits, and 4 values per suit.
-In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands).
-The agent is dealt a hand, and then has to choose to bet 0, 1, or 2.
-If it wins, it is rewarded the value of the bet, if it loses, it receives the negative of the value.
-This doesn't require long term planning, but does incorporate the stochastic feedback aspect of reinforcement learning.
-We considered a variety of games:
-\begin{itemize}
-\item \textbf{High card:} Highest card wins.
-\item \textbf{Pairs and high:} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
-\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
-\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
-\item \textbf{Sum under:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
-\end{itemize}
-These games are simplified analogs of various card games, including poker and blackjack. We also considered three binary options that could be altered to produce variants of these games:
-\begin{itemize}
-\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
-\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
-\item \textbf{Switch suit:} Switches which of the suits is more valuable.
-\end{itemize}
-Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. \par
+Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet.
+There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
+If it wins, it is rewarded the value of the bet, if it loses, it loses that value (i.e.
+receives a negative reward).
+This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
+We considered five games that are simplified analogs of various real card games, including poker and blackjack (see Appendix \ref{meth_data_cards} for details of the games).
+We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable.
+These are challenging manipulations, for instance trying to lose requires completely inverting the learned $Q$-function for the task.
+\par
 In order to switch the system to an RL meta learning system, we made a very simple change.
@@
 In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
-It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 tasks leads to good generalization.
-Furthermore, starting from this ``guess'' at the correct strategy, the system can rapidly learn to achieve optimal performance ($< 20$ epochs, figure TODO).
+It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
 \par
@@
 \subsubsection{Card games}
+\label{meth_data_cards}
+Our card games were played with two suits, and 4 values per suit.
+In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands).
+The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available).
+We considered a variety of games which depend on different features of the hand:
+\begin{itemize}
+\item \textbf{High card:} Highest card wins.
+\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
+\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
+\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
+\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
+\end{itemize}
+We also considered three binary options that could be altered to produce variants of these games:
+\begin{itemize}
+\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
+\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
+\item \textbf{Switch suit:} Switches which of the suits is more valuable.
+\end{itemize}
+Any combination of these options can be applied to any of the 5 games, yielding 40 possible games.
+The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose, so we have omitted it from our analyses.\par
 

### 2019-05-01 meta_RL_analyses.Rmd
TSNE!

@@
 
-summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2") {
+summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2", continuous_x=F) {
 
@@
                  position=position_nudge(x=-0.5)) 
+  }
+
+  if (continuous_x) {
+    p = p + 
+      geom_line(stat="summary", fun.y=mean, size=2) 
   }
@@
 ggsave("writing/figures/basic_meta_learning.png", width=4.2, height=3)
+```
+
+```{r}
+summary_plot(reward_d %>%
+               filter(run_type %in% c("basic", "basic_random_holdout_longer", "meta_batch_128", "language_simplified_random_holdout")),
+             "epoch", "reward", "is_new_game",
+             continuous_x=T) +
+  facet_wrap(. ~ named_run_type) +
+  geom_smooth(method="lm")
+
+#ggsave("writing/figures/basic_meta_learning_integrating_over_time.png", width=4.2, height=3)
 ```
@@
 # embeddings
+```{r}
+library(tsne)
+```
 
 ```{r}
-for (result_subdir in result_subdirs) {
-  for (emb_type in c("guess", "final")) {
+#for (result_subdir in result_subdirs) {
+#  for (emb_type in c("guess", "final")) {
+for (result_subdir in c("basic")) {
+  for (emb_type in c("final")) {
     emb_d = data.frame()
@@
 
+    set.seed(0) # reproducible tsne
     pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
@@
     pc_d$task = row.names(pc_d)
-    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
+    pc_d = pc_d %>% 
+      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type))
+    ggplot(pc_d, aes(x=PC1, y=PC2, shape=named_game_type, color=losers, size=black_valuable)) +
       geom_point() +
-      geom_text(aes(label=task)) +
-      guides(color=F)
+      scale_color_brewer(palette="Dark2") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(size=guide_legend(title="Switch suits"),
+             shape=guide_legend(title="Game"),
+             color=guide_legend(title="Losers"))
     ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)
 
-    pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
+    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")) %>% as.matrix() %>% t(),
+                         perplexity=5,
+                         initial_dims=10))
+    ts$task = pc_d$task
+    ts = ts %>% 
+      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type))
+    ggplot(ts, aes(x=X1, y=X2, shape=named_game_type, color=losers, size=black_valuable)) +
+      geom_point() + 
+      scale_color_brewer(palette="Dark2") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(size=guide_legend(title="Switch suits"),
+             shape=guide_legend(title="Game"),
+             color=guide_legend(title="Losers"))
+    ggsave(sprintf("plots/%s_tsne_basic_%s.png", result_subdir, emb_type), width=7, height=7)
+
+    set.seed(0) # reproducible tsne
+    pcs = prcomp(emb_d %>% select(-dimension, -run, -contains("suits_rule")), center=T, scale=T)
     pc_d = data.frame(pcs$rotation)
@@
     ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)
+
+    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -contains("suits_rule")) %>% as.matrix() %>% t(),
+                         perplexity=5,
+                         initial_dims=10))
+    ts$task = row.names(pc_d)
+    ts = ts %>%
+      mutate(is_meta = grepl("is_|toggle_", task),
+             meta_type = ifelse(is_meta, str_extract(task, "toggle|is"), NA),
+             game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type),
+             type_var = ifelse(is_meta, task, "basic"),
+             type_var = factor(type_var,
+                               levels=c('basic', 'is_high_card', 'is_straight_flush', 'is_match', 'is_pairs_and_high', 'is_sum_under', 'is_suits_rule', 'is_losers', 'is_black_valuable', 'toggle_suits_rule', 'toggle_losers', 'toggle_black_valuable'),
+                               labels=c('Basic', 'is_high_card', 'is_poker', 'is_match', 'is_pairs', 'is_blackjack', 'is_suits_rule', 'is_losers', 'is_switched_suits', 'toggle_suits_rule', 'toggle_losers', 'toggle_switch_suits'))
+             )
+    ggplot(ts, aes(x=X1, y=X2, color=type_var, alpha=is_meta)) +
+      geom_point() +
+      geom_text(data=ts %>% filter(is_meta),
+                aes(label=type_var),
+                position=position_nudge(y=40, x=-100),
+                size=4) +
+      scale_alpha_manual(values=c(0.33, 1)) + 
+      scale_color_brewer(palette="Set3") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(alpha=F,
+             color=guide_legend(title="Task"))
+    ggsave(sprintf("plots/%s_tsne_full_%s.png", result_subdir, emb_type), width=7, height=6)
   }

### 2019-05-01 writing/embedded_meta_learning.tex
TSNE + poly datasets to appendix + tweaks

@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
+\usepackage[pdfborder={0 0 0}]{hyperref}       % hyperlinks
 \usepackage{url}            % simple URL typesetting
@@
 %% TODO: appendix
-We randomly sampled the train and test polynomials as follows:
-\begin{enumerate}
-\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
-\item Sample the subset of $k$ variables that are relevant uniformly at random.
-\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random intercept drawn from $\mathcal{N}(0, 2.5)$.
-\end{enumerate}
-The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial.
-The datasets were resampled every 50 epochs of training.
-\par
 
@@
 \subsection{Datasets}
-\subsubsection{Polynomials}
+\subsubsection{Polynomials} \label{meth_data_poly}
+We randomly sampled the train and test polynomials as follows:
+\begin{enumerate}
+\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
+\item Sample the subset of $k$ variables that are relevant from all the variables.
+\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
+\end{enumerate}
+The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial.
+The datasets were resampled every 50 epochs of training.
+\par
 
@@
 
+\section{Card game $t$-SNE} \label{app_cards_tsne}
+We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
+In fig.
+\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
+The embeddings show systematic grouping by game attributes.
+In fig.
+\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
+\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/basic_tsne_basic_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
+(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
+\label{fig_cards_tsne_basic}
+\end{figure}%
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
+\label{fig_cards_tsne_full}
+\end{figure}
+
 \end{document}

### 2019-05-02 writing/embedded_meta_learning.tex
Continual learning, tweaks

@@
 This output would be generated as follows:
-$$\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)$$
+\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
 where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-$$f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
-\right\}\right)\right)$$
+\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
+\right\}\right)\right)\]
 This system can be trained end-to-end if labels are provided for a second set of inputs.
@@
 We define our total loss computed on some dataset $D_2$ as:
-$$\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
+\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
 More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and an embedded dataset $D_Z$ of (embedding, target embedding) pairs $\{(z_{in,0}, z_{out,0})\}$.
 Then we can generate an output $\hat{z}_{out} \in Z$ as:
-$$\hat{z}_{out} = f_{D_Z}(z_{in}) \qquad \text{where } f_{D_Z} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left(D_Z\right)\right)$$
+\[\hat{z}_{out} = f_{D_Z}(z_{in}) \qquad \text{where } f_{D_Z} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left(D_Z\right)\right)\]
 This output can then be appropriately dispatched depending on the task at hand.
@@
 
-\subsubsection{Results}
-
 \subsection{Continual learning}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
+\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
+Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.}
+\label{poly_continual_results}
+\end{figure}
 Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step.
@@
 That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
-In this section, we demonstrate the effectiveness of this solution by training on new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-We show that this yields very good results if the model has been pre-trained on a sufficient distribution of tasks.
+To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
+We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
+The results are shown in fig.
+\ref{poly_continual_results}.
+The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding.
+Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
 \par
-%% TODO: Baselines and the fact that something interesting is being learned
-
-\subsubsection{Results}
 
@@
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
-(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as still a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
-That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure of the game.
+(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
+That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.
 \par
@@
 \par
-
-\newpage
-\subsubsection{Results}
 \textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig.
@@
 It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-\par
+Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.\par
 \begin{figure}
@@
 \end{figure}
-\newpage
 %\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone.
@@
 %\end{figure}
+\section{Related work}
+
+Our work builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- as well as work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}.
+
+Other authors have proposed using a hyper network to guess parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
+
+In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
+They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters.
+Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model, and also allows for remapping of behavior by meta-tasks.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{figures/basic_tsne_basic_final.png}
+\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
 \caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
@@
 
+\section{Supplemental figures}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.66\textwidth]{figures/continual/continual_learning_direct_comparison.png}
+\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
+Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding.
+Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
+\label{supp_poly_continual_results}
+\end{figure}
+
 \end{document}

### 2019-05-02 writing/embedded_meta_learning.tex
Working on background

@@
 \section{Related work}
-
-Our work builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- as well as work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}.
-
-Other authors have proposed using a hyper network to guess parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
-
+Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018} and continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
+There has also been interesting recent work on hybrid approaches, such as meta-learning in an online setting \citep{Finn2019}.
+Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than gradient descent \citep[e.g.][]{Wang2016a, Duan2016}.
+\par
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications of it, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
+This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}.
+It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
+\par
+There has also been some interest in task (or function) embeddings.
 In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
-They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters.
-Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model, and also allows for remapping of behavior by meta-tasks.
+They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
+Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
+Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
+\par
 

### 2019-05-03 writing/embedded_meta_learning.tex
Very preliminary poly section

@@
 \begin{enumerate}
-\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$
+\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
 \item A meta-learning system which:
@@
 \par
-
 \begin{figure}
@@
 \section{Experiments}
-
 %\subsection{Boolean functions}
@@
 \subsection{Learning multivariate polynomials}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/poly/basic_results.png}
+\caption{Basic meta-learning successfully generalizes to held out tasks. The solid line indicates optimal performance.}
+\label{poly_basic_results}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/poly/meta_results.png}
+\caption{The system generalizes to meta-mapping new tasks. The solid line indicates optimal performance.} 
+\label{poly_meta_map_results}
+\end{figure}
 As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e.
@@
 \par
-%% TODO: appendix
+
+\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig. \ref{poly_basic_results}. \par
+
+\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
+\ref{poly_meta_map_results}.
+\par
 
@@
 \par
-In order to switch the system to an RL meta learning system, we made a very simple change.
+In order to switch the system, we made a very simple change.
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
@@
 \section{Related work}
-Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018} and continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
+Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018} and continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
 There has also been interesting recent work on hybrid approaches, such as meta-learning in an online setting \citep{Finn2019}.
@@
 Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications of it, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}.
+This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}.
 It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
 \par
-There has also been some interest in task (or function) embeddings.
+There has also been some recent interest in task (or function) embeddings.
 In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
@@
 \par
+\section{Discussion}
 
-\section{Discussion}
+We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
+This naturally suggests the idea of manipulating task representations just like we manipulate data.
 

### 2019-05-03 writing/embedded_meta_learning.tex
More on meta-mapping, and rough-sketch of discussion

@@
 
+\setcitestyle{square}
+
 \begin{document}
@@
 In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep{?????}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}.
 However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/poly/meta_results.png}
-\caption{The system generalizes to meta-mapping new tasks. The solid line indicates optimal performance.} 
+\includegraphics[width=0.75\textwidth]{figures/poly/meta_results.png}
+\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples. The solid line indicates optimal performance.} 
 \label{poly_meta_map_results}
@@
 \ref{poly_meta_map_results}.
+We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
+We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
+The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application.
 \par
@@
 \section{Related work}
-Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018} and continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
-There has also been interesting recent work on hybrid approaches, such as meta-learning in an online setting \citep{Finn2019}.
+Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
+It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
+Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
 Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than gradient descent \citep[e.g.][]{Wang2016a, Duan2016}.
 \par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications of it, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
 This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}.
@@
 There has also been some recent interest in task (or function) embeddings.
-In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
+In simultaneous work Achille et al.
+\citep{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
 They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
@@
 
-We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
+* We've suggested that the separation of computations from knowledge of what is being computed in neural networks is limiting.
+
+* We've suggested that the solution to this problem is the explicit representation of task alongside the computation.
+
+* We've proposed a new type of generalization challenge?
+
+* We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
 This naturally suggests the idea of manipulating task representations just like we manipulate data.
+
+* We've proposed an architecture which represents data and tasks within the same latent space, and have demonstrated its flexibility.
+
+* We've also shown that our approach provides a useful perspective on continual learning.
+
+* We hope that these results will lead to the development of more powerful and flexible deep-learning models.
 

### 2019-05-03 meta_RL_analyses.Rmd
Integration time

--- 2019-04-30 meta_RL_analyses.Rmd
@@
 result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
-                   "basic", #"basic_su_heldout", 
-                   "basic_random_holdout_longer") # "basic_only_one", "basic_only_one_ho")
+                   "basic", "basic_slower_integration", #"basic_su_heldout", 
+                   "basic_random_holdout_longer", "basic_random_holdout_longer_slower_integration") # "basic_only_one", "basic_only_one_ho")
 
@@
             run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
+            run_type == "basic_slower_integration" ~ "Targeted 10% holdout",
+            run_type == "basic_random_holdout_longer_slower_integration" ~ "Random 50% holdout",
             run_type == "language_noncompositional_old" ~ "Old language (targeted 10%)",
@@
                  position=position_nudge(x=-0.5)) 
+  }
+
+  if (continuous_x) {
+    p = p + 
+      geom_line(stat="summary", fun.y=mean, size=1.5) 
   }
@@
 ggsave("writing/figures/basic_meta_learning.png", width=4.2, height=3)
+```
+
+```{r}
+summary_plot(reward_d %>%
+               filter(run_type %in% c("basic_slower_integration", "basic_random_holdout_longer_slower_integration"),
+                      epoch <= 200),
+             "epoch", "reward", "is_new_game",
+             continuous_x=T) +
+  facet_wrap(. ~ named_run_type) +
+  geom_hline(yintercept=mean(optimal_baselines$expected_reward),
+             alpha=0.5) +
+  labs(x = "Epoch after introducing new tasks") +
+  theme(plot.margin=margin(b=1, units="cm"))
+
+ggsave("writing/figures/basic_meta_learning_integrating_over_time.png", width=4.2, height=3)
 ```
@@
 
+    set.seed(0) # reproducible tsne even if result_subdirs change
     pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
+    pc_d = data.frame(pcs$rotation)
+    pc_d$task = row.names(pc_d)
+    pc_d = pc_d %>% 
+      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type))
+    ggplot(pc_d, aes(x=PC1, y=PC2, shape=named_game_type, color=losers, size=black_valuable)) +
+      geom_point() +
+      scale_color_brewer(palette="Dark2") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(size=guide_legend(title="Switch suits"),
+             shape=guide_legend(title="Game"),
+             color=guide_legend(title="Losers"))
+    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)
+
+    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")) %>% as.matrix() %>% t(),
+                         perplexity=5,
+                         initial_dims=10))
+    ts$task = pc_d$task
+    ts = ts %>% 
+      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type))
+    ggplot(ts, aes(x=X1, y=X2, shape=named_game_type, color=losers, size=black_valuable)) +
+      geom_point() + 
+      scale_color_brewer(palette="Dark2") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(size=guide_legend(title="Switch suits"),
+             shape=guide_legend(title="Game"),
+             color=guide_legend(title="Losers"))
+    ggsave(sprintf("plots/%s_tsne_basic_%s.png", result_subdir, emb_type), width=6, height=4.5)
+
+    pcs = prcomp(emb_d %>% select(-dimension, -run, -contains("suits_rule")), center=T, scale=T)
     pc_d = data.frame(pcs$rotation)
@@
       guides(color=F)
-    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)
+    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=8, height=6)
 
-    pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
-    pc_d = data.frame(pcs$rotation)
-    pc_d$task = row.names(pc_d)
-    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
+    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -contains("suits_rule")) %>% as.matrix() %>% t(),
+                         perplexity=4,
+                         initial_dims=10))
+    ts$task = row.names(pc_d)
+    ts = ts %>%
+      mutate(is_meta = grepl("is_|toggle_", task),
+             meta_type = ifelse(is_meta, str_extract(task, "toggle|is"), NA),
+             game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
+             losers = grepl("l_1", task),
+             black_valuable = grepl("bv_1", task),
+             suits_rule = grepl("sr_1", task),
+             named_game_type = name_game_type(game_type),
+             type_var = ifelse(is_meta, task, "basic"),
+             type_var = factor(type_var,
+                               levels=c('basic', 'is_high_card', 'is_straight_flush', 'is_match', 'is_pairs_and_high', 'is_sum_under', 'is_suits_rule', 'is_losers', 'is_black_valuable', 'toggle_suits_rule', 'toggle_losers', 'toggle_black_valuable'),
+                               labels=c('Basic', 'is_high_card', 'is_poker', 'is_match', 'is_pairs', 'is_blackjack', 'is_suits_rule', 'is_losers', 'is_switched_suits', 'toggle_suits_rule', 'toggle_losers', 'toggle_switch_suits'))
+             )
+    ggplot(ts, aes(x=X1, y=X2, color=type_var, alpha=is_meta)) +
       geom_point() +
-      geom_text(aes(label=task)) +
-      guides(color=F)
-    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)
+      geom_text(data=ts %>% filter(is_meta),
+                aes(label=type_var),
+                position=position_nudge(y=40, x=-100),
+                size=4) +
+      scale_alpha_manual(values=c(0.33, 1)) + 
+      scale_color_brewer(palette="Set3") + 
+      labs(x="Dimension 1", y="Dimension 2") +
+      guides(alpha=F,
+             color=guide_legend(title="Task"))
+    ggsave(sprintf("plots/%s_tsne_full_%s.png", result_subdir, emb_type), width=6, height=4)
     }

### 2019-05-03 writing/embedded_meta_learning.tex
Integration time
Abstract + intro tweaks

@@
 
+\begin{abstract}
+How can deep learning systems flexibly reuse their knowledge?
+We suggest that the key is representing the task being performed along with the computations used to perform it.
+Specifically, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors.
+We draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space.
+We demonstrate the flexibility of these architectures by showing that they can exhibit zero-shot remapping of behavior on new tasks.
+\end{abstract}
+
 \section{Introduction}
@@
 One fundamental reason for this is that humans are aware of what we are trying to compute and why.
-By contrasts, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
+By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
 That is, neural networks knowledge about what is being computed is only implicitly accessible to those computations.
 \par
-There are a number of advantages to representing knowledge about data and tasks.
+There are a number of advantages to representing knowledge about data and tasks together.
 In particular, it can grant the ability to rapidly adapt behavior to a new task.
@@
 \par
-In this paper, we propose a new class of architectures which essentially take a functional perspective on meta-learning and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}.
-By treating tasks and data as functions, we can conceptually think of both data \emph{and} learned behaviors as transformable.
-This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands.
+In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e.
+mappings between tasks.
+For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play with an alteration in the reward function.
+The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess'').
+These mappings essentially provide a new opportunity for zero-shot transfer from one task to another -- that is, the system must transform its behavior to adapt to a new task without ever having seen training data from that task.
+This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
+\par
+To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}.
+By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
+By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as the same types of functional mappings.
+This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands.
 We suggest that this ability will be key to building more intelligent and flexible deep learning systems.
 \par
-In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space.
-We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits such as a useful framework for continual learning.
+In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute meta-mappings over this space.
+We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits, such as a useful framework for continual learning.
 \par
-\section{Method}
-\subsection{Architecture}
-The essential idea of the architecture is that we separate the system into two parts: 
+\section{Embedded Meta-Learning (EML) architecture}
+We propose a new class of Embedded Meta-Learning (EML) architectures which essentially separate the system into two parts: 
 \begin{enumerate}
@@
 The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data.
-In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior).
+In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples).
 This is a step closer to the flexible reasoning humans display.
@@
 It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.\par
+Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
+Finally, the system can integrate new tasks quite rapidly (fig.
+\ref{cards_basic_integration_results}).\par
 \begin{figure}
 \centering
-\includegraphics[width=0.5\textwidth]{figures/basic_meta_learning.png}
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
 \caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
@@
 \label{cards_basic_results}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
+\caption{The system can rapidly adapt to new tasks.}
+\label{cards_basic_integration_results}
+\end{subfigure}
 \end{figure}

### 2019-05-03 writing/embedded_meta_learning.tex
Tweaks and future directions

@@
 Without training on these mappings, of course, the system will not be able to execute them well.
-However, ideally if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution.
+However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below.
 For instances that fall outside its data distribution or for optimal performance it may require some retraining.
@@
 
-\node [conc] at (-6, -4) (perc) {\textbf{Basic Input}};
-\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-6, 4) (act) {\textbf{Basic Output}};
+\node [conc] at (-6, -4) (perc) {\textbf{Input}};
+%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
+\node [conc] at (-6, 4) (act) {\textbf{Output}};
 \node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
-\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
+%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
 \node [block, text width=2.2cm] at (-3.5, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
@@
 \path [line] (perc.north) to (IE.south);
-\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
+%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
 \path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
-\path [line] (LE.east) to (rep.west);
+%%\path [line] (LE.east) to (rep.west);
 \path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
@@
 \caption{Schematic of our general architecure.
-Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$.} \label{architecture_fig}
+Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$.
+Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
+both language and vision.} \label{architecture_fig}
 \end{figure}
@@
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and an embedded dataset $D_Z$ of (embedding, target embedding) pairs $\{(z_{in,0}, z_{out,0})\}$.
+More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$.
 Then we can generate an output $\hat{z}_{out} \in Z$ as:
-\[\hat{z}_{out} = f_{D_Z}(z_{in}) \qquad \text{where } f_{D_Z} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left(D_Z\right)\right)\]
+\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
 This output can then be appropriately dispatched depending on the task at hand.
@@
 Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language.
-The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified system.
+The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.
 
-\section{Experiments}
 %\subsection{Boolean functions}
@@
 %
-\subsection{Learning multivariate polynomials}
+\section{Learning multivariate polynomials (very in progress)}
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{figures/poly/basic_results.png}
-\caption{Basic meta-learning successfully generalizes to held out tasks. The solid line indicates optimal performance.}
+\caption{The system solves the meta-learning problem and successfully generalizes to held out tasks.
+The solid line indicates optimal performance.
+Error-bars throughout are bootstrap 95\%-confidence intervals.}
 \label{poly_basic_results}
@@
 
-\subsection{A stochastic learning setting: simple card games}
+\section{A stochastic learning setting: simple card games}
 Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet.
@@
 \includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{The system can rapidly adapt to new tasks.}
+\caption{The system can rapidly adapt to new tasks. (This figure shows training all parameters while replaying old tasks, unlike the continual learning strategy above.)}
 \label{cards_basic_integration_results}
@@
 It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
+In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
 \par
@@
 Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
+To the best of our knowledge none of the prior work has explored meta-mapping.
 \par
-\section{Discussion}
-
+\section{Future directions}
+We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
+We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here.
+For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017}.
+Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.
+\par
+We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems, although it has a number of desirable characteristics.
+However, because of the way the architecture is factorized, it is relatively easy to change any aspect of it without altering the others.
+In particular, although we only considered task networks $f$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
+Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
+\par
+\section{Conclusions}
 * We've suggested that the separation of computations from knowledge of what is being computed in neural networks is limiting.

### 2019-05-04 writing/embedded_meta_learning.tex
Conclusions, schematic fixes, tweaks

@@
 How can deep learning systems flexibly reuse their knowledge?
-We suggest that the key is representing the task being performed along with the computations used to perform it.
-Specifically, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors.
-We draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space.
-We demonstrate the flexibility of these architectures by showing that they can exhibit zero-shot remapping of behavior on new tasks.
+Toward this goal, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors.
+We suggest that the key to achieving this flexibility is representing the task being performed along with the computations used to perform it.
+We therfore draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space.
+We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
+that they can exhibit zero-shot remapping of behavior on new tasks.
 \end{abstract}
@@
 mappings between tasks.
-For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play with an alteration in the reward function.
+For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play without using a certain action.
 The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess'').
-These mappings essentially provide a new opportunity for zero-shot transfer from one task to another -- that is, the system must transform its behavior to adapt to a new task without ever having seen training data from that task.
+These mappings provide a new type of zero-shot transfer from one task to another -- the system must transform its behavior to adapt to a new task without ever having seen training data from that task.
 This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
@@
 By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as the same types of functional mappings.
+By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as mappings in function space.
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands.
@@
 \section{Embedded Meta-Learning (EML) architecture}
-We propose a new class of Embedded Meta-Learning (EML) architectures which essentially separate the system into two parts: 
+We propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
 \begin{enumerate}
@@
 However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below.
-For instances that fall outside its data distribution or for optimal performance it may require some retraining.
+For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
 This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow.
@@
 \centering
-\begin{tikzpicture}[auto]
-
+\begin{tikzpicture}[auto, scale=0.9]
 \node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
@@
 
-\node [conc] at (-6, -4) (perc) {\textbf{Input}};
+\node [conc] at (-7, -4) (perc) {\textbf{Input}};
 %%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-6, 4) (act) {\textbf{Output}};
-\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
+\node [conc] at (-7, 4) (act) {\textbf{Output}};
+\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
 %%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-3.5, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
+\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
 \node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target Encoder}};
@@
 (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
-\par
 We can then interpret most machine learning tasks as a mapping of functions to functions.
@@
 \right\}\right)\right)\]
-This system can be trained end-to-end if labels are provided for a second set of inputs.
+This system can be trained end-to-end if labels are provided for the second set of inputs.
 In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
@@
 \end{figure}
-As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e.
-the task was to learn functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$).
+As a proof of concept, we first evaluated the system on the simple task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
+the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$).
 This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables).
@@
 Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows the potential to optimize these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task.
+This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task.
 That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
@@
 \ref{poly_continual_results}.
-The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding.
+The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp.
+fig.
+\ref{supp_poly_continual_results} for a more direct comparison).
 Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
@@
 \includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{Basic meta-learning successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.}
+\caption{Generalization to held-out tasks.}
 \label{cards_basic_results}
@@
 \includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{The system can rapidly adapt to new tasks. (This figure shows training all parameters while replaying old tasks, unlike the continual learning strategy above.)}
+\caption{Rapid integration once held-out tasks are introduced.}
 \label{cards_basic_integration_results}
 \end{subfigure}
+\caption{Basic meta learning in the cards domain.
+(a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
+The gray dashed line indicates chance performance, while the solid lines are optimal performance.
+The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen.
+The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.
+(b) The system can rapidly adapt to new tasks.
+(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.)}
 \end{figure}
@@
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
-Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than gradient descent \citep[e.g.][]{Wang2016a, Duan2016}.
+Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates \citep[e.g.][]{Wang2016a, Duan2016}.
 \par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}.
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep{Brock2018a}.
+This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}.
 It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
@@
 Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
-To the best of our knowledge none of the prior work has explored meta-mapping.
+To the best of our knowledge none of the prior work has explored meta-mappings.
 \par
@@
 \section{Conclusions}
-* We've suggested that the separation of computations from knowledge of what is being computed in neural networks is limiting.
-
-* We've suggested that the solution to this problem is the explicit representation of task alongside the computation.
-
-* We've proposed a new type of generalization challenge?
-
-* We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
+In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
+We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
+We've proposed that representing the task explicitly as the computation provides a solution to this problem.
+To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.
+We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
 This naturally suggests the idea of manipulating task representations just like we manipulate data.
-
-* We've proposed an architecture which represents data and tasks within the same latent space, and have demonstrated its flexibility.
-
-* We've also shown that our approach provides a useful perspective on continual learning.
-
-* We hope that these results will lead to the development of more powerful and flexible deep-learning models.
+We've shown that this approach yields considerable flexibility, most importantly the ability to adapt zero-shot to a new task from examples of task transformations.
+We've also shown that our approach provides a useful perspective on continual learning.
+We hope that these results will lead to the development of more powerful and flexible deep-learning models.
+\par
+%\subsubsection*{Acknowledgements}
+%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
 
@@
 Any combination of these options can be applied to any of the 5 games, yielding 40 possible games.
-The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose, so we have omitted it from our analyses.\par
+The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
 

### 2019-05-08 writing/embedded_meta_learning.tex
Starting section on meta-mappings

@@
 \par
+
+\section{Meta-mappings}
+We propose the challenge of meta-mappings, that is, mappings over tasks.
+These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
+While the first two categories have been considered in prior work, the latter is more novel.
+\par
+We argue that these meta-mappings are a useful way to think about the flexibility that humans have.
+For example, suppose an agent knows how to navigate from the airport to downtown.
+It should be able to adapt to changes of the environment such as street closures.
+This can be viewed as a change in the task being performed, from navigating through one map to navigating through another.
+Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color.
+These again can be seen as two related tasks.
+We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to use.
+While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.
+In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task.
+\par
+
 \section{Embedded Meta-Learning (EML) architecture}

### 2019-05-08 writing/embedded_meta_learning.tex
Stealing an example from tenenbaum

@@
 This can be viewed as a change in the task being performed, from navigating through one map to navigating through another.
-Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color.
-These again can be seen as two related tasks.
-We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to use.
+Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color, or a system that learns to play go should be able to adapt to a different board size.
+These again can be seen as pairs of related tasks.
+We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.

### 2019-05-09 writing/embedded_meta_learning.tex
Going even more over length

@@
 \par
-We argue that these meta-mappings are a useful way to think about the flexibility that humans have.
-For example, suppose an agent knows how to navigate from the airport to downtown.
+We argue that these meta-mappings are a useful way to think about the flexibility that humans possess.
+For example, a system that learns to play go should be able to adapt to a different board size.
+These tasks clearly share a great deal of structure, and a human can easily transfer much of their knowledge from one board size to another without retraining, but deep learning models generally have no way of achieving this.
+Similarly, suppose an agent knows how to navigate from the airport to downtown.
 It should be able to adapt to changes of the environment such as street closures.
-This can be viewed as a change in the task being performed, from navigating through one map to navigating through another.
-Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color, or a system that learns to play go should be able to adapt to a different board size.
-These again can be seen as pairs of related tasks.
 We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
@@
 \par
+We are inspired by these observations to propose the challenge of meta-mappings -- mappings of tasks to tasks.
+These mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
+Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
+\par
 
 \section{Embedded Meta-Learning (EML) architecture}
-We propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
+To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
 \begin{enumerate}
@@
 Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
-It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}.
+It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019} or external memory \citep[e.g.][]{Sprechmann2018}.
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
-Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates \citep[e.g.][]{Wang2016a, Duan2016}.
+Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or by conditioning on a task input \citep[e.g.][]{Borsa2019}.
 \par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep{Brock2018a}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017}.
-It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.]{Brock2018a, Zhang2019}.
+This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
+It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
 In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
@@
 Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
+Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
 Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
@@
 This naturally suggests the idea of manipulating task representations just like we manipulate data.
-We've shown that this approach yields considerable flexibility, most importantly the ability to adapt zero-shot to a new task from examples of task transformations.
+We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task from examples of task transformations.
 We've also shown that our approach provides a useful perspective on continual learning.

### 2019-05-09 writing/embedded_meta_learning.tex
Typing this hyperparameter table sucked

@@
 
+\subsection{Model}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|ccc|}
+\hline 
+& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\
+\hline
+$Z$-dimension & 512 & 512 & 512 \\
+$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
+$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
+$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
+$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
+$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
+$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
+$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
+$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
+$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
+$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
+Nonlinearities & \multicolumn{3}{c|}{Leaky ReLU, no non-linearity at final layer of $T$, $M$, $f$.} \\
+\hline
+Optimizer & Adam & RMSProp & RMSProp \\
+Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\
+Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\
+L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\
+L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\
+L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\
+L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\
+L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\
+Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\
+Num. training epochs & 4000 & 3000 & 40000 \\
+\hline
+Num. base tasks (eval) & 60 & 100 & 36 or 20 \\
+Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\
+Num. meta classifications & 6 & - & 8  \\
+Num. meta mappings & 20 & - & 3  \\
+Num. new base tasks & 40 & 30 & 4 or 20 \\ 
+Num. new meta mappings & 16 & - & 0  \\
+Num. new meta classifications &  \multicolumn{3}{c|}{0} \\
+Base dataset size & \multicolumn{3}{c|}{1024} \\
+Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\
+$\mathcal{M}$ batch size & 50 & 128 & 768 \\
+\hline
+\end{tabular}
+\caption{Detailed hyperparameter specification for different experiments.
+A ``-'' indicates a parameter that does not apply to that experiment.
+Where only one value is given, it applied to all the experiments discussed.
+Hyperparameters were generally found by a heuristic search.
+(Some of these parameters take the values they do for fairly arbitrary reasons, e.g.
+the continual learning experiments were run before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.)} \label{supp_hyperparameter_table}
+\end{table}
+
+As a reminder: the shared representational space is denoted by $Z$.
+Input encoder: $\mathcal{I}: \text{input} \rightarrow Z$.
+Output decoder $\mathcal{O}: Z \rightarrow \text{output}$.
+Target encoder $\mathcal{T}: \text{targets} \rightarrow Z$.
+Meta-network $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- takes a set of (input embedding, target embedding) pairs and produces a function embedding.
+Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters.
+Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.
+\par
+
 \section{Card game $t$-SNE} \label{app_cards_tsne}

### 2019-05-09 writing/embedded_meta_learning.tex
Repo links

--- 2019-05-09 writing/embedded_meta_learning.tex
@@
 
+\subsection{Model \& training}
+See table \ref{supp_hyperparameter_table} for detailed architectural description and hyperparameters for each experiment.
+Hyperparameters were generally found by a heuristic search, where mostly only the optimizer, learning rate annealing schedule, and number of training epochs were varied, not the architectural parameters.
+Some of the parameters take the values they do for fairly arbitrary reasons, e.g.
+the continual learning experiments were run with the current polynomial hyperparameters before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.
+\par
+Each epoch consisted of a separate learning step on each task (both base and meta), in a random order.
+The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, the
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|ccc|}
+\hline 
+& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\
+\hline
+$Z$-dimension & 512 & 512 & 512 \\
+$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
+$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
+$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
+$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
+$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
+$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
+$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
+$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
+$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
+$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
+Nonlinearities & \multicolumn{3}{c|}{Leaky ReLU, no non-linearity at final layer of $T$, $M$, $f$.} \\
+\hline
+Optimizer & Adam & RMSProp & RMSProp \\
+Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\
+Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\
+L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\
+L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\
+L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\
+L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\
+L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\
+Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\
+Num. training epochs & 4000 & 3000 & 40000 \\
+\hline
+Num. base tasks (eval) & 60 & 100 & 36 or 20 \\
+Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\
+Num. meta classifications & 6 & - & 8  \\
+Num. meta mappings & 20 & - & 3  \\
+Num. new base tasks & 40 & 30 & 4 or 20 \\ 
+Num. new meta mappings & 16 & - & 0  \\
+Num. new meta classifications &  \multicolumn{3}{c|}{0} \\
+Base dataset size & \multicolumn{3}{c|}{1024} \\
+Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\
+$\mathcal{M}$ batch size & 50 & 128 & 768 \\
+\hline
+\end{tabular}
+\caption{Detailed hyperparameter specification for different experiments.
+A ``-'' indicates a parameter that does not apply to that experiment.
+Where only one value is given, it applied to all the experiments discussed.
+As a reminder: the shared representational space is denoted by $Z$.
+Input encoder: $\mathcal{I}: \text{input} \rightarrow Z$.
+Output decoder $\mathcal{O}: Z \rightarrow \text{output}$.
+Target encoder $\mathcal{T}: \text{targets} \rightarrow Z$.
+Meta-network $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- takes a set of (input embedding, target embedding) pairs and produces a function embedding.
+Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters.
+Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.} \label{supp_hyperparameter_table}
+\end{table}
+\subsection{Source repositories}
+The full code can be found on github:
+\begin{itemize}
+\item \url{https://github.com/lampinen/polynomials}
+    \begin{itemize}
+        \item See the continual\_learning branch for those results. 
+    \end{itemize}
+\item \url{https://github.com/lampinen/meta_cards} 
+\end{itemize}
+%%(will be made available in the de-anonymized version.)
 \section{Card game $t$-SNE} \label{app_cards_tsne}

### 2019-05-09 writing/embedded_meta_learning.tex
Meta-task details

@@
 \par
+\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
+\begin{itemize}
+\item Classifying polynomials as constant/non-constant.
+\item Classifying polynomials as zero/non-zero intercept.
+\item For each variable, identifying whether that variable was relevant to the polynomial.
+\end{itemize}
+We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
+\begin{itemize}
+\item Squaring polynomials (where applicable).
+\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
+\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
+\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
+\end{itemize}
 
@@
 \end{itemize}
-We also considered three binary options that could be altered to produce variants of these games:
+We also considered three binary attributes that could be altered to produce variants of these games:
 \begin{itemize}
@@
 The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
-
+\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
 \subsection{Model \& training}
-See table \ref{supp_hyperparameter_table} for detailed architectural description and hyperparameters for each experiment.
-Hyperparameters were generally found by a heuristic search, where mostly only the optimizer, learning rate annealing schedule, and number of training epochs were varied, not the architectural parameters.
-Some of the parameters take the values they do for fairly arbitrary reasons, e.g.
-the continual learning experiments were run with the current polynomial hyperparameters before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.
-\par
-Each epoch consisted of a separate learning step on each task (both base and meta), in a random order.
-The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, the
-\begin{table}[H]
+\begin{table}
 \centering
@@
 \end{table}
+See table \ref{supp_hyperparameter_table} for detailed architectural description and hyperparameters for each experiment.
+Hyperparameters were generally found by a heuristic search, where mostly only the optimizer, learning rate annealing schedule, and number of training epochs were varied, not the architectural parameters.
+Some of the parameters take the values they do for fairly arbitrary reasons, e.g.
+the continual learning experiments were run with the current polynomial hyperparameters before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.
+\par
+Each epoch consisted of a separate learning step on each task (both base and meta), in a random order.
+The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, the
 \subsection{Source repositories}

### 2019-05-09 writing/embedded_meta_learning.tex
Updates

@@
 \section{Introduction}
-Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016}.
+Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}.
 One fundamental reason for this is that humans are aware of what we are trying to compute and why.
@@
 These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
-While the first two categories have been considered in prior work, the latter is more novel.
+While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
 \par
@@
 \par
-We are inspired by these observations to propose the challenge of meta-mappings -- mappings of tasks to tasks.
-These mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
+In the machine-learning setting, these mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
 Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 \caption{The system solves the meta-learning problem and successfully generalizes to held out tasks.
-The solid line indicates optimal performance.
+The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
 Error-bars throughout are bootstrap 95\%-confidence intervals.}
@@
 \includegraphics[width=0.75\textwidth]{figures/poly/meta_results.png}
-\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples. The solid line indicates optimal performance.} 
+\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples.
+The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
+Error-bars are bootstrap 95\%-CIs.}
 \label{poly_meta_map_results}
 \end{figure}
-As a proof of concept, we first evaluated the system on the simple task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
-the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$).
+As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
+the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
 This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables).
@@
 \caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.}
+Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
+Error-bars are bootstrap 95\%-CIs.}
 \label{poly_continual_results}
@@
 (b) The system can rapidly adapt to new tasks.
-(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.)}
+(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}
 \end{figure}
@@
 The system generally exceeds these baselines by a wide margin, although the switch-suits baseline is more difficult with the targeted holdout.
-Furthermore, the system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).}
+The system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
+Error-bars are bootstrap 95\%-CIs.}
 \label{cards_meta_map_results}
@@
 In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
+Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}, our approach is more general.
 \par
-There has also been some recent interest in task (or function) embeddings.
+There has also been other recent interest in task (or function) embeddings.
 In simultaneous work Achille et al.
@@
 They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
-Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
+Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
 Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
@@
 We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here.
-For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017}.
+For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}.
 Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.
@@
 To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.
+The system can do this with quite small meta-task sample complexity, since it can generalize to unseen meta-mappings after training on only 20 examples.\par
 We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
 This naturally suggests the idea of manipulating task representations just like we manipulate data.
-We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task from examples of task transformations.
+We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task, from examples of task transformations.
 We've also shown that our approach provides a useful perspective on continual learning.

### 2019-05-09 writing/embedded_meta_learning.tex
Tweaks

@@
 $f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
-Nonlinearities & \multicolumn{3}{c|}{Leaky ReLU, no non-linearity at final layer of $T$, $M$, $f$.} \\
+Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $T$, $M$, $f$, and sigmoid for meta-classification outputs.} \\
 \hline
@@
 Each epoch consisted of a separate learning step on each task (both base and meta), in a random order.
-The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, the
+In each task, the meta-learner would receive only a subset (the ``batch size`` above) of the examples to generate a function embedding, and would have to generalize to the remainder of the examples in the dataset.
+The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, these embeddings would get ``stale,'' but this did not seem to be too detrimental.
+\par
+
 \subsection{Source repositories}

### 2019-05-10 writing/embedded_meta_learning.tex
cutting length, hopefully improving clarity

@@
 In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e.
-mappings between tasks.
-For example, once a system has been trained to play a game, it should be able to alter its strategy in accordance with a change in task demands, such as trying to lose the game, or trying to play without using a certain action.
-The challenge is that the system must adapt to performing these tasks without seeing any data from the new task, only from either examples of similar transformations on different tasks (``here's how to change your go strategy to a losing one, here's how to change your checkers strategy to a losing one, now try to lose at chess'') or from natural language instructions (``try to lose at chess'').
-These mappings provide a new type of zero-shot transfer from one task to another -- the system must transform its behavior to adapt to a new task without ever having seen training data from that task.
+mappings between tasks (see below).
 This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
-\par
 To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}.
-By treating task behaviors and data as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-By embedding task behaviors, data, and language in the same space, we can conceptually think of both basic task solutions and adaptive functions, such as following instructions or altering behavior, as mappings in function space.
+By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands.
-We suggest that this ability will be key to building more intelligent and flexible deep learning systems.
-\par
-In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute meta-mappings over this space.
 We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits, such as a useful framework for continual learning.
+We suggest that approaches like this will be key to building more intelligent and flexible deep learning systems.
 \par
@@
 \section{Meta-mappings}
-We propose the challenge of meta-mappings, that is, mappings over tasks.
+We propose the challenge of meta-mappings, that is, mappings where an input or output (or both) is a task.
 These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
@@
 To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
-\begin{enumerate}
-\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system which:
-    \begin{enumerate}
-    \item Embeds tasks into the shared embedding space $Z$.
-    \item Learns to perform tasks in accordance with their embeddings.
+\vspace{-0.75em}
+\begin{enumerate} \setlength \itemsep{0em}
+\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
+\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to perform tasks in accordance with their embeddings.
 \end{enumerate}
-\end{enumerate}
+\vspace{-0.75em}
 The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data.
@@
 Without training on these mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a braod enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below.
+However, if it is trained on a broad enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below.
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
@@
 \centering
-\begin{tikzpicture}[auto, scale=0.9]
+\begin{tikzpicture}[auto, scale=0.75]
 \node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
@@
 \begin{matrix}
-(\text{in}_0, \text{out}_0),\\
-(\text{in}_1, \text{out}_1),\\
+(z_{in,0}, z_{out,0}),\\
+(z_{in,1}, z_{out,1}),\\
 $\vdots$
@@
 We can then interpret most machine learning tasks as a mapping of functions to functions.
-These functions could represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, or they could be functions that operate on functions themselves.
-Under this perspective, learning tasks and learning to flexibly map between tasks, or learning to map from language to tasks, are all the same type of problem.
+The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
+The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves.
+This is related to the idea of a homoiconic programming language, where programs can be manipulated like data.
+Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem.
 \par
@@
 Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
-(Targets do not necessarily need to be output-like, e.g.
-in our RL tasks, we use (action, outcome) tuples as ``targets.'') \par
+\par
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets.
-These transformations are performed by a system with the following components:
-\begin{itemize}
+These transformations are performed by a system with the following components (see Fig.
+\ref{architecture_fig} for a schematic):
+\vspace{-0.75em}
+\begin{itemize} \setlength\itemsep{0em}
 \item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
-\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which takes a function embedding and produces a set of parameters. 
-\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network with parameters specified by $\mathcal{H}$.
+\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. 
+\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
 \end{itemize}
-See Fig. \ref{architecture_fig} for a schematic of the architecture. \par
+\vspace{-0.75em}
+A basic forward pass through the system would proceed as follows.
+First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
+Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training).
+This function embedding is mapped through $\mathcal{H}$ to parameterize $f$, and then $f$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This system can be trained end-to-end.
+See appendix \ref{app_model_details} for detailed, architecture, operation, and hyper-parameters.
+\par
 
-\subsection{Operation}
-A basic forward pass through the system might look as follows.
-\begin{enumerate}
-\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
-Another set of (possibly unlabeled) inputs is provided and embedded.
-\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
-\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
-\end{enumerate}
 To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$.
@@
 
-\subsection{Continual learning}
 \begin{figure}
@@
 \end{figure}
-Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step.
+\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step.
 We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined.
@@
 \section{A stochastic learning setting: simple card games}
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
+\caption{Generalization to held-out tasks.}
+\label{cards_basic_results}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
+\caption{Rapid integration once held-out tasks are introduced.}
+\label{cards_basic_integration_results}
+\end{subfigure}
+\caption{Basic meta learning in the cards domain.
+(a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
+The gray dashed line indicates chance performance, while the solid lines are optimal performance.
+The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
+The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
+(b) The system can rapidly adapt to new tasks.
+(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}
+\end{figure}
 Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet.
@@
 \ref{cards_basic_integration_results}).\par
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{Generalization to held-out tasks.}
-\label{cards_basic_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{Rapid integration once held-out tasks are introduced.}
-\label{cards_basic_integration_results}
-\end{subfigure}
-\caption{Basic meta learning in the cards domain.
-(a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The colored dashed lines show how well the system could perform by playing the strategy from the most correlated game it has seen.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest one.
-(b) The system can rapidly adapt to new tasks.
-(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}
-\end{figure}
 \textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
@@
 We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here.
+To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
 For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}.
@@
 \textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
-\subsection{Model \& training}
+\subsection{Model \& training} \label{app_model_details}
+Basic task operation:
+\begin{enumerate}
+\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
+Another set of (possibly unlabeled) inputs is provided and embedded.
+\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
+\item The system is trained end-to-end to minimize the loss on these outputs.
+\end{enumerate}
+Meta-task operation:
+\begin{enumerate}
+\item A meta-dataset of (input, target) task embeddings is collected. Another set (possibly only inputs) is provided.
+\item The meta network $\mathcal{M}$ maps this set of (input, target) task-embedding pairs to a function embedding.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
+\end{enumerate}
+Note that there are two kinds of hold-out in the training of this system.
+First, some of the trained tasks are held-out on each training step, in order to force the system to generalize rather than just memorize.
+Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.
+
+\subsubsection{Detailed hyper-parameters}
 \begin{table}
 \centering
-\begin{tabular}{|c|ccc|}
+\begin{tabular}{|c||c|c|c|}
 \hline 
-& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\
+& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\\hline
 \hline
-$Z$-dimension & 512 & 512 & 512 \\
-$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
-$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
-$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
-$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
-$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
-$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
-$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
-$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
-$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
-$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
-Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $T$, $M$, $f$, and sigmoid for meta-classification outputs.} \\
+$Z$-dimension & 512 & 512 & 512 \\\hline
+$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\\hline 
+$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
+$\mathcal{O}$ num. layers & 1 & 1 & 3 \\\hline 
+$\mathcal{O}$ num. hidden units & - & - & 512 \\\hline 
+$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\\hline 
+$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\\hline 
+$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
+$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\\hline 
+$f$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
+$f$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
+Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $T$, $M$, $f$, and sigmoid for meta-classification outputs.} \\\hline
+Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification}\\\hline
 \hline
-Optimizer & Adam & RMSProp & RMSProp \\
-Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\
-Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\
-L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\
-L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\
-L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\
-L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\
-L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\
-Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\
-Num. training epochs & 4000 & 3000 & 40000 \\
+Optimizer & Adam & RMSProp & RMSProp \\\hline
+Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\\hline
+Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\\hline
+L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\\hline
+L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\\hline
+L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\\hline
+L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\\hline
+L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\\hline
+Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\\hline
+Num. training epochs & 4000 & 3000 & 40000 \\\hline
 \hline
-Num. base tasks (eval) & 60 & 100 & 36 or 20 \\
-Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\
-Num. meta classifications & 6 & - & 8  \\
-Num. meta mappings & 20 & - & 3  \\
-Num. new base tasks & 40 & 30 & 4 or 20 \\ 
-Num. new meta mappings & 16 & - & 0  \\
-Num. new meta classifications &  \multicolumn{3}{c|}{0} \\
-Base dataset size & \multicolumn{3}{c|}{1024} \\
-Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\
-$\mathcal{M}$ batch size & 50 & 128 & 768 \\
-\hline
+Num. base tasks (eval) & 60 & 100 & 36 or 20 \\\hline
+Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\\hline
+Num. meta classifications & 6 & - & 8  \\\hline
+Num. meta mappings & 20 & - & 3  \\\hline
+Num. new base tasks & 40 & 30 & 4 or 20 \\\hline 
+Num. new meta mappings & 16 & - & 0  \\\hline
+Num. new meta classifications &  \multicolumn{3}{c|}{0} \\\hline
+Base dataset size & \multicolumn{3}{c|}{1024} \\\hline
+Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\\hline
+$\mathcal{M}$ batch size & 50 & 128 & 768 \\\hline
 \end{tabular}

### 2019-05-10 writing/embedded_meta_learning.tex
Further tweaks

@@
 \title{Embedded Meta-Learning: Toward more flexible deep-learning models}
-\author{Andrew K. Lampinen}
+\author{%
+Andrew K. Lampinen\\
+Department of Psychology\\
+Stanford University\\
+\textt{lampinen@stanford.edu}\\
+\And
+James L. McClelland\\
+Department of Psychology\\
+Stanford University\\
+\textt{mcclelland@stanford.edu}\\
+}
 \date{}
@@
 Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
-both language and vision.} \label{architecture_fig}
+both language and vision.
+See appendix \ref{app_model_details} for details.} \label{architecture_fig}
 \end{figure}
@@
 This system can be trained end-to-end.
-See appendix \ref{app_model_details} for detailed, architecture, operation, and hyper-parameters.
+See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
 \par
-
 To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$.
@@
 We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
-We can also train the system to map language to games, i.e.
-playing a game based on hearing its name, and then ask whether the system can generalize this to held-out games based on the systematicity of the language.
-For example, if trained to play ``straight flush'' but never ``losers straight flush,'' will it nevertheless be able to generalize to this case based on its experience with other games?
-Finally, we can use language denote meta-mappings.
+For example, if trained to play ``straight flush'' but never ``losers straight flush,'' will it nevertheless be able to adapt to trying to lose at this game, based on analogous experiences with other games?
 \par
@@
 Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
-It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019} or external memory \citep[e.g.][]{Sprechmann2018}.
+It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
@@
 \par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.]{Brock2018a, Zhang2019}.
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}.
 This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
@@
 In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
-Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}, our approach is more general.
+Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general.
 \par

### 2019-05-10 writing/embedded_meta_learning.tex
Further tightening

@@
 \end{figure}
-\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step.
-We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined.
-Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}.
+\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
+We would like to be able to store our knowledge more efficiently, and allow for further refinement.
+Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
 \par

### 2019-05-14 writing/embedded_meta_learning.tex
Beginning to incorporate Erin's comments

@@
 How can deep learning systems flexibly reuse their knowledge?
-Toward this goal, we propose a new class of challenges, meta-mappings, which involve systematically transforming task behaviors.
-We suggest that the key to achieving this flexibility is representing the task being performed along with the computations used to perform it.
-We therfore draw inspiration from meta-learning and functional programming to propose a class of architectures that represent both data and tasks in a shared latent space.
+Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them.
+The challenges are in the form of meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks.
+We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
+We therefore draw inspiration from meta-learning and functional programming to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
 We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
@@
 By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
-That is, neural networks knowledge about what is being computed is only implicitly accessible to those computations.
+That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations.
 \par
@@
 The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}.
-However, humans can take our knowledge and flexibly alter our behavior in accordance with a change in task demands or a single instruction.
+However, humans can use our knowledge of a task flexibly alter our behavior in accordance with a change in task demands or a single instruction.
 For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
 zero-shot).
-Deep learning systems at present generally lack this representational flexiblity.
+Deep learning systems at present generally lack this representational flexibility.
 \par
@@
 This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands.
-We demonstrate that this approach allows flexible remapping of behavior, as well as offering other benefits, such as a useful framework for continual learning.
-We suggest that approaches like this will be key to building more intelligent and flexible deep learning systems.
+We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge.
+EML may also offer other benefits, such as a useful framework for continual learning.
+We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
 \par
@@
 \section{Meta-mappings}
-We propose the challenge of meta-mappings, that is, mappings where an input or output (or both) is a task.
+We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output.
 These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
@@
 For example, a system that learns to play go should be able to adapt to a different board size.
-These tasks clearly share a great deal of structure, and a human can easily transfer much of their knowledge from one board size to another without retraining, but deep learning models generally have no way of achieving this.
+Go on a large board or a small board share a great deal of structure, and a human can easily transfer much of their knowledge from one size to another without retraining, but deep learning models generally have no way of achieving this.
 Similarly, suppose an agent knows how to navigate from the airport to downtown.
@@
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.
-In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task.
+In particular, we can use our knowledge of a task to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
 \par
-In the machine-learning setting, these mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
+Meta-mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
 Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.

### 2019-05-14 writing/embedded_meta_learning.tex
Rest of Erin's comments

@@
 We therefore draw inspiration from meta-learning and functional programming to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
+EML architectures are applicable to any type of machine learning task, including supervised learning and reinforcement learning.
 We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
@@
 \item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to perform tasks in accordance with their embeddings.
+\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
 \end{enumerate}
@@
 Without training on these mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a broad enough set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution, as we demonstrate below.
+However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below.
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow.
+This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[c.f.][]{Kumaran2016}.
 \par
@@
 \node [conc] at (-7, 4) (act) {\textbf{Output}};
-\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input Encoder}};
+\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
 %%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output Decoder}};
-\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target Encoder}};
+\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
+\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
 \path [line] (perc.north) to (IE.south);
@@
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Targets are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
+Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
+Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
 \par
-Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to the (embedded) targets.
+Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
 These transformations are performed by a system with the following components (see Fig.
@@
 \par
-To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ for which we wish to generate a predicted output $\hat{y}$.
+To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which we wish to generate a predicted output $\hat{y}$.
 This output would be generated as follows:
@@
 \right\}\right)\right)\]
-This system can be trained end-to-end if labels are provided for the second set of inputs.
+This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$.
 In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
@@
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-More generally, suppose we have some input which is already embedded in the representation space $z_{in} \in Z$, and a task/function embedding $z_{\text{function}} \in Z$.
-Then we can generate an output $\hat{z}_{out} \in Z$ as:
-\[\hat{z}_{out} = f_{z_{\text{function}}}(z_{in}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{function}}\right)\]
-This output can then be appropriately dispatched depending on the task at hand.
-For example, if the $z_{in,i}$ are the system's embeddings for trying to win various games, and the $z_{out,i}$ are the corresponding embeddings for trying to lose those games, then $z_{out}$ could be interpreted as the system's guess at a losing strategy for the game embedded as $z_{in}$, and then could be used to play that game.
-We could then evaluate performance by how well the system actually performs at losing with the $z_{out}$ strategy.
+However, the system is not limited to simply mapping inputs to outputs.
+The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
+For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$.
+Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
+\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $z_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+We could then evaluate performance by how well the system actually loses at go with the $z_{new}$ strategy.
 \par
@@
 
-\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig. \ref{poly_basic_results}. \par
+\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. \par
 

### 2019-05-14 writing/embedded_meta_learning.tex
Language meta for polynomials + tweaks

@@
 \[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $z_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate performance by how well the system actually loses at go with the $z_{new}$ strategy.
+For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+We could then evaluate performance by how well the system actually loses at go with the $\hat{z}_{new}$ strategy.
 \par
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figures/poly/meta_results.png}
-\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples.
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
+\caption{From examples of mapping.}
+\label{poly_meta_map_results_examples}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
+\caption{From language input.}
+\label{poly_meta_map_results_language}
+\end{subfigure}
+\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language.
 The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
+The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
 Error-bars are bootstrap 95\%-CIs.}
@@
 the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
-This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables).
+This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
 This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
@@
 We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application.
+The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction.
 \par
@@
 To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
-We trained on these new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
+We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
 The results are shown in fig.
@@
 Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters.
-Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.} \label{supp_hyperparameter_table}
+Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.
+Where language was used to cue meta-mappings, it was processed by language encoder: $\mathcal{L}: \text{natural language} \rightarrow Z$.
+} \label{supp_hyperparameter_table}
 \end{table}

### 2019-05-14 writing/embedded_meta_learning.tex
Tweaks, details

@@
 This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
-To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}.
-By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands.
+To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
+(A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
+This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands.
 We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge.
@@
 We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output.
-These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
+These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
 While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
 \par
-We argue that these meta-mappings are a useful way to think about the flexibility that humans possess.
-For example, a system that learns to play go should be able to adapt to a different board size.
-Go on a large board or a small board share a great deal of structure, and a human can easily transfer much of their knowledge from one size to another without retraining, but deep learning models generally have no way of achieving this.
-Similarly, suppose an agent knows how to navigate from the airport to downtown.
+We argue that these meta-mappings are a useful way to think about human-like flexibility.
+For example, a go-playing system should be able to adapt to a different board size.
+Go on a large board and go on a small board share a great deal of structure.
+Humans can exploit this to play on a different board without retraining, but deep learning models generally have no way of achieving this.
+Similarly, suppose an agent knows how to navigate a town.
 It should be able to adapt to changes of the environment such as street closures.
@@
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.
-In particular, we can use our knowledge of a task to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
+Meta-mapping allows us to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
 \par
-Meta-mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
+Meta-mappings can be cued in different ways, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
 Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 \node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
-\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(f: \text{rep} \rightarrow \text{rep}\)};
+\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(F: \text{rep} \rightarrow \text{rep}\)};
 
@@
 \caption{Schematic of our general architecure.
-Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$.
+Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
 Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
@@
 The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves.
-This is related to the idea of a homoiconic programming language, where programs can be manipulated like data.
+This is related to the idea of a homoiconicity, defined above.
 Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem.
@@
 Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
-\par
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
@@
 \item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. 
-\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
+\item $F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
 \end{itemize}
@@
 Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training).
-This function embedding is mapped through $\mathcal{H}$ to parameterize $f$, and then $f$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs.
 This system can be trained end-to-end.
@@
 This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$.
-In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
+In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
 We define our total loss computed on some dataset $D_2$ as:
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
+\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
 However, the system is not limited to simply mapping inputs to outputs.
@@
 %
-\section{Learning multivariate polynomials (very in progress)}
+\section{Learning multivariate polynomials}
 \begin{figure}
@@
 As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
-the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
+the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
 This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
 This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
-\par
+Details of architecture and training can be found in appendix \ref{app_detailed_methods}.\par
 
@@
 \par
-In order to switch the system, we made a very simple change.
+In order to adapt the EML architecture, we made a very simple change.
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
@@
 That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.
-\par
-We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
-For example, if trained to play ``straight flush'' but never ``losers straight flush,'' will it nevertheless be able to adapt to trying to lose at this game, based on analogous experiences with other games?
+We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
+Details of architecture and training can be found in appendix \ref{app_detailed_methods}.
 \par
@@
 \end{subfigure}
-\caption{The system generalizes to meta-mapping new tasks.
+\caption{The system generalizes to meta-mapping new tasks in the cards domain.
 The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
@@
 The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
-The system generally exceeds these baselines by a wide margin, although the switch-suits baseline is more difficult with the targeted holdout.
-The system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
+The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout.
+The meta-mappings can be cued either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
 Error-bars are bootstrap 95\%-CIs.}
@@
 \par
-We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems, although it has a number of desirable characteristics.
-However, because of the way the architecture is factorized, it is relatively easy to change any aspect of it without altering the others.
-In particular, although we only considered task networks $f$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
+We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems generally, although it has a number of desirable characteristics.
+However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others.
+In particular, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
 Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
@@
 
-\section{Detailed methods}
+\section{Detailed methods} \label{app_detailed_methods}
 \subsection{Datasets}
@@
 \end{itemize}
+\textbf{Language:} We encoded the meta-tasks in language by sequences as follows:
+\begin{itemize}
+\item Classifying polynomials as constant/non-constant: \verb|[``is'', ``constant'']|
+\item Classifying polynomials as zero/non-zero intercept: \verb|[``is'', ``intercept_nonzero'']|
+\item For each variable, identifying whether that variable was relevant to the polynomial: \verb|[``is'', <variable-name>, ``relevant'']|
+\item Squaring polynomials: \verb|[``square'']|
+\item Adding a constant: \verb|[``add'', <value>]|
+\item Multiplying by a constant: \verb|[``multiply'', <value>]|
+\item Permuting inputs: 
+\begin{verbatim}[``permute'', <variable-name>, <variable-name>, <variable-name>, 
+<variable-name>]\end{verbatim}
+\end{itemize}
+All sequences were front-padded with ``<PAD>'' to the length of the longest sequence.
 
@@
 \textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
+\par
+\textbf{Language:} We encoded the meta-tasks in language by sequences of the form \verb|[``toggle'', <attribute-name>]| for the meta-mapping tasks, and \verb|[``is'', <attribute-or-game-name>]|.
 \subsection{Model \& training} \label{app_model_details}
-Basic task operation:
+\textbf{Basic task operation:}
 \begin{enumerate}
-\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
-Another set of (possibly unlabeled) inputs is provided and embedded.
+\item A training dataset $D_1$ of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
+Another set of (possibly unlabeled) inputs $D_2$ is provided and embedded.
 \item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
 \item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
@@
 \end{enumerate}
-Meta-task operation:
+The model is trained to minimize 
+\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
+where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]
+\textbf{Meta-task operation:}
 \begin{enumerate}
-\item A meta-dataset of (input, target) task embeddings is collected. Another set (possibly only inputs) is provided.
-\item The meta network $\mathcal{M}$ maps this set of (input, target) task-embedding pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
+\item A meta-dataset of (source-task-embedding, target-task-embedding) pairs, $D_1$, is collected. Another dataset $D_2$ (possibly only source tasks) is provided.
+\item The meta network $\mathcal{M}$ maps this set of (source, target) task-embedding pairs to a function embedding.
+\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
 \item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
 \end{enumerate}
+The model is trained to minimize
+\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, f_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
+where $\mathfrak{L}$ is $\ell_2$ loss, and $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
 Note that there are two kinds of hold-out in the training of this system.
-First, some of the trained tasks are held-out on each training step, in order to force the system to generalize rather than just memorize.
+First, some of the trained tasks are held-out on each training step (i.e.
+$D_2$), in order to force the system to generalize rather than just memorize.
 Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.
@@
 $\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
+$\mathcal{L}$ architecture & \multicolumn{1}{p{2.5cm}|}{2-layer LSTM + 2 fully-connected} & - & \multicolumn{1}{p{2.5cm}|}{1-layer LSTM + 2 fully-connected} \\\hline 
+$\mathcal{L}$ num. hidden units & 512 & - & 512 \\\hline 
 $\mathcal{O}$ num. layers & 1 & 1 & 3 \\\hline 
@@
 $\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\\hline 
-$f$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
-$f$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
-Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $T$, $M$, $f$, and sigmoid for meta-classification outputs.} \\\hline
-Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification}\\\hline
+$F$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
+$F$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
+Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $\mathcal{T}$, $\mathcal{M}$, $\mathcal{L}$, $F$, and sigmoid for meta-classification outputs.} \\\hline
+Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification.}\\\hline
 \hline
@@
 Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters.
-Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.
+Task network $F: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.
 Where language was used to cue meta-mappings, it was processed by language encoder: $\mathcal{L}: \text{natural language} \rightarrow Z$.
@@
 \subsection{Source repositories}
-The full code can be found on github:
+The full code for the simulations and analyses can be found on github:
 \begin{itemize}
@@
     \begin{itemize}
-        \item See the continual\_learning branch for those results. 
+        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
     \end{itemize}

### 2019-05-15 writing/embedded_meta_learning.tex
Work work work

@@
 The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}.
-However, humans can use our knowledge of a task flexibly alter our behavior in accordance with a change in task demands or a single instruction.
+However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
 For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
@@
 This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands.
-We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge.
+We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
 EML may also offer other benefits, such as a useful framework for continual learning.
@@
 \section{Embedded Meta-Learning (EML) architecture}
-To achieve this, we propose a new class of Embedded Meta-Learning (EML) architectures which consist of two parts: 
+EML architectures consist of two parts: 
 \vspace{-0.75em}
@@
 Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.
+Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
 These transformations are performed by a system with the following components (see Fig.
-\ref{architecture_fig} for a schematic):
-\vspace{-0.75em}
-\begin{itemize} \setlength\itemsep{0em}
-\item $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding. 
-\item $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters. 
-\item $F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
-\end{itemize}
-\vspace{-0.75em}
+\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding.
+$\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters.
+$F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
+\par
 A basic forward pass through the system would proceed as follows.
 First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
-Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training).
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs.
-This system can be trained end-to-end.
+These examples are fed to $\mathcal{M}$ to produce a function embedding.
+This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a second dataset, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This system can be trained end-to-end on targets for the second dataset.
 See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
@@
 For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate performance by how well the system actually loses at go with the $\hat{z}_{new}$ strategy.
+We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy.
 \par
-Similarly, we could map from language to a task embedding, and then ask how well the system performs at the task specified by language.
+Similarly, we could map from language to a task embedding, and then evaluate the system at the specified task.
 The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.
@@
 This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
-Details of architecture and training can be found in appendix \ref{app_detailed_methods}.\par
+Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
 
@@
 There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
-If it wins, it is rewarded the value of the bet, if it loses, it loses that value (i.e.
-receives a negative reward).
 This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
-We considered five games that are simplified analogs of various real card games, including poker and blackjack (see Appendix \ref{meth_data_cards} for details of the games).
+We considered five games that are simplified analogs of various real card games (see Appendix \ref{meth_data_cards}).
 We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable.
-These are challenging manipulations, for instance trying to lose requires completely inverting the learned $Q$-function for the task.
+These are challenging manipulations, for instance trying to lose requires completely inverting a learned $Q$-function.
 \par
@@
 We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
-Details of architecture and training can be found in appendix \ref{app_detailed_methods}.
+Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.
 \par
-\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out task from a few examples in Fig.
+\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
 \ref{cards_basic_results}.
-We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``Losers'' variations of the ``straight flush'' game.
+We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game.
 In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
-It is worth noting that the sample complexity in terms of number of tasks trained on is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
+Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
 Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
-Finally, the system can integrate new tasks quite rapidly (fig.
+Finally, the system can integrate new tasks rapidly (fig.
 \ref{cards_basic_integration_results}).\par
@@
 This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out).
-Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so it is encouraging to see rewards that are substantially above 0.
-Again, given a small amount of additional training on the new games, the system can learn how to achieve this mapping perfectly.
+Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good.
 \par
@@
 \end{figure}
-%\textbf{Basic language (language $\rightarrow$ task):} Next, we show that the system is able to perform a held-out task based on a linguistic description alone.
-The system is significantly better than chance at this task, as shown in Fig.
-\ref{cards_language_basic_results}, but it is substantially less successful at this task than at learning from examples.
-This is perhaps unsurprising, however, since examples contain richer information about the structure of the task.
-(Note that the targeted 10\% was run using an older version of the code.
-Results may improve slightly when it is re-run, but based on the random 50\% hold-out results, the change doesn't make too substantial a difference.)\par
-%Intriguingly, the system also shows more run-to-run variability in its generalization from language, especially with a targeted hold-out.
-This suggests that language learning in this context may be quite sensitive to initialization, possibily because of the poverty of the signal relative to the capacity of the network.
-Interestingly, simply applying dropout does not seem to ameliorate this.
-\par
-%\begin{figure}[H]
-%\begin{subfigure}[t]{0.5\textwidth}
-%\centering
-%\includegraphics[width=\textwidth]{figures/language_basic.png}
-%\caption{Average rewards}
-%\end{subfigure}%
-%\begin{subfigure}[t]{0.5\textwidth}
-%\includegraphics[width=\textwidth]{figures/language_basic_by_run.png}
-%\caption{Density plot of rewards received on different held-out tasks on different runs of the model.}
-%\end{subfigure}
-%\caption{The system generalizes to held out tasks based on language alone.
-However, it is substantially less good at this task than generalizing to a held-out task based on examples.
-Furthermore, it shows more run-to-run variability and within-run variability.}
-%\label{cards_language_basic_results}
-%\end{figure}
-%\newpage
-%\textbf{Meta language (language $\rightarrow (\text{task} \rightarrow \text{task})$):} Finally, in Fig, \ref{cards_language_meta_results}, we show that the system is able to perform meta-mappings from language comparably to how it performs them from examples.
-Note that this is in some ways an easier task than the basic language-mapping task.
-\par
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.66\textwidth]{figures/language_meta_mapping.png}
-%\caption{The system generalizes to meta-mapping new tasks based on language. It performs this comparably to meta-mapping based on examples of mappings.}
-%\label{cards_language_meta_results}
-%\end{figure}
 \section{Related work}
@@
 In simultaneous work Achille et al.
-\citep{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task.
+\citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task.
 They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
@@
 We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
-We hope that our work will inspire more exploration of behavior adaptation, especially in tasks beyond the simple domains we considered here.
+We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here.
 To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
@@
 Num. training epochs & 4000 & 3000 & 40000 \\\hline
+Num. runs & 5 & 5 & 10 \\ \hline
 \hline
@@
 \subsection{Source repositories}
-The full code for the simulations and analyses can be found on github:
+The full code for the experiments and analyses can be found on github:
 \begin{itemize}

### 2019-05-15 writing/embedded_meta_learning.tex
Tweaks and cutting

@@
 \section{Embedded Meta-Learning (EML) architecture}
-EML architectures consist of two parts: 
+EML architectures are composed of two components: 
 \vspace{-0.75em}
@@
 \end{tikzpicture}
-\caption{Schematic of our general architecure.
-Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
+\caption{The EML architecture.
+Blocks with solid edges denote learnable deep networks, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
 Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
@@
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
+Model outputs are decoded from $Z$ by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
 Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
@@
 The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
-For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$.
+For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g.
+from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}\right) \right\}\right)$.
 Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
@@
 \end{subfigure}
-\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language.
-The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
-The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
+\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
+The solid line indicates optimal performance; the dashed line indicates chance (untrained).
 Error-bars are bootstrap 95\%-CIs.}
@@
 \end{figure}
-Our next case study was in the setting of simple card games, where the agent receives a hand and has to decide on a bet.
+We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
 There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
@@
 \end{figure}
-\section{Related work}
-Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
+\section{Discussion}
+\textbf{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
-Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or by conditioning on a task input \citep[e.g.][]{Borsa2019}.
+Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or a task input \citep[e.g.][]{Borsa2019}.
 \par
@@
 This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
-It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}.
+It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}.
 In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
@@
 \par
-\section{Future directions}
-We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
+\textbf{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
 We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here.
@@
 \par
-\section{Conclusions}
-In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
+\textbf{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
 We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
@@
 Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.
+\par
+\textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.
+\par
 

### 2019-05-15 writing/embedded_meta_learning.tex
Style tweaks + more length

@@
 Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
-
-\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. \par
-
-\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
+\vspace{-0.7em}
+\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. \par 
+\vspace{-0.7em}
+\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
 \ref{poly_meta_map_results}.
@@
 \end{figure}
-\textbf{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
+\vspace{-0.7em}
+\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
 We would like to be able to store our knowledge more efficiently, and allow for further refinement.
@@
 \ref{poly_continual_results}.
-The meta-network embeddings offers good immediate performance, and substantially accelerates the optimization the process, compared to a randomly-initialized embedding (see supp.
+The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
 fig.
@@
 \par
-\textbf{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
+\vspace{-0.7em}
+\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
 \ref{cards_basic_results}.
@@
 \ref{cards_basic_integration_results}).\par
-\textbf{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
+\vspace{-0.7em}
+\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
 For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
@@
 \section{Discussion}
-\textbf{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
+\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
@@
 \par
-\textbf{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
+\vspace{-1em}
+\paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
 We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here.
@@
 \par
-\textbf{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
+\vspace{-1em}
+\paragraph{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
 We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-We've proposed that representing the task explicitly as the computation provides a solution to this problem.
+We've proposed that explicitly representing the tasks by embeddings, and deriving the computation from these embeddings, provides a solution to this problem.
 To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.
-The system can do this with quite small meta-task sample complexity, since it can generalize to unseen meta-mappings after training on only 20 examples.\par
+The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
 We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
-This naturally suggests the idea of manipulating task representations just like we manipulate data.
-We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task, from examples of task transformations.
+This naturally leads to the idea of manipulating task representations just like we manipulate data.
+We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task.
 We've also shown that our approach provides a useful perspective on continual learning.

### 2019-05-15 writing/embedded_meta_learning.tex
Further Tweaks

@@
 For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g.
-from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}\right) \right\}\right)$.
+from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}, ...\right) \right\}\right)$.
 Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
@@
 We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-We've proposed that explicitly representing the tasks by embeddings, and deriving the computation from these embeddings, provides a solution to this problem.
+To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork.
+This allows transformations over task embeddings to transform the system's behavior.
 To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.

### 2019-05-16 meta_RL_analyses.Rmd
Astronomy

@@
 library(tidyverse)
+library(stargazer)
 ```
@@
 
+And some stargazing:
+```{r}
+optimal_baselines %>%
+  select(-game_type) %>%
+  mutate_at(vars(expected_reward), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
+```
+
+```{r}
+most_correlated_baselines[,c('run_type','game_type','is_new_game','named_run_type','named_game_type','expected_reward')] %>%
+  ungroup() %>%
+  filter(run_type %in% c("basic", "basic_random_holdout_longer")) %>%
+  select(-game_type, -run_type) %>%
+  mutate(is_new_game=as.character(is_new_game)) %>%
+  mutate_at(vars(expected_reward), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
+```
+
 # meta-learning tests
@@
   filter(epoch == 0) %>%
-  group_by(run_type, game_type, named_game_type, is_new_game) %>%
-  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
-            se_reward = sd_reward/sqrt(n()), 
-            ci_lo = avg_reward - 1.96*se_reward, 
-            ci_hi = avg_reward + 1.96*se_reward)
+  group_by(named_run_type, run_type, game_type, named_game_type, is_new_game) %>%
+  do(data.frame(mean_cl_boot(.$reward))) %>% 
+  ungroup() %>%
+  rename(average_reward=y, avg_rwd_CI_low=ymin, avg_rwd_CI_high=ymax)
+
+```
+
+```{r}
+avg_reward_d %>%
+  filter(run_type %in% c("basic", "basic_random_holdout_longer")) %>%
+  select(-game_type, -run_type) %>%
+  mutate(is_new_game=as.character(is_new_game)) %>%
+  mutate_at(vars(average_reward, contains("CI")), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
 ```
@@
                filter(run_type %in% c("basic_slower_integration", "basic_random_holdout_longer_slower_integration"),
-                      epoch <= 200),
+                      epoch < 500),
              "epoch", "reward", "is_new_game",
@@
   labs(x = "Epoch after introducing new tasks") +
-  theme(plot.margin=margin(b=1, units="cm"))
+  theme(plot.margin=margin(t=0.24, b=1.7, unit="cm"))
 
@@
 ```{r}
+meta_baseline_unmapped_d %>%
+  ungroup() %>%
+  filter(run_type %in% c("basic", "basic_random_holdout_longer"),
+         meta_task != "toggle_suits_rule") %>%
+  select(-meta_task, -run_type) %>%
+  mutate(is_new=as.character(is_new)) %>%
+  mutate_at(vars(expected_reward), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
+```
+
+```{r}
 meta_d = load_d(results_dir, result_subdirs, num_runs, "new_meta_true_losses")
@@
   group_by(run_type, named_run_type, meta_task, named_meta_task, is_new) %>%
-  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
-            se_reward = sd_avg_reward/sqrt(n()), 
-            ci_lo = avg_avg_reward - 1.96*se_reward, 
-            ci_hi = avg_avg_reward + 1.96*se_reward)
+  do(data.frame(mean_cl_boot(.$avg_reward))) %>%
+  ungroup() %>%
+  rename(average_reward=y, avg_rwd_CI_low=ymin, avg_rwd_CI_high=ymax)
 
+```
+
+```{r}
+avg_meta_d %>%
+  filter(run_type %in% c("basic", "basic_random_holdout_longer"),
+         meta_task != "toggle_suits_rule") %>%
+  select(-meta_task, -run_type) %>%
+  mutate(is_new=as.character(is_new)) %>%
+  mutate_at(vars(average_reward, contains("CI")), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
 ```
@@
 
+```{r}
+avg_lang_meta_d = lang_meta_d %>%
+  group_by(run_type, named_run_type, run, meta_task, named_meta_task, is_new) %>%
+  summarize(avg_reward = mean(reward)) %>%
+  group_by(run_type, named_run_type, meta_task, named_meta_task, is_new) %>%
+  do(data.frame(mean_cl_boot(.$avg_reward))) %>%
+  ungroup() %>%
+  rename(average_reward=y, avg_rwd_CI_low=ymin, avg_rwd_CI_high=ymax)
+
+```
+
+```{r}
+avg_lang_meta_d %>%
+  filter(run_type %in% c("meta_batch_128", "language_simplified_random_holdout"),
+         meta_task != "toggle_suits_rule") %>%
+  select(-meta_task, -run_type) %>%
+  mutate(is_new=as.character(is_new)) %>%
+  mutate_at(vars(average_reward, contains("CI")), function(x) {round(x, digits=3)}) %>%
+  stargazer(summary = F, rownames = F, digits=2)
+```
 # embeddings

### 2019-05-16 writing/embedded_meta_learning.tex
Astronomy

@@
 
+\section{Numerical results}
+In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures.
+Tables were generated with stargazer \citep{Hlavac2018}.
+
+\subsection{Cards}
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_run\_type & named\_game\_type & is\_new\_game & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
+\hline \\[-1.8ex]
+Random 50\% holdout & High card & Trained & 0.53 & 0.521 & 0.541 \\
+Random 50\% holdout & High card & Held out & 0.441 & 0.42 & 0.462 \\
+Random 50\% holdout & Match & Trained & 0.537 & 0.524 & 0.55 \\
+Random 50\% holdout & Match & Held out & 0.539 & 0.523 & 0.556 \\
+Random 50\% holdout & Pairs & Trained & 0.521 & 0.504 & 0.536 \\
+Random 50\% holdout & Pairs & Held out & 0.453 & 0.434 & 0.47 \\
+Random 50\% holdout & Straight flush & Trained & 0.525 & 0.508 & 0.54 \\
+Random 50\% holdout & Straight flush & Held out & 0.484 & 0.466 & 0.502 \\
+Random 50\% holdout & Blackjack & Trained & 0.582 & 0.557 & 0.603 \\
+Random 50\% holdout & Blackjack & Held out & 0.492 & 0.468 & 0.513 \\
+Targeted 10\% holdout & High card & Trained & 0.527 & 0.518 & 0.536 \\
+Targeted 10\% holdout & Match & Trained & 0.536 & 0.526 & 0.546 \\
+Targeted 10\% holdout & Pairs & Trained & 0.522 & 0.512 & 0.531 \\
+Targeted 10\% holdout & Straight flush & Trained & 0.524 & 0.509 & 0.538 \\
+Targeted 10\% holdout & Straight flush & Held out & 0.361 & 0.332 & 0.39 \\
+Targeted 10\% holdout & Blackjack & Trained & 0.586 & 0.575 & 0.598 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for basic meta-learning, figure \ref{cards_basic_results}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
+\hline \\[-1.8ex]
+Trained & Targeted 10\% holdout & High card & 0.531 \\
+Trained & Targeted 10\% holdout & Match & 0.541 \\
+Trained & Targeted 10\% holdout & Pairs & 0.532 \\
+Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
+Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
+Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
+Trained & Random 50\% holdout & High card & 0.531 \\
+Held out & Random 50\% holdout & High card & 0.396 \\
+Trained & Random 50\% holdout & Match & 0.541 \\
+Held out & Random 50\% holdout & Match & 0.541 \\
+Trained & Random 50\% holdout & Pairs & 0.532 \\
+Held out & Random 50\% holdout & Pairs & 0.37 \\
+Trained & Random 50\% holdout & Straight flush & 0.536 \\
+Held out & Random 50\% holdout & Straight flush & 0.452 \\
+Trained & Random 50\% holdout & Blackjack & 0.595 \\
+Held out & Random 50\% holdout & Blackjack & 0.456 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_game\_type & expected\_reward \\
+\hline \\[-1.8ex]
+Blackjack & 0.592 \\
+High card & 0.531 \\
+Match & 0.541 \\
+Pairs & 0.532 \\
+Straight flush & 0.536 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for playing optimal rewards for basic meta-learning, solid lines in figure \ref{cards_basic_results}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
+\hline \\[-1.8ex]
+Trained & Targeted 10\% holdout & High card & 0.531 \\
+Trained & Targeted 10\% holdout & Match & 0.541 \\
+Trained & Targeted 10\% holdout & Pairs & 0.532 \\
+Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
+Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
+Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
+Trained & Random 50\% holdout & High card & 0.531 \\
+Held out & Random 50\% holdout & High card & 0.396 \\
+Trained & Random 50\% holdout & Match & 0.541 \\
+Held out & Random 50\% holdout & Match & 0.541 \\
+Trained & Random 50\% holdout & Pairs & 0.532 \\
+Held out & Random 50\% holdout & Pairs & 0.37 \\
+Trained & Random 50\% holdout & Straight flush & 0.536 \\
+Held out & Random 50\% holdout & Straight flush & 0.452 \\
+Trained & Random 50\% holdout & Blackjack & 0.595 \\
+Held out & Random 50\% holdout & Blackjack & 0.456 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
+\hline \\[-1.8ex]
+Targeted 10\% holdout & Switch suits & Trained & 0.523 & 0.512 & 0.534 \\
+Targeted 10\% holdout & Switch suits & Held out & 0.234 & 0.196 & 0.273 \\
+Targeted 10\% holdout & Losers & Trained & 0.532 & 0.511 & 0.546 \\
+Targeted 10\% holdout & Losers & Held out & 0.289 & 0.241 & 0.322 \\
+Random 50\% holdout & Switch suits & Trained & 0.528 & 0.521 & 0.533 \\
+Random 50\% holdout & Switch suits & Held out & 0.375 & 0.368 & 0.382 \\
+Random 50\% holdout & Losers & Trained & 0.531 & 0.523 & 0.538 \\
+Random 50\% holdout & Losers & Held out & 0.427 & 0.417 & 0.436 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for meta-mapping from examples, figure \ref{cards_meta_map_results_examples}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
+\hline \\[-1.8ex]
+Language (random 50\%) & Switch suits & Trained & 0.525 & 0.52 & 0.534 \\
+Language (random 50\%) & Switch suits & Held out & 0.371 & 0.353 & 0.384 \\
+Language (random 50\%) & Losers & Trained & 0.524 & 0.521 & 0.527 \\
+Language (random 50\%) & Losers & Held out & 0.426 & 0.413 & 0.44 \\
+Language (targeted 10\%) & Switch suits & Trained & 0.531 & 0.52 & 0.542 \\
+Language (targeted 10\%) & Switch suits & Held out & 0.225 & 0.146 & 0.305 \\
+Language (targeted 10\%) & Losers & Trained & 0.539 & 0.533 & 0.544 \\
+Language (targeted 10\%) & Losers & Held out & 0.341 & 0.308 & 0.367 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for meta-mapping from language, figure \ref{cards_meta_map_results_language}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} cccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_run\_type & named\_meta\_task & is\_new & expected\_reward \\
+\hline \\[-1.8ex]
+Targeted 10\% holdout & Switch suits & Trained & 0.298 \\
+Targeted 10\% holdout & Switch suits & Held out & 0.368 \\
+Targeted 10\% holdout & Losers & Trained & -0.446 \\
+Targeted 10\% holdout & Losers & Held out & -0.463 \\
+Random 50\% holdout & Switch suits & Trained & 0.37 \\
+Random 50\% holdout & Switch suits & Held out & 0.278 \\
+Random 50\% holdout & Losers & Trained & -0.465 \\
+Random 50\% holdout & Losers & Held out & -0.444 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in figure \ref{cards_meta_map_results}}
+\end{table}
+
 \end{document}

### 2019-05-16 meta_RL_analyses.Rmd
integration stuff

@@
              alpha=0.5) +
-  labs(x = "Epoch after introducing new tasks") +
-  theme(plot.margin=margin(t=0.24, b=1.7, unit="cm"))
+  labs(x = "Epoch after introducing new tasks")
 

### 2019-05-16 writing/embedded_meta_learning.tex
integration stuff

@@
 Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
-\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{function}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-For example, if the $z_{old}$ is the system's embedding for trying to win at go, and $z_{meta}$ is the meta-task of switching to trying to lose a game, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+For example, if the $z_{old}$ is the system's embedding for trying to win at go, and the meta-dataset consists of examples of a winning strategy and a losing strategy for different games, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
 We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy.
@@
 %
-\section{Learning multivariate polynomials}
+\section{Learning multivariate polynomials} \label{sec_poly}
 \begin{figure}
 \centering
-\includegraphics[width=0.5\textwidth]{figures/poly/basic_results.png}
-\caption{The system solves the meta-learning problem and successfully generalizes to held out tasks.
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/poly/basic_results.png}
+\caption{The polynomials domain, section \ref{sec_poly}.}
+\label{poly_basic_results}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
+\caption{The cards domain, section \ref{sec_cards}.}
+\label{cards_basic_results}
+\end{subfigure}%
+\caption{The EML system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
+(\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}.
+The system successfully generalizes to held out polynomials.
 The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
-Error-bars throughout are bootstrap 95\%-confidence intervals.}
-\label{poly_basic_results}
+(\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}.
+The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
+The gray dashed line indicates chance performance, while the solid lines are optimal performance.
+The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
+The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
+Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
 \end{figure}
@@
 \caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
+This shows the loss produced when evaluating the mapped embedding on the target task.
+For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $f(x)$ and evaluating how the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
 The solid line indicates optimal performance; the dashed line indicates chance (untrained).
@@
 The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction.
+However, it generalizes better to new meta-mappings from examples than language, which is not completely surprising, since the examples provide a richer dataset to learn from.
 \par
@@
 
-\section{A stochastic learning setting: simple card games}
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{Generalization to held-out tasks.}
-\label{cards_basic_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{Rapid integration once held-out tasks are introduced.}
-\label{cards_basic_integration_results}
-\end{subfigure}
-\caption{Basic meta learning in the cards domain.
-(a) The system successfully generalizes to held out tasks, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
-(b) The system can rapidly adapt to new tasks.
-(This figure shows the effect of training all parameters while replaying old tasks, unlike the continual learning strategy above.) Error-bars are bootstrap 95\%-CIs.}
-\end{figure}
+\section{A stochastic learning setting: simple card games}\label{sec_cards}
 We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
@@
 Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
-Finally, the system can integrate new tasks rapidly (fig.
-\ref{cards_basic_integration_results}).\par
+\par
 \vspace{-0.7em}
@@
 \par
+The results reported in the figures in this paper are averages across multiple runs, with different trained and held-out tasks (in the polynomial case) and different network initializations (in all cases), to ensure the robustness of the findings.
+\par
 
@@
 
-\section{Numerical results}
+\begin{figure}[H]
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
+\caption{The polynomials domain, section \ref{sec_poly}.}
+\label{supp_poly_integration_results}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
+\caption{The cards domain, section \ref{sec_cards}.}
+\label{supp_cards_integration_results}
+\end{subfigure}%
+\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
+\label{supp_integration_results}
+\end{figure}
+
+\section{Numerical results} \label{app_numerical_results}
 In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures.
 Tables were generated with stargazer \citep{Hlavac2018}.
+\par
+
+\subsection{Polynomials}
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} ccccc}
+\\[-1.8ex]\hline
+\hline \\[-1.8ex]
+named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
+\hline \\[-1.8ex]
+EML & Trained & 0.014 & 0.011 & 0.017 \\
+EML & Held out & 0.218 & 0.153 & 0.291 \\
+Untrained EML network & Trained & 5.735 & 4.787 & 6.787 \\
+Untrained EML network & Held out & 5.968 & 4.967 & 6.975 \\
+\hline \\[-1.8ex]
+\end{tabular}
+\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
+\end{table}
 

### 2019-05-16 writing/embedded_meta_learning.tex
Astronomy part II

@@
 We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy.
+All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the function embedding.
 \par
-Similarly, we could map from language to a task embedding, and then evaluate the system at the specified task.
-The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.
+Alternatively, we could map from language to a meta-mapping embedding, rather than inducing it from examples of the meta-mapping.
+This corresponds to the human ability to change behavior in response to instructions.
+The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows for substantial flexibility within a unified framework.
 
@@
 \caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
-This shows the loss produced when evaluating the mapped embedding on the target task.
-For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $f(x)$ and evaluating how the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
+The plots show the loss produced when evaluating the mapped embedding on the target task.
+For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
 The solid line indicates optimal performance; the dashed line indicates chance (untrained).
@@
 The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction.
-However, it generalizes better to new meta-mappings from examples than language, which is not completely surprising, since the examples provide a richer dataset to learn from.
+However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task.
 \par
@@
 \par
-\vspace{-1em}
-\paragraph{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
+%\vspace{-1em}
+%\paragraph{Conclusions:}
+\section{Conclusions}
+In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
 We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
@@
 
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
+\hline \\[-1.8ex] 
+EML & Trained mapping, on trained task & 0.084 & 0.08 & 0.088 \\ 
+EML & Trained mapping, on held-out task & 1.664 & 1.345 & 2.077 \\ 
+EML & Held-out mapping, on trained task & 1.07 & 0.996 & 1.14 \\ 
+EML & Held-out mapping, on held-out task & 1.52 & 1.444 & 1.604 \\ 
+Untrained EML network & Trained mapping, on trained task & 13.378 & 12.213 & 14.84 \\ 
+Untrained EML network & Trained mapping, on held-out task & 15.469 & 13.778 & 17.303 \\ 
+Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.766 & 8.687 \\ 
+Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.165 & 9.127 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
+\end{table}
+
+\begin{table}[H]
+\scriptsize
+\centering
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
+\hline \\[-1.8ex] 
+Language & Trained mapping, on trained task & 0.515 & 0.483 & 0.552 \\ 
+Language & Trained mapping, on held-out task & 2.244 & 1.921 & 2.623 \\ 
+Language & Held-out mapping, on trained task & 2.072 & 1.958 & 2.19 \\ 
+Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
+Untrained EML network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
+Untrained EML network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
+Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
+Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
+\hline \\[-1.8ex] 
+\end{tabular}
+\caption{Table for meta-mapping results from language, figure \ref{poly_meta_map_results_language}}
+\end{table}
+
 \subsection{Cards}

### 2019-05-16 writing/embedded_meta_learning.tex
Lesion experiment and referencing the one/few-shot word learning paper

@@
 Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task.
+This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[c.f.][]{Rumelhart1993, Lampinen2018a}.
 That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
@@
 
+\section{Lesion experiments}
+
+\subsection{Hyper network vs. conditioned task network}
+Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
+Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks.
+We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks.
+While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
+\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks.}
+\label{supp_lesion_hyper}
+\end{figure}
+
 \section{Numerical results} \label{app_numerical_results}

### 2019-05-16 writing/embedded_meta_learning.tex
Sweeping poly

@@
 \vspace{-0.7em}
-\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. \par 
+\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
+\ref{poly_basic_results}.
+Furthermore, it is able to do this in a sample-efficient manner, see supp.
+fig.
+\ref{supp_poly_sweep_results}.
+\par
 \vspace{-0.7em}
@@
 \centering
-\includegraphics[width=0.66\textwidth]{figures/continual/continual_learning_direct_comparison.png}
+\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
+\caption{The system is able to infer polynomials from only seeing a few data points (i.e.
+evaluations of the polynomial), despite the fact that during training it always saw 50.
+A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
+\label{supp_poly_sweep_results}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/continual/continual_learning_direct_comparison.png}
 \caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.

### 2019-05-16 writing/embedded_meta_learning_appendix.tex
Splitting file so that we can compile without appendix

--- 2019-05-16 writing/embedded_meta_learning.tex
@@
-\documentclass{article}
-
-\usepackage{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage[pdfborder={0 0 0}]{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-\usepackage{subcaption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm}
-\usepackage{relsize}
-\usepackage{natbib}
-\usepackage{float}
-\usepackage{tikz}
-
-\usetikzlibrary{shapes,arrows}
-
-\tikzstyle{block} = [rectangle, draw, thick, align=center, rounded corners]
-\tikzstyle{boundingbox} = [very thick, dotted, gray]
-\tikzstyle{dashblock} = [rectangle, draw, thick, align=center, dashed]
-\tikzstyle{conc} = [ellipse, draw, thick, dashed, align=center]
-\tikzstyle{netnode} = [circle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
-\tikzstyle{relunode} = [rectangle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
-\tikzstyle{line} = [draw, very thick, -latex']
-
-\setlength{\parskip}{1em}
-\setlength{\parindent}{0em}
-
-\setcitestyle{square}
-
-\begin{document}
-\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
-\author{%
-Andrew K. Lampinen\\
-Department of Psychology\\
-Stanford University\\
-\textt{lampinen@stanford.edu}\\
-\And
-James L. McClelland\\
-Department of Psychology\\
-Stanford University\\
-\textt{mcclelland@stanford.edu}\\
-}
-\date{}
-\maketitle
-
-\begin{abstract}
-How can deep learning systems flexibly reuse their knowledge?
-Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them.
-The challenges are in the form of meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks.
-We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
-We therefore draw inspiration from meta-learning and functional programming to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
-EML architectures are applicable to any type of machine learning task, including supervised learning and reinforcement learning.
-We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
-that they can exhibit zero-shot remapping of behavior on new tasks.
-\end{abstract}
-
-\section{Introduction}
-Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}.
-One fundamental reason for this is that humans are aware of what we are trying to compute and why.
-By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
-That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations.
-\par
-There are a number of advantages to representing knowledge about data and tasks together.
-In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}.
-However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
-For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
-zero-shot).
-Deep learning systems at present generally lack this representational flexibility.
-\par
-In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e.
-mappings between tasks (see below).
-This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
-To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
-(A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands.
-We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
-EML may also offer other benefits, such as a useful framework for continual learning.
-We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
-\par
-
-\section{Meta-mappings}
-We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output.
-These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
-While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
-\par
-We argue that these meta-mappings are a useful way to think about human-like flexibility.
-For example, a go-playing system should be able to adapt to a different board size.
-Go on a large board and go on a small board share a great deal of structure.
-Humans can exploit this to play on a different board without retraining, but deep learning models generally have no way of achieving this.
-Similarly, suppose an agent knows how to navigate a town.
-It should be able to adapt to changes of the environment such as street closures.
-We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
-While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.
-Meta-mapping allows us to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
-\par
-Meta-mappings can be cued in different ways, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
-Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
-\par
-
-\section{Embedded Meta-Learning (EML) architecture}
-EML architectures are composed of two components: 
-\vspace{-0.75em}
-\begin{enumerate} \setlength \itemsep{0em}
-\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
-\end{enumerate}
-\vspace{-0.75em}
-The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data.
-In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples).
-This is a step closer to the flexible reasoning humans display.
-\par
-Without training on these mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below.
-For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[c.f.][]{Kumaran2016}.
-\par
-\begin{figure}
-\centering
-\begin{tikzpicture}[auto, scale=0.75]
-\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
-
-% inputs, outputs
-
-\draw [boundingbox] (-9, -5) rectangle (-2.1, 5); 
-\node [text=gray] at (-8.5, 4.65) {\textbf{I/O}};
-
-\node [conc] at (-7, -4) (perc) {\textbf{Input}};
-%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-7, 4) (act) {\textbf{Output}};
-\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
-%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
-\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
-\path [line] (perc.north) to (IE.south);
-%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
-\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
-%%\path [line] (LE.east) to (rep.west);
-\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
-\path [line] (OD.north) to (act.south);
-\path [line] (act.south) to (TE.north);
-\path [line] (TE.east) to (rep.north west);
-
-% meta
-\draw [boundingbox] (-1.9, 5) rectangle (6, -5); 
-\node [text=gray] at (-0.4, 4.7) {\textbf{Meta Learner}};
-
-\node [dashblock] at (0, -2.5) (collection) {
-\(\left\{
-\begin{matrix}
-(z_{in,0}, z_{out,0}),\\
-(z_{in,1}, z_{out,1}),\\
-$\vdots$
-\end{matrix}\right\}\)};
-\path [line] (rep.south) to (collection);
-\path [line] ([xshift=-1em]rep.south) to (collection);
-\path [line] ([xshift=1em]rep.south) to (collection);
-
-\node [block] at (4, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
-\path [line] (collection.south) to [out=-90, in=-90] (meta.south);
-\path [line] (meta.west) to (rep.east);
-
-% hyper
-
-\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
-\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(F: \text{rep} \rightarrow \text{rep}\)};
-
-\path [draw, ->, very thick] (rep.north east) to (hyper.south);
-\path [draw, ->, very thick] (hyper.west) to (transform.north east);
-\path [draw, ->, very thick] ([xshift=-1em]transform.south) to ([xshift=-1em]rep.north);
-\path [draw, ->, very thick] ([xshift=1em]rep.north) to ([xshift=1em]transform.south);
-
-\end{tikzpicture}
-\caption{The EML architecture.
-Blocks with solid edges denote learnable deep networks, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
-Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
-both language and vision.
-See appendix \ref{app_model_details} for details.} \label{architecture_fig}
-\end{figure}
-More formally, we take a \emph{functional} perspective on learning.
-A datum can be represented by a constant function which outputs it.
-(For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
-We can then interpret most machine learning tasks as a mapping of functions to functions.
-The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves.
-This is related to the idea of a homoiconicity, defined above.
-Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem.
-\par
-Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
-Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Model outputs are decoded from $Z$ by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
-Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
-These transformations are performed by a system with the following components (see Fig.
-\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding.
-$\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters.
-$F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
-\par
-A basic forward pass through the system would proceed as follows.
-First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
-These examples are fed to $\mathcal{M}$ to produce a function embedding.
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a second dataset, and $\mathcal{O}$ to map the resultant embeddings to outputs.
-This system can be trained end-to-end on targets for the second dataset.
-See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
-\par
-To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which we wish to generate a predicted output $\hat{y}$.
-This output would be generated as follows:
-\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
-where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
-\right\}\right)\right)\]
-This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$.
-In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
-We define our total loss computed on some dataset $D_2$ as:
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-However, the system is not limited to simply mapping inputs to outputs.
-The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
-For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g.
-from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}, ...\right) \right\}\right)$.
-Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
-\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-For example, if the $z_{old}$ is the system's embedding for trying to win at go, and the meta-dataset consists of examples of a winning strategy and a losing strategy for different games, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy.
-All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the function embedding.
-\par
-Alternatively, we could map from language to a meta-mapping embedding, rather than inducing it from examples of the meta-mapping.
-This corresponds to the human ability to change behavior in response to instructions.
-The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows for substantial flexibility within a unified framework.
-
-%\subsection{Boolean functions}
-%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
-Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input.
-We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs.
-\par
-%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
-%
-\section{Learning multivariate polynomials} \label{sec_poly}
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/basic_results.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
-\label{poly_basic_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{The cards domain, section \ref{sec_cards}.}
-\label{cards_basic_results}
-\end{subfigure}%
-\caption{The EML system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
-(\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}.
-The system successfully generalizes to held out polynomials.
-The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
-(\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}.
-The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
-Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
-\caption{From examples of mapping.}
-\label{poly_meta_map_results_examples}
-\end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
-\caption{From language input.}
-\label{poly_meta_map_results_language}
-\end{subfigure}
-\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
-The plots show the loss produced when evaluating the mapped embedding on the target task.
-For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
-The solid line indicates optimal performance; the dashed line indicates chance (untrained).
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_meta_map_results}
-\end{figure}
-As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
-the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
-This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
-This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
-\vspace{-0.7em}
-\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
-\ref{poly_basic_results}.
-Furthermore, it is able to do this in a sample-efficient manner, see supp.
-fig.
-\ref{supp_poly_sweep_results}.
-\par
-\vspace{-0.7em}
-\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
-\ref{poly_meta_map_results}.
-We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
-We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction.
-However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task.
-\par
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_continual_results}
-\end{figure}
-\vspace{-0.7em}
-\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
-We would like to be able to store our knowledge more efficiently, and allow for further refinement.
-Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
-\par
-A very simple solution to these problems is naturally suggested by our architecture.
-Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[c.f.][]{Rumelhart1993, Lampinen2018a}.
-That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
-To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
-We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in fig.
-\ref{poly_continual_results}.
-The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-fig.
-\ref{supp_poly_continual_results} for a more direct comparison).
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
-\par
-
-\section{A stochastic learning setting: simple card games}\label{sec_cards}
-We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
-There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
-This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
-We considered five games that are simplified analogs of various real card games (see Appendix \ref{meth_data_cards}).
-We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable.
-These are challenging manipulations, for instance trying to lose requires completely inverting a learned $Q$-function.
-\par
-In order to adapt the EML architecture, we made a very simple change.
-Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
-(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
-That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.
-We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.
-\par
-\vspace{-0.7em}
-\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
-\ref{cards_basic_results}.
-We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game.
-In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
-Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
-\par
-\vspace{-0.7em}
-\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
-For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
-In Fig.
-\ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
-This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out).
-Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good.
-\par
-\begin{figure}
-\centering
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/meta_mapping.png}
-\caption{From examples of mapping.}
-\label{cards_meta_map_results_examples}
-\end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/language_meta_mapping.png}
-\caption{From language input.}
-\label{cards_meta_map_results_language}
-\end{subfigure}
-\caption{The system generalizes to meta-mapping new tasks in the cards domain.
-The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
-For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
-When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
-This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
-The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
-The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout.
-The meta-mappings can be cued either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
-Error-bars are bootstrap 95\%-CIs.}
-\label{cards_meta_map_results}
-\end{figure}
-\section{Discussion}
-\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
-It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
-Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
-Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or a task input \citep[e.g.][]{Borsa2019}.
-\par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
-It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}.
-In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
-Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general.
-\par
-There has also been other recent interest in task (or function) embeddings.
-In simultaneous work Achille et al.
-\citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task.
-They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
-Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
-Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
-Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
-To the best of our knowledge none of the prior work has explored meta-mappings.
-\par
-\vspace{-1em}
-\paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
-We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here.
-To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
-For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}.
-Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.
-\par
-We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems generally, although it has a number of desirable characteristics.
-However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others.
-In particular, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
-Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
-\par
-%\vspace{-1em}
-%\paragraph{Conclusions:}
-\section{Conclusions}
-In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
-We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork.
-This allows transformations over task embeddings to transform the system's behavior.
-To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.
-The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
-We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
-This naturally leads to the idea of manipulating task representations just like we manipulate data.
-We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task.
-We've also shown that our approach provides a useful perspective on continual learning.
-We hope that these results will lead to the development of more powerful and flexible deep-learning models.
-\par
-%\subsubsection*{Acknowledgements}
-%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
-
-\bibliographystyle{acm}
-\bibliography{arrr}
-
-\newpage
 \appendix
@@
 \end{table}
-
-\end{document}

### 2019-05-16 writing/embedded_meta_learning_main.tex
Splitting file so that we can compile without appendix

--- 2019-05-16 writing/embedded_meta_learning.tex
@@
 \newpage
-\appendix
-
-\section{Detailed methods} \label{app_detailed_methods}
-\subsection{Datasets}
-\subsubsection{Polynomials} \label{meth_data_poly}
-We randomly sampled the train and test polynomials as follows:
-\begin{enumerate}
-\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
-\item Sample the subset of $k$ variables that are relevant from all the variables.
-\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
-\end{enumerate}
-The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial.
-The datasets were resampled every 50 epochs of training.
-\par
-\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
-\begin{itemize}
-\item Classifying polynomials as constant/non-constant.
-\item Classifying polynomials as zero/non-zero intercept.
-\item For each variable, identifying whether that variable was relevant to the polynomial.
-\end{itemize}
-We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
-\begin{itemize}
-\item Squaring polynomials (where applicable).
-\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
-\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
-\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
-\end{itemize}
-\textbf{Language:} We encoded the meta-tasks in language by sequences as follows:
-\begin{itemize}
-\item Classifying polynomials as constant/non-constant: \verb|[``is'', ``constant'']|
-\item Classifying polynomials as zero/non-zero intercept: \verb|[``is'', ``intercept_nonzero'']|
-\item For each variable, identifying whether that variable was relevant to the polynomial: \verb|[``is'', <variable-name>, ``relevant'']|
-\item Squaring polynomials: \verb|[``square'']|
-\item Adding a constant: \verb|[``add'', <value>]|
-\item Multiplying by a constant: \verb|[``multiply'', <value>]|
-\item Permuting inputs: 
-\begin{verbatim}[``permute'', <variable-name>, <variable-name>, <variable-name>, 
-<variable-name>]\end{verbatim}
-\end{itemize}
-All sequences were front-padded with ``<PAD>'' to the length of the longest sequence.
-
-\subsubsection{Card games}
-\label{meth_data_cards}
-Our card games were played with two suits, and 4 values per suit.
-In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands).
-The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available).
-We considered a variety of games which depend on different features of the hand:
-\begin{itemize}
-\item \textbf{High card:} Highest card wins.
-\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
-\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
-\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
-\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
-\end{itemize}
-We also considered three binary attributes that could be altered to produce variants of these games:
-\begin{itemize}
-\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
-\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
-\item \textbf{Switch suit:} Switches which of the suits is more valuable.
-\end{itemize}
-Any combination of these options can be applied to any of the 5 games, yielding 40 possible games.
-The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
-\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
-\par
-\textbf{Language:} We encoded the meta-tasks in language by sequences of the form \verb|[``toggle'', <attribute-name>]| for the meta-mapping tasks, and \verb|[``is'', <attribute-or-game-name>]|.
-\subsection{Model \& training} \label{app_model_details}
-\textbf{Basic task operation:}
-\begin{enumerate}
-\item A training dataset $D_1$ of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings.
-Another set of (possibly unlabeled) inputs $D_2$ is provided and embedded.
-\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
-\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
-\item The system is trained end-to-end to minimize the loss on these outputs.
-\end{enumerate}
-The model is trained to minimize 
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]
-\textbf{Meta-task operation:}
-\begin{enumerate}
-\item A meta-dataset of (source-task-embedding, target-task-embedding) pairs, $D_1$, is collected. Another dataset $D_2$ (possibly only source tasks) is provided.
-\item The meta network $\mathcal{M}$ maps this set of (source, target) task-embedding pairs to a function embedding.
-\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
-\item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
-\end{enumerate}
-The model is trained to minimize
-\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, f_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
-where $\mathfrak{L}$ is $\ell_2$ loss, and $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
-Note that there are two kinds of hold-out in the training of this system.
-First, some of the trained tasks are held-out on each training step (i.e.
-$D_2$), in order to force the system to generalize rather than just memorize.
-Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.
-\par
-\textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.
-\par
-
-\subsubsection{Detailed hyper-parameters}
-\begin{table}
-\centering
-\begin{tabular}{|c||c|c|c|}
-\hline 
-& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\\hline
-\hline
-$Z$-dimension & 512 & 512 & 512 \\\hline
-$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\\hline 
-$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
-$\mathcal{L}$ architecture & \multicolumn{1}{p{2.5cm}|}{2-layer LSTM + 2 fully-connected} & - & \multicolumn{1}{p{2.5cm}|}{1-layer LSTM + 2 fully-connected} \\\hline 
-$\mathcal{L}$ num. hidden units & 512 & - & 512 \\\hline 
-$\mathcal{O}$ num. layers & 1 & 1 & 3 \\\hline 
-$\mathcal{O}$ num. hidden units & - & - & 512 \\\hline 
-$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\\hline 
-$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\\hline 
-$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
-$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\\hline 
-$F$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
-$F$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
-Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $\mathcal{T}$, $\mathcal{M}$, $\mathcal{L}$, $F$, and sigmoid for meta-classification outputs.} \\\hline
-Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification.}\\\hline
-\hline
-Optimizer & Adam & RMSProp & RMSProp \\\hline
-Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\\hline
-Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\\hline
-L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\\hline
-L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\\hline
-L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\\hline
-L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\\hline
-L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\\hline
-Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\\hline
-Num. training epochs & 4000 & 3000 & 40000 \\\hline
-Num. runs & 5 & 5 & 10 \\ \hline
-\hline
-Num. base tasks (eval) & 60 & 100 & 36 or 20 \\\hline
-Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\\hline
-Num. meta classifications & 6 & - & 8  \\\hline
-Num. meta mappings & 20 & - & 3  \\\hline
-Num. new base tasks & 40 & 30 & 4 or 20 \\\hline 
-Num. new meta mappings & 16 & - & 0  \\\hline
-Num. new meta classifications &  \multicolumn{3}{c|}{0} \\\hline
-Base dataset size & \multicolumn{3}{c|}{1024} \\\hline
-Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\\hline
-$\mathcal{M}$ batch size & 50 & 128 & 768 \\\hline
-\end{tabular}
-\caption{Detailed hyperparameter specification for different experiments.
-A ``-'' indicates a parameter that does not apply to that experiment.
-Where only one value is given, it applied to all the experiments discussed.
-As a reminder: the shared representational space is denoted by $Z$.
-Input encoder: $\mathcal{I}: \text{input} \rightarrow Z$.
-Output decoder $\mathcal{O}: Z \rightarrow \text{output}$.
-Target encoder $\mathcal{T}: \text{targets} \rightarrow Z$.
-Meta-network $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- takes a set of (input embedding, target embedding) pairs and produces a function embedding.
-Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters.
-Task network $F: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$.
-Where language was used to cue meta-mappings, it was processed by language encoder: $\mathcal{L}: \text{natural language} \rightarrow Z$.
-} \label{supp_hyperparameter_table}
-\end{table}
-See table \ref{supp_hyperparameter_table} for detailed architectural description and hyperparameters for each experiment.
-Hyperparameters were generally found by a heuristic search, where mostly only the optimizer, learning rate annealing schedule, and number of training epochs were varied, not the architectural parameters.
-Some of the parameters take the values they do for fairly arbitrary reasons, e.g.
-the continual learning experiments were run with the current polynomial hyperparameters before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.
-\par
-Each epoch consisted of a separate learning step on each task (both base and meta), in a random order.
-In each task, the meta-learner would receive only a subset (the ``batch size`` above) of the examples to generate a function embedding, and would have to generalize to the remainder of the examples in the dataset.
-The embeddings of the tasks for the meta-learner were computed once per epoch, so as the network learned over the course of the epoch, these embeddings would get ``stale,'' but this did not seem to be too detrimental.
-\par
-The results reported in the figures in this paper are averages across multiple runs, with different trained and held-out tasks (in the polynomial case) and different network initializations (in all cases), to ensure the robustness of the findings.
-\par
-
-\subsection{Source repositories}
-The full code for the experiments and analyses can be found on github:
-\begin{itemize}
-\item \url{https://github.com/lampinen/polynomials}
-    \begin{itemize}
-        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
-    \end{itemize}
-\item \url{https://github.com/lampinen/meta_cards} 
-\end{itemize}
-%%(will be made available in the de-anonymized version.)
-\section{Card game $t$-SNE} \label{app_cards_tsne}
-We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
-In fig.
-\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
-The embeddings show systematic grouping by game attributes.
-In fig.
-\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
-\par
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
-(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
-\label{fig_cards_tsne_basic}
-\end{figure}%
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
-\label{fig_cards_tsne_full}
-\end{figure}
-
-\section{Supplemental figures}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.66\textwidth]{figures/continual/continual_learning_direct_comparison.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding.
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
-\label{supp_poly_continual_results}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
-\label{supp_poly_integration_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{The cards domain, section \ref{sec_cards}.}
-\label{supp_cards_integration_results}
-\end{subfigure}%
-\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
-\label{supp_integration_results}
-\end{figure}
-
-\section{Numerical results} \label{app_numerical_results}
-In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures.
-Tables were generated with stargazer \citep{Hlavac2018}.
-\par
-
-\subsection{Polynomials}
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} ccccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
-\hline \\[-1.8ex]
-EML & Trained & 0.014 & 0.011 & 0.017 \\
-EML & Held out & 0.218 & 0.153 & 0.291 \\
-Untrained EML network & Trained & 5.735 & 4.787 & 6.787 \\
-Untrained EML network & Held out & 5.968 & 4.967 & 6.975 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
-\hline \\[-1.8ex] 
-EML & Trained mapping, on trained task & 0.084 & 0.08 & 0.088 \\ 
-EML & Trained mapping, on held-out task & 1.664 & 1.345 & 2.077 \\ 
-EML & Held-out mapping, on trained task & 1.07 & 0.996 & 1.14 \\ 
-EML & Held-out mapping, on held-out task & 1.52 & 1.444 & 1.604 \\ 
-Untrained EML network & Trained mapping, on trained task & 13.378 & 12.213 & 14.84 \\ 
-Untrained EML network & Trained mapping, on held-out task & 15.469 & 13.778 & 17.303 \\ 
-Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.766 & 8.687 \\ 
-Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.165 & 9.127 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
-\hline \\[-1.8ex] 
-Language & Trained mapping, on trained task & 0.515 & 0.483 & 0.552 \\ 
-Language & Trained mapping, on held-out task & 2.244 & 1.921 & 2.623 \\ 
-Language & Held-out mapping, on trained task & 2.072 & 1.958 & 2.19 \\ 
-Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
-Untrained EML network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
-Untrained EML network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
-Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
-Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
-\hline \\[-1.8ex] 
-\end{tabular}
-\caption{Table for meta-mapping results from language, figure \ref{poly_meta_map_results_language}}
-\end{table}
-
-\subsection{Cards}
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_run\_type & named\_game\_type & is\_new\_game & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
-\hline \\[-1.8ex]
-Random 50\% holdout & High card & Trained & 0.53 & 0.521 & 0.541 \\
-Random 50\% holdout & High card & Held out & 0.441 & 0.42 & 0.462 \\
-Random 50\% holdout & Match & Trained & 0.537 & 0.524 & 0.55 \\
-Random 50\% holdout & Match & Held out & 0.539 & 0.523 & 0.556 \\
-Random 50\% holdout & Pairs & Trained & 0.521 & 0.504 & 0.536 \\
-Random 50\% holdout & Pairs & Held out & 0.453 & 0.434 & 0.47 \\
-Random 50\% holdout & Straight flush & Trained & 0.525 & 0.508 & 0.54 \\
-Random 50\% holdout & Straight flush & Held out & 0.484 & 0.466 & 0.502 \\
-Random 50\% holdout & Blackjack & Trained & 0.582 & 0.557 & 0.603 \\
-Random 50\% holdout & Blackjack & Held out & 0.492 & 0.468 & 0.513 \\
-Targeted 10\% holdout & High card & Trained & 0.527 & 0.518 & 0.536 \\
-Targeted 10\% holdout & Match & Trained & 0.536 & 0.526 & 0.546 \\
-Targeted 10\% holdout & Pairs & Trained & 0.522 & 0.512 & 0.531 \\
-Targeted 10\% holdout & Straight flush & Trained & 0.524 & 0.509 & 0.538 \\
-Targeted 10\% holdout & Straight flush & Held out & 0.361 & 0.332 & 0.39 \\
-Targeted 10\% holdout & Blackjack & Trained & 0.586 & 0.575 & 0.598 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for basic meta-learning, figure \ref{cards_basic_results}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
-\hline \\[-1.8ex]
-Trained & Targeted 10\% holdout & High card & 0.531 \\
-Trained & Targeted 10\% holdout & Match & 0.541 \\
-Trained & Targeted 10\% holdout & Pairs & 0.532 \\
-Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
-Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
-Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
-Trained & Random 50\% holdout & High card & 0.531 \\
-Held out & Random 50\% holdout & High card & 0.396 \\
-Trained & Random 50\% holdout & Match & 0.541 \\
-Held out & Random 50\% holdout & Match & 0.541 \\
-Trained & Random 50\% holdout & Pairs & 0.532 \\
-Held out & Random 50\% holdout & Pairs & 0.37 \\
-Trained & Random 50\% holdout & Straight flush & 0.536 \\
-Held out & Random 50\% holdout & Straight flush & 0.452 \\
-Trained & Random 50\% holdout & Blackjack & 0.595 \\
-Held out & Random 50\% holdout & Blackjack & 0.456 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_game\_type & expected\_reward \\
-\hline \\[-1.8ex]
-Blackjack & 0.592 \\
-High card & 0.531 \\
-Match & 0.541 \\
-Pairs & 0.532 \\
-Straight flush & 0.536 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for playing optimal rewards for basic meta-learning, solid lines in figure \ref{cards_basic_results}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
-\hline \\[-1.8ex]
-Trained & Targeted 10\% holdout & High card & 0.531 \\
-Trained & Targeted 10\% holdout & Match & 0.541 \\
-Trained & Targeted 10\% holdout & Pairs & 0.532 \\
-Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
-Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
-Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
-Trained & Random 50\% holdout & High card & 0.531 \\
-Held out & Random 50\% holdout & High card & 0.396 \\
-Trained & Random 50\% holdout & Match & 0.541 \\
-Held out & Random 50\% holdout & Match & 0.541 \\
-Trained & Random 50\% holdout & Pairs & 0.532 \\
-Held out & Random 50\% holdout & Pairs & 0.37 \\
-Trained & Random 50\% holdout & Straight flush & 0.536 \\
-Held out & Random 50\% holdout & Straight flush & 0.452 \\
-Trained & Random 50\% holdout & Blackjack & 0.595 \\
-Held out & Random 50\% holdout & Blackjack & 0.456 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
-\hline \\[-1.8ex]
-Targeted 10\% holdout & Switch suits & Trained & 0.523 & 0.512 & 0.534 \\
-Targeted 10\% holdout & Switch suits & Held out & 0.234 & 0.196 & 0.273 \\
-Targeted 10\% holdout & Losers & Trained & 0.532 & 0.511 & 0.546 \\
-Targeted 10\% holdout & Losers & Held out & 0.289 & 0.241 & 0.322 \\
-Random 50\% holdout & Switch suits & Trained & 0.528 & 0.521 & 0.533 \\
-Random 50\% holdout & Switch suits & Held out & 0.375 & 0.368 & 0.382 \\
-Random 50\% holdout & Losers & Trained & 0.531 & 0.523 & 0.538 \\
-Random 50\% holdout & Losers & Held out & 0.427 & 0.417 & 0.436 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for meta-mapping from examples, figure \ref{cards_meta_map_results_examples}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
-\hline \\[-1.8ex]
-Language (random 50\%) & Switch suits & Trained & 0.525 & 0.52 & 0.534 \\
-Language (random 50\%) & Switch suits & Held out & 0.371 & 0.353 & 0.384 \\
-Language (random 50\%) & Losers & Trained & 0.524 & 0.521 & 0.527 \\
-Language (random 50\%) & Losers & Held out & 0.426 & 0.413 & 0.44 \\
-Language (targeted 10\%) & Switch suits & Trained & 0.531 & 0.52 & 0.542 \\
-Language (targeted 10\%) & Switch suits & Held out & 0.225 & 0.146 & 0.305 \\
-Language (targeted 10\%) & Losers & Trained & 0.539 & 0.533 & 0.544 \\
-Language (targeted 10\%) & Losers & Held out & 0.341 & 0.308 & 0.367 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table for meta-mapping from language, figure \ref{cards_meta_map_results_language}}
-\end{table}
-
-\begin{table}[H]
-\scriptsize
-\centering
-\begin{tabular}{@{\extracolsep{5pt}} cccc}
-\\[-1.8ex]\hline
-\hline \\[-1.8ex]
-named\_run\_type & named\_meta\_task & is\_new & expected\_reward \\
-\hline \\[-1.8ex]
-Targeted 10\% holdout & Switch suits & Trained & 0.298 \\
-Targeted 10\% holdout & Switch suits & Held out & 0.368 \\
-Targeted 10\% holdout & Losers & Trained & -0.446 \\
-Targeted 10\% holdout & Losers & Held out & -0.463 \\
-Random 50\% holdout & Switch suits & Trained & 0.37 \\
-Random 50\% holdout & Switch suits & Held out & 0.278 \\
-Random 50\% holdout & Losers & Trained & -0.465 \\
-Random 50\% holdout & Losers & Held out & -0.444 \\
-\hline \\[-1.8ex]
-\end{tabular}
-\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in figure \ref{cards_meta_map_results}}
-\end{table}
+% comment the following to compile without appendix but with references
+\include{embedded_meta_learning_appendix}
 

### 2019-05-19 writing/embedded_meta_learning_appendix.tex
Anonymized
Organization & numerical results with all runs

@@
 \appendix
-
+The supplemental material is organized as follows: in section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses.
+In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
+In section \ref{app_supp_figures} we provide supplemental figures.
+In section \ref{app_lesion_results} we provide some lesion studies.
+In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper.
 \section{Detailed methods} \label{app_detailed_methods}
@@
 The full code for the experiments and analyses can be found on github:
-\begin{itemize}
-\item \url{https://github.com/lampinen/polynomials}
-    \begin{itemize}
-        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
-    \end{itemize}
-\item \url{https://github.com/lampinen/meta_cards} 
-\end{itemize}
-%%(will be made available in the de-anonymized version.)
+%%\begin{itemize}
+%%\item \url{https://github.com/lampinen/polynomials}
+%%    \begin{itemize}
+%%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
+%%    \end{itemize}
+%%\item \url{https://github.com/lampinen/meta_cards} 
+%%\end{itemize}
+(will be made available in the de-anonymized version.)
 \section{Card game $t$-SNE} \label{app_cards_tsne}
@@
 
-\section{Supplemental figures}
+\section{Supplemental figures} \label{app_supp_figures}
 \begin{figure}[H]
@@
 
-\section{Lesion experiments}
+\section{Lesion experiments} \label{app_lesion_results}
 
@@
 \hline \\[-1.8ex]
-EML & Trained & 0.014 & 0.011 & 0.017 \\
-EML & Held out & 0.218 & 0.153 & 0.291 \\
-Untrained EML network & Trained & 5.735 & 4.787 & 6.787 \\
-Untrained EML network & Held out & 5.968 & 4.967 & 6.975 \\
+EML & Trained & 0.015 & 0.012 & 0.018 \\
+EML & Held out & 0.246 & 0.188 & 0.308 \\
+Untrained EML network & Trained & 5.735 & 4.823 & 6.74 \\
+Untrained EML network & Held out & 5.968 & 4.984 & 6.991 \\
 \hline \\[-1.8ex]
@@
 \hline \\[-1.8ex]
-EML & Trained mapping, on trained task & 0.084 & 0.08 & 0.088 \\ 
-EML & Trained mapping, on held-out task & 1.664 & 1.345 & 2.077 \\ 
-EML & Held-out mapping, on trained task & 1.07 & 0.996 & 1.14 \\ 
-EML & Held-out mapping, on held-out task & 1.52 & 1.444 & 1.604 \\ 
-Untrained EML network & Trained mapping, on trained task & 13.378 & 12.213 & 14.84 \\ 
-Untrained EML network & Trained mapping, on held-out task & 15.469 & 13.778 & 17.303 \\ 
-Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.766 & 8.687 \\ 
-Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.165 & 9.127 \\ 
+EML & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
+EML & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
+EML & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
+EML & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
+Untrained EML network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
+Untrained EML network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
+Untrained EML network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
+Untrained EML network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
 \hline \\[-1.8ex]

### 2019-05-19 writing/embedded_meta_learning_appendix.tex
Learning curves + unshared Z comparison

@@
 (will be made available in the de-anonymized version.)
-\section{Card game $t$-SNE} \label{app_cards_tsne}
-We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
-In fig.
-\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
-The embeddings show systematic grouping by game attributes.
-In fig.
-\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
-\par
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
-(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
-\label{fig_cards_tsne_basic}
-\end{figure}%
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
-\label{fig_cards_tsne_full}
-\end{figure}
-
 \section{Supplemental figures} \label{app_supp_figures}
@@
 \label{supp_poly_sweep_results}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves.png}
+\caption{Learning curves for meta-mappings in the polynomials domain.
+Although the results seem to be leveling off at the end, we found that generalization performance was slightly increasing or stable in this region, which may have interesting implications about the structure of these tasks \citep{Lampinen2019}.}
+\label{supp_poly_meta_learning_curves}
 \end{figure}
@@
 
+\section{Card game $t$-SNE} \label{app_cards_tsne}
+We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
+In fig.
+\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
+The embeddings show systematic grouping by game attributes.
+In fig.
+\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
+\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
+(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
+\label{fig_cards_tsne_basic}
+\end{figure}%
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
+\label{fig_cards_tsne_full}
+\end{figure}
+
 \section{Lesion experiments} \label{app_lesion_results}
+In this section we consider a few variations of the architecture, to justify the choices made in the paper.
 
-\subsection{Hyper network vs. conditioned task network}
+\subsection{Shared $Z$ vs. separate task-embedding and data-embedding space} \label{app_lesion_results_shared_z}
+Instead of having a shared $Z$ where data and tasks are embedded, why not have a separate embedding space for data, tasks, and so on?
+There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}.
+In this section, we further show that training with a separate task encoding space worsens performance, see fig.
+\ref{supp_lesion_shared_z_fig}.
+This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see fig.
+\ref{supp_lesion_shared_z_learn_fig}.
+(It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_results_unshared_vs_shared.png}
+\caption{Having a separate embedding space for tasks results in worse performance on meta-mappings. (Results are from only 1 run.)}
+\label{supp_lesion_shared_z_fig}
+\end{figure}
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves_with_separate.png}
+\caption{Having a separate embedding space for tasks results in noisier, slower learning of meta-mappings. (Results are from only 1 run.)}
+\label{supp_lesion_shared_z_learn_fig}
+\end{figure}
+
+\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
 Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
@@
 \includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
-\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks.}
+\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks. Results are from only 2 runs.}
 \label{supp_lesion_hyper}

### 2019-05-19 writing/embedded_meta_learning_main.tex
Learning curves + unshared Z comparison

@@
 \par
-Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$.
+Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$ (see appendix \ref{app_lesion_results_shared_z} for some discussion of why this space should be shared).
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
@@
 \par
-To write this explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which we wish to generate a predicted output $\hat{y}$.
-This output would be generated as follows:
+More explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which to predict an output $\hat{y}$.
+$\hat{y}$ would be generated as follows:
 \[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
@@
 However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others.
-In particular, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
+(Note that we compare some variations in appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
 Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.

### 2019-05-20 meta_RL_analyses.Rmd
Comparing different methods of performing a new task -- why is meta-mapping useful?

@@
     geom_point(stat="summary", fun.y=mean, size=2) +
-    scale_color_manual(values=c("#555093", "#f38f22"))
+    scale_color_manual(values=c("#555093", "#f38f22", "#88e1e1", "#008822"))
 
@@
 summary_plot(language_d %>%
-               filter(epoch == 0),
-             "game_type", "reward", "is_new_game",
+               filter(epoch == 0, run_type == "meta_batch_128"),
+             "named_game_type", "reward", "is_new_game",
              optimal_baselines) +
@@
   separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
-  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
+  mutate(is_new_source = check_if_new_game(run_type, source),
+         is_new_target = check_if_new_game(run_type, target),
+         is_new =  is_new_source | is_new_target,
          is_new = factor(is_new, labels=c("Trained", "Held out")),
@@
 ```
+
+# Comparing different ways of performing a new task: from examples, from language, or from meta-mappings
+
+```{r}
+summary_plot(bind_rows(lang_meta_d %>%
+                         filter(epoch == 0,
+                                is_new_target & !is_new_source,
+                                meta_task == "toggle_losers",
+                                run_type == "meta_batch_128") %>%
+                         mutate(result_type = "Meta-mapping old task (language cue)") %>%
+                         select(result_type, target, run, reward) %>%
+                         rename(game_str=target),
+                       reward_d %>%                         
+                         filter(epoch == 0,
+                                is_new_game != "Trained",
+                                run_type == "basic") %>%
+                         mutate(result_type = "Examples of new task") %>%
+                         select(result_type, game_str, run, reward),
+                       language_d %>%                         
+                         filter(epoch == 0,
+                                is_new_game != "Trained",
+                                run_type == "meta_batch_128") %>%
+                         mutate(result_type = "Language directly") %>%
+                         select(result_type, game_str, run, reward),
+                       meta_d %>%
+                         filter(epoch == 0,
+                                is_new_target & !is_new_source,
+                                meta_task =="toggle_losers",
+                                run_type == "meta_batch_128") %>%
+                         mutate(result_type = "Meta-mapping old task (example cue)") %>%
+                         select(result_type, target, run, reward) %>%
+                         rename(game_str=target)) %>%
+               mutate(named_run_type = "Targeted 10% holdout",
+                      result_type=str_wrap(result_type, width=20),
+                      result_type=factor(result_type, levels=sort(unique(result_type))[c(1,3,4,2)])), # ugh
+             "result_type", "reward", "result_type") +
+  guides(color=F) +
+  labs(x="Performing from ...", y="Average reward on held-out tasks")
+
+#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
+ggsave("writing/figures/why_meta_mapping.png", width=6, height=3)
+
+```
+
 # embeddings

### 2019-05-21 writing/embedded_meta_learning_appendix.tex
More learning curves
Clarity tweaks

@@
 \appendix
-The supplemental material is organized as follows: in section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses.
+The supplemental material is organized as follows: In section \ref{app_why_meta_mapping} we discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
 In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
@@
 In section \ref{app_lesion_results} we provide some lesion studies.
+In section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses.
 In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper.
+\par
+
+\section{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
+Why are meta-mappings between tasks useful?
+To answer this, we consider various ways of adapting to a new task in figure \ref{fig_why_meta_mapping} (based on results from the cards domain, section \ref{sec_cards}).
+The system could adapt from seeing examples of the new task, but this requires going out and collecting data, which may be expensive and does not allow zero-shot adaptation.
+Alternatively, the system could perform the new task via a meta-mapping from a prior learned task, where the meta-mapping is either induced from examples of the meta-mapping, or from language.
+Finally, the system could perform a new task from language alone, if it is trained to map instructions to tasks.
+\par
+To address this latter possibility, we trained a version of the model where we included training the language system to produce embeddings for the basic tasks (while simultaneously training the system on all the other objectives, such as performing the tasks from examples, in order to provide the strongest possible structuring of the system's knowledge for the strongest possible comparison).
+We compare this model's performance at held-out tasks to that of systems learning from examples of the new task directly, or from meta-mapping, see fig.
+\ref{fig_why_meta_mapping}.
+\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/why_meta_mapping.png}
+\caption{Comparison of a variety of methods for performing one of the 10\% held-out tasks in the more difficult hold-out set in the cards domain.
+There are a number of ways the system could adapt to a new task: from seeing example of the new task, from hearing the new task described from language alone, or from leveraging its knowledge about prior tasks via meta-mappings (in this case, from the non-losers variations of the same games).
+The meta-mappings offer a happy medium between the other two alternatives -- they only require cached knowledge of prior tasks, rather than needing to collect experience on the task before a policy can be derived, but they outperform a system that simply tries to construct the task embedding from a description alone.
+Language alone is not nearly as rich a cue as knowledge of how a new task relates to prior tasks.}
+\label{fig_why_meta_mapping}
+\end{figure}
+These results demonstrate the advantage of meta-mapping.
+While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation.
+Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks.
+Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz.
+prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language).
+That is, meta-mapping has the advantage of requiring no new data collection, like performing from language alone, but results in much better performance by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par
+
+\section{Supplemental figures} \label{app_supp_figures}
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
+\caption{The system is able to infer polynomials from only seeing a few data points (i.e.
+evaluations of the polynomial), despite the fact that during training it always saw 50.
+A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
+\label{supp_poly_sweep_results}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/base_learning_curves.png}
+\caption{Learning curves for basic regression in the polynomials domain.}
+\label{supp_poly_basic_learning_curves}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves.png}
+\caption{Learning curves for meta-mappings in the polynomials domain.
+Although the results seem to be leveling off at the end, we found that generalization performance was slightly increasing or stable in this region, which may have interesting implications about the structure of these tasks \citep{Lampinen2019}.}
+\label{supp_poly_meta_learning_curves}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/continual/continual_learning_direct_comparison.png}
+\caption{Continual learning in the polynomials domain: a more direct comparison.
+Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
+Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding.
+Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
+\label{supp_poly_continual_results}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
+\caption{The polynomials domain, section \ref{sec_poly}.}
+\label{supp_poly_integration_results}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
+\caption{The cards domain, section \ref{sec_cards}.}
+\label{supp_cards_integration_results}
+\end{subfigure}%
+\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
+\label{supp_integration_results}
+\end{figure}
+
+\section{Card game $t$-SNE} \label{app_cards_tsne}
+We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
+In fig.
+\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
+The embeddings show systematic grouping by game attributes.
+In fig.
+\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
+\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
+(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
+\label{fig_cards_tsne_basic}
+\end{figure}%
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
+\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
+\label{fig_cards_tsne_full}
+\end{figure}
+
+\section{Lesion experiments} \label{app_lesion_results}
+In this section we consider a few variations of the architecture, to justify the choices made in the paper. \par
+
+\subsection{Shared $Z$ vs. separate task-embedding and data-embedding space} \label{app_lesion_results_shared_z}
+Instead of having a shared $Z$ where data and tasks are embedded, why not have a separate embedding space for data, tasks, and so on?
+There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}.
+In this section, we further show that training with a separate task encoding space worsens performance, see fig.
+\ref{supp_lesion_shared_z_fig}.
+This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see fig.
+\ref{supp_lesion_shared_z_learn_fig}.
+(It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_results_unshared_vs_shared.png}
+\caption{Having a separate embedding space for tasks results in worse performance on meta-mappings. (Results are from only 1 run.)}
+\label{supp_lesion_shared_z_fig}
+\end{figure}
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves_with_separate.png}
+\caption{Having a separate embedding space for tasks results in noisier, slower learning of meta-mappings. (Results are from only 1 run.)}
+\label{supp_lesion_shared_z_learn_fig}
+\end{figure}
+
+\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
+Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
+Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks.
+We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks.
+While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
+\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks. Results are from only 2 runs.}
+\label{supp_lesion_hyper}
+\end{figure}
+
 \section{Detailed methods} \label{app_detailed_methods}
@@
 \textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.
-\par
+The systems that were trained from language were also trained with the example-based meta-tasks.\par
 
@@
 (will be made available in the de-anonymized version.)
-\section{Supplemental figures} \label{app_supp_figures}
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
-\caption{The system is able to infer polynomials from only seeing a few data points (i.e.
-evaluations of the polynomial), despite the fact that during training it always saw 50.
-A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
-\label{supp_poly_sweep_results}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves.png}
-\caption{Learning curves for meta-mappings in the polynomials domain.
-Although the results seem to be leveling off at the end, we found that generalization performance was slightly increasing or stable in this region, which may have interesting implications about the structure of these tasks \citep{Lampinen2019}.}
-\label{supp_poly_meta_learning_curves}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/continual/continual_learning_direct_comparison.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding.
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
-\label{supp_poly_continual_results}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
-\label{supp_poly_integration_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{The cards domain, section \ref{sec_cards}.}
-\label{supp_cards_integration_results}
-\end{subfigure}%
-\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
-\label{supp_integration_results}
-\end{figure}
-
-\section{Card game $t$-SNE} \label{app_cards_tsne}
-We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
-In fig.
-\ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
-The embeddings show systematic grouping by game attributes.
-In fig.
-\ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
-\par
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
-(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
-\label{fig_cards_tsne_basic}
-\end{figure}%
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
-\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
-\label{fig_cards_tsne_full}
-\end{figure}
-
-\section{Lesion experiments} \label{app_lesion_results}
-In this section we consider a few variations of the architecture, to justify the choices made in the paper.
-
-\subsection{Shared $Z$ vs. separate task-embedding and data-embedding space} \label{app_lesion_results_shared_z}
-Instead of having a shared $Z$ where data and tasks are embedded, why not have a separate embedding space for data, tasks, and so on?
-There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}.
-In this section, we further show that training with a separate task encoding space worsens performance, see fig.
-\ref{supp_lesion_shared_z_fig}.
-This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see fig.
-\ref{supp_lesion_shared_z_learn_fig}.
-(It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/poly/meta_results_unshared_vs_shared.png}
-\caption{Having a separate embedding space for tasks results in worse performance on meta-mappings. (Results are from only 1 run.)}
-\label{supp_lesion_shared_z_fig}
-\end{figure}
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves_with_separate.png}
-\caption{Having a separate embedding space for tasks results in noisier, slower learning of meta-mappings. (Results are from only 1 run.)}
-\label{supp_lesion_shared_z_learn_fig}
-\end{figure}
-
-\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
-Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
-Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks.
-We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks.
-While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
-\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks. Results are from only 2 runs.}
-\label{supp_lesion_hyper}
-\end{figure}
-
 \section{Numerical results} \label{app_numerical_results}

### 2019-05-21 writing/embedded_meta_learning_main.tex
Clarity tweaks

@@
 Meta-mapping allows us to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
-\par
+(See appendix \ref{app_why_meta_mapping} for a discussion of why this is better than e.g.
+conditioning on a task description.)\par
 Meta-mappings can be cued in different ways, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
@@
 \vspace{-0.75em}
-The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data.
-In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior based on examples).
+Why have a completely shared space $Z$ for data and tasks?
+The primary advantage is that it allows for arbitrary mappings between these entities.
+In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explain behavior), or tasks to tasks (change behavior).
 This is a step closer to the flexible reasoning humans display.
@@
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[c.f.][]{Kumaran2016}.
+This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016}.
 \par
@@
 Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[c.f.][]{Rumelhart1993, Lampinen2018a}.
-That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
+This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
+That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
 To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.

### 2019-05-22 writing/embedded_meta_learning_appendix.tex
Clarity, clarity, clarity

@@
 \appendix
-The supplemental material is organized as follows: In section \ref{app_why_meta_mapping} we discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
+The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
 In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
@@
 
-\section{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
+\section{Clarifying meta-mappings} \label{app_clarifying_meta_mapping}
+\subsection{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
 Why are meta-mappings between tasks useful?
@@
 \par
+These results demonstrate the advantage of meta-mapping.
+While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation.
+Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks.
+Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz.
+prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language).
+That is, meta-mapping has the advantage of requiring no new data collection, like performing from language alone, but results in much better performance by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par
+\subsection{A definitional note}
+When we discussed meta-mappings in the main task, we equivocated between tasks and behaviors for the sake of brevity.
+For a perfect model, this is somewhat justifiable, because each task will have a corresponding optimal behavior, and the sytem's embedding of the task will be precisely the embedding which produces this optimal behavior.
+However, behavior-irrelevant details of the task, like the color of the board, may not be embedded, so this should not really be thought of as a task-to-task mapping.
+This problem is exacerbated when the system is imperfect, e.g.
+during learning.
+It is thus more precise to distinguish between a ground-truth meta-mapping, which maps tasks to tasks, and the computational approach to achieving that meta-mapping, which really maps between representations which combine both task and behavior.
+\par
 \begin{figure}[H]
@@
 \end{figure}
-These results demonstrate the advantage of meta-mapping.
-While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation.
-Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks.
-Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz.
-prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language).
-That is, meta-mapping has the advantage of requiring no new data collection, like performing from language alone, but results in much better performance by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par
 

### 2019-05-22 writing/embedded_meta_learning_main.tex
Clarity, clarity, clarity

@@
 Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them.
-The challenges are in the form of meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks.
+The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot.
 We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
@@
 We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
-that they can exhibit zero-shot remapping of behavior on new tasks.
+that they can exhibit zero-shot remapping of behavior to adapt to new tasks.
 \end{abstract}
@@
 \par
-We argue that these meta-mappings are a useful way to think about human-like flexibility.
+We argue that these task-to-task meta-mappings are a useful way to think about human-like flexibility.
 For example, a go-playing system should be able to adapt to a different board size.
@@
 Humans can exploit this to play on a different board without retraining, but deep learning models generally have no way of achieving this.
-Similarly, suppose an agent knows how to navigate a town.
-It should be able to adapt to changes of the environment such as street closures.
 We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
-While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility.
-Meta-mapping allows us to adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
-(See appendix \ref{app_why_meta_mapping} for a discussion of why this is better than e.g.
-conditioning on a task description.)\par
-Meta-mappings can be cued in different ways, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'').
-Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
+While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture this human flexibility.
+We can adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
+We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
+Their are different ways this adaptation can be cued, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a discussion of why this is better than e.g.
+conditioning on a task description.).
+Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
 \par
@@
 \section{Embedded Meta-Learning (EML) architecture}
-EML architectures are composed of two components: 
-\vspace{-0.75em}
+To address these challenges, we propose EML architectures, which are composed of two components: 
+\vspace{-1em}
 \begin{enumerate} \setlength \itemsep{0em}
@@
 The primary advantage is that it allows for arbitrary mappings between these entities.
-In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explain behavior), or tasks to tasks (change behavior).
-This is a step closer to the flexible reasoning humans display.
+In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explain behavior), or meta-map tasks to tasks (change behavior).
+This is a step closer to the human flexibility.
 \par
@@
 \par
-A basic forward pass through the system would proceed as follows.
-First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
+\vspace{-0.5em}
+\paragraph{Basic operation:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
 These examples are fed to $\mathcal{M}$ to produce a function embedding.
@@
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-However, the system is not limited to simply mapping inputs to outputs.
+\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
 The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
-For example, suppose we have some task embedding $z_{old} \in Z$, and a meta-mapping embedding $z_{\text{meta}} \in Z$, e.g.
-from $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{source,0},z_{target,0}, ...\right) \right\}\right)$.
+Because tasks are embedded in $Z$, this allows for meta-mappings.
+For example, suppose we have some embedding $z_{go} \in Z$ for the task of playing go.
+We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of winning and trying-to-lose: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{checkers},z_{checkers,lose}\right), ...
+\right\}\right)$.
 Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
-\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{old}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-For example, if the $z_{old}$ is the system's embedding for trying to win at go, and the meta-dataset consists of examples of a winning strategy and a losing strategy for different games, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy.
-All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the function embedding.
+\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{go}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+Then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.
+All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
 \par
@@
 \end{subfigure}
-\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
+\caption{The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
 The plots show the loss produced when evaluating the mapped embedding on the target task.
-For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
-The solid line indicates optimal performance; the dashed line indicates chance (untrained).
+For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
+The solid line indicates optimal performance; the dashed line is chance (untrained).
 Error-bars are bootstrap 95\%-CIs.}
@@
 \paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
-\ref{poly_basic_results}.
-Furthermore, it is able to do this in a sample-efficient manner, see supp.
+\ref{poly_basic_results} (with good sample-efficiency, see supp.
 fig.
-\ref{supp_poly_sweep_results}.
+\ref{supp_poly_sweep_results}).
 \par

### 2019-05-22 writing/embedded_meta_learning_main.tex
Notation, notation, notation

@@
 $\hat{y}$ would be generated as follows:
-\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
-where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
+\[\hat{y} = \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
+where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
 \right\}\right)\right)\]
@@
 We define our total loss computed on some dataset $D_2$ as:
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
+\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
 \paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
@@
 Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
-\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{go}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
 Then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.

### 2019-05-22 writing/embedded_meta_learning_appendix.tex
Part II

@@
 The model is trained to minimize 
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]
+\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
+where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]
 \textbf{Meta-task operation:}
@@
 The model is trained to minimize
-\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, f_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
-where $\mathfrak{L}$ is $\ell_2$ loss, and $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
+\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, F_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
+where $\mathfrak{L}$ is $\ell_2$ loss, and $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
+\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
 Note that there are two kinds of hold-out in the training of this system.

### 2019-05-23 writing/embedded_meta_learning_main.tex
Continuing clarity tweaks

@@
 \par
-We argue that these task-to-task meta-mappings are a useful way to think about human-like flexibility.
-For example, a go-playing system should be able to adapt to a different board size.
-Go on a large board and go on a small board share a great deal of structure.
-Humans can exploit this to play on a different board without retraining, but deep learning models generally have no way of achieving this.
+We argue that these task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to a variation on that task.
+For example, go on a large board and go on a small board share a great deal of structure.
+Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way of achieving this.
 We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
-While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture this human flexibility.
-We can adapt to task alterations zero-shot, that is, without seeing a single example from the new task.
+While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
+We can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task.
 We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-Their are different ways this adaptation can be cued, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a discussion of why this is better than e.g.
-conditioning on a task description.).
+Their are different ways this adaptation can be cued, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
 Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 \par
-Without training on these mappings, of course, the system will not be able to execute them well.
+Without training on meta-mappings, of course, the system will not be able to execute them well.
 However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below.
@@
 The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves.
+The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on functions that represent tasks.
 This is related to the idea of a homoiconicity, defined above.
@@
 Because tasks are embedded in $Z$, this allows for meta-mappings.
-For example, suppose we have some embedding $z_{go} \in Z$ for the task of playing go.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of winning and trying-to-lose: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{checkers},z_{checkers,lose}\right), ...
+For example, suppose we have an embedding $z_{go} \in Z$ for the task of playing go.
+We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of winning and trying-to-lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{checkers},z_{checkers,lose}\right), ...
 \right\}\right)$.
-Then we can generate a new task embedding $\hat{z}_{new} \in Z$ as:
+We can generate a new task embedding $\hat{z}_{new} \in Z$:
 \[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-Then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
 We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.

### 2019-05-23 writing/embedded_meta_learning_main.tex
Beginning to incorporate Jay's comments

@@
 
-\section{Meta-mappings}
-We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output.
-These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
+\section{Meta-mapping}
+%Can cut "the task"s in go sentence if needed
+We propose the meta-mapping challenge.
+We define a meta-mapping as a task, or mapping, that takes a task as an input, output, or both.
+These include mappings from tasks to language (explaining), mappings from language to tasks (following instructions), and mappings from tasks to tasks (adapting behavior).
 While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
 \par
-We argue that these task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to a variation on that task.
-For example, go on a large board and go on a small board share a great deal of structure.
+We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to a variation on that task.
+For example, the task of playing go on a large board is closely related to the task of playing go on a small board.
 Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way of achieving this.
@@
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
-We can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task.
+Given appropriate conditioning (see below), we can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
 We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-Their are different ways this adaptation can be cued, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
+There are different ways this adaptation can be cued, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
 Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 The primary advantage is that it allows for arbitrary mappings between these entities.
-In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explain behavior), or meta-map tasks to tasks (change behavior).
-This is a step closer to the human flexibility.
+In addition to basic tasks, the system could in principle learn to perform meta-mappings to follow instructions or change behavior.
+This is a step closer to human-like flexibility.
 \par
@@
 More formally, we take a \emph{functional} perspective on learning.
-A datum can be represented by a constant function which outputs it.
-(For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions.
-We can then interpret most machine learning tasks as a mapping of functions to functions.
+A datum can be represented by a constant function which outputs that datum.
+(For example, each point in the latent space of an autoencoder can be thought of this way.) Adopting this perspective allows us to interpret model inputs or outputs as functions.
+Most machine learning tasks then become a mapping of functions to functions.
 The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on functions that represent tasks.
+The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on functions that represent tasks.
 This is related to the idea of a homoiconicity, defined above.
-Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem.
+Under this perspective, basic tasks and meta-mappings are really the same type of problem.
 \par
-Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$ (see appendix \ref{app_lesion_results_shared_z} for some discussion of why this space should be shared).
+Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$ (see appendix \ref{app_lesion_results_shared_z} for discussion of why this space should be shared).
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
@@
 These transformations are performed by a system with the following components (see Fig.
-\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which takes a set of (input embedding, target embedding) pairs and produces a function embedding.
+\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
 $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters.
@@
 \vspace{-0.5em}
-\paragraph{Basic operation:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
+\paragraph{Basic meta-learning:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
 These examples are fed to $\mathcal{M}$ to produce a function embedding.
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a second dataset, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
 This system can be trained end-to-end on targets for the second dataset.
+(Having two distinct datasets forces generalization at the meta-learning level).
 See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
@@
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
+%\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
 The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
@@
 We can generate a new task embedding $\hat{z}_{new} \in Z$:
+%\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+%This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
+We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.
+All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
+\par
+\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
+The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
+Because tasks are embedded in $Z$, this allows for meta-mappings.
+For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing go.
+We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
+\right\}\right)$.
+We can generate a new task embedding $\hat{z}_{new} \in Z$:
 \[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.
+This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
+We could then evaluate whether the system loses with this $\hat{z}_{new}$ strategy.
 All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
@@
 The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The colored dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
+The orange dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
 The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.

### 2019-05-23 writing/embedded_meta_learning_main.tex
More comments/clarity

@@
 This system can be trained end-to-end on targets for the second dataset.
-(Having two distinct datasets forces generalization at the meta-learning level).
-See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
-\par
+(Having two distinct datasets forces generalization at the meta-learning level, see appendix
+ref{app_clarifying_holdouts}.) See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 
 More explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which to predict an output $\hat{y}$.
@@
 \vspace{-0.7em}
-\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
 \ref{poly_basic_results} (with good sample-efficiency, see supp.
@@
 \vspace{-0.7em}
-\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
 \ref{poly_meta_map_results}.
@@
 \vspace{-0.7em}
-\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
 \ref{cards_basic_results}.
@@
 \vspace{-0.7em}
-\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
 For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.

### 2019-05-23 writing/embedded_meta_learning_appendix.tex
Clarifying hold-outs

@@
 \end{figure}
+\subsection{Clarifying hold-outs} \label{app_clarifying_holdouts}
+There are several distinct types of hold-outs in the basic training of our architecture:
+\begin{enumerate}
+\item On each basic task, some of the data ($D_1$) is fed to the meta-network $\mathcal{M}$ while some ($D_2$) is held out.
+This encourages the model to actually infer the underlying function, rather than just memorizing the examples.
+\item There are also truly held-out tasks that the system has never seen in training. These are the held-out tasks that we evaluate on at the end of training and report results.
+\end{enumerate}
+This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization.
+There are also meta-mappings which have never been encountered during training, and those are the meta-mappings we evaluate on at hte end of training.
+We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.
 
@@
 \[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
-Note that there are two kinds of hold-out in the training of this system.
-First, some of the trained tasks are held-out on each training step (i.e.
-$D_2$), in order to force the system to generalize rather than just memorize.
-Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.
-\par
+Note that there are three kinds of hold-out in the training of this system, see section 
+ref{app_clarifying_holdouts}. \par
 \textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.

### 2019-05-23 writing/embedded_meta_learning_appendix.tex
Further tweaks

@@
 
-\section{Clarifying meta-mappings} \label{app_clarifying_meta_mapping}
+\section{Clarifying meta-mapping} \label{app_clarifying_meta_mapping}
 \subsection{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
@@
 This encourages the model to actually infer the underlying function, rather than just memorizing the examples.
-\item There are also truly held-out tasks that the system has never seen in training. These are the held-out tasks that we evaluate on at the end of training and report results.
+\item There are also truly held-out tasks that the system has never seen in training.
+These are the held-out tasks that we evaluate on at the end of training and that are plotted in the ``Held out'' sections in the main plots.
 \end{enumerate}
 This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization.
-There are also meta-mappings which have never been encountered during training, and those are the meta-mappings we evaluate on at hte end of training.
+There are also meta-mappings which have never been encountered during training, which we evaluate on at the end of training, those are the meta-mappings which are plotted in the ``held out'' section in the relevant plots.
 We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.
+\par
 

### 2019-05-23 writing/embedded_meta_learning_main.tex
Polynomial example that would be nice to have.
Cut note
Cutting back to length

@@
 
+\vspace{-0.75em} % section
 \section{Introduction}
+\vspace{-0.5em} % section
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}.
@@
 \section{Meta-mapping}
+\vspace{-0.5em} % section
 %Can cut "the task"s in go sentence if needed
@@
 \section{Embedded Meta-Learning (EML) architecture}
+\vspace{-0.5em} % section
 To address these challenges, we propose EML architectures, which are composed of two components: 
@@
 In addition to basic tasks, the system could in principle learn to perform meta-mappings to follow instructions or change behavior.
-This is a step closer to human-like flexibility.
 \par
@@
 \end{figure}
+\looseness=-1
 More formally, we take a \emph{functional} perspective on learning.
@@
 This system can be trained end-to-end on targets for the second dataset.
-(Having two distinct datasets forces generalization at the meta-learning level, see appendix
-ref{app_clarifying_holdouts}.) See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 
+(Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.) See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
+\par
 More explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which to predict an output $\hat{y}$.
@@
 \paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
-The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
+Anything that is embedded in $Z$ can be transformed using the same system.
 Because tasks are embedded in $Z$, this allows for meta-mappings.
-For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing go.
+For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.
 We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
@@
 \[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+\looseness=-1
 This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
 We could then evaluate whether the system loses with this $\hat{z}_{new}$ strategy.
-All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
+This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding.
 \par
@@
 \section{Learning multivariate polynomials} \label{sec_poly}
+\vspace{-0.5em} % section
 \begin{figure}
@@
 \end{figure}
+%% Cut example if necessary
 As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
 the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
+For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2, 1.3, -4; 2)$, and be evaluated on its output for points like $(-1, -1, 0.5, 0.3)$.
 This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
@@
 \section{A stochastic learning setting: simple card games}\label{sec_cards}
+\vspace{-0.5em} % section
 We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
@@
 \par
+%% Can cut The hand is explicitly ..., maybe some other stuff
 In order to adapt the EML architecture, we made a very simple change.
@@
 \section{Discussion}
+\vspace{-0.5em} % section
 \paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
@@
 \section{Conclusions}
+\vspace{-0.5em} % section
 In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
@@
 % comment the following to compile without appendix but with references
-\include{embedded_meta_learning_appendix}
+%\include{embedded_meta_learning_appendix}
 

### 2019-05-23 writing/embedded_meta_learning_main.tex
Continuing to tweak: D1 vs D2 and related work

@@
 In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Santoro2016, Finn2017a, Finn2018, Stadie2018}.
 However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
@@
 We define a meta-mapping as a task, or mapping, that takes a task as an input, output, or both.
-These include mappings from tasks to language (explaining), mappings from language to tasks (following instructions), and mappings from tasks to tasks (adapting behavior).
+These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
 While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
-\par
-We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to a variation on that task.
+(We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) \par
+We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to some variation on that task.
 For example, the task of playing go on a large board is closely related to the task of playing go on a small board.
-Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way of achieving this.
-We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose.
+Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way to achieve this.
+We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose, or trying to achieve some orthogonal goal.
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
@@
 \vspace{-0.5em}
-\paragraph{Basic meta-learning:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$.
+\paragraph{Basic meta-learning:} To perform a basic task, a dataset $D_1$ is encoded by $\mathcal{I}$ and $\mathcal{T}$.
 These examples are fed to $\mathcal{M}$ to produce a function embedding.
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset $D_2$ of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
 This system can be trained end-to-end on targets for the second dataset.
-(Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.) See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
+Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.
+See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
 \par
@@
 the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
-For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2, 1.3, -4; 2)$, and be evaluated on its output for points like $(-1, -1, 0.5, 0.3)$.
+For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2.1, 1.3, -4; 2.1)$, and be evaluated on its output for points like $(-1, -1.3, 0.5, 0.3)$.
 This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
@@
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
 \ref{poly_meta_map_results}.
@@
 We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction.
-However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task.
+The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language instruction.
+It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping.
 \par
@@
 \end{figure}
-\section{Discussion}
+\section{Discussion} \label{sec_discussion}
 \vspace{-0.5em} % section
@@
 % comment the following to compile without appendix but with references
-%\include{embedded_meta_learning_appendix}
+\include{embedded_meta_learning_appendix}
 

### 2019-05-23 writing/embedded_meta_learning_appendix.tex
Cutting back to length
Tweak tweak tweak

@@
 The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
+In section \ref{app_supp_figures} we provide supplemental figures.
 In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
-In section \ref{app_supp_figures} we provide supplemental figures.
 In section \ref{app_lesion_results} we provide some lesion studies.
@@
 \par
-
+\newpage
 \section{Supplemental figures} \label{app_supp_figures}
@@
 
-\section{Lesion experiments} \label{app_lesion_results}
+\section{Architecture experiments} \label{app_lesion_results}
 In this section we consider a few variations of the architecture, to justify the choices made in the paper. \par
@@
 (It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
+\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
+Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
+Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks.
+We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks.
+While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par
 \begin{figure}[H]
@@
 \end{figure}
-
-\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
-Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input.
-Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks.
-We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks.
-While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par
 \begin{figure}[H]
@@
 \begin{enumerate}
-\item A meta-dataset of (source-task-embedding, target-task-embedding) pairs, $D_1$, is collected. Another dataset $D_2$ (possibly only source tasks) is provided.
+\item A meta-dataset of (source-task-embedding, target-task-embedding) pairs, $D_1$, is collected.
+Another dataset $D_2$ (possibly only source tasks) is provided.
+(All embeddings included in $D_1$ during training are for basic tasks that have themselves been trained, to ensure that there is useful signal.
+During evaluation, the embeddings in $D_1$ are for tasks that have been trained on, but those in $D_2$ may be new.
 \item The meta network $\mathcal{M}$ maps this set of (source, target) task-embedding pairs to a function embedding.
@@
 \[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
-Note that there are three kinds of hold-out in the training of this system, see section 
-ref{app_clarifying_holdouts}. \par
+Note that there are three kinds of hold-out in the training of this system, see section \ref{app_clarifying_holdouts}. \par
 \textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.

### 2019-05-23 writing/embedded_meta_learning_main.tex
Tweak tweak tweak

@@
 \par
+\looseness=-1
 There are a number of advantages to representing knowledge about data and tasks together.
 In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Santoro2016, Finn2017a, Finn2018, Stadie2018}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
 However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
@@
 (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands.
+This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing task demands.
 We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
@@
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016}.
+This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}.
 \par
@@
 \vspace{-0.5em} % section
-\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018}.
+\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
@@
 \paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
-We hope that our work will inspire more exploration of behavioral adaptation in areas beyond the simple domains we considered here.
+We hope that our work will inspire more exploration of behavioral adaptation, in areas beyond the simple domains we considered here.
 To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
@@
 \vspace{-0.5em} % section
-In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks.
+In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
 We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork.
+To address this, we've proposed explicitly representing tasks by function embeddings, and deriving the computation from these embeddings via a HyperNetwork.
 This allows transformations over task embeddings to transform the system's behavior.
-To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space.
+This is analogous to how transformations over data perform basic tasks.
+Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
 The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par

### 2019-05-23 writing/embedded_meta_learning_main.tex
Schematic tweaks

@@
 Without training on meta-mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below.
+However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-task distribution, as we demonstrate below.
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
@@
 \begin{tikzpicture}[auto, scale=0.75]
-\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
+\node [dashblock] at (0.2, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
 
@@
 
-\node [conc] at (-7, -4) (perc) {\textbf{Input}};
+\node [conc] at (-7, -3.5) (perc) {\textbf{Input}};
 %%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-7, 4) (act) {\textbf{Output}};
-\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
+\node [conc] at (-7.2, 4) (act) {\textbf{Output}};
+\node [conc] at (-7.2, 2.8) (tar) {\textbf{Targets}};
+\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
 %%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
-\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
-\path [line] (perc.north) to (IE.south);
+\node [block, text width=2.2cm] at (-4, 3) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
+\node [block, text width=2cm] at (-4, 1.5) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
+\path [line] (perc.north) to (IE.west);
 %%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
-\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
+\path [line] (IE.east) to (rep.south west);
 %%\path [line] (LE.east) to (rep.west);
 \path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
-\path [line] (OD.north) to (act.south);
-\path [line] (act.south) to (TE.north);
+\path [line] (OD.north) to (act.east);
+\path [line] (tar.south) to (TE.west);
 \path [line] (TE.east) to (rep.north west);
@@
 
-\node [dashblock] at (0, -2.5) (collection) {
+\node [dashblock] at (0.2, -2.5) (collection) {
 \(\left\{
@@
 
-\node [block] at (4, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
+\node [block] at (4.2, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
 \path [line] (collection.south) to [out=-90, in=-90] (meta.south);
@@
 
-\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
-\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(F: \text{rep} \rightarrow \text{rep}\)};
+\node [block] at (4.2, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
+\node [block, dash pattern=on 9pt off 2pt] at (0.2, 2) (transform) {\(F: \bm{Z} \rightarrow \bm{Z}\)};
 

### 2019-07-25 writing/embedded_meta_learning_main.tex
Fixing bug, preprint
Starting response

@@
 \documentclass{article}
+
+\PassOptionsToPackage{numbers}{natbib}
 
@@
 Stanford University\\
-\textt{lampinen@stanford.edu}\\
+\texttt{lampinen@stanford.edu}\\
 \And
@@
 Stanford University\\
-\textt{mcclelland@stanford.edu}\\
+\texttt{mcclelland@stanford.edu}\\
 }
@@
 We can generate a new task embedding $\hat{z}_{new} \in Z$:
-\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+\[\hat{z}_{new} = F_{z_{\text{meta}}}(z_{game1}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
 \looseness=-1

### 2019-07-25 writing/nips_submission/response/EML_response.tex
Starting response

--- 2019-05-23 writing/embedded_meta_learning_main.tex
@@
 
-\usepackage{neurips_2019}
+\usepackage{neurips_2019_author_response}
 
@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage[pdfborder={0 0 0}]{hyperref}       % hyperlinks
+\usepackage{hyperref}       % hyperlinks
 \usepackage{url}            % simple URL typesetting
@@
 
-\usepackage{subcaption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm}
-\usepackage{relsize}
-\usepackage{natbib}
-\usepackage{float}
-\usepackage{tikz}
-
-\usetikzlibrary{shapes,arrows}
-
-\tikzstyle{block} = [rectangle, draw, thick, align=center, rounded corners]
-\tikzstyle{boundingbox} = [very thick, dotted, gray]
-\tikzstyle{dashblock} = [rectangle, draw, thick, align=center, dashed]
-\tikzstyle{conc} = [ellipse, draw, thick, dashed, align=center]
-\tikzstyle{netnode} = [circle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
-\tikzstyle{relunode} = [rectangle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
-\tikzstyle{line} = [draw, very thick, -latex']
-
-\setlength{\parskip}{1em}
-\setlength{\parindent}{0em}
-
-\setcitestyle{square}
+\usepackage{lipsum}
 
 \begin{document}
-\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
-\author{%
-Andrew K. Lampinen\\
-Department of Psychology\\
-Stanford University\\
-\textt{lampinen@stanford.edu}\\
-\And
-James L. McClelland\\
-Department of Psychology\\
-Stanford University\\
-\textt{mcclelland@stanford.edu}\\
-}
-\date{}
-\maketitle
-
-\begin{abstract}
-How can deep learning systems flexibly reuse their knowledge?
-Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them.
-The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot.
-We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
-We therefore draw inspiration from meta-learning and functional programming to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
-EML architectures are applicable to any type of machine learning task, including supervised learning and reinforcement learning.
-We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
-that they can exhibit zero-shot remapping of behavior to adapt to new tasks.
-\end{abstract}
-
-\vspace{-0.75em} % section
-\section{Introduction}
-\vspace{-0.5em} % section
-Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}.
-One fundamental reason for this is that humans are aware of what we are trying to compute and why.
-By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
-That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations.
-\par
-\looseness=-1
-There are a number of advantages to representing knowledge about data and tasks together.
-In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
-However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
-For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
-zero-shot).
-Deep learning systems at present generally lack this representational flexibility.
-\par
-In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e.
-mappings between tasks (see below).
-This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
-To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
-(A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
-This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing task demands.
-We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
-EML may also offer other benefits, such as a useful framework for continual learning.
-We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
-\par
-
-\section{Meta-mapping}
-\vspace{-0.5em} % section
-%Can cut "the task"s in go sentence if needed
-We propose the meta-mapping challenge.
-We define a meta-mapping as a task, or mapping, that takes a task as an input, output, or both.
-These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior).
-While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
-(We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) \par
-We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to some variation on that task.
-For example, the task of playing go on a large board is closely related to the task of playing go on a small board.
-Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way to achieve this.
-We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose, or trying to achieve some orthogonal goal.
-While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
-Given appropriate conditioning (see below), we can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
-We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-There are different ways this adaptation can be cued, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
-Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
-\par
-
-\section{Embedded Meta-Learning (EML) architecture}
-\vspace{-0.5em} % section
-To address these challenges, we propose EML architectures, which are composed of two components: 
-\vspace{-1em}
-\begin{enumerate} \setlength \itemsep{0em}
-\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
-\end{enumerate}
-\vspace{-0.75em}
-Why have a completely shared space $Z$ for data and tasks?
-The primary advantage is that it allows for arbitrary mappings between these entities.
-In addition to basic tasks, the system could in principle learn to perform meta-mappings to follow instructions or change behavior.
-\par
-Without training on meta-mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same data/task distribution, as we demonstrate below.
-For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}.
-\par
-\begin{figure}
-\centering
-\begin{tikzpicture}[auto, scale=0.75]
-\node [dashblock] at (0, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
-
-% inputs, outputs
-
-\draw [boundingbox] (-9, -5) rectangle (-2.1, 5); 
-\node [text=gray] at (-8.5, 4.65) {\textbf{I/O}};
-
-\node [conc] at (-7, -4) (perc) {\textbf{Input}};
-%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-7, 4) (act) {\textbf{Output}};
-\node [block, text width=2cm] at (-4.5, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
-%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 2.5) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
-\node [block, text width=2cm] at (-5.5, 1) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
-\path [line] (perc.north) to (IE.south);
-%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
-\path [line] ([xshift=-0.05cm, yshift=-0.05cm]IE.north east) to (rep.south west);
-%%\path [line] (LE.east) to (rep.west);
-\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
-\path [line] (OD.north) to (act.south);
-\path [line] (act.south) to (TE.north);
-\path [line] (TE.east) to (rep.north west);
-
-% meta
-\draw [boundingbox] (-1.9, 5) rectangle (6, -5); 
-\node [text=gray] at (-0.4, 4.7) {\textbf{Meta Learner}};
-
-\node [dashblock] at (0, -2.5) (collection) {
-\(\left\{
-\begin{matrix}
-(z_{in,0}, z_{out,0}),\\
-(z_{in,1}, z_{out,1}),\\
-$\vdots$
-\end{matrix}\right\}\)};
-\path [line] (rep.south) to (collection);
-\path [line] ([xshift=-1em]rep.south) to (collection);
-\path [line] ([xshift=1em]rep.south) to (collection);
-
-\node [block] at (4, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
-\path [line] (collection.south) to [out=-90, in=-90] (meta.south);
-\path [line] (meta.west) to (rep.east);
-
-% hyper
-
-\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
-\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(F: \text{rep} \rightarrow \text{rep}\)};
-
-\path [draw, ->, very thick] (rep.north east) to (hyper.south);
-\path [draw, ->, very thick] (hyper.west) to (transform.north east);
-\path [draw, ->, very thick] ([xshift=-1em]transform.south) to ([xshift=-1em]rep.north);
-\path [draw, ->, very thick] ([xshift=1em]rep.north) to ([xshift=1em]transform.south);
-
-\end{tikzpicture}
-\caption{The EML architecture.
-Blocks with solid edges denote learnable deep networks, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
-Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
-both language and vision.
-See appendix \ref{app_model_details} for details.} \label{architecture_fig}
-\end{figure}
-\looseness=-1
-More formally, we take a \emph{functional} perspective on learning.
-A datum can be represented by a constant function which outputs that datum.
-(For example, each point in the latent space of an autoencoder can be thought of this way.) Adopting this perspective allows us to interpret model inputs or outputs as functions.
-Most machine learning tasks then become a mapping of functions to functions.
-The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on functions that represent tasks.
-This is related to the idea of a homoiconicity, defined above.
-Under this perspective, basic tasks and meta-mappings are really the same type of problem.
-\par
-Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$ (see appendix \ref{app_lesion_results_shared_z} for discussion of why this space should be shared).
-Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Model outputs are decoded from $Z$ by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
-Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
-These transformations are performed by a system with the following components (see Fig.
-\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
-$\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters.
-$F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.
-\par
-\vspace{-0.5em}
-\paragraph{Basic meta-learning:} To perform a basic task, a dataset $D_1$ is encoded by $\mathcal{I}$ and $\mathcal{T}$.
-These examples are fed to $\mathcal{M}$ to produce a function embedding.
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset $D_2$ of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
-This system can be trained end-to-end on targets for the second dataset.
-Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.
-See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
-\par
-More explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which to predict an output $\hat{y}$.
-$\hat{y}$ would be generated as follows:
-\[\hat{y} = \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
-where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
-\right\}\right)\right)\]
-This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$.
-In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
-We define our total loss computed on some dataset $D_2$ as:
-\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-%\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
-The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
-Because tasks are embedded in $Z$, this allows for meta-mappings.
-For example, suppose we have an embedding $z_{go} \in Z$ for the task of playing go.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of winning and trying-to-lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{checkers},z_{checkers,lose}\right), ...
-\right\}\right)$.
-We can generate a new task embedding $\hat{z}_{new} \in Z$:
-%\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-%This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.
-All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
-\par
-\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
-Anything that is embedded in $Z$ can be transformed using the same system.
-Because tasks are embedded in $Z$, this allows for meta-mappings.
-For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
-\right\}\right)$.
-We can generate a new task embedding $\hat{z}_{new} \in Z$:
-\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-\looseness=-1
-This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
-We could then evaluate whether the system loses with this $\hat{z}_{new}$ strategy.
-This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding.
-\par
-Alternatively, we could map from language to a meta-mapping embedding, rather than inducing it from examples of the meta-mapping.
-This corresponds to the human ability to change behavior in response to instructions.
-The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows for substantial flexibility within a unified framework.
-
-%\subsection{Boolean functions}
-%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
-Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input.
-We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs.
-\par
-%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
-%
-\section{Learning multivariate polynomials} \label{sec_poly}
-\vspace{-0.5em} % section
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/basic_results.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
-\label{poly_basic_results}
-\end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{The cards domain, section \ref{sec_cards}.}
-\label{cards_basic_results}
-\end{subfigure}%
-\caption{The EML system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
-(\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}.
-The system successfully generalizes to held out polynomials.
-The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
-(\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}.
-The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The orange dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
-Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
-\caption{From examples of mapping.}
-\label{poly_meta_map_results_examples}
-\end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
-\caption{From language input.}
-\label{poly_meta_map_results_language}
-\end{subfigure}
-\caption{The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
-The plots show the loss produced when evaluating the mapped embedding on the target task.
-For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
-The solid line indicates optimal performance; the dashed line is chance (untrained).
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_meta_map_results}
-\end{figure}
-%% Cut example if necessary
-As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
-the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms).
-For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2.1, 1.3, -4; 2.1)$, and be evaluated on its output for points like $(-1, -1.3, 0.5, 0.3)$.
-This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables).
-This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
-\vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
-\ref{poly_basic_results} (with good sample-efficiency, see supp.
-fig.
-\ref{supp_poly_sweep_results}).
-\par
-\vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
-\ref{poly_meta_map_results}.
-We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
-We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language instruction.
-It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping.
-\par
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_continual_results}
-\end{figure}
-\vspace{-0.7em}
-\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
-We would like to be able to store our knowledge more efficiently, and allow for further refinement.
-Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
-\par
-A very simple solution to these problems is naturally suggested by our architecture.
-Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
-That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
-To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
-We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in fig.
-\ref{poly_continual_results}.
-The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-fig.
-\ref{supp_poly_continual_results} for a more direct comparison).
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
-\par
-
-\section{A stochastic learning setting: simple card games}\label{sec_cards}
-\vspace{-0.5em} % section
-We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
-There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
-This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
-We considered five games that are simplified analogs of various real card games (see Appendix \ref{meth_data_cards}).
-We also considered several binary options that could be applied to the games, including trying to lose instead of trying to win, or switching which suit was more valuable.
-These are challenging manipulations, for instance trying to lose requires completely inverting a learned $Q$-function.
-\par
-%% Can cut The hand is explicitly ..., maybe some other stuff
-In order to adapt the EML architecture, we made a very simple change.
-Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
-(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
-That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.
-We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.
-\par
-\vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
-\ref{cards_basic_results}.
-We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game.
-In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
-Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
-\par
-\vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
-For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
-In Fig.
-\ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
-This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out).
-Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good.
-\par
-\begin{figure}
-\centering
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/meta_mapping.png}
-\caption{From examples of mapping.}
-\label{cards_meta_map_results_examples}
-\end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/language_meta_mapping.png}
-\caption{From language input.}
-\label{cards_meta_map_results_language}
-\end{subfigure}
-\caption{The system generalizes to meta-mapping new tasks in the cards domain.
-The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
-For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
-When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
-This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
-The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
-The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout.
-The meta-mappings can be cued either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
-Error-bars are bootstrap 95\%-CIs.}
-\label{cards_meta_map_results}
-\end{figure}
-\section{Discussion} \label{sec_discussion}
-\vspace{-0.5em} % section
-\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
-It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
-Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
-Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or a task input \citep[e.g.][]{Borsa2019}.
-\par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
-It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}.
-In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture.
-Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general.
-\par
-There has also been other recent interest in task (or function) embeddings.
-In simultaneous work Achille et al.
-\citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task.
-They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
-Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}.
-Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
-Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
-To the best of our knowledge none of the prior work has explored meta-mappings.
-\par
- \vspace{-1em}
-\paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
-We hope that our work will inspire more exploration of behavioral adaptation, in areas beyond the simple domains we considered here.
-To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
-For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}.
-Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.
-\par
-We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems generally, although it has a number of desirable characteristics.
-However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others.
-(Note that we compare some variations in appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
-Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
-\par
-%\vspace{-1em}
-%\paragraph{Conclusions:}
-\section{Conclusions}
-\vspace{-0.5em} % section
-In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
-We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-To address this, we've proposed explicitly representing tasks by function embeddings, and deriving the computation from these embeddings via a HyperNetwork.
-This allows transformations over task embeddings to transform the system's behavior.
-This is analogous to how transformations over data perform basic tasks.
-Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
-The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
-We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
-This naturally leads to the idea of manipulating task representations just like we manipulate data.
-We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task.
-We've also shown that our approach provides a useful perspective on continual learning.
-We hope that these results will lead to the development of more powerful and flexible deep-learning models.
-\par
-%\subsubsection*{Acknowledgements}
-%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
-
-\bibliographystyle{acm}
-\bibliography{arrr}
-
-\newpage
-% comment the following to compile without appendix but with references
-\include{embedded_meta_learning_appendix}
-
+We thank the reviewers for their thorough reviews. We have attemtped to respond below. \par
+\textbf{Major points:} \par
+\textbf{Minor points:} We have fixed typos in the explanation of the meta-mapping.\par
 \end{document}

### 2019-07-26 writing/nips_submission/response/EML_response.tex
Continuing to draft

@@
 \begin{document}
-We thank the reviewers for their thorough reviews. We have attemtped to respond below. \par
-\textbf{Major points:} \par
-\textbf{Minor points:} We have fixed typos in the explanation of the meta-mapping.\par
+We thank the reviewers for their thoughtful and thorough reviews. We have attemtped to respond below. \par
+\textbf{miniImageNet:} \par
+\looseness=-1
+\textbf{Novelty and contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to thing about transfer in terms of meta-mappings and task transformations.
+The architecture we propose is designed with this idea in mind.
+It is true that previous work has considered task embeddings (some of the works suggested by the reviewers we have mentioned in the related works section, but some we were not familiar with, we appreciate the pointers).
+Most of these have developed some way of embedding a dataset into some latent space.
+However, what we think is fundamentally novel about our architecture is that \textbf{we use the same latent space for the dataset as we use for an individual input to the network}.
+This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces for basic inputs and tasks.
+We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose.
+While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance in these domains too.
+We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work.
+As we point out in the future directions, we do not expect the exact approach we've proposed to be the best way of solving these problems.
+However, it does provide a useful starting point.
+We think that the primary contribution of this work is highlighting the idea of meta-mappings for transfer, and providing some starting points for how to approach them by taking a functional perspective, which we hope will inspire future work.
+\par
+\looseness=-1
+\textbf{Meta-mapping training details:} Consider a meta-mapping task, like trying to map from winning games to losing them.
+For concreteness, imagine we have three tasks, chess, poker, and go, and losing variations of each.
+We generate task embeddings for each game, e.g.
+$z_{poker}$, by applying the meta network $\mathcal{M}$ to experiences from the game.
+We randomly select some games (poker, go) to use as training examples to generate the meta-mapping parameters, and hold-out the rest (chess) to make the generated meta-mapping generalize.
+We thus generate a dataset $D = {(z_{poker}, z_{lose-poker}), (z_{go}, z_{lose-go})}$.
+Per above, we process this dataset using the same meta-network $\mathcal{M}$ to get a function embedding $z_{lose} = \mathcal{M}(D)$ for the meta-mapping.
+We can then pass this embedding through the hypernetwork $\mathcal{H}$ in order to parameterize a mapping $F_{z_lose}$ which attempts to map game strategies to strategies for the losing variation of that game.
+We use this mapping to transform each input embedding and compute the $\ell_2$ loss between the result and the target function embedding, e.g.
+for chess the loss would be $(F_{z_lose}(z_{chess}) - z_{lose-chess})^2$.
+We minimize this loss across all held-out and training examples (using both accelerates learning).
+We continue with the next meta-mapping.
+\par
+\looseness=-1
+To evaluate performance on a meta-mapping, we generate the training dataset as above, but we do not assume we have an embedding for the held-out targets.
+For example, we may know how to play chess via a task embedding $z_{chess}$, but our goal is to figure how to lose at chess.
+So we take $\hat{z}_{lose-chess} = F_{z_{lose}}(z_{chess})$, and use it to play losing chess by parameterizing a function $F_{\hat{z}_{lose-chess}}$.
+We then evaluate this function's actual performance on losing chess, which tells us the true quality of the meta-mapping.
+We hope this clarifies the training and evaluation of meta-mappings.
+We have revised the manuscript to be more explicit about this and fix typos noted by reviewer 1, and if our manuscript is accepted we will also incorporate more details of tasks and training from the appendix as space allows.
+\par
+\looseness=-1
+\textbf{Datasets:} We will release the code for this paper on github and provide links in the de-anonymized version, and both the polynomials and cards tasks and baselines are implemented as stand-alone python modules that other researchers can use.
+As we mention in the future directions, creating complex datasets for meta-mappings is an important future direction.
+\par
+\looseness=-1
+\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
+We explored some variations in appendix D to justify a few hoices, and showed that some more parsimonious choices resulted in worse performance.
+However, we acknowledge that we have not explored the full space of models or algorithms which could be used to approach this problem, and we see this as an important direction for future work.
+This problem is not exactly a standard supervised problem because you predict rewards for several actions, but only observe the reward for the action you execute, but we are not using a full DQN.
+We have revised the manuscript to clarify this point.
+\par
+\looseness=-1
+\textbf{Natural language:} was simply used as a meta-mapping cue in the main text.
+Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters.
+In appendix A we compare to specifying new tasks directly from language.
+Meta-mappings perform better, presumably by leveraging task knowledge.
+\par
+\looseness=-1
+\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work use this.
+We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model.
+For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume even up to hundreds of thousands of tasks.
+We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it.
+\par
+
 \end{document}

### 2019-07-26 writing/embedded_meta_learning_main.tex
Further tweaking

@@
 This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
-We could then evaluate whether the system loses with this $\hat{z}_{new}$ strategy.
+To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guess and the embedding of the losing task.
+Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy.
 This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding.
@@
 We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language instruction.
+The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language cue to the meta-mapping.
 It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping.
@@
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
-(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
+(A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, because the outcome is only observed for the action you take, it is not a standard supervised task.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
 That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.

### 2019-07-26 writing/nips_submission/response/EML_response.tex
Further tweaking

@@
 We thank the reviewers for their thoughtful and thorough reviews. We have attemtped to respond below. \par
-\textbf{miniImageNet:} \par
+\textbf{miniImageNet:} TBD. \par
 \looseness=-1
@@
 However, what we think is fundamentally novel about our architecture is that \textbf{we use the same latent space for the dataset as we use for an individual input to the network}.
-This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces for basic inputs and tasks.
+This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces.
 We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose.
@@
 However, we acknowledge that we have not explored the full space of models or algorithms which could be used to approach this problem, and we see this as an important direction for future work.
-This problem is not exactly a standard supervised problem because you predict rewards for several actions, but only observe the reward for the action you execute, but we are not using a full DQN.
-We have revised the manuscript to clarify this point.
+The problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN.
+We have revised the manuscript to clarify these points.
 \par
 \looseness=-1
-\textbf{Natural language:} was simply used as a meta-mapping cue in the main text.
+\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text.
 Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters.
 In appendix A we compare to specifying new tasks directly from language.
-Meta-mappings perform better, presumably by leveraging task knowledge.
+Meta-mapping works better, presumably by better using task knowledge.
 \par
 \looseness=-1
-\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work use this.
+\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this.
 We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model.
-For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume even up to hundreds of thousands of tasks.
-We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it.
+For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks.
+We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the text.
 \par
-
 \end{document}

### 2019-07-27 writing/nips_submission/response/EML_response.tex
Tweaks, meta arch details

@@
 \looseness=-1
-\textbf{Novelty and contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to thing about transfer in terms of meta-mappings and task transformations.
+\textbf{Contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
 The architecture we propose is designed with this idea in mind.
@@
 This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces.
-We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose.
-While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance in these domains too.
+We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the meta-mappings we propose.
+While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance with other algorithms too.
 We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work.
@@
 \looseness=-1
-\textbf{Meta-mapping training details:} Consider a meta-mapping task, like trying to map from winning games to losing them.
-For concreteness, imagine we have three tasks, chess, poker, and go, and losing variations of each.
+\textbf{Meta-mapping details:} For a concrete training example, imagine trying to map from winning tasks to losing them.
+Suppose we have three tasks, chess, poker, and go, and losing variations of each.
 We generate task embeddings for each game, e.g.
@@
 We minimize this loss across all held-out and training examples (using both accelerates learning).
-We continue with the next meta-mapping.
+We then proceed with the next meta-mapping.
 \par
@@
 \looseness=-1
-\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
+\textbf{Architecture:} The meta network processes each data point independently for two layers, max pools elementwise across them, and then applies two more layers of processing.
+The reviewers noted that some of the architectural choices seemed arbitrary.
 We explored some variations in appendix D to justify a few hoices, and showed that some more parsimonious choices resulted in worse performance.
@@
 \textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this.
-We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model.
+This approach does requires storing an embedding vector per task, but many other approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model.
 For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks.

### 2019-07-29 writing/nips_submission/response/EML_response.tex
Revised with some comments from Jay

--- 2019-07-26 writing/nips_submission/response/EML_response.tex
@@
 
-\usepackage{lipsum}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bm}
+
+\usepackage{wrapfig}
+
+\usepackage{tikz}
+
+\usetikzlibrary{shapes,arrows}
+
+\tikzstyle{block} = [rectangle, draw, thick, align=center, rounded corners]
+\tikzstyle{boundingbox} = [very thick, dotted, gray]
+\tikzstyle{dashblock} = [rectangle, draw, thick, align=center, dashed]
+\tikzstyle{conc} = [ellipse, draw, thick, dashed, align=center]
+\tikzstyle{netnode} = [circle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{relunode} = [rectangle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{line} = [draw, very thick, -latex']
+\tikzstyle{arrow} = [draw, ->, very thick]
 
 \begin{document}
-We thank the reviewers for their thoughtful and thorough reviews. We have attemtped to respond below. \par
-\textbf{miniImageNet:} TBD. \par
+\begin{wrapfigure}{r}{0.27\textwidth}
+\begin{center}
+\begin{tikzpicture}[auto, scale=0.75]
+\node at (-1.5, -3.5) (examples) {Examples};
+\node at (-1.5, -2.5) (D1) {
+\(\left\{
+\begin{matrix}
+(z^{ex}_{in,0}, z^{ex}_{targ,0})\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (1.5, -3.5) (examples) {Probes};
+\node at (1.5, -2.5) (D2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (-0.33, -0.66) (zfunc) {\(z^{func}\)};
+
+\path [arrow] (D1) to [in=-145, out=90] ([xshift=3, yshift=3]zfunc.south west) node [xshift=-16, yshift=-5] {\(\mathcal{M}\)};
+
+\node at (1.5, -0.25) (F) {\(F\)};
+
+\path [arrow, bend left] ([xshift=-5, yshift=-5]zfunc.north east) to [in=165, out=25] ([xshift=3]F.west) node [xshift=-13, yshift=5]{\(\mathcal{H}\)};
+
+\path [arrow, dashed] (D2) to (F);
+
+\node at (1.5, 1.75) (outputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 2.8) (predictions) {Predictions};
+
+\path [arrow, dashed] (F) to ([yshift=3]outputs.south);
+
+\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (dispatch) {Loss or eval or ...};
+
+\path [arrow, dashed] (outputs.west) to ([xshift=-3]dispatch.east);
+\end{tikzpicture}
+\end{center}
+\vspace{-1.5em}
+\end{wrapfigure}
 \looseness=-1
-\textbf{Novelty and contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to thing about transfer in terms of meta-mappings and task transformations.
+We thank the reviewers for their thoughtful and thorough reviews. \par
+\looseness=-1
+\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
+We would like to clarify how the architecture functions and how it is novel.
+To begin, we will clarify how a basic polynomial like $x + 1$ is learned.
+This is depicted schematically in the figure.
+As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e.
+the polynomial value) at each point.
+The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding.
+Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, then max pools elementwise across them, and then applies two more layers of processing to produce the function embedding which represents this polynomial.
+This procedure is permutation invariant by design.
+We then pass the function embedding $z^{func}$ through the hyper network $\mathcal{H}$ to parameterize a function $F$ which ideally performs the mapping from inputs to outputs.
+We can then take a new set of probe inputs (i.e.
+points we want to evaluate the polynomial at), transform them according to $F$ to produce a set of predictions, and then train the model or evaluate it if we have targets.
+As the reviewers noted, this is similar to many existing meta-learning approaches.
+\par
+\looseness=-1
+\textbf{The insight of our paper is that meta-mappings over polynomials are exactly analogous to basic meta-learning of a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for a more abstract function that operates over polynomials (e.g.
+multiplying by 2).
+These polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding.
+We then can take these pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for this meta-task.
+Just as above, we can pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2.
+We can then pass a probe polynomial through $F$ to produce a predicted output.
+The only differences from the basic case are 1) where the inputs and targets come from and 2) how the loss or evaluation is computed from the predictions.
+For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task.
+To evaluate the real performance on a meta-mapping, we actually computed the performance of the predicted output embedding at regressing the target polynomial.
+For example, if the meta-mapping was ``multiply by 2'' and the probe input was $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding inputs to this function, and then measuring its predicted outputs.
+We hope this clarifies how our architecture works, and why it is fundamentally different from prior work.
+All three reviewers highlighted the novelty of considering transformations over tasks.
+That is the conceptual contribution of our paper, but the architectural contribution of our paper is to show a way that meta-mappings can be parsimoniously integrated into a meta-learning architecture without adding a single parameter.
+We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.
+These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points, so we are revising the main text to clarify this.
+\par
+\looseness=-1
+\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
+We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, and we see alternatives as an exciting future direction.
+Our work proposes the challenge of meta-mappings, and a starting point for thinking about the solutions.
+A note on the DQN: the problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN.
+\par
+%\textbf{Relation to other work:} We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work. \par 
+%\looseness=-1
+%\textbf{Contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
 The architecture we propose is designed with this idea in mind.
 It is true that previous work has considered task embeddings (some of the works suggested by the reviewers we have mentioned in the related works section, but some we were not familiar with, we appreciate the pointers).
-Most of these have developed some way of embedding a dataset into some latent space.
+Most of this work has developed some way of embedding a task or dataset into some latent space.
 However, what we think is fundamentally novel about our architecture is that \textbf{we use the same latent space for the dataset as we use for an individual input to the network}.
-This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces.
-We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose.
-While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance in these domains too.
+This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings.
+We show in appendix D.1 that this performs better than separate embedding spaces.
+We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the meta-mappings we propose.
+While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance with other algorithms too.
 We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work.
@@
 \par
-\looseness=-1
-\textbf{Meta-mapping training details:} Consider a meta-mapping task, like trying to map from winning games to losing them.
-For concreteness, imagine we have three tasks, chess, poker, and go, and losing variations of each.
+%\looseness=-1
+%\textbf{Meta-mapping details:} For a concrete training example, imagine trying to map from winning tasks to losing them.
+Suppose we have three tasks, chess, poker, and go, and losing variations of each.
 We generate task embeddings for each game, e.g.
@@
 We minimize this loss across all held-out and training examples (using both accelerates learning).
-We continue with the next meta-mapping.
+We then proceed with the next meta-mapping.
 \par
-\looseness=-1
-To evaluate performance on a meta-mapping, we generate the training dataset as above, but we do not assume we have an embedding for the held-out targets.
+%\looseness=-1
+%To evaluate performance on a meta-mapping, we generate the training dataset as above, but we do not assume we have an embedding for the held-out targets.
 For example, we may know how to play chess via a task embedding $z_{chess}$, but our goal is to figure how to lose at chess.
@@
 \looseness=-1
-\textbf{Datasets:} We will release the code for this paper on github and provide links in the de-anonymized version, and both the polynomials and cards tasks and baselines are implemented as stand-alone python modules that other researchers can use.
-As we mention in the future directions, creating complex datasets for meta-mappings is an important future direction.
+\textbf{miniImageNet:} TBD. \par
+\looseness=-1
+\textbf{Datasets:} The polynomials and cards tasks are implemented as stand-alone python modules that other researchers can use, and will be released on github.
+Creating complex datasets for meta-mappings is an important future direction.
 \par
 \looseness=-1
-\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
-We explored some variations in appendix D to justify a few hoices, and showed that some more parsimonious choices resulted in worse performance.
-However, we acknowledge that we have not explored the full space of models or algorithms which could be used to approach this problem, and we see this as an important direction for future work.
-The problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN.
-We have revised the manuscript to clarify these points.
-\par
-\looseness=-1
-\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text.
+\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text (but c.f.
+appendix A).
 Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters.
-In appendix A we compare to specifying new tasks directly from language.
-Meta-mapping works better, presumably by better using task knowledge.
 \par
@@
 \textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this.
-We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model.
+This approach does requires storing an embedding vector per task, but many other approaches (such as EWC) require storing an extra ``importance'' parameter for each model parameter.
 For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks.
-We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the text.
+We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the main text.
 \par

### 2019-07-29 writing/nips_submission/response/EML_response.tex
Revised with some comments from Jay

@@
 We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.
-These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points, so we are revising the main text to clarify this.
-\par
+These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points.
+(We are revising the main text to clarify this.) \par
 \looseness=-1

### 2019-07-30 writing/nips_submission/response/EML_response.tex
slowly getting better

--- 2019-07-29 writing/nips_submission/response/EML_response.tex
@@
 \begin{center}
+\vspace{-0.85em}
 \begin{tikzpicture}[auto, scale=0.75]
@@
 \end{center}
-\vspace{-1.5em}
+\vspace{-2.3em}
 \end{wrapfigure}
@@
 \textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
-We would like to clarify how the architecture functions and how it is novel.
-To begin, we will clarify how a basic polynomial like $x + 1$ is learned.
-This is depicted schematically in the figure.
+We would like to clarify the architecture and training.
+First we will clarify how a basic polynomial is learned.
+This is depicted schematically on the right.
 As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e.
-the polynomial value) at each point.
+the polynomial evaluated at that point).
 The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding.
-Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, then max pools elementwise across them, and then applies two more layers of processing to produce the function embedding which represents this polynomial.
-This procedure is permutation invariant by design.
-We then pass the function embedding $z^{func}$ through the hyper network $\mathcal{H}$ to parameterize a function $F$ which ideally performs the mapping from inputs to outputs.
-We can then take a new set of probe inputs (i.e.
-points we want to evaluate the polynomial at), transform them according to $F$ to produce a set of predictions, and then train the model or evaluate it if we have targets.
-As the reviewers noted, this is similar to many existing meta-learning approaches.
+Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial.
+We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs.
+We can then use $F$ to transform a new set of probe inputs (i.e.
+points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets.
 \par
 \looseness=-1
-\textbf{The insight of our paper is that meta-mappings over polynomials are exactly analogous to basic meta-learning of a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for a more abstract function that operates over polynomials (e.g.
+\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g.
 multiplying by 2).
-These polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding.
-We then can take these pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for this meta-task.
-Just as above, we can pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2.
+Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one.
+We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another.
+Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2.
 We can then pass a probe polynomial through $F$ to produce a predicted output.
-The only differences from the basic case are 1) where the inputs and targets come from and 2) how the loss or evaluation is computed from the predictions.
+The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions.
 For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task.
-To evaluate the real performance on a meta-mapping, we actually computed the performance of the predicted output embedding at regressing the target polynomial.
-For example, if the meta-mapping was ``multiply by 2'' and the probe input was $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding inputs to this function, and then measuring its predicted outputs.
-We hope this clarifies how our architecture works, and why it is fundamentally different from prior work.
+One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig.
+3).
+To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial.
+For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
+We hope this clarifies our approach, and why it is fundamentally different from prior work.
 All three reviewers highlighted the novelty of considering transformations over tasks.
-That is the conceptual contribution of our paper, but the architectural contribution of our paper is to show a way that meta-mappings can be parsimoniously integrated into a meta-learning architecture without adding a single parameter.
-We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.
-These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points, so we are revising the main text to clarify this.
+That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge.
+Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model.
+(We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well.
+However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions.
+For now, we are revising the main text to clarify our message.
 \par
@@
 \textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
-We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, and we see alternatives as an exciting future direction.
-Our work proposes the challenge of meta-mappings, and a starting point for thinking about the solutions.
-A note on the DQN: the problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN.
+We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work.
+On the DQN: the problem is not exactly a standard supervised problem because you have multiple betting actions and only observe the reward for the bet you execute, we have clarified this in the text.
 \par
@@
 \looseness=-1
-\textbf{miniImageNet:} TBD. \par
-\looseness=-1
-\textbf{Datasets:} The polynomials and cards tasks are implemented as stand-alone python modules that other researchers can use, and will be released on github.
-Creating complex datasets for meta-mappings is an important future direction.
+\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a 50-layer ResNet as the input encoder, we achieved test accuracy of 58.9\% on 5-shot, 5-way classification, competitive with e.g.
+MAML.
+We expect that given more than a few days to tune hyperparameters and architecture we could do much better.
 \par
 \looseness=-1
-\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text (but c.f.
-appendix A).
-Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters.
-\par
+\textbf{Datasets:} Our tasks will be released on github as stand-alone python modules that other researchers can use. \par
 \looseness=-1
-\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this.
-This approach does requires storing an embedding vector per task, but many other approaches (such as EWC) require storing an extra ``importance'' parameter for each model parameter.
-For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks.
-We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the main text.
-\par
+\textbf{Language \& continual learning:} We wanted to include language because it provides a simpler way to cue meta-mappings.
+Specifically, we used the language embedding as input to $H$ instead of using examples.
+For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings.
+Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter.
+For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead would be advantageous even up to millions of tasks.
+In revising the paper, we will emphasize the main points before discussing these extensions.
 \end{document}

### 2019-07-30 writing/nips_submission/response/EML_response.tex
Some tweaks and mini imagenet results

@@
 The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions.
-For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task.
+For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ between the predicted task embedding and the embedding of the target task.
 One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig.
@@
 To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial.
-For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
+For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$, by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
 We hope this clarifies our approach, and why it is fundamentally different from prior work.
@@
 \looseness=-1
-\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a 50-layer ResNet as the input encoder, we achieved test accuracy of 58.9\% on 5-shot, 5-way classification, competitive with e.g.
+\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet-50 as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g.
 MAML.
-We expect that given more than a few days to tune hyperparameters and architecture we could do much better.
+We expect that with more than a few days to tune hyperparameters and train larger models we could do much better.
 \par
@@
 \looseness=-1
-\textbf{Language \& continual learning:} We wanted to include language because it provides a simpler way to cue meta-mappings.
-Specifically, we used the language embedding as input to $H$ instead of using examples.
+\textbf{Language \& continual learning:} In the revised paper we will emphasize the main points before discussing these extensions.
+We wanted to include language because it provides a simpler way to cue meta-mappings.
+Specifically, we used the language embedding as input to $\mathcal{H}$ instead of using examples via $\mathcal{M}$.
 For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings.
 Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter.
-For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead would be advantageous even up to millions of tasks.
-In revising the paper, we will emphasize the main points before discussing these extensions.
+For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead could require less memory even up to millions of tasks.
 \end{document}

### 2019-07-30 writing/nips_submission/response/EML_response.tex
Tweaks

@@
 \looseness=-1
-\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet-50 as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g.
+\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g.
 MAML.
-We expect that with more than a few days to tune hyperparameters and train larger models we could do much better.
+We expect that with more than a few days to tune hyperparameters and refine the model we could do much better.
 \par

### 2019-07-30 writing/embedded_meta_learning_main.tex
Tweaks

@@
 We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
-that they can exhibit zero-shot remapping of behavior to adapt to new tasks.
+that they can exhibit zero-shot remapping of behavior to adapt to new tasks, and explore several extensions.
 \end{abstract}
@@
 We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
-EML may also offer other benefits, such as a useful framework for continual learning.
+Furthermore, the architecture may also offer other benefits, such as a useful framework for continual learning.
 We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
@@
 \paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
+From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
 Anything that is embedded in $Z$ can be transformed using the same system.
-Because tasks are embedded in $Z$, this allows for meta-mappings.
+Because tasks are embedded in $Z$, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$.
 For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.
@@
 This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
-To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guess and the embedding of the losing task.
+To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task.
 Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy.
-This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding.
+This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks.
 \par
@@
 We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
-There is no action besides betting, and depending on the opponent's hand the agent either wins or loses the amount bet.
-This doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
+There are three possible bets (including ``don't bet''), and depending on the opponent's hand the agent either wins or loses the amount bet.
+This task doesn't require long term planning, but does incorporate some aspects of reinforcement learning, namely stochastic feedback on only the action chosen.
 We considered five games that are simplified analogs of various real card games (see Appendix \ref{meth_data_cards}).
@@
 \par
-Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}.
-This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
+Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}, and meta-learning \citep[e.g.]{Li2019a, Rusu2019}.
+Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
 It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}.

### 2019-07-31 writing/nips_submission/response/EML_response.tex
More tweaks

@@
 \looseness=-1
-\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g.
+\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of embeddings of input polynomials and output polynomials for a meta-mapping that operates over polynomials (e.g.
 multiplying by 2).
@@
 Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2.
-We can then pass a probe polynomial through $F$ to produce a predicted output.
+We can then pass a novel probe polynomial through $F$ to produce a predicted output, which is the embedding of a novel function obtained by transforming the input polynomial.
 The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions.
-For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ between the predicted task embedding and the embedding of the target task.
-One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig.
+For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ loss between the predicted task embedding and the embedding of the target task.
+One of the main algorithmic insights of our work is that this loss produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig.
 3).
 To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial.
-For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$, by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
+For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$, by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
 We hope this clarifies our approach, and why it is fundamentally different from prior work.
 All three reviewers highlighted the novelty of considering transformations over tasks.
-That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge.
-Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model.
-(We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well.
-However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions.
-For now, we are revising the main text to clarify our message.
+That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge, by using the same computational structure for both basic tasks and meta-mappings.
+Because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model.
+(This actually performs better than having separate networks for basic tasks and meta-mappings, see appendix D.1.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well.
+However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, could be exciting future directions.
+For now, we are revising the paper to clarify our message.
 \par
 \looseness=-1
-\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary.
-We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work.
-On the DQN: the problem is not exactly a standard supervised problem because you have multiple betting actions and only observe the reward for the bet you execute, we have clarified this in the text.
+\textbf{Architecture:} We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work.
+Cards/DQN: this is not exactly a supervised problem because you have multiple betting actions and only observe the reward for the one you take, we have clarified this in the text.
 \par
@@
 \looseness=-1
-\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g.
-MAML.
-We expect that with more than a few days to tune hyperparameters and refine the model we could do much better.
+\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.4\% on 5-shot, 5-way classification, competitive with MAML and Meta-LSTM.
+We expect that with more than a few days to tune and refine the model we could do much better.
 \par

### 2019-07-31 writing/nips_submission/response/EML_response.tex
Further tweaks

@@
 \textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
-We would like to clarify the architecture and training.
-First we will clarify how a basic polynomial is learned.
-This is depicted schematically on the right.
-As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e.
-the polynomial evaluated at that point).
-The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding.
-Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial.
+First we clarify how our architecture and training work for learning basic polynomials (see the diagram), then turn to the issue of meta-mappings.
+As in standard meta-learning, we generate a set of examples, consisting of (input, target) tuples exemplifying the polynomial to be learned.
+We embed the inputs and targets, then pass them to he meta-network $\mathcal{M}$ which processes them to produce a function embedding.
+$\mathcal{M}$ concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial.
 We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs.
@@
 \looseness=-1
-\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of embeddings of input polynomials and output polynomials for a meta-mapping that operates over polynomials (e.g.
-multiplying by 2).
-Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one.
+\textbf{The insight of our paper is to show how both basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.} To learn a meta-mapping that operates over polynomials (e.g.
+multiplying by 2), we use example (input, target) tuples, except that now each input or target is an embedding of a polynomial.
+These embeddings are constructed as above, by passing examples of the polynomial through the meta network $\mathcal{M}$.
 We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another.
@@
 One of the main algorithmic insights of our work is that this loss produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig.
-3).
-To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial.
-For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$, by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
+3a, held-out mapping, on held-out task).
+To obtain those results, we actually evaluated the performance of the predicted output embedding at computing the target polynomial.
+For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$ by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs.
 We hope this clarifies our approach, and why it is fundamentally different from prior work.
@@
 \looseness=-1
-\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.4\% on 5-shot, 5-way classification, competitive with MAML and Meta-LSTM.
-We expect that with more than a few days to tune and refine the model we could do much better.
+\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM.
+We expect that with more than a few days to tune and refine the model we could do better.
 \par

### 2019-08-01 writing/nips_submission/response/EML_response.tex
More tweaks

@@
 \end{wrapfigure}
-\looseness=-1
+\vspace{-0.1em}\looseness=-1
 We thank the reviewers for their thoughtful and thorough reviews. \par
-\looseness=-1
-\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
+\vspace{-0.1em}\looseness=-1
+\textbf{Approach \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
 First we clarify how our architecture and training work for learning basic polynomials (see the diagram), then turn to the issue of meta-mappings.
@@
 \par
-\looseness=-1
+\vspace{-0.1em}\looseness=-1
 \textbf{The insight of our paper is to show how both basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.} To learn a meta-mapping that operates over polynomials (e.g.
@@
 \par
-\looseness=-1
+\vspace{-0.1em}\looseness=-1
 \textbf{Architecture:} We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work.
@@
 %\textbf{Relation to other work:} We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work. \par 
-%\looseness=-1
+%\vspace{-0.1em}\looseness=-1
 %\textbf{Contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations.
@@
 \par
-%\looseness=-1
+%\vspace{-0.1em}\looseness=-1
 %\textbf{Meta-mapping details:} For a concrete training example, imagine trying to map from winning tasks to losing them.
@@
 \par
-%\looseness=-1
+%\vspace{-0.1em}\looseness=-1
 %To evaluate performance on a meta-mapping, we generate the training dataset as above, but we do not assume we have an embedding for the held-out targets.
@@
 \par
-\looseness=-1
-\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM.
-We expect that with more than a few days to tune and refine the model we could do better.
-\par
-\looseness=-1
-\textbf{Datasets:} Our tasks will be released on github as stand-alone python modules that other researchers can use. \par
-\looseness=-1
-\textbf{Language \& continual learning:} In the revised paper we will emphasize the main points before discussing these extensions.
+\vspace{-0.1em}\looseness=-1
+\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM.
+We expect that with more than a few days to tune we could do better.
+Our tasks will be released on github as stand-alone python modules that other researchers can use.
+Developing more complex meta-learning datasets which include meta-mappings will be an important direction for future work.\par
+\vspace{-0.1em}\looseness=-1
+\textbf{Language \& continual learning:} If accepted, our revised paper will emphasize the main points before discussing these extensions.
 We wanted to include language because it provides a simpler way to cue meta-mappings.

### 2019-08-01 writing/nips_submission/response/EML_response.tex
Newer scores

@@
 \vspace{-0.1em}\looseness=-1
-\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM.
+\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 63.2\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM.
 We expect that with more than a few days to tune we could do better.

### 2019-08-11 writing/embedded_meta_learning_main.tex
Minor tweaks to related lit, following up on reviews

@@
 Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}, and meta-learning \citep[e.g.]{Li2019a, Rusu2019}.
-Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}.
+Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017, Garnelo2018} and continual learning \citep[e.g.]{Hu2019}.
 It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}.
@@
 Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general.
-\par
+Indeed, our insights could be combined with model-based approaches, for example our approach could be used to adapt a task embedding, which would then be fed to a learned planning model to execute that behavior.\par
 There has also been other recent interest in task (or function) embeddings.

### 2019-08-11 writing/embedded_meta_learning_main.tex
Incorporating response figure, some clarifications

@@
 \tikzstyle{line} = [draw, very thick, -latex']
+\tikzstyle{arrow} = [draw, ->, very thick]
 
@@
 We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
+By allowing the network to recurse on its representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
 Furthermore, the architecture may also offer other benefits, such as a useful framework for continual learning.
@@
 \centering
-\begin{tikzpicture}[auto, scale=0.75]
-\node [dashblock] at (0.2, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: \textbf{Shared} \\ \textbf{representation}\end{tabular}};
+\begin{subfigure}[b]{0.72\textwidth}
+\begin{tikzpicture}[auto, scale=0.66, every node/.style={scale=0.85}]
+\node [dashblock] at (0.2, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: Shared \\ representation\end{tabular}};
 
@@
 
-\node [conc] at (-7, -3.5) (perc) {\textbf{Input}};
-%%\node [conc] at (-7.25, -2.5) (lang) {\textbf{Language}};
-\node [conc] at (-7.2, 4) (act) {\textbf{Output}};
-\node [conc] at (-7.2, 2.8) (tar) {\textbf{Targets}};
-\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: \textbf{Input encoder}};
+\node [conc] at (-7, -3.5) (perc) {Input};
+%%\node [conc] at (-7.25, -2.5) (lang) {Language};
+\node [conc] at (-7.2, 4) (act) {Output};
+\node [conc] at (-7.2, 2.8) (tar) {Targets};
+\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: Input encoder};
 %%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 3) (OD) {$\bm{\mathcal{O}}$: \textbf{Output decoder}};
-\node [block, text width=2cm] at (-4, 1.5) (TE) {$\bm{\mathcal{T}}$: \textbf{Target encoder}};
+\node [block, text width=2.2cm] at (-4, 3) (OD) {$\bm{\mathcal{O}}$: Output decoder};
+\node [block, text width=2cm] at (-4, 1.5) (TE) {$\bm{\mathcal{T}}$: Target encoder};
 \path [line] (perc.north) to (IE.west);
@@
 % meta
-\draw [boundingbox] (-1.9, 5) rectangle (6, -5); 
+\draw [boundingbox] (-1.9, 5) rectangle (5.85, -5); 
 \node [text=gray] at (-0.4, 4.7) {\textbf{Meta Learner}};
@@
 
-\node [block] at (4.2, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: \textbf{Meta} \\ \textbf{network}\end{tabular}};
+\node [block] at (4.2, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: Meta \\ network\end{tabular}};
 \path [line] (collection.south) to [out=-90, in=-90] (meta.south);
@@
 
-\node [block] at (4.2, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
+\node [block] at (4.2, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: Hyper \\ network\end{tabular}};
 \node [block, dash pattern=on 9pt off 2pt] at (0.2, 2) (transform) {\(F: \bm{Z} \rightarrow \bm{Z}\)};
@@
 \end{tikzpicture}
-\caption{The EML architecture.
+\caption{Schematic of the architecture}
+\end{subfigure}%
+\begin{subfigure}[b]{0.28\textwidth}
+\begin{tikzpicture}[auto, scale=0.66, every node/.style={scale=0.85}]
+\node at (-1.5, -3.6) (examples) {Examples};
+\node at (-1.5, -2.5) (D1) {
+\(\left\{
+\begin{matrix}
+(z^{ex}_{in,0}, z^{ex}_{targ,0})\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (1.5, -3.6) (examples) {Probes};
+\node at (1.5, -2.5) (D2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (-0.33, -0.66) (zfunc) {\(z^{func}\)};
+
+\path [arrow] (D1) to [in=-145, out=90] ([xshift=3, yshift=3]zfunc.south west) node [xshift=-16, yshift=-5] {\(\mathcal{M}\)};
+
+\node at (1.5, -0.25) (F) {\(F\)};
+
+\path [arrow, bend left] ([xshift=-5, yshift=-5]zfunc.north east) to [in=165, out=25] ([xshift=3]F.west) node [xshift=-13, yshift=5]{\(\mathcal{H}\)};
+
+\path [arrow, dashed] (D2) to (F);
+
+\node at (1.5, 1.75) (outputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 2.9) (predictions) {Predictions};
+
+\path [arrow, dashed] (F) to ([yshift=3]outputs.south);
+
+\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (dispatch) {Loss or eval or ...};
+
+\path [arrow, dashed] (outputs.west) to ([xshift=-3]dispatch.east);
+
+% for spacing
+
+\node at (0, -5.5) {};
+\end{tikzpicture}
+\caption{Meta-learner inference}
+\end{subfigure}
+\caption{The EML architecture and an inference step.
+(a) A schematic of the architecture.
 Blocks with solid edges denote learnable deep networks, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
@@
 both language and vision.
-See appendix \ref{app_model_details} for details.} \label{architecture_fig}
+See appendix \ref{app_model_details} for details.
+(b) Depiction of a meta-learner forward pass.
+This process is identical between basic tasks and meta-mappings, except for where the example and probe embeddings come from, and how the loss or evaluation is computed.
+For basic inference, the example and probe embeddings come from basic inputs and outputs, and loss is computed in the output space.
+FOr meta-mapping, the example and probe input and outputs are task embeddings of basic tasks, and loss for training is computed in the embedding space, while evaluation is done by using the predicted embedding to perform the target task.} \label{architecture_inference_fig}
 \end{figure}
@@
 These transformations are performed by a system with the following components (see Fig.
-\ref{architecture_fig} for a schematic): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
+\ref{architecture_inference_fig}): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
 $\mathcal{H}: Z \rightarrow \text{parameters}$ -- the hyper network, which maps a function embedding to parameters.

### 2019-08-11 writing/embedded_meta_learning_main.tex
Refactoring, clarifying

@@
 \paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
+The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.
 From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
 Anything that is embedded in $Z$ can be transformed using the same system.
-Because tasks are embedded in $Z$, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$.
+Because tasks are embedded in $Z$ for basic meta-learning, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$ that we use for basic tasks.
 For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.
@@
 The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows for substantial flexibility within a unified framework.
+Furthermore, our approach is parsimonious.
+Because it uses the same meta-learner for both basic tasks and meta-mappings, this increased flexibility does not require any added parameters.\footnote{At least in principle, in practice of course increasing network size might be more beneficial for EML architectures performing meta-mappings as well as basic tasks than for those performing only basic tasks.}
 
@@
 \includegraphics[width=\textwidth]{figures/poly/meta_results.png}
-\caption{From examples of mapping.}
+\caption{The polynomials domain, section \ref{sec_poly}.}
 \label{poly_meta_map_results_examples}
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
-\caption{From language input.}
-\label{poly_meta_map_results_language}
-\end{subfigure}
-\caption{The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}).
+\includegraphics[width=\textwidth]{figures/meta_mapping.png}
+\caption{The cards domain, section \ref{sec_cards}.}
+\label{cards_meta_map_results_examples}
+\end{subfigure}%
+\caption{The EML architecture performs well at meta-mappings.
+(\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings.
 The plots show the loss produced when evaluating the mapped embedding on the target task.
@@
 The solid line indicates optimal performance; the dashed line is chance (untrained).
+(\subref{cards_meta_map_results_examples}) The system generalizes to meta-mapping new tasks in the cards domain.
+The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
+For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
+When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
+This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
+The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
+The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout.
 Error-bars are bootstrap 95\%-CIs.} 
-\label{poly_meta_map_results}
+\label{meta_map_results}
 \end{figure}
+
 %% Cut example if necessary
@@
 \ref{poly_basic_results} (with good sample-efficiency, see supp.
-fig.
+Fig.
 \ref{supp_poly_sweep_results}).
@@
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in Fig.
 \ref{poly_meta_map_results}.
@@
 We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language cue to the meta-mapping.
-It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping.
-\par
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_continual_results}
-\end{figure}
-\vspace{-0.7em}
-\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
-We would like to be able to store our knowledge more efficiently, and allow for further refinement.
-Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
-\par
-A very simple solution to these problems is naturally suggested by our architecture.
-Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
-That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par
-To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
-We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in fig.
-\ref{poly_continual_results}.
-The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-fig.
-\ref{supp_poly_continual_results} for a more direct comparison).
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
+The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping.
 \par
@@
 \par
+\section{Extensions}
+%% TODO: language
+
 \begin{figure}
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[width=\textwidth]{figures/meta_mapping.png}
-\caption{From examples of mapping.}
-\label{cards_meta_map_results_examples}
+\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
+\caption{From language input.}
+\label{poly_meta_map_results_language}
 \end{subfigure}%
@@
 \end{subfigure}
-\caption{The system generalizes to meta-mapping new tasks in the cards domain.
-The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
-For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
-When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
-This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
-The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping.
-The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout.
-The meta-mappings can be cued either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}).
+\caption{The EML system can perform meta-mappings from language cues rather than meta-mapping examples, and can even generalize these.
+Compare to Fig.
+\ref{meta_map_results}, which shows the same results when using examples instead of language.
+(\subref{poly_meta_map_results_language}) In the polynomials domain, language cues still lead to good performance, even on held-out tasks or held-out meta-mappings, although examples perform slightly better (Fig.
+\ref{poly_meta_map_results_examples}).
+(\subref{cards_meta_map_results_language}) Similarly, in the cards domain, language cues perform well.
 Error-bars are bootstrap 95\%-CIs.}
-\label{cards_meta_map_results}
+\label{language_meta_map_results}
 \end{figure}
+\paragraph{Language:} Language is a fundamental piece of human flexibility, and we would be remiss to ignore it.
+In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world.
+For example, ``try to lose at go'' does not give explicit examples of the ``lose'' meta-mapping, but rather relies on prior knowledge of what losing means.
+This is a much more efficient way to achieve zero-shot performance on a new losing task.
+In order to replicate this, we trained the EML system with both meta-mappings based on examples, and meta-mappings based on language.
+In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is provided to the network.
+This language input is encoded by a language encoder, and then provided as input to $\mathcal{H}$ instead of the output of $\mathcal{M}$.
+The meta-mapping then proceeds as normal --- $\mathcal{H}$ parameterizes $F$, which is used to transform the embedding of the input task to produce an embedding for the target task.
+\par
+This language-cued meta-mapping approach also yields good performance (Fig.
+\ref{language_meta_map_results}).
+However, examples of the meta-mapping are slightly better, especially for meta-mappings not seen during training, presumably because examples provide a richer description.
+In Appendix \ref{app_why_meta_mapping} we show that using language to specify a meta-mapping performs better than using language to directly specify the target task, presumably by leveraging the richer task representation of the task embedding.
+\par
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
+\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
+Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
+Error-bars are bootstrap 95\%-CIs.}
+\label{poly_continual_results}
+\end{figure}
+\vspace{-0.7em}
+\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
+We would like to be able to store our knowledge more efficiently, and allow for further refinement.
+Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
+\par
+A very simple solution to these problems is naturally suggested by our architecture.
+Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
+This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
+That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} While this is not a traditional continual learning perspective, we think it provides an interesting perspective on the issue.\par
+To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
+We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
+The results are shown in Fig.
+\ref{poly_continual_results}.
+The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
+Fig.
+\ref{supp_poly_continual_results} for a more direct comparison).
+Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
+\par
 \section{Discussion} \label{sec_discussion}

### 2019-08-11 writing/embedded_meta_learning_main.tex
per CMoS, figure references not capitalized

@@
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
-These transformations are performed by a system with the following components (see Fig.
+These transformations are performed by a system with the following components (see fig.
 \ref{architecture_inference_fig}): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
@@
 \vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig.
 \ref{poly_basic_results} (with good sample-efficiency, see supp.
-Fig.
+fig.
 \ref{supp_poly_sweep_results}).
@@
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in Fig.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
 \ref{poly_meta_map_results}.
@@
 \vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in fig.
 \ref{cards_basic_results}.
@@
 For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
-In Fig.
+In fig.
 \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
@@
 \section{Extensions}
-%% TODO: language
-
 \begin{figure}
@@
 \caption{The EML system can perform meta-mappings from language cues rather than meta-mapping examples, and can even generalize these.
-Compare to Fig.
+Compare to fig.
 \ref{meta_map_results}, which shows the same results when using examples instead of language.
-(\subref{poly_meta_map_results_language}) In the polynomials domain, language cues still lead to good performance, even on held-out tasks or held-out meta-mappings, although examples perform slightly better (Fig.
+(\subref{poly_meta_map_results_language}) In the polynomials domain, language cues still lead to good performance, even on held-out tasks or held-out meta-mappings, although examples perform slightly better (fig.
 \ref{poly_meta_map_results_examples}).
@@
 \par
-This language-cued meta-mapping approach also yields good performance (Fig.
+This language-cued meta-mapping approach also yields good performance (fig.
 \ref{language_meta_map_results}).
@@
 We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in Fig.
+The results are shown in fig.
 \ref{poly_continual_results}.
 The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-Fig.
+fig.
 \ref{supp_poly_continual_results} for a more direct comparison).

### 2019-09-04 writing/embedded_meta_learning_main.tex
Title + framing shift

@@
 \begin{document}
-\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
+\title{Zero-shot task adaptation by meta-mapping from task to task}
 \author{%
@@
 We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
-We therefore draw inspiration from meta-learning and functional programming to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
+We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
 EML architectures are applicable to any type of machine learning task, including supervised learning and reinforcement learning.
-We demonstrate the flexibility of these architectures by showing that they can perform meta-mappings, i.e.
-that they can exhibit zero-shot remapping of behavior to adapt to new tasks, and explore several extensions.
+We demonstrate the utility of this perspective by exhibiting zero-shot remapping of behavior to adapt to new tasks.
 \end{abstract}
@@
 This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
-To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
+To address this challenge, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
 (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
@@
 By allowing the network to recurse on its representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
-Furthermore, the architecture may also offer other benefits, such as a useful framework for continual learning.
 We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
@@
 \vspace{-0.75em}
-Why have a completely shared space $Z$ for data and tasks?
+Why have a completely shared space $Z$ for individual data points and tasks?
 The primary advantage is that it allows for arbitrary mappings between these entities.
@@
 For basic inference, the example and probe embeddings come from basic inputs and outputs, and loss is computed in the output space.
-FOr meta-mapping, the example and probe input and outputs are task embeddings of basic tasks, and loss for training is computed in the embedding space, while evaluation is done by using the predicted embedding to perform the target task.} \label{architecture_inference_fig}
+For meta-mapping, the example and probe input and outputs are task embeddings of basic tasks, and loss for training is computed in the embedding space, while evaluation is done by using the predicted embedding to perform the target task.} \label{architecture_inference_fig}
 \end{figure}
@@
 \par
-Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$ (see appendix \ref{app_lesion_results_shared_z} for discussion of why this space should be shared).
+Specifically, we embed each input, target, or mapping into a shared representational space $Z$.
+This means that single data points are embedded in the same space as the representation of a functionr or an entire dataset.
+See appendix \ref{app_lesion_results_shared_z} for discussion of why $Z$ should be shared.
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
@@
 Because tasks are embedded in $Z$ for basic meta-learning, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$ that we use for basic tasks.
+Just as we would take a set of paired embeddings of data points for a basic task, and use them to compute a function embedding for that task, we can take a set of paired function embeddings, and use them to create an embedding for the meta-mapping.
+We can then use this meta-mapping embedding to transform another task.
+We can thus behave zero-shot on a novel task based on its relationship to a prior task.
+\par
 For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.

### 2019-09-04 writing/embedded_meta_learning_appendix.tex
Tweaks, continual -> appendix, continuing reframing

@@
 The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
+In section
+\ref{app_continual} we describe a continual-learning like perspective based on our approach.
 In section \ref{app_supp_figures} we provide supplemental figures.
@@
 We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.
+\par
+\section{Continual learning} \label{app_continual}
+\begin{figure}[H]
+\centering
+\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
+\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
+Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
+Error-bars are bootstrap 95\%-CIs.}
+\label{poly_continual_results}
+\end{figure}
+\vspace{-0.7em}
+\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
+We would like to be able to store our knowledge more efficiently, and allow for further refinement.
+Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
+\par
+A very simple solution to these problems is naturally suggested by our architecture.
+Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
+This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
+This is like the procedure of \citet{Rusu2019}, except considered across episodes.
+That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.
+While this is not a traditional continual learning perspective, we think it provides an interesting perspective on the issue.
+It might in fact be much more memory-efficient to store an embedding per task, compared to storing an extra ``importance'' parameter for every parameter in our model, as in e.g.
+elastic weight consolidation \citep{Kirkpatrick2016}.
+It also provides a stronger guarantee of non-interference.
+\par
+To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
+We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
+The results are shown in fig.
+\ref{poly_continual_results}.
+The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
+fig.
+\ref{supp_poly_continual_results} for a more direct comparison).
+Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
 \par

### 2019-09-04 writing/embedded_meta_learning_main.tex
Tweaks, continual -> appendix, continuing reframing

@@
 \par
-\section{Extensions}
+\section{An extension via language}
 \begin{figure}
@@
 \end{figure}
-\paragraph{Language:} Language is a fundamental piece of human flexibility, and we would be remiss to ignore it.
+Language is a fundamental piece of human flexibility, and we would be remiss to ignore it.
 In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
-\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks.
-Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well.
-Error-bars are bootstrap 95\%-CIs.}
-\label{poly_continual_results}
-\end{figure}
-\vspace{-0.7em}
-\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step.
-We would like to be able to store our knowledge more efficiently, and allow for further refinement.
-Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}.
-\par
-A very simple solution to these problems is naturally suggested by our architecture.
-Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step.
-This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}.
-That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} While this is not a traditional continual learning perspective, we think it provides an interesting perspective on the issue.\par
-To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks.
-We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in fig.
-\ref{poly_continual_results}.
-The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-fig.
-\ref{supp_poly_continual_results} for a more direct comparison).
-Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.
-\par
 \section{Discussion} \label{sec_discussion}
@@
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
+We also connect to a different perspective on continual learning in appendix \ref{app_continual}.
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
@@
 There has also been other recent interest in task (or function) embeddings.
-In simultaneous work Achille et al.
-\citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task.
+Achille et al.
+\citep{Achille2019} recently proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task.
 They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.
@@
 Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
-Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks.
-To the best of our knowledge none of the prior work has explored meta-mappings.
+Our perspective can be seen as a generalization of these that allows for remapping of behavior by meta-tasks.
+To the best of our knowledge none of the prior work has explored meta-mappings, and therefore it has not allowed for zero-shot performance of a new task.
 \par
@@
 In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
-We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed.
-To address this, we've proposed explicitly representing tasks by function embeddings, and deriving the computation from these embeddings via a HyperNetwork.
-This allows transformations over task embeddings to transform the system's behavior.
+Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks.
+However, achieving this type of flexibility is difficult in architectures that separate computation from the knowledge of what is being computed.
+To address this, our EML architecture explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
+This allows for our key insight: using transformations over task embeddings to transform the system's behavior.
 This is analogous to how transformations over data perform basic tasks.
 Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
-The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
+The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.
+That is, we are able to achieve zero-shot performance on a novel task based on a relationship between tasks that was never trained on.
+This is a step closer to human-level flexibility.\par
 We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.
@@
 We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task.
-We've also shown that our approach provides a useful perspective on continual learning.
 We hope that these results will lead to the development of more powerful and flexible deep-learning models.

### 2019-09-04 writing/embedded_meta_learning_main.tex
Further tweaks, cutting a bit

@@
 \begin{document}
-\title{Zero-shot task adaptation by meta-mapping from task to task}
+\title{Zero-shot adaptation by meta-mapping between tasks}
 \author{%
@@
 \vspace{-0.5em} % section
-Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}.
+Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}.
 One fundamental reason for this is that humans are aware of what we are trying to compute and why.
@@
 In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
 However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
@@
 \section{An extension via language}
+\vspace{-0.5em} % section
 \begin{figure}
@@
 \end{subfigure}
-\caption{The EML system can perform meta-mappings from language cues rather than meta-mapping examples, and can even generalize these.
+\caption{The EML system can perform meta-mappings from language cues rather than meta-mapping examples.
 Compare to fig.
@@
 \end{figure}
-Language is a fundamental piece of human flexibility, and we would be remiss to ignore it.
+Language is fundamental to human flexibility, and we would be remiss to ignore it.
 In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world.
@@
 In order to replicate this, we trained the EML system with both meta-mappings based on examples, and meta-mappings based on language.
-In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is provided to the network.
-This language input is encoded by a language encoder, and then provided as input to $\mathcal{H}$ instead of the output of $\mathcal{M}$.
-The meta-mapping then proceeds as normal --- $\mathcal{H}$ parameterizes $F$, which is used to transform the embedding of the input task to produce an embedding for the target task.
+In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is encoded by a language encoder, and then provided as the input to $\mathcal{H}$ (instead of an output from $\mathcal{M}$).
+The meta-mapping then proceeds as normal --- $\mathcal{H}$ parameterizes $F$, which is used to transform the embedding of the input task to produce an embedding for the target.
 \par
@@
 Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general.
-Indeed, our insights could be combined with model-based approaches, for example our approach could be used to adapt a task embedding, which would then be fed to a learned planning model to execute that behavior.\par
+Indeed, our insights could be combined with model-based approaches, for example our approach could be used to adapt a task embedding, which would then be used by a learned planning model.\par
 There has also been other recent interest in task (or function) embeddings.
@@
 Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning.
-Our perspective can be seen as a generalization of these that allows for remapping of behavior by meta-tasks.
-To the best of our knowledge none of the prior work has explored meta-mappings, and therefore it has not allowed for zero-shot performance of a new task.
+Our perspective can be seen as a generalization of these that allows for remapping of behavior via meta-tasks.
+To the best of our knowledge none of the prior work has explored zero-shot performance of a task via meta-mappings.
 \par
@@
 To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
-For example, as we alluded to above, tasks such as visual question-answering \citep[e.g.][]{Antol2015} can be usefully interpreted from this perspective (a question essentially yields a function from images to answers, and there are many systematic relationships between these functions), as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019}.
+For example,  as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019} can be usefully interpreted from this perspective.
 Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.
 \par
-We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems generally, although it has a number of desirable characteristics.
-However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others.
-(Note that we compare some variations in appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
+We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems, although it has a number of desirable characteristics.
+However, the modularization of the architecture makes it easy to modify.
+(We compare some variations in appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
 Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
@@
 \vspace{-0.5em} % section
-In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
+\looseness=-1
+We've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
 Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks.
@@
 This is analogous to how transformations over data perform basic tasks.
-Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
-The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.
+Following this analogy, the EML architecture takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
+This approach is parsiomious, because it uses the same networks for basic- and meta-mappings.
+Perhaps because of this, the requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.
 That is, we are able to achieve zero-shot performance on a novel task based on a relationship between tasks that was never trained on.

### 2019-09-04 writing/embedded_meta_learning_main.tex
Fixing some references

@@
 By allowing the network to recurse on its representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
-We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems.
+We suggest that approaches like ourswill be key to building more intelligent and flexible deep learning systems.
 \par
@@
 \paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
-\ref{poly_meta_map_results}.
+\ref{poly_meta_map_results_examples}.
 We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
@@
 In fig.
-\ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
+\ref{cards_meta_map_results_examples} we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
 This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out).

### 2019-09-05 writing/embedded_meta_learning_main.tex
Incorporating some of Jay's added comments

@@
 We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
-By allowing the network to recurse on its representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
-We suggest that approaches like ourswill be key to building more intelligent and flexible deep learning systems.
+By allowing the network to recursively treat its task representations as data points that can be transformed to produce new task representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
+We suggest that approaches like ours will be key to building more intelligent and flexible deep learning systems.
 \par
@@
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
-Given appropriate conditioning (see below), we can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
+Given appropriate conditioning (see below), our architecture can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
 We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-There are different ways this adaptation can be cued, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
+There are different ways this adaptation can be cued, for example by examples of similar task mappings (``you've played winning and losing poker, now try to lose at blackjack'') or simply by natural-language instructions (``try to lose at blackjack'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
 Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 \item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system which embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
+\item A meta-learning system that embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
 \end{enumerate}
@@
 The primary advantage is that it allows for arbitrary mappings between these entities.
-In addition to basic tasks, the system could in principle learn to perform meta-mappings to follow instructions or change behavior.
+In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior.
+That is, it can transform task representations using the same components it uses to transform basic data points, because the task representations and basic data points are embedded in the same space.
 \par
 Without training on meta-mappings, of course, the system will not be able to execute them well.
-However, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-task distribution, as we demonstrate below.
+However, as we will show, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-task distribution.
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
@@
 More formally, we take a \emph{functional} perspective on learning.
-A datum can be represented by a constant function which outputs that datum.
-(For example, each point in the latent space of an autoencoder can be thought of this way.) Adopting this perspective allows us to interpret model inputs or outputs as functions.
-Most machine learning tasks then become a mapping of functions to functions.
-The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term.
-The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on functions that represent tasks.
+From this perspective, the data points that one function receives can themselves be functions\footnote{Indeed, any data point can be represented as a constant function that outputs the data point.}.
+The key insight is that then our architecture can transform data points\footnote{Where ``data'' is a quite flexible term.
+The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.} to perform basic tasks (as is standard in machine learning), but it can also transform these task functions to adapt to new tasks.
 This is related to the idea of a homoiconicity, defined above.
-Under this perspective, basic tasks and meta-mappings are really the same type of problem.
+Under this perspective, basic tasks and meta-mappings from task to task are really the same type of problem.
+The functions at one level of abstraction (the basic tasks) become inputs and outputs for higher-level functions at the next level of abstraction (meta-mapping between tasks).
 \par

### 2019-09-05 writing/embedded_meta_learning_main.tex
New figure + tweaks

--- 2019-09-04 writing/embedded_meta_learning_main.tex
@@
 \tikzstyle{block} = [rectangle, draw, thick, align=center, rounded corners]
-\tikzstyle{boundingbox} = [very thick, dotted, gray]
+\tikzstyle{boundingbox} = [thick, lightgray]
 \tikzstyle{dashblock} = [rectangle, draw, thick, align=center, dashed]
@@
 \tikzstyle{line} = [draw, very thick, -latex']
-\tikzstyle{arrow} = [draw, ->, very thick]
+\tikzstyle{arrow} = [draw, ->, thick]
+
+\definecolor{bpurp}{HTML}{984ea3}
+\definecolor{bblue}{HTML}{377eb8}
 
@@
 \centering
-\begin{subfigure}[b]{0.72\textwidth}
-\begin{tikzpicture}[auto, scale=0.66, every node/.style={scale=0.85}]
-\node [dashblock] at (0.2, 0) (rep) {\begin{tabular}{c}$\bm{Z}$: Shared \\ representation\end{tabular}};
+\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
+%% basic meta learning
+\begin{scope}[shift={(0.4, 0.4)}]
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\end{scope}
+\begin{scope}[shift={(0.2, 0.2)}]
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\end{scope}
 
-% inputs, outputs
-
-\draw [boundingbox] (-9, -5) rectangle (-2.1, 5); 
-\node [text=gray] at (-8.5, 4.65) {\textbf{I/O}};
-
-\node [conc] at (-7, -3.5) (perc) {Input};
-%%\node [conc] at (-7.25, -2.5) (lang) {Language};
-\node [conc] at (-7.2, 4) (act) {Output};
-\node [conc] at (-7.2, 2.8) (tar) {Targets};
-\node [block, text width=2cm] at (-4, -2) (IE) {$\bm{\mathcal{I}}$: Input encoder};
-%%\node [block, text width=2cm] at (-5, -0.5) (LE) {$\bm{\mathcal{L}}$: \textbf{Lang. Encoder}};
-\node [block, text width=2.2cm] at (-4, 3) (OD) {$\bm{\mathcal{O}}$: Output decoder};
-\node [block, text width=2cm] at (-4, 1.5) (TE) {$\bm{\mathcal{T}}$: Target encoder};
-\path [line] (perc.north) to (IE.west);
-%%\path [line] (lang.north) to ([xshift=0.05cm, yshift=0.05cm]LE.south west);
-\path [line] (IE.east) to (rep.south west);
-%%\path [line] (LE.east) to (rep.west);
-\path [line] (rep.north west) to ([xshift=-0.05cm, yshift=0.05cm]OD.south east);
-\path [line] (OD.north) to (act.east);
-\path [line] (tar.south) to (TE.west);
-\path [line] (TE.east) to (rep.north west);
-
-% meta
-\draw [boundingbox] (-1.9, 5) rectangle (5.85, -5); 
-\node [text=gray] at (-0.4, 4.7) {\textbf{Meta Learner}};
-
-\node [dashblock] at (0.2, -2.5) (collection) {
-\(\left\{
-\begin{matrix}
-(z_{in,0}, z_{out,0}),\\
-(z_{in,1}, z_{out,1}),\\
-$\vdots$
-\end{matrix}\right\}\)};
-\path [line] (rep.south) to (collection);
-\path [line] ([xshift=-1em]rep.south) to (collection);
-\path [line] ([xshift=1em]rep.south) to (collection);
-
-\node [block] at (4.2, 0) (meta) {\begin{tabular}{c}$\bm{\mathcal{M}}$: Meta \\ network\end{tabular}};
-\path [line] (collection.south) to [out=-90, in=-90] (meta.south);
-\path [line] (meta.west) to (rep.east);
-
-% hyper
-
-\node [block] at (4.2, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: Hyper \\ network\end{tabular}};
-\node [block, dash pattern=on 9pt off 2pt] at (0.2, 2) (transform) {\(F: \bm{Z} \rightarrow \bm{Z}\)};
-
-\path [draw, ->, very thick] (rep.north east) to (hyper.south);
-\path [draw, ->, very thick] (hyper.west) to (transform.north east);
-\path [draw, ->, very thick] ([xshift=-1em]transform.south) to ([xshift=-1em]rep.north);
-\path [draw, ->, very thick] ([xshift=1em]rep.north) to ([xshift=1em]transform.south);
-
-\end{tikzpicture}
-\caption{Schematic of the architecture}
-\end{subfigure}%
-\begin{subfigure}[b]{0.28\textwidth}
-\begin{tikzpicture}[auto, scale=0.66, every node/.style={scale=0.85}]
-\node at (-1.5, -3.6) (examples) {Examples};
-\node at (-1.5, -2.5) (D1) {
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\node[lightgray] at (-1.45, 2.9) {Basic meta-learning};
+\node at (-1.5, -4) (examples) {Examples};
+\node at (-1.5, -3.2) (D1) {
 \(\left\{
@@
 
-\node at (1.5, -3.6) (examples) {Probes};
-\node at (1.5, -2.5) (D2) {
+\node at (1.5, -4) (probes) {Probes};
+\node at (1.5, -3.2) (D2) {
 %\(z^{prb}_{in}\)};
@@
 
-\node at (-0.33, -0.66) (zfunc) {\(z^{func}\)};
+\node [block] at (-1.5, -1.75) (M) {\(\mathcal{M}\)};
+\path [arrow] ([yshift=-5]D1.north) to (M);
 
-\path [arrow] (D1) to [in=-145, out=90] ([xshift=3, yshift=3]zfunc.south west) node [xshift=-16, yshift=-5] {\(\mathcal{M}\)};
+\node at (-1, -0.7) (zfunc) {\(z^{func}\)};
+\path [arrow, out=90, in=-135] (M.north) to ([xshift=6,yshift=3]zfunc.south west);
 
-\node at (1.5, -0.25) (F) {\(F\)};
+\node[block] at (0, -0.25) (H) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]zfunc.north) to (H.west);
 
-\path [arrow, bend left] ([xshift=-5, yshift=-5]zfunc.north east) to [in=165, out=25] ([xshift=3]F.west) node [xshift=-13, yshift=5]{\(\mathcal{H}\)};
+\node [block, dashed] at (1.5, -0.25) (F) {\(F_{z^{func}}\)};
+\path[arrow] (H.east) to (F.west);
 
@@
 \end{matrix}\right\}\)};
-\node at (1.5, 2.9) (predictions) {Predictions};
+\node at (1.5, 2.65) (predictions) {Predictions};
 
@@
 
-\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (dispatch) {Loss or eval or ...};
+\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (dispatch) {\baselineskip=12pt Loss or eval or ...\par};
 
@@
 
-% for spacing
+%% meta mapping
+\begin{scope}[shift={(6.4, 2)}]
+\draw[boundingbox, draw=bpurp, fill=white] (-3, -4.3) rectangle (2.6, 3.2);
+\node[bpurp] at (-1.85, 2.9) {Meta-mapping};
+\node at (-1.5, -4) (metaexamples) {Examples};
+\node at (-1.5, -3.2) (metaD1) {
+\(\left\{
+\begin{matrix}
+(z^{func}_{in,0}, z^{func}_{targ,0})\\
+$\vdots$
+\end{matrix}\right\}\)};
 
-\node at (0, -5.5) {};
+\node at (1.5, -4) (metaprobes) {Probes};
+\node at (1.5, -3.2) (metaD2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{func,prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [block] at (-1.5, -1.75) (metaM) {\(\mathcal{M}\)};
+\path [arrow] ([yshift=-5]metaD1.north) to (metaM);
+
+\node at (-1, -0.7) (metazfunc) {\(z^{meta}\)};
+\path [arrow, out=90, in=-135] (metaM.north) to ([xshift=6,yshift=3]metazfunc.south west);
+
+\node[block] at (0, -0.25) (metaH) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]metazfunc.north) to (metaH.west);
+
+\node [block, dashed] at (1.5, -0.25) (metaF) {\(F_{z^{meta}}\)};
+\path[arrow] (metaH.east) to (metaF.west);
+
+\path [arrow, dashed] (metaD2) to (metaF);
+
+\node at (1.5, 1.75) (metaoutputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{func,pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 2.65) (metapredictions) {Predictions};
+
+\path [arrow, dashed] (metaF) to ([yshift=3]metaoutputs.south);
+
+\node [align=center, text width=1.5 cm] at (-1.5, 1.75) (metadispatch) {Loss (training)};
+\path [arrow, dashed] (metaoutputs.west) to ([xshift=-3]metadispatch.east);
+\end{scope}
+\path [arrow, draw=bpurp, dotted, out=-40, in=-140] ([xshift=-1, yshift=3]zfunc.south) to ([xshift=19, yshift=3]metaD1.west);
+
+%% evaluating meta mapping
+\begin{scope}[shift={(11.8, 0)}]
+\draw[boundingbox, draw=bblue, fill=white] (-2.25, -4.3) rectangle (2.5, 3.2);
+\node[bblue, text width=2.5cm] at (-0.9, 2.75) {Meta-mapping evaluation};
+
+\node at (1.5, -4) (metaevalprobes) {Probes};
+\node at (1.5, -3.2) (metaevalD2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (-1, -0.7) (metaevalzfunc) {\(z^{func,pred}\)};
+
+\node[block] at (0, -0.25) (metaevalH) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]metaevalzfunc.north) to (metaevalH.west);
+
+\node [block, dashed] at (1.5, -0.25) (metaevalF) {\(F_{z^{func,pred}}\)};
+\path[arrow] (metaevalH.east) to (metaevalF.west);
+
+\path [arrow, dashed] (metaevalD2) to (metaevalF);
+
+\node at (1.5, 1.75) (metaevaloutputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 2.65) (metaevalpredictions) {Predictions};
+
+\path [arrow, dashed] (metaevalF) to ([yshift=3]metaevaloutputs.south);
+
+\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (metaevaldispatch) {Loss (eval)};
+\path [arrow, dashed] (metaevaloutputs.west) to ([xshift=-3]metaevaldispatch.east);
+\end{scope}
+\path [arrow, very thick, draw=bblue, dotted, out=-30, in=160] (metaoutputs.center) to ([xshift=5, yshift=-5]metaevalzfunc.north west);
 \end{tikzpicture}
-\caption{Meta-learner inference}
-\end{subfigure}
-\caption{The EML architecture and an inference step.
-(a) A schematic of the architecture.
-Blocks with solid edges denote learnable deep networks, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$.
-Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g.
-both language and vision.
-See appendix \ref{app_model_details} for details.
-(b) Depiction of a meta-learner forward pass.
-This process is identical between basic tasks and meta-mappings, except for where the example and probe embeddings come from, and how the loss or evaluation is computed.
-For basic inference, the example and probe embeddings come from basic inputs and outputs, and loss is computed in the output space.
-For meta-mapping, the example and probe input and outputs are task embeddings of basic tasks, and loss for training is computed in the embedding space, while evaluation is done by using the predicted embedding to perform the target task.} \label{architecture_inference_fig}
+\caption{The EML architecture allows for transformations at different levels of abstraction.
+Basic meta-learning proceeds as in the gray box: a dataset consisting of (input, output) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
+However, our approach goes byeond this basic meta-learning step.
+The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping.
+To evaluate meta-mapping performance, a probe embedding from a held-out funciton is transformed by the architecture to yield a predicted embedding for the transformed task.
+The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task.
+Because the function embedding is predicted by a transformation rather than computed from examples, this allows for zero-shot performance of a new task.
+(Blocks with solid edges denote learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
+See the text and appendix \ref{app_model_details} for further details.)} \label{architecture_inference_fig}
 \end{figure}
@@
 \vspace{-0.5em}
-\paragraph{Basic meta-learning:} To perform a basic task, a dataset $D_1$ is encoded by $\mathcal{I}$ and $\mathcal{T}$.
-These examples are fed to $\mathcal{M}$ to produce a function embedding.
-This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset $D_2$ of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples.
+These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network including an element-wise max across the examples).
+This function embedding is mapped through they hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
 This system can be trained end-to-end on targets for the second dataset.
@@
 \par
-More explicitly, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from some other dataset $D_2$ for which to predict an output $\hat{y}$.
+More explicitly, suppose we have a dataset of example input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from a probe dataset $D_2$ for which to predict an output $\hat{y}$.
 $\hat{y}$ would be generated as follows:
-\[\hat{y} = \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
-where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
-\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ...
-\right\}\right)\right)\]
-This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$.
+\[\hat{y} = \mathcal{O}\left(F_{z^{func}}\left(\mathcal{I} \left(x\right)\right) \right)\]
+where $F_{z^{func}}$ is the meta-learners guess at a representation for the function underlying the training dataset $D_1$:
+\[F_{z^{func}} \text{ is parameterized by } \mathcal{H}\left(z^{func}\right), \text{ where } z^{func} = \mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), ...
+\right\}\right)\]
+This system can be trained end-to-end if labels are provided for the probe dataset $D_2$.
 In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
-We define our total loss computed on some dataset $D_2$ as:
+We define our total loss computed on the probe dataset $D_2$ as:
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-%\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
-The key advantage of our architecture is that it allows transforming anything that is embedded in $Z$ using the same system.
-Because tasks are embedded in $Z$, this allows for meta-mappings.
-For example, suppose we have an embedding $z_{go} \in Z$ for the task of playing go.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of winning and trying-to-lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{checkers},z_{checkers,lose}\right), ...
-\right\}\right)$.
-We can generate a new task embedding $\hat{z}_{new} \in Z$:
-%\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
-%This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go.
-We could then evaluate whether the system loses with the $\hat{z}_{new}$ strategy.
-All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the task embedding.
-\par
-\paragraph{Meta-mapping:} However, the system is not limited to simply mapping inputs to outputs.
+\paragraph{Meta-mapping:} However, the system is not limited to basic meta-learning.
 The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.

### 2019-09-05 writing/embedded_meta_learning_main.tex
Further tweaks

@@
 \paragraph{Meta-mapping:} However, the system is not limited to basic meta-learning.
-The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.
+The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig.
+\ref{architecture_inference_fig}).
 From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
@@
 To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task.
-Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy.
+Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding.
 This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks.

### 2019-09-07 writing/embedded_meta_learning_main.tex
Tweaking figure, trying to cut length

@@
 \begin{document}
-\title{Zero-shot adaptation by meta-mapping between tasks}
+\title{Zero-shot task adaptation by homoiconic meta-mapping}
 \author{%
@@
 We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
-We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Embedded Meta-Learning (EML) architectures that represent both data and tasks in a shared latent space.
-EML architectures are applicable to any type of machine learning task, including supervised learning and reinforcement learning.
+We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space.
+HoMM approaches can be applied to any type of machine learning task, including supervised learning and reinforcement learning.
 We demonstrate the utility of this perspective by exhibiting zero-shot remapping of behavior to adapt to new tasks.
@@
 We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge.
-By allowing the network to recursively treat its task representations as data points that can be transformed to produce new task representations, our approach is able to achieve this flexibility parsimoniously, without adding additional parameters beyond what we use for basic meta-learning.
+By allowing the network to recursively treat its task representations as data points, and transform them to produce new task representations, our approach is able to achieve this flexibility parsimoniously.
 We suggest that approaches like ours will be key to building more intelligent and flexible deep learning systems.
@@
 
+\vspace{-0.25em}
 \section{Meta-mapping}
@@
 We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-There are different ways this adaptation can be cued, for example by examples of similar task mappings (``you've played winning and losing poker, now try to lose at blackjack'') or simply by natural-language instructions (``try to lose at blackjack'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
-Achieving the flexibility to adapt to meta-map to new tasks will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
+This adaptation can be cued in different ways, for example by examples of similar task mappings (after winning and losing at poker, try to lose at blackjack) or simply by natural-language instructions (``try to lose at blackjack'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
+Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
 \par
 
-\section{Embedded Meta-Learning (EML) architecture}
+\vspace{-0.25em}
+\section{Homoiconic meta-mapping (HoMM) architecture}
 \vspace{-0.5em} % section
-To address these challenges, we propose EML architectures, which are composed of two components: 
+To address these challenges, we propose HoMM architectures, composed of two components: 
 \vspace{-1em}
 \begin{enumerate} \setlength \itemsep{0em}
-\item An input/output system: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system that embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior.
+\item Input/output systems: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
+\item A meta-learning system that embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior, and to systematically transform task embeddings.
 \end{enumerate}
 \vspace{-0.75em}
-Why have a completely shared space $Z$ for individual data points and tasks?
+These architectures are homoiconic because they have a completely shared space $Z$ for individual data points and tasks.
+Why is this useful?
 The primary advantage is that it allows for arbitrary mappings between these entities.
 In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior.
-That is, it can transform task representations using the same components it uses to transform basic data points, because the task representations and basic data points are embedded in the same space.
-\par
+That is, it can transform task representations using the same components it uses to transform basic data points.
+(See appendix \ref{app_lesion_results_shared_z} for further discussion.) \par
 Without training on meta-mappings, of course, the system will not be able to execute them well.
-However, as we will show, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-task distribution.
+However, as we will show, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-mapping distribution.
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
@@
 
-\node [block] at (-1.5, -1.75) (M) {\(\mathcal{M}\)};
+\node [block] at (-1.5, -1.95) (M) {\(\mathcal{M}\)};
 \path [arrow] ([yshift=-5]D1.north) to (M);
 
-\node at (-1, -0.7) (zfunc) {\(z^{func}\)};
+\node at (-1, -1) (zfunc) {\(z^{func}\)};
 \path [arrow, out=90, in=-135] (M.north) to ([xshift=6,yshift=3]zfunc.south west);
 
-\node[block] at (0, -0.25) (H) {\(\mathcal{H}\)};
+\node[block] at (0, -0.55) (H) {\(\mathcal{H}\)};
 \path [arrow, out=45, in=180] ([yshift=-3]zfunc.north) to (H.west);
 
-\node [block, dashed] at (1.5, -0.25) (F) {\(F_{z^{func}}\)};
+\node [block, dashed] at (1.5, -0.55) (F) {\(F_{z^{func}}\)};
 \path[arrow] (H.east) to (F.west);
@@
 
-\node at (1.5, 1.75) (outputs) {
+\node at (1.5, 1) (outputs) {
 %\(z^{pred}_{out}\)};
@@
 \end{matrix}\right\}\)};
-\node at (1.5, 2.65) (predictions) {Predictions};
+\node at (1.5, 1.75) (predictions) {Predictions};
 
@@
 
-\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (dispatch) {\baselineskip=12pt Loss or eval or ...\par};
+\node at (-1.5, 1.75) (probetargs) {Probe targets};
+\node at (-1.5, 1) (D2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
 
-\path [arrow, dashed] (outputs.west) to ([xshift=-3]dispatch.east);
+\node [align=center, text width=1.25 cm] at (0, 2.25) (dispatch) {\baselineskip=12pt Loss\par};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]outputs.west) to (dispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=-3.5]D2targs.east) to (dispatch.south);
 
 %% meta mapping
-\begin{scope}[shift={(6.4, 2)}]
+\begin{scope}[shift={(6.4, 1.5)}]
 \draw[boundingbox, draw=bpurp, fill=white] (-3, -4.3) rectangle (2.6, 3.2);
@@
 
-\node [block] at (-1.5, -1.75) (metaM) {\(\mathcal{M}\)};
+\node [block] at (-1.5, -1.95) (metaM) {\(\mathcal{M}\)};
 \path [arrow] ([yshift=-5]metaD1.north) to (metaM);
 
-\node at (-1, -0.7) (metazfunc) {\(z^{meta}\)};
+\node at (-1, -1) (metazfunc) {\(z^{meta}\)};
 \path [arrow, out=90, in=-135] (metaM.north) to ([xshift=6,yshift=3]metazfunc.south west);
 
-\node[block] at (0, -0.25) (metaH) {\(\mathcal{H}\)};
+\node[block] at (0, -0.55) (metaH) {\(\mathcal{H}\)};
 \path [arrow, out=45, in=180] ([yshift=-3]metazfunc.north) to (metaH.west);
 
-\node [block, dashed] at (1.5, -0.25) (metaF) {\(F_{z^{meta}}\)};
+\node [block, dashed] at (1.5, -0.55) (metaF) {\(F_{z^{meta}}\)};
 \path[arrow] (metaH.east) to (metaF.west);
@@
 
-\node at (1.5, 1.75) (metaoutputs) {
+\node at (1.5, 1) (metaoutputs) {
 %\(z^{pred}_{out}\)};
@@
 \end{matrix}\right\}\)};
-\node at (1.5, 2.65) (metapredictions) {Predictions};
+\node at (1.5, 1.75) (metapredictions) {Predictions};
 
@@
 
-\node [align=center, text width=1.5 cm] at (-1.5, 1.75) (metadispatch) {Loss (training)};
-\path [arrow, dashed] (metaoutputs.west) to ([xshift=-3]metadispatch.east);
+\node at (-1.5, 1.75) (metaprobetargs) {Probe targets};
+\node at (-1.5, 1) (metaD2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{func,prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [align=center] at (0, 2.25) (metadispatch) {Loss (train)};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]metaoutputs.west) to (metadispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=1]metaD2targs.east) to (metadispatch.south);
+
 \end{scope}
-\path [arrow, draw=bpurp, dotted, out=-40, in=-140] ([xshift=-1, yshift=3]zfunc.south) to ([xshift=19, yshift=3]metaD1.west);
+\path [arrow, very thick, draw=bpurp, dotted, out=-40, in=-140] ([xshift=-1, yshift=3]zfunc.south) to ([xshift=19, yshift=3]metaD1.west);
 
@@
 \draw[boundingbox, draw=bblue, fill=white] (-2.25, -4.3) rectangle (2.5, 3.2);
-\node[bblue, text width=2.5cm] at (-0.9, 2.75) {Meta-mapping evaluation};
+\node[bblue] at (-0.35, 2.9) {Meta-mapping evaluation};
 
@@
 
-\node at (-1, -0.7) (metaevalzfunc) {\(z^{func,pred}\)};
+\node at (-1, -1) (metaevalzfunc) {\(z^{func,pred}\)};
 
-\node[block] at (0, -0.25) (metaevalH) {\(\mathcal{H}\)};
+\node[block] at (0, -0.55) (metaevalH) {\(\mathcal{H}\)};
 \path [arrow, out=45, in=180] ([yshift=-3]metaevalzfunc.north) to (metaevalH.west);
 
-\node [block, dashed] at (1.5, -0.25) (metaevalF) {\(F_{z^{func,pred}}\)};
+\node [block, dashed] at (1.5, -0.55) (metaevalF) {\(F_{z^{func,pred}}\)};
 \path[arrow] (metaevalH.east) to (metaevalF.west);
@@
 
-\node at (1.5, 1.75) (metaevaloutputs) {
+\node at (1.5, 1) (metaevaloutputs) {
 %\(z^{pred}_{out}\)};
@@
 \end{matrix}\right\}\)};
-\node at (1.5, 2.65) (metaevalpredictions) {Predictions};
+\node at (1.5, 1.75) (metaevalpredictions) {Predictions};
 
@@
 
-\node [align=center, text width=1.25 cm] at (-1.5, 1.75) (metaevaldispatch) {Loss (eval)};
-\path [arrow, dashed] (metaevaloutputs.west) to ([xshift=-3]metaevaldispatch.east);
+\node at (-1, 1.75) (metaevalprobetargs) {Probe targets};
+\node at (-1, 1) (metaevalD2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [align=center] at (0.3, 2.25) (metaevaldispatch) {Loss (eval)};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]metaevaloutputs.west) to (metaevaldispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=-0.5]metaevalD2targs.east) to (metaevaldispatch.south);
 \end{scope}
@@
 \end{tikzpicture}
-\caption{The EML architecture allows for transformations at different levels of abstraction.
+\caption{The HoMM architecture allows for transformations at different levels of abstraction.
 Basic meta-learning proceeds as in the gray box: a dataset consisting of (input, output) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
-However, our approach goes byeond this basic meta-learning step.
-The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping.
+However, our approach goes beyond this basic meta-learning step.
+The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (purple box).
 To evaluate meta-mapping performance, a probe embedding from a held-out funciton is transformed by the architecture to yield a predicted embedding for the transformed task.
-The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task.
+The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (blue box).
 Because the function embedding is predicted by a transformation rather than computed from examples, this allows for zero-shot performance of a new task.
 (Blocks with solid edges denote learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
-See the text and appendix \ref{app_model_details} for further details.)} \label{architecture_inference_fig}
+See the text and appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
 \end{figure}
 \looseness=-1
-More formally, we take a \emph{functional} perspective on learning.
+More formally, we treat functions and data as entities of the same type.
 From this perspective, the data points that one function receives can themselves be functions\footnote{Indeed, any data point can be represented as a constant function that outputs the data point.}.
@@
 The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.} to perform basic tasks (as is standard in machine learning), but it can also transform these task functions to adapt to new tasks.
-This is related to the idea of a homoiconicity, defined above.
+This is related to the idea of homoiconicity, defined above, and the concept of higher-order functions.
 Under this perspective, basic tasks and meta-mappings from task to task are really the same type of problem.
@@
 Specifically, we embed each input, target, or mapping into a shared representational space $Z$.
-This means that single data points are embedded in the same space as the representation of a functionr or an entire dataset.
-See appendix \ref{app_lesion_results_shared_z} for discussion of why $Z$ should be shared.
+This means that single data points are embedded in the same space as the representation of a function or an entire dataset.
 Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$.
-Model outputs are decoded from $Z$ by a deep network $\mathcal{O}: Z \rightarrow \text{output}$.
-Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$.\par
+Model outputs are decoded from $Z$ by $\mathcal{O}: Z \rightarrow \text{output}$.
+Target outputs are encoded by $\mathcal{T}: \text{targets} \rightarrow Z$.\par
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
@@
 \par
-More explicitly, suppose we have a dataset of example input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from a probe dataset $D_2$ for which to predict an output $\hat{y}$.
-$\hat{y}$ would be generated as follows:
+More explicitly, suppose we have a dataset of example input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some input $x$ from a probe dataset $D_2$.
+The system would predict a corresponding output $\hat{y}$ as:
 \[\hat{y} = \mathcal{O}\left(F_{z^{func}}\left(\mathcal{I} \left(x\right)\right) \right)\]
-where $F_{z^{func}}$ is the meta-learners guess at a representation for the function underlying the training dataset $D_1$:
+where $F_{z^{func}}$ is the meta-learner's representation for the function underlying the examples in $D_1$:
 \[F_{z^{func}} \text{ is parameterized by } \mathcal{H}\left(z^{func}\right), \text{ where } z^{func} = \mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), ...
@@
 Furthermore, our approach is parsimonious.
-Because it uses the same meta-learner for both basic tasks and meta-mappings, this increased flexibility does not require any added parameters.\footnote{At least in principle, in practice of course increasing network size might be more beneficial for EML architectures performing meta-mappings as well as basic tasks than for those performing only basic tasks.}
+Because it uses the same meta-learner for both basic tasks and meta-mappings, this increased flexibility does not require any added parameters.\footnote{At least in principle, in practice of course increasing network size might be more beneficial for HoMM architectures performing meta-mappings as well as basic tasks than for those performing only basic tasks.}
 
@@
 \end{subfigure}%
-\caption{The EML system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
+\caption{The HoMM system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
 (\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}.
@@
 \end{subfigure}%
-\caption{The EML architecture performs well at meta-mappings.
+\caption{The HoMM architecture performs well at meta-mappings.
 (\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings.
@@
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig.
-\ref{poly_meta_map_results_examples}.
+\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig.
+\ref{poly_meta_map_results_examples}).
 We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
-We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on.
-The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping.
+We then test its ability to generalize to held-out mappings, for example a held-out input permutation, or an unseen additive shift.
+The system is both able to apply learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping.
 \par
@@
 %% Can cut The hand is explicitly ..., maybe some other stuff
-In order to adapt the EML architecture, we made a very simple change.
+In order to adapt the HoMM architecture, we made a very simple change.
 Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
@@
 \vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to play a held-out game from examples in fig.
 \ref{cards_basic_results}.
-We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game.
+We compare two different hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game.
 In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case.
 Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}.
+Furthermore, the task embeddings generated by the system are semantically organized, see appendix \ref{app_cards_tsne}.
 \par
@@
 \end{subfigure}
-\caption{The EML system can perform meta-mappings from language cues rather than meta-mapping examples.
+\caption{The HoMM system can perform meta-mappings from language cues rather than meta-mapping examples.
 Compare to fig.
@@
 This is a much more efficient way to achieve zero-shot performance on a new losing task.
-In order to replicate this, we trained the EML system with both meta-mappings based on examples, and meta-mappings based on language.
+In order to replicate this, we trained the HoMM system with both meta-mappings based on examples, and meta-mappings based on language.
 In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is encoded by a language encoder, and then provided as the input to $\mathcal{H}$ (instead of an output from $\mathcal{M}$).
@@
 However, achieving this type of flexibility is difficult in architectures that separate computation from the knowledge of what is being computed.
-To address this, our EML architecture explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
-This allows for our key insight: using transformations over task embeddings to transform the system's behavior.
-This is analogous to how transformations over data perform basic tasks.
-Following this analogy, the EML architecture takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space.
+To address this, our HoMM approach explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
+This allows for our key insight: by embedding tasks and individual data points in a shared latent space, the same meta-learning architecture can be used both to transform data for basic tasks, and to transformat task embeddings to adapt to task variations.
 This approach is parsiomious, because it uses the same networks for basic- and meta-mappings.

### 2019-09-07 writing/embedded_meta_learning_appendix.tex
Fixing some references
length cuts

@@
 \hline \\[-1.8ex]
-EML & Trained & 0.015 & 0.012 & 0.018 \\
-EML & Held out & 0.246 & 0.188 & 0.308 \\
-Untrained EML network & Trained & 5.735 & 4.823 & 6.74 \\
-Untrained EML network & Held out & 5.968 & 4.984 & 6.991 \\
+HoMM & Trained & 0.015 & 0.012 & 0.018 \\
+HoMM & Held out & 0.246 & 0.188 & 0.308 \\
+Untrained HoMM network & Trained & 5.735 & 4.823 & 6.74 \\
+Untrained HoMM network & Held out & 5.968 & 4.984 & 6.991 \\
 \hline \\[-1.8ex]
@@
 \hline \\[-1.8ex]
-EML & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
-EML & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
-EML & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
-EML & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
-Untrained EML network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
-Untrained EML network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
-Untrained EML network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
-Untrained EML network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
+HoMM & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
+HoMM & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
+HoMM & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
+HoMM & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
+Untrained HoMM network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
+Untrained HoMM network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
+Untrained HoMM network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
+Untrained HoMM network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
 \hline \\[-1.8ex]
@@
 Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
-Untrained EML network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
-Untrained EML network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
-Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
-Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
+Untrained HoMM network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
+Untrained HoMM network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
+Untrained HoMM network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
+Untrained HoMM network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
 \hline \\[-1.8ex] 
@@
 \end{tabular}
-\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in figure \ref{cards_meta_map_results}}
+\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in figure \ref{cards_meta_map_results_examples}}
 \end{table}

### 2019-09-07 writing/embedded_meta_learning_main.tex
length cuts

@@
 We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-This adaptation can be cued in different ways, for example by examples of similar task mappings (after winning and losing at poker, try to lose at blackjack) or simply by natural-language instructions (``try to lose at blackjack'', see appendix \ref{app_why_meta_mapping} for a comparison to conditioning on a task description.).
+This adaptation can be cued in different ways, for example by examples of similar task mappings (after winning and losing at poker, try to lose at blackjack) or simply by natural-language instructions (``try to lose at blackjack'').
 Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
@@
 The approach is agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.} to perform basic tasks (as is standard in machine learning), but it can also transform these task functions to adapt to new tasks.
-This is related to the idea of homoiconicity, defined above, and the concept of higher-order functions.
+This is related to the concepts of homoiconicity, defined above, and higher-order functions.
 Under this perspective, basic tasks and meta-mappings from task to task are really the same type of problem.
@@
 \paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples.
-These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network including an element-wise max across the examples).
+These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples).
 This function embedding is mapped through they hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
-This system can be trained end-to-end on targets for the second dataset.
+This system can be trained end-to-end on target outputs for the probes.
 Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.
-See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters.
+See appendix \ref{app_model_details} for detailed architecture, and hyper-parameters.
 \par
@@
 \par
+\vspace{-0.5em}
 \section{An extension via language}
@@
 \end{figure}
-Language is fundamental to human flexibility, and we would be remiss to ignore it.
-In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world.
+Language is fundamental to human flexibility.
+Often the examples of the meta-mapping are implicit in prior knowledge about the world that is cued by language.
 For example, ``try to lose at go'' does not give explicit examples of the ``lose'' meta-mapping, but rather relies on prior knowledge of what losing means.
-This is a much more efficient way to achieve zero-shot performance on a new losing task.
+This is a much more efficient way to cue a known meta-mapping.
 In order to replicate this, we trained the HoMM system with both meta-mappings based on examples, and meta-mappings based on language.
@@
 
+\vspace{-0.5em}
 \section{Discussion} \label{sec_discussion}
@@
 \looseness=-1
-We've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks.
+We've highlighted a new type of flexibility in the form of meta-mapping between tasks.
 Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks.
-However, achieving this type of flexibility is difficult in architectures that separate computation from the knowledge of what is being computed.
-To address this, our HoMM approach explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
+However, achieving this flexibility is difficult in architectures that separate computation from the knowledge of what is being computed.
+To address this, our Homoiconic Meta-Mapping (HoMM) approach explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
 This allows for our key insight: by embedding tasks and individual data points in a shared latent space, the same meta-learning architecture can be used both to transform data for basic tasks, and to transformat task embeddings to adapt to task variations.
@@
 Perhaps because of this, the requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.
-That is, we are able to achieve zero-shot performance on a novel task based on a relationship between tasks that was never trained on.
+That is, we are able to achieve zero-shot performance on a novel task based on a held-out relationship between tasks.
 This is a step closer to human-level flexibility.\par

### 2019-09-08 writing/homoiconic_meta_mapping_main.tex
Name tweaks
preprint version
Further tweaks from Jay

--- 2019-09-07 writing/embedded_meta_learning_main.tex
@@
 
-\usepackage{neurips_2019}
+\usepackage[preprint]{neurips_2019}
 
@@
 While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
-(We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) \par
+(We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) This adaptation can be cued in several ways, including examples of the mapping (after winning and losing at poker, try to lose at blackjack) or natural-language instructions (``try to lose at blackjack'').
+\par
 We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to some variation on that task.
@@
 Given appropriate conditioning (see below), our architecture can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
-We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.\par
-This adaptation can be cued in different ways, for example by examples of similar task mappings (after winning and losing at poker, try to lose at blackjack) or simply by natural-language instructions (``try to lose at blackjack'').
-Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to exactly the training domains it has seen.
+We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.
+Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to precisely the training domains it has seen.
 \par
@@
 \item Input/output systems: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
-\item A meta-learning system that embeds tasks into the shared embedding space $Z$, and learns to map task embeddings to behavior, and to systematically transform task embeddings.
-\end{enumerate}
+\item A meta-learning system that a) learns to embed tasks into the shared embedding space $Z$, b) learns to use these task embeddings to perform task-appropriate behavior, c) learns to embed meta-mappings into the same space, and d) learns to use these meta-mapping embeddings to transform basic task embeddings in a meta-mapping appropriate way.\end{enumerate}
 \vspace{-0.75em}
-These architectures are homoiconic because they have a completely shared space $Z$ for individual data points and tasks.
+\looseness=-1
+These architectures are homoiconic because they have a completely shared $Z$ for individual data points, tasks, and meta-mappings.
 Why is this useful?
-The primary advantage is that it allows for arbitrary mappings between these entities.
+The primary advantage is that it parsimoniously allows for arbitrary mappings between these entities.
 In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior.
 That is, it can transform task representations using the same components it uses to transform basic data points.
-(See appendix \ref{app_lesion_results_shared_z} for further discussion.) \par
+(See also appendix \ref{app_lesion_results_shared_z}.) \par
 Without training on meta-mappings, of course, the system will not be able to execute them well.
@@
 For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however.
-This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relatively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}.
+This reflects the structure of human behavior -- we are able to adapt rapidly when new knowledge is relatively consistent with our prior knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}.
 \par
@@
 \draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
-\node[lightgray] at (-1.45, 2.9) {Basic meta-learning};
+\node[lightgray] at (-1.2, 2.9) {(a) Basic meta-learning};
 \node at (-1.5, -4) (examples) {Examples};
@@
 \draw[boundingbox, draw=bpurp, fill=white] (-3, -4.3) rectangle (2.6, 3.2);
-\node[bpurp] at (-1.85, 2.9) {Meta-mapping};
+\node[bpurp] at (-1.6, 2.9) {(b) Meta-mapping};
 \node at (-1.5, -4) (metaexamples) {Examples};
@@
 \draw[boundingbox, draw=bblue, fill=white] (-2.25, -4.3) rectangle (2.5, 3.2);
-\node[bblue] at (-0.35, 2.9) {Meta-mapping evaluation};
+\node[bblue] at (-0.1, 2.9) {(c) Meta-mapping evaluation};
 
@@
 \caption{The HoMM architecture allows for transformations at different levels of abstraction.
-Basic meta-learning proceeds as in the gray box: a dataset consisting of (input, output) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
-However, our approach goes beyond this basic meta-learning step.
+For basic meta-learning (gray), a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
+However, our approach goes beyond basic meta-learning.
 The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (purple box).
-To evaluate meta-mapping performance, a probe embedding from a held-out funciton is transformed by the architecture to yield a predicted embedding for the transformed task.
+To evaluate meta-mapping performance, a probe embedding of a held-out function is transformed by the architecture to yield a predicted embedding for the transformed task.
 The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (blue box).
 Because the function embedding is predicted by a transformation rather than computed from examples, this allows for zero-shot performance of a new task.
-(Blocks with solid edges denote learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
+(\(M\) and \(H\) are learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
+Input and output encoders/decoders are omitted for simplicity.
 See the text and appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
@@
 \vspace{-0.5em}
-\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples.
+\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig.
+\ref{architecture_inference_fig}a).
 These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples).
@@
 \right\}\right)\]
-This system can be trained end-to-end if labels are provided for the probe dataset $D_2$.
-In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$.
-We define our total loss computed on the probe dataset $D_2$ as:
+Then, given some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and an actual model output $\hat{y}$, we define our total loss computed on the probe dataset $D_2$ as: 
 \[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
-\paragraph{Meta-mapping:} However, the system is not limited to basic meta-learning.
-The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig.
-\ref{architecture_inference_fig}).
+The system can then be trained end-to-end on this loss to adjust the weights of \(\mathcal{T,H,M,O}\), and \(\mathcal{I}\).
+\paragraph{Meta-mapping:} The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig.
+\ref{architecture_inference_fig}b,c).
 From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
@@
 To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task.
-Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding.
+Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding (fig.
+\ref{architecture_inference_fig}c).
 This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks.
@@
 The system successfully generalizes to held out polynomials.
-The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model).
+The solid line indicates optimal performance; the dashed line indicates untrained model performance.
 (\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}.
@@
 For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
-The solid line indicates optimal performance; the dashed line is chance (untrained).
+The solid line indicates optimal performance; the dashed line is untrained model performance.
 (\subref{cards_meta_map_results_examples}) The system generalizes to meta-mapping new tasks in the cards domain.
-The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on.
+The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to perform novel tasks it has not been trained on.
 For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
-When given a novel game, it is able to apply this mapping to guess how to play the losers variation.
+When given a held-out game, it is able to apply the mapping to guess how to play the losing variation.
 This plot shows the reward produced by taking the mapped embedding and playing the targeted game.
@@
 \par
-%\subsubsection*{Acknowledgements}
-%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
+\subsubsection*{Acknowledgements}
+We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
 
@@
 % comment the following to compile without appendix but with references
-\include{embedded_meta_learning_appendix}
+\include{homoiconic_meta_mapping_appendix}
 

### 2019-09-12 writing/homoiconic_meta_mapping_main.tex
Some small tweaks, starting to switch to ICLR format

@@
 
-\PassOptionsToPackage{numbers}{natbib}
+%\PassOptionsToPackage{numbers}{natbib}
 
-\usepackage[preprint]{neurips_2019}
+%\usepackage{neurips_2019}
+\usepackage{iclr2020_conference,times}
 
@@
 
-\setcitestyle{square}
+%\setcitestyle{square}
 
+%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 
-\vspace{-0.75em} % section
+%\vspace{-0.75em} % section
 \section{Introduction}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}.
@@
 
-\vspace{-0.25em}
+%\vspace{-0.25em}
 \section{Meta-mapping}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 %Can cut "the task"s in go sentence if needed
@@
 
-\vspace{-0.25em}
+%\vspace{-0.25em}
 \section{Homoiconic meta-mapping (HoMM) architecture}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 To address these challenges, we propose HoMM architectures, composed of two components: 
-\vspace{-1em}
+%\vspace{-1em}
 \begin{enumerate} \setlength \itemsep{0em}
@@
 \item A meta-learning system that a) learns to embed tasks into the shared embedding space $Z$, b) learns to use these task embeddings to perform task-appropriate behavior, c) learns to embed meta-mappings into the same space, and d) learns to use these meta-mapping embeddings to transform basic task embeddings in a meta-mapping appropriate way.\end{enumerate}
-\vspace{-0.75em}
+%\vspace{-0.75em}
 \looseness=-1
@@
 \par
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 \par
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig.
@@
 These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples).
-This function embedding is mapped through they hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
+This function embedding is mapped through the hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
 This system can be trained end-to-end on target outputs for the probes.
@@
 \section{Learning multivariate polynomials} \label{sec_poly}
-\vspace{-0.5em} % section
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 \end{subfigure}%
-\caption{The HoMM system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings.
-(\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}.
+\caption{The HoMM system succeeds at basic meta-learning, which is a necessary prerequisite for meta-mappings.
+(\subref{poly_basic_results}) The polynomials domain, section \ref{sec_poly}.
 The system successfully generalizes to held out polynomials.
 The solid line indicates optimal performance; the dashed line indicates untrained model performance.
-(\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}.
+(\subref{cards_basic_results}) The card games domain, section \ref{sec_cards}.
 The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
 The gray dashed line indicates chance performance, while the solid lines are optimal performance.
-The orange dashed lines show how well the system could perform by playing the strategy from the most correlated trained task.
-The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest.
+The orange dashed lines shows performance on held-out tasks of playing the strategy from the most correlated trained task.
+The fact that the system generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing strategies and picking the closest.
 Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
+The system succeeds at applying meta-mappings it is trained on to held-out polynomials, as well as applying held-out meta-mappings to either trained or held-out polynomials.
 The solid line indicates optimal performance; the dashed line is untrained model performance.
 (\subref{cards_meta_map_results_examples}) The system generalizes to meta-mapping new tasks in the cards domain.
-The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to perform novel tasks it has not been trained on.
+The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to perform novel tasks zero-shot.
 For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants.
@@
 
-%% Cut example if necessary
 As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e.
@@
 Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
-\vspace{-0.7em}
+%\vspace{-0.7em}
 \paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig.
@@
 \par
-\vspace{-0.7em}
+%\vspace{-0.7em}
 \paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig.
@@
 We then test its ability to generalize to held-out mappings, for example a held-out input permutation, or an unseen additive shift.
-The system is both able to apply learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping.
+The system is both able to apply learned meta-mappings to held-out basic tasks, and to apply held-out meta-mappings it has not been trained on, simply by seeing examples of the mapping.
 \par
@@
 \section{A stochastic learning setting: simple card games}\label{sec_cards}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
@@
 \par
-\vspace{-0.7em}
+%\vspace{-0.7em}
 \paragraph{Basic meta-learning:} First, we show that the system is able to play a held-out game from examples in fig.
@@
 \par
-\vspace{-0.7em}
+%\vspace{-0.7em}
 \paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
@@
 \par
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \section{An extension via language}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 \begin{figure}
@@
 
-\vspace{-0.5em}
+%\vspace{-0.5em}
 \section{Discussion} \label{sec_discussion}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 \paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
@@
 \par
- \vspace{-1em}
+% \vspace{-1em}
 \paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
@@
 \section{Conclusions}
-\vspace{-0.5em} % section
+%\vspace{-0.5em} % section
 \looseness=-1
@@
 \par
-\subsubsection*{Acknowledgements}
-We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
+%\subsubsection*{Acknowledgements}
+%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
 
-\bibliographystyle{acm}
+\bibliographystyle{apalike}
 \bibliography{arrr}

### 2019-09-13 writing/homoiconic_meta_mapping_main.tex
Tweaks

@@
 To address these challenges, we propose HoMM architectures, composed of two components: 
-%\vspace{-1em}
+\vspace{-0.5em}
 \begin{enumerate} \setlength \itemsep{0em}
@@
 \item A meta-learning system that a) learns to embed tasks into the shared embedding space $Z$, b) learns to use these task embeddings to perform task-appropriate behavior, c) learns to embed meta-mappings into the same space, and d) learns to use these meta-mapping embeddings to transform basic task embeddings in a meta-mapping appropriate way.\end{enumerate}
-%\vspace{-0.75em}
+\vspace{-0.5em}
 \looseness=-1
@@
 \caption{The HoMM architecture allows for transformations at different levels of abstraction.
-For basic meta-learning (gray), a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
+(a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
 However, our approach goes beyond basic meta-learning.
-The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (purple box).
+The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (b).
 To evaluate meta-mapping performance, a probe embedding of a held-out function is transformed by the architecture to yield a predicted embedding for the transformed task.
-The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (blue box).
-Because the function embedding is predicted by a transformation rather than computed from examples, this allows for zero-shot performance of a new task.
+The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (c).
+Because the function embedding is predicted by a transformation rather than from examples, new tasks can be performed zero-shot.
 (\(M\) and \(H\) are learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
@@
 \par
-%\vspace{-0.5em}
+\vspace{-0.5em}
 \paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig.
 \ref{architecture_inference_fig}a).
-These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples).
+These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, with several layers of parallel processing across examples, followed by an element-wise max across examples, and several more layers).
 This function embedding is mapped through the hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs.
@@
 The system can then be trained end-to-end on this loss to adjust the weights of \(\mathcal{T,H,M,O}\), and \(\mathcal{I}\).
+\vspace{-0.25em}
 \paragraph{Meta-mapping:} The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig.
@@
 \caption{The HoMM architecture performs well at meta-mappings.
-(\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings.
+(\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and even to apply unseen meta-mappings.
 The plots show the loss produced when evaluating the mapped embedding on the target task.
-For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$.
-The system succeeds at applying meta-mappings it is trained on to held-out polynomials, as well as applying held-out meta-mappings to either trained or held-out polynomials.
+For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by transforming the embedding of $p(x)$ and evaluating how well the mapped embedding regresses on to $p(x)^2 = x^2 + 2x + 1$.
+The results show that the system succeeds at applying meta-mappings it is trained on to held-out polynomials, as well as applying held-out meta-mappings to either trained or held-out polynomials.
 The solid line indicates optimal performance; the dashed line is untrained model performance.
@@
 Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
-%\vspace{-0.7em}
+\vspace{-0.7em}
 \paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig.
@@
 \par
-%\vspace{-0.7em}
+\vspace{-0.7em}
 \paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig.
@@
 We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial.
-We then test its ability to generalize to held-out mappings, for example a held-out input permutation, or an unseen additive shift.
-The system is both able to apply learned meta-mappings to held-out basic tasks, and to apply held-out meta-mappings it has not been trained on, simply by seeing examples of the mapping.
+We then test its ability to generalize to held-out mappings from examples, for example a held-out input permutation, or an unseen additive shift.
+The system is both able to apply learned meta-mappings to held-out polynomials, and to apply held-out meta-mappings it has not been trained on, simply by seeing examples of the mapping.
 \par
@@
 In order to adapt the HoMM architecture, we made a very simple change.
-Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state.
+Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it to predict rewards for each bet in each state.
 (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, because the outcome is only observed for the action you take, it is not a standard supervised task.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues.
 That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game.
-We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose.
+We also trained the system to make meta-mappings, for example switching from trying to win a game to trying to lose.
 Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.
@@
 % \vspace{-1em}
-\paragraph{Future Directions:} We think that the general perspective of embedding tasks and considering meta-mappings will yield many fruitful future directions.
+\paragraph{Future Directions:} We think that the general perspective of considering meta-mappings will yield many fruitful future directions.
 We hope that our work will inspire more exploration of behavioral adaptation, in areas beyond the simple domains we considered here.
 To this end, we suggest the creation of meta-learning datasets which include information not only about tasks, but about the relationships between them.
-For example,  as can reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019} can be usefully interpreted from this perspective.
+For example, reinforcement learning tasks which involve executing instructions \citep[e.g.][]{Hermann2017, Co-Reyes2019} can be usefully interpreted from this perspective.
 Furthermore, we think our work provides a novel perspective on the types of flexibility that human intelligence exhibits, and thus hope that it may have implications for cognitive science.

### 2019-09-23 writing/homoiconic_meta_mapping_main.tex
Tweaks
Reframing intro/conclusions slightly

@@
 The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot.
-We suggest that the key to achieving these challenges is representing the task being performed along with the computations used to perform it.
+We suggest that the key to achieving these challenges is representing the task being perform in such a way that this representation is itself transformable.
 We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space.
@@
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
+However, humans can use our knowledge of a task to flexibly adapt when the task changes.
+In particular, we can often perform an altered task zero-shot, that is, without seeing any data at all.
+For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can perform reasonably on our first attempt.
+\par
 One fundamental reason for this is that humans are aware of what we are trying to compute and why.
-By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks.
-That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations.
-\par
-\looseness=-1
-There are a number of advantages to representing knowledge about data and tasks together.
-In particular, it can grant the ability to rapidly adapt behavior to a new task.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
-However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction.
-For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e.
-zero-shot).
-Deep learning systems at present generally lack this representational flexibility.
+This allows us to adapt our task representations to perform a new task zero-shot.
+By contrast, most deep learning models do not explicitly represent tasks at all.
+Those that do (such as some meta-learning models) generally do not represent relationships between tasks, and so cannot adapt to a new task without data from the new task.
+To address this, it is necessary to represent tasks in a transformable space.
+This can grant the ability to rapidly adapt behavior to a new task.
 \par
@@
 mappings between tasks (see below).
-This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models.
+As noted above, this type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to deep-learning models.
 To address this challenge, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
@@
 While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility.
-Given appropriate conditioning (see below), our architecture can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
-We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it.
-Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to precisely the training domains it has seen.
+Given appropriate conditioning (see below), our architecture can use meta-mappings to adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}.
+Achieving this flexibility to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to precisely the training tasks it has seen.
 \par
@@
 \par
-For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
+For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game, and we want to switch to trying to lose this game.
+We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
 \right\}\right)$.
-We can generate a new task embedding $\hat{z}_{new} \in Z$:
-\[\hat{z}_{new} = F_{z_{\text{meta}}}(z_{game1}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
+We can generate a new task embedding $\hat{z}_{game1,lose} \in Z$:
+\[\hat{z}_{game1,lose} = F_{z_{\text{meta}}}(z_{game1}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
 \looseness=-1
-This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1.
-To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task.
-Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding (fig.
+This $\hat{z}_{games1,lose}$ can be interpreted as the system's guess at a losing strategy for game 1.
+To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guessed embedding and the embedding of the target task\footnote{The gradients do not update the example function embeddings, only the weights of \(\mathcal{M}\) and \(\mathcal{H}\), due to memory contraints.
+Allowing this might be useful in more complex applications.}.
+Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{game1,lose}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding (fig.
 \ref{architecture_inference_fig}c).
@@
 Furthermore, our approach is parsimonious.
-Because it uses the same meta-learner for both basic tasks and meta-mappings, this increased flexibility does not require any added parameters.\footnote{At least in principle, in practice of course increasing network size might be more beneficial for HoMM architectures performing meta-mappings as well as basic tasks than for those performing only basic tasks.}
+Because it uses the same meta-learner for both basic tasks and meta-mappings, this increased flexibility does not require any added parameters.\footnote{At least in principle, in practice of course increasing network size might be more beneficial for HoMM architectures performing meta-mappings as well as basic tasks, compared to those performing only basic tasks.}
 
@@
 \includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
-\caption{From language input.}
+\caption{The polynomials domain.}
 \label{poly_meta_map_results_language}
@@
 \includegraphics[width=\textwidth]{figures/language_meta_mapping.png}
-\caption{From language input.}
+\caption{The cards domain.}
 \label{cards_meta_map_results_language}
@@
 Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks.
-However, achieving this flexibility is difficult in architectures that separate computation from the knowledge of what is being computed.
+This is a key aspect of human flexibility, but is lacking from most contemporary deep-learning models.
+Achieving this flexibility requires representing tasks in a transformable way.
 To address this, our Homoiconic Meta-Mapping (HoMM) approach explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
-This allows for our key insight: by embedding tasks and individual data points in a shared latent space, the same meta-learning architecture can be used both to transform data for basic tasks, and to transformat task embeddings to adapt to task variations.
+This allows for our key insight: by embedding tasks and individual data points in a shared latent space, the same meta-learning architecture can be used both to transform data for basic tasks, and to transform task embeddings to adapt to task variations.
 This approach is parsiomious, because it uses the same networks for basic- and meta-mappings.

### 2019-09-24 writing/homoiconic_meta_mapping_main.tex
Typo + wording

@@
 The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot.
-We suggest that the key to achieving these challenges is representing the task being perform in such a way that this representation is itself transformable.
+The key to achieving these challenges is representing the task being performed in such a way that this task representation is itself transformable.
 We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space.

### 2019-10-29 writing/homoiconic_meta_mapping_main.tex
Preprint version
Tweaks and formatting for camera-ready for workshop

@@
 
-%\PassOptionsToPackage{numbers}{natbib}
+\PassOptionsToPackage{numbers}{natbib}
 
-%\usepackage{neurips_2019}
-\usepackage{iclr2020_conference,times}
+\usepackage[final]{neurips_2019}
+%\usepackage{iclr2020_conference,times}
 
@@
 
+%\iclrpreprintcopy
 %\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
@@
 
-%\vspace{-0.75em} % section
+\vspace{-0.75em} % section
 \section{Introduction}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}.
@@
 
-%\vspace{-0.25em}
+\vspace{-0.25em}
 \section{Meta-mapping}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 %Can cut "the task"s in go sentence if needed
@@
 
-%\vspace{-0.25em}
+\vspace{-0.25em}
 \section{Homoiconic meta-mapping (HoMM) architecture}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 To address these challenges, we propose HoMM architectures, composed of two components: 
@@
 \section{Learning multivariate polynomials} \label{sec_poly}
+\vspace{-0.8em}
 \begin{figure}[t]
@@
 The orange dashed lines shows performance on held-out tasks of playing the strategy from the most correlated trained task.
-The fact that the system generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing strategies and picking the closest.
-Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
+The system generally exceeds this difficult baseline, thus showing deeper generalization than just memorizing strategies and picking the closest.
+Error-bars are bootstrap 95\%-CIs, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
+\vspace{-0.5em}
 \end{figure}
@@
 \section{A stochastic learning setting: simple card games}\label{sec_cards}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 We next explored the setting of simple card games, where the agent is dealt a hand and must bet.
@@
 \par
-%\vspace{-0.7em}
+\vspace{-1em}
 \paragraph{Basic meta-learning:} First, we show that the system is able to play a held-out game from examples in fig.
@@
 \par
-%\vspace{-0.7em}
+\vspace{-0.7em}
 \paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
@@
 \par
-%\vspace{-0.5em}
+\vspace{-0.5em}
 \section{An extension via language}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 \begin{figure}
@@
 
-%\vspace{-0.5em}
+\vspace{-0.5em}
 \section{Discussion} \label{sec_discussion}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 \paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
@@
 \par
-% \vspace{-1em}
+\vspace{-1em}
 \paragraph{Future Directions:} We think that the general perspective of considering meta-mappings will yield many fruitful future directions.
@@
 %\paragraph{Conclusions:}
+\vspace{-0.5em}
 \section{Conclusions}
-%\vspace{-0.5em} % section
+\vspace{-0.5em} % section
 \looseness=-1

### 2019-10-29 compute_baselines.py
Fixing suits rule

@@ -7,7 +7,7 @@ losers = [True, False]
 black_valuable = [True, False]
 max_bet = 2.
 
-with open("baseline_data_no_ties.csv", "w") as fout:
+with open("baseline_data_for_humans_sr_fixed.csv", "w") as fout:
     fout.write("game, policy, expected_reward\n")
     for game_type in game_types:
         for sr in suits_rule:

### 2019-10-29 simple_card_games.py

@@ -35,7 +35,7 @@ class card_game(object):
         self.game_type = game_type
         self.black_valuable = black_valuable
         self.suits_rule = suits_rule
-        suit_mult = 0.5 if not suits_rule else 4
+        suit_mult = 0.5 if not suits_rule else 1000
         self.losers = losers
         self.cards = [(value, suit) for suit in range(2) for value in range(4)] 
         self.hands = [(c1, c2) for c1 in self.cards for c2 in self.cards]

### 2019-11-06 meta_learning.py
Slightly better

@@ -39,7 +39,7 @@ config = {
     "epsilon": 0.5,
     "init_learning_rate": 1e-4,
     "init_language_learning_rate": 1e-4,
-    "init_meta_learning_rate": 1e-4,
+    "init_meta_learning_rate": 5e-5,
 
     "new_init_learning_rate": 1e-5,
     "new_init_language_learning_rate": 1e-5,
@@ -57,7 +57,7 @@ config = {
     "refresh_meta_cache_every": 1, # how many epochs between updates to meta_cache
     "refresh_mem_buffs_every": 50, # how many epochs between updates to buffers
 
-    "max_base_epochs": 10000,
+    "max_base_epochs": 40000,
     "max_new_epochs": 1000,
     "num_task_hidden_layers": 3,
     "num_hyper_hidden_layers": 3,
@@ -66,20 +66,20 @@ config = {
                              # that because of multiplicative effects and depth
                              # impact can be dramatic.
 
-    "softmax_beta": 5, # 1/temperature on action softmax, sharpens if > 1
+    "softmax_beta": 8, # 1/temperature on action softmax, sharpens if > 1
     "task_weight_weight_mult": 1., # not a typo, the init range of the final
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "./results_for_humans/results/",
-    "save_every": 20, 
+    "output_dir": "./results_for_humans/results_6/",
+    "save_every": 200, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
-    "sweep_meta_batch_sizes": [10, 20, 30, 50, 100, 200, 400, 800], # if not None,
+    "sweep_meta_batch_sizes": None,#[10, 20, 30, 50, 100, 200, 400, 800], # if not None,
                                                                     # eval each at
                                                                     # training ends
 
     "memory_buffer_size": 1024, # How many memories of each task are stored
-    "meta_batch_size": 128, # how many meta-learner sees
+    "meta_batch_size": 768, # how many meta-learner sees
     "early_stopping_thresh": 0.05,
 #    "new_tasks": "random",
     "new_tasks": [{"game": "straight_flush", "losers": True,
@@ -110,7 +110,7 @@ config = {
 
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
 if config["meta_toggling"]:
-    config["base_meta_mappings"] = ["toggle_" + o for o in config["option_names"]]
[…]

### 2019-11-07 writing/homoiconic_meta_mapping_main.tex
Adding some things suggested by reviewers

@@
 One fundamental reason for this is that humans are aware of what we are trying to compute and why.
-This allows us to adapt our task representations to perform a new task zero-shot.
-By contrast, most deep learning models do not explicitly represent tasks at all.
-Those that do (such as some meta-learning models) generally do not represent relationships between tasks, and so cannot adapt to a new task without data from the new task.
+This allows us to adapt our task representations to perform an altered task.
+By contrast, most prior work on zero-shot learning relies on generating a completely new representation for a new task, e.g.
+from a natural language description \citep[e.g.]{Socher2013, Oh2017a}.
+These systems must therefore throw away much of their prior knowledge of the task and regenerate it from scratch, rather than just transforming what needs to be transformed.
+Other approaches use relationships between tasks as an auxiliary learning signal \citep[e.g.]{Yao2019, Pal2019}, but cannot adapt to a new task by transforming their task representations.
 To address this, it is necessary to represent tasks in a transformable space.
-This can grant the ability to rapidly adapt behavior to a new task.
+This can grant the ability to rapidly and precisely adapt behavior to a new task.
 \par
@@
 mappings between tasks (see below).
-As noted above, this type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to deep-learning models.
-To address this challenge, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
+Meta-mappings allow zero-shot performance of a new task based on its relationship to old tasks.
+To address the challenge of performing meta-mappings, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity.
 (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable.
@@
 \vspace{-0.5em} % section
-\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
+\paragraph{Related work:} There has been a variety of past work on zero-shot learning, mostly based on natural-language descriptions of tasks.
+For example, \citet{Larochelle2008} considered the general problem of behaving in accordance with language instructions as simply asking a model to adapt its response when conditioned on different ``instruction'' inputs.
+Later work explored zero-shot classification based on only a natural language description of the target class \citep{Socher2013,Romera-Paredes2015,Xian2018}, or of a novel task in a language-conditioned RL system \citep{Hermann2017}.
+Some work has even exploited relationships between tasks as a learning signal \citep{Oh2017a, Pal2019}.
+However, to our knowledge none of the prior work has proposed using meta-mapping approaches to adapt to new tasks.
+\par
+Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
@@
 Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}, and meta-learning \citep[e.g.]{Li2019a, Rusu2019}.
+In particular, recent work in natural language processing has shown that having contextually generated parameters can allow for zero-shot task performance, assuming that a good representation for the novel task is given \citep{Platanios2017} -- in their work this representation was evident from the factorial structure of translating between many pairs of languages.
 Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017, Garnelo2018} and continual learning \citep[e.g.]{Hu2019}.
@@
 Our perspective can be seen as a generalization of these that allows for remapping of behavior via meta-tasks.
-To the best of our knowledge none of the prior work has explored zero-shot performance of a task via meta-mappings.
+While there have been other approaches to zero-shot task performance, to the best of our knowledge none of the prior work has explored zero-shot performance of a task via meta-mappings.
 \par
@@
 Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks.
-This is a key aspect of human flexibility, but is lacking from most contemporary deep-learning models.
-Achieving this flexibility requires representing tasks in a transformable way.
+This is a key aspect of human flexibility.
+The meta-mapping perspective suggests that this flexibility requires representing tasks in a transformable way.
 To address this, our Homoiconic Meta-Mapping (HoMM) approach explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork.
@@
 That is, we are able to achieve zero-shot performance on a novel task based on a held-out relationship between tasks.
-This is a step closer to human-level flexibility.\par
+Furthermore, the meta-mapping approach yields better task performance than a zero-shot approach based on performing the task based on just a natural language description (supplementary fig.
+\ref{fig_why_meta_mapping}).
+This is a step closer to human-level flexibility.
+\par
 We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks.

### 2019-11-08 meta_learning.py
Fewer mappings here

@@ -71,7 +71,7 @@ config = {
                                    # hyper weights that generate the task
                                    # parameters. 
 
-    "output_dir": "./results_for_humans/results_6/",
+    "output_dir": "./results_for_humans/results_8/",
     "save_every": 200, 
     "eval_all_hands": False, # whether to save guess probs on each hand & each game
     "sweep_meta_batch_sizes": None,#[10, 20, 30, 50, 100, 200, 400, 800], # if not None,
@@ -110,7 +110,7 @@ config = {
 
 config["base_meta_tasks"] = ["is_" + g for g in config["game_types"]] + ["is_" + o for o in config["option_names"]]
 if config["meta_toggling"]:
-    config["base_meta_mappings"] = ["toggle_" + o for o in config["option_names"]] # ["losers"]] #
+    config["base_meta_mappings"] = ["toggle_losers"] #["toggle_" + o for o in config["option_names"]] # 
 else:
     config["base_meta_mappings"] = ["turnON_" + o for o in config["option_names"]] + ["turnOF_" + o for o in config["option_names"]]
 

### 2019-11-09 writing/homoiconic_meta_mapping_appendix.tex
Further tweaks from Jay
More reviewer suggestions

--- 2019-09-07 writing/embedded_meta_learning_appendix.tex
@@
 \section{Clarifying meta-mapping} \label{app_clarifying_meta_mapping}
+\subsection{Clarifying hold-outs} \label{app_clarifying_holdouts}
+There are several distinct types of hold-outs in the basic training of our architecture:
+\begin{enumerate}
+\item On each basic task, some of the data ($D_1$) is fed to the meta-network as examples $\mathcal{M}$ while some probes ($D_2$) is held out.
+This encourages the model to actually infer the underlying function, rather than just memorizing the examples.
+However, the probe labels are still used in training the system end-to-end, in order to encourage it to generalize.
+\item There are also truly held-out tasks that the system has never seen in training.
+These are the held-out tasks that we evaluate on at the end of training and that are plotted in the ``Held out'' sections in the main plots.
+\end{enumerate}
+This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization.
+There are also meta-mappings which have never been encountered during training, which we evaluate on at the end of training, those are the meta-mappings which are plotted in the ``held out'' section in the relevant plots.
+We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.
+\par
 \subsection{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
@@
 \end{figure}
-\subsection{Clarifying hold-outs} \label{app_clarifying_holdouts}
-There are several distinct types of hold-outs in the basic training of our architecture:
-\begin{enumerate}
-\item On each basic task, some of the data ($D_1$) is fed to the meta-network $\mathcal{M}$ while some ($D_2$) is held out.
-This encourages the model to actually infer the underlying function, rather than just memorizing the examples.
-\item There are also truly held-out tasks that the system has never seen in training.
-These are the held-out tasks that we evaluate on at the end of training and that are plotted in the ``Held out'' sections in the main plots.
-\end{enumerate}
-This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization.
-There are also meta-mappings which have never been encountered during training, which we evaluate on at the end of training, those are the meta-mappings which are plotted in the ``held out'' section in the relevant plots.
-We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.
-\par
 \section{Continual learning} \label{app_continual}
@@
 The full code for the experiments and analyses can be found on github:
-%%\begin{itemize}
-%%\item \url{https://github.com/lampinen/polynomials}
-%%    \begin{itemize}
-%%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
-%%    \end{itemize}
-%%\item \url{https://github.com/lampinen/meta_cards} 
-%%\end{itemize}
-(will be made available in the de-anonymized version.)
+\begin{itemize}
+\item \url{https://github.com/lampinen/polynomials}
+    \begin{itemize}
+        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
+    \end{itemize}
+\item \url{https://github.com/lampinen/meta_cards} 
+\end{itemize}
 \section{Numerical results} \label{app_numerical_results}

### 2019-11-09 writing/homoiconic_meta_mapping_main.tex
Tweaks
More reviewer suggestions

@@
 These architectures are homoiconic because they have a completely shared $Z$ for individual data points, tasks, and meta-mappings.
-Why is this useful?
-The primary advantage is that it parsimoniously allows for arbitrary mappings between these entities.
-In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior.
+This parsimoniously allows for arbitrary mappings between these entities.
+In addition to basic tasks, the system can learn to perform meta-mappings to systematically alter task behavior based on relationships to other tasks.
 That is, it can transform task representations using the same components it uses to transform basic data points.
@@
 This system can be trained end-to-end on target outputs for the probes.
-Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}.
-See appendix \ref{app_model_details} for detailed architecture, and hyper-parameters.
+Having two distinct datasets forces generalization at the meta-learning level, in exactly the same way as standard meta-learning algorithms learn to generalize.
 \par
@@
 The system can then be trained end-to-end on this loss to adjust the weights of \(\mathcal{T,H,M,O}\), and \(\mathcal{I}\).
+That is, the meta-learning training procedure optimizes the system for generalizing the function implied by the examples it sees, in order to respond appropriately to probe inputs.
+As in training a standard meta-learning model, these probes are held-out from the meta-network, but are still provided during training.
+Other examples are held-out entirely during training, and only used for evaluation, see appendix \ref{app_clarifying_holdouts} for some detailed description.
+See appendix \ref{app_model_details} for details on the architecture and hyper-parameters.
+\par
 \vspace{-0.25em}
@@
 \ref{architecture_inference_fig}b,c).
-From the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
+That is, we propose to transform a prior task representation in order to perform a related new task zero-shot.
+The relationship by which the prior task embedding should be transformed to perform the new task is specified by example tuples of (input, output) task embeddings.
+This is precisely analogous to how a basic task is specified in terms of (input, output) embeddings of data points, except that the embeddings now represent tasks that are being transformed, rather than individual data points.
+\par
+Thus from the perspective of our architecture, learning a meta-mapping between tasks is exactly analogous to learning a basic task.
 Anything that is embedded in $Z$ can be transformed using the same system.
 Because tasks are embedded in $Z$ for basic meta-learning, this allows for meta-mappings using exactly the same $\mathcal{M}$ and $\mathcal{H}$ that we use for basic tasks.
-Just as we would take a set of paired embeddings of data points for a basic task, and use them to compute a function embedding for that task, we can take a set of paired function embeddings, and use them to create an embedding for the meta-mapping.
-We can then use this meta-mapping embedding to transform another task.
+Just as we would take a set of paired embeddings of data points for a basic task, and use them to compute a function embedding for that task, we can take a set of paired function embeddings representing a meta-mapping, and use them to create an embedding for that meta-mapping.
+We can then use this meta-mapping embedding to transform the embedding of another basic task.
 We can thus behave zero-shot on a novel task based on its relationship to a prior task.
@@
 For example, suppose we have an embedding $z_{game1} \in Z$ for the task of playing some game, and we want to switch to trying to lose this game.
-We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of embeddings generated by the system when it is trying to win and lose various games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
+We can generate a meta-mapping embedding $z_{\text{meta}} \in Z$ from examples of embeddings generated by the system when it is trying to win and lose various other games: $z_{\text{meta}} = \mathcal{M}\left( \left\{\left((z_{game2},z_{game2,lose}\right), ...
 \right\}\right)$.
@@
 Later work explored zero-shot classification based on only a natural language description of the target class \citep{Socher2013,Romera-Paredes2015,Xian2018}, or of a novel task in a language-conditioned RL system \citep{Hermann2017}.
-Some work has even exploited relationships between tasks as a learning signal \citep{Oh2017a, Pal2019}.
-However, to our knowledge none of the prior work has proposed using meta-mapping approaches to adapt to new tasks.
+Some of this work has even exploited relationships between tasks as a learning signal \citep{Oh2017a}.
+Other work has considered how similarity between tasks can be useful for generating representations for a new task \citep{Pal2019}, but without transforming task representations to do so.
+(Furthermore, similarity cannot specify as rich of functions as an input-output mapping.) To our knowledge none of the prior work has proposed using meta-mapping approaches to adapt to new tasks by transforming task representations, nor has the prior work proposed a parsimonious homoiconic model which can perform these mappings.
 \par

### 2019-11-11 writing/iclr2020_submission/rebuttal.txt
Responding to comments

Reviewer 1:

Thank you for the thorough review. We have made substantial revisions to the paper that we hope will clarify some points and address your concerns. We respond to your comments inline below.

- A key issue is that the paper claims to be the first to propose a method for zero-shot task adaptation (pg 8, para before “Future Directions”). The paper seems to have missed papers such as (1) Zero-Shot Task Transfer, Pal et. al, CVPR 2019, and, (2) Zero-Shot Task Generalization with Multi-Task Deep Reinforcement Learning, Junhyuk Oh et al, ICML 2017. In particular, the CVPR 2019 paper proposes zero-shot task transfer using meta-mappings. Citing these papers and comparing against them is essential, considering this paper addresses the same objective.

We did not intend to claim to be the first to perform a task zero-shot, and we have added some review of the papers you cite (and a few others) to the related work section. We do however, maintain that our paper is the first to propose performing a task by transforming a prior task representation from examples of the relationship between the tasks (i.e. the first to propose meta-mapping as such). The paper by Pal et al. does not transform task representations as such, and does not use systematic analogies between tasks, but rather a scalar measure of task similarity (to multiple tasks), which is essentially just another way of describing the task. We believe that functions that take in a task and output another have more representational specificity than scalar similarity, which does not allow for as rich a notion of *along which dimensions* two tasks are similar. We have added some discussion to the paper to clarify this.

- The proposed methodology does not clearly detail how the zero-shot problem setting is used. Section F.2 (Appendix) gives the formulation of a meta-learner and zero-shot task a bit. However, how the meta-learner performs zero-shot task parameter regression is not clear. The notations used in mathematical equations are also not very clear, and a reader needs to swap between different sections to understand the proposed method. (Moving Sec F.2 to the main paper would be very useful. Similarly, moving Figs 5, 7, 8 etc. to the main paper would have helped greatly too.)

We perform a new task zero-shot by transforming the embedding of a prior task according to a meta-mapping. We originally had most of the material from section F.2 in the main text already, but slightly more terse due to the length constraints. We have expanded these sections to hopefully give clearer intuitions, and have tried to clarify a number of aspects of the presentation. We have also included the former Fig. 5 in the main text, which, as you suggest, is an important part of the story. We are not sure we can include further material unless you suggest something we should cut in correspondence.

- How is the notion of a “task” defined? Are different classes of a dataset tasks (already done in [3]), or are different vision-related objectives as tasks (reference [1])? Are language-related objectives (such as: document classification, sentiment analysis, Named-entity recognition etc.) tasks? In an RL setting, do zero-shot tasks deal with a new environment? It would have been nice to see clearer definitions for the kind of tasks that this method is suited to.

A task is a function, i.e. a mapping of inputs to outputs. This is a general definition which can accomodate almost any machine learning framework. For example, the inputs might be images and the outputs classes, or the inputs states, and the outputs Q-values. We therefore think our method may be applicable to many types of tasks, but exploring all applications seems beyond the scope of this paper.

- It was not clear on how the relationship between source tasks and zero-shot tasks are modeled or computed. Clearly, the performance of such a system depends on the correlations between the tasks, and these details are not clear, especially in generalizing the proposed method. The paper seems to correlate tasks and language-related hints; however getting a language hint is not always available, especially for datasets such as Taskonomy [1, see Refs below] - which is a dataset for multiple tasks.

We do not in general rely on language hints. Those were only used as an example. In general, the system can compute a zero-shot embedding of a new task based on examples of the mapping -- i.e. on pairs of input task, output task that implicitly specify the function by which to transform the prior task embedding.

- The zero-shot part is described using a winning-losing scenario, where we have a partial/side knowledge of winning of task_1 and the model can predict losing strategy. Now, what if:
We do not have any knowledge of the winning strategy (or losing strategy) of a zero-shot task?
Can we predict the losing strategy of a game, let’s say card game, from the knowledge of other games like: soccer, tennis, badminton etc. (the initial motivation of the paper). This is quite possible in the continual learning scenario (the paper mentioned some studies on continual learning). If so, then please comment on the negative transfers in that scenario and how it will affect the inference of the meta-learner.
The proposed method also mentioned language descriptions. In case of tasks that are not easy to describe (say, a vision task such as segmentation), how will the proposed method will compute the task-prior of seen-tasks and zero-shot tasks?
The paper mentions “winning-losing” strategy and the metanetwork gives losing strategy parameters. What if the scenario is the otehr way - given a losing strategy, we now have to perform the winning strategy (IMHO this has more value in the real world). Does the paper show the result on this, or am I missing something?

The main point of our results is that we are indeed able to predict the losing strategy of a game from knowledge of other games. While generalizing from soccer to card games is beyond the scope of our paper (we only showed mapping of the meaning of "losing" from one card game to another), the hope is that it would be possible. This understanding will not be perfect, however, is that what you mean by negative transfer? In general, even humans cannot perfectly perform a novel task zero-shot. We are simply able to reach reasonable performance, and then learn further from examples.

Regarding switching from losing to winning -- in our cards domain, winning and losing are perfectly symmetric, in the sense that if you want to bet on a hand when you're trying to win, you don't want to bet when you're trying to lose, and vice versa. In more complex games, such as chess, this is not true. Winning requires more knowledge than losing, and so we would expect it to be easier to try to lose when you know how to win than to try to win when we know how to lose. We do not think this is a fundamental limitation of our technique, but rather a limitation of the type of knowledge that is available when a task changes. Some things are easier to infer than others. We think exploring how the structure of a task affects its transformability is an important direction for future work.

- Experiments are limited to synthetic data and card games, and it would be nice to see the validation of the proposed method on different domains. The notion of zero-shot tasks are also not clear for multivariate polynomial experiment and card-game experiment.

We already have more material than fits in this paper. We remained with synthetic tasks for two reasons: 1) to illustrate the method in settings we thought would be clearer, 2) because as we highlight in the future directions, there is a lack of meta-learning datasets that contain as structured of relationships between tasks as we consider. (Taskonomy, for example, has at best a notion of "similarity" in terms of transfer.) We are working on creating several such datasets, but we think that this paper as it stands is a useful contribution that illustrates the concept and ideas -- the datasets themselves will also require further description, and including them in a paper of this length would likely result in even more material being cut, and so a less clear presentation.

- Figure 1: please clearly mention in the caption what is the meaning and purpose of probes. It is not completely clear whether probes (also referred as held-out set In figure 1 caption) are taking part in training, or only at the time of validation?

As in standard meta-learning, the probe labels are used during training to encourage the system to generalize. We have added a note about this in the caption and clarified further in the text.

- Shared Z vs. Separate task embedding: reuse of M (or, H network) network will only be possible if the input and output dimensions are same - i.e. the dimension of Z_output of M is the same as the dimension of Z_input of the M. What if  input and output dimensions are not the same?

Because Z is a latent space, we can choose its dimensionality however we wish, so we can choose for those embeddings to be the same. If we have pre-trained encoders we would like to use, we can either choose a latent the same size as their output, or map their latents into Z with an additional layer.

Other minor comments:

* One general comment is: please mention the “Zero-shot” experiments more clearly (may be a separate paragraph or subsection), otherwise it is hard to follow.
    Thanks, we have noted the sections and clarified this in the figure captions.
* Figure 2(a) please remove the question mark (?) after Held-out. Similarly, Figure 5: Please complete the sentence “ Performing from …”. 
    Done.
* Figure 1: (a)  Basic meta-learning: Please use some other color to highlight “(a)  Basic meta-learning”, the grey gives an illusion that the step ((a)  Basic meta-learning is not important.
    We chose this color because our main contribution is about meta-mapping, not meta-learning, so we wanted to highlight the latter panels.
* A term such as “Homoiconic” would have benefited from a formal definition, especially considering it’s not a commonly used term.
    There are debates about how to precisely define this term (see e.g. https://www.expressionsofchange.org/dont-say-homoiconic/), so we didn't want to wade into such a definitional conundrum. However, we provide a statement of the general agreed-upon part of the definition in the introduction.
* The presentation is in general not well-polished, and needs revision.
    Are there specific points that would benefit from further clarification?

Reviewer 2:

Thank you for your thoughtful review. We appreciate that you think our problem and approach are interesting! We have made some substantial revisions to clarify the presentation, we hope that these will help address your concerns. We respond to some specific comments below:

> No comparisons were provided to any baselines/alternative methods.

We do compare to a number of lesions in the supplement, and to an alternative method (performing tasks from a description alone). We have moved this latter comparison to the main text at the suggestion of Reviewer 1.

> in Sections 4 and 5 I was hoping to see comparisons to methods like MAML. Also, I felt that the proposed approach in Section 5 is very similar to MAML intuitively. This makes a comparison with MAML even more desirable. Without any comparisons it’s hard to tell how difficult the tasks under consideration are and what would amount to good performance on the held-out tasks.

Our main contribution is to propose a framework and method for zero-shot task performance. MAML as such is not a method of zero-shot task performance, it requires examples to learn from. We could therefore compare to MAML for our basic-meta-learning results, but those are simply a sanity check. We also compare to a variety of baselines, including chance and optimal performance, untransformed representations, and the most correlated task experienced (in the cards domain). However, if our paper is accepted, and you feel that the comparison to MAML for basic meta-learning is useful, we will run MAML on our tasks before the camera-ready submission.

One might take inspiration from our framework try to use MAML for zero-shot task performance by transforming task representations would require adopting our meta-mapping framework, as well as a number of ideas of our architecture (where do the task representations come from, and how are they used?), and so its not clear to us that this is an appropriate baseline, rather than simply another implementation of our technique. Instead, we feel the more appropriate baseline is performing tasks from a natural language description, as many prior zero-shot works have, and so we have moved this result to the main text, as noted above.

> The experimental results presented were all done on small synthetic datasets and it’s hard to evaluate whether the method is practically useful.

We already have more material than fits in this paper, especially now that we have added clarifications that all reviewers requested. We remained with synthetic tasks for two reasons: 1) to illustrate the method in settings we thought would be clearer, 2) because as we highlight in the future directions, there is a lack of meta-learning datasets that contain as structured of relationships between tasks as we consider. (Taskonomy, for example, has at best a notion of "similarity" in terms of transfer.) We are working on creating several such datasets, but we think that this paper as it stands is a useful contribution that illustrates the concept and ideas -- the datasets themselves will also require further description, and including them in a paper of this length would likely result in even more material being cut, and so a less clear presentation. We do think this is an important direction, but we think this paper makes a useful contribution by highlighting this new perspective. We hope that you agree.

> Also, the work by Platanios, et al. on contextual parameter generation is very relevant to this work as it tackles multi-task learning using HyperNetworks. It may be worth adding a short discussion/comparison to that work as it also considers zero-shot learning.

Thanks, we weren't familiar with this very interesting work! We have added a reference and a brief discussion of the relationship.

- Capitalize: “section” -> “Section”, “appendix” -> “Appendix”, “fig.” -> “Figure”. Sometimes these are capitalized, but the use is inconsistent throughout the paper.
    Thanks for pointing this out, fixed.
- “Hold-out” vs “held-out”. Be consistent and use “held-out” throughout.
    We are making a grammatical distinction here -- "held-out" is an adjective and "hold-out" is a noun. That is, one might refer to a "held-out task" or to a "a hold-out." Hopefully this clarifies things.

We hope that this clarifies

Reviewer 3:

Thank you for the thorough and thoughtful review. We appreciate that you think our work is tackling zero-shot adaptation in an innovative way! We have made substantial revisions to try to clarify the presentation. We respond to some of your comments inline below.

- The major concern for this work is its lack of discussion and comparison with state-of-the-art meta-learning baselines. 
    o	In fact, the meta-mapping this work learns is the relationship between tasks, and the meta-task the authors mentioned is a group of tasks. In this sense, I strongly suggest the authors to go through the recent work [1], and compare with it. Even the datasets constructed in that paper can be used as a benchmark to validate the proposed method in image classification.
    o	Other basic meta-learning algorithms like MAML[3] and many others should still be compared and discussed, especially in the basic meta-learning setting in Figure 2.

Our main contribution is to propose a framework and method for zero-shot task performance. MAML as such is not a method of zero-shot task performance, it requires examples to learn from. We could therefore compare to MAML for our basic-meta-learning results, but those are simply a sanity check. We also compare to a variety of baselines, including chance and optimal performance, untransformed representations, and the most correlated task experienced (in the cards domain). However, if our paper is accepted, and you feel that the comparison to MAML for basic meta-learning is useful, we will run MAML on our tasks before the camera-ready submission.

One might take inspiration from our framework try to use MAML for zero-shot task performance by transforming task representations would require adopting our meta-mapping framework, as well as a number of ideas of our architecture (where do the task representations come from, and how are they used?), and so its not clear to us that this is an appropriate baseline, rather than simply another implementation of our technique. Instead, we feel the more appropriate baseline is performing tasks from a natural language description, as many prior zero-shot works have, and so we have moved this result to the main text, as noted above.

o More recent work on explicitly learning the embedding of a task should be noted and compared, including [1][2]. The meta-mapping in this work is still based on embedding of a task, i.e., z_func, which is obtained by the function network. So is it possible to replace the embedding with recent SOTA algorithms?

Thanks for the useful and interesting references! We believe that it might be possible to replace our method for generating task embeddings with another algorithm. We have added a reference, and we do mention some other methods for constructing function embeddings (last paragraph of the related work).

- Many important details and ablation studies are missing, making the work less convincing.
    We do include a number of ablation studies in Appendix E.

`
o Why don’t merge the results Fig. 2 and Fig. 3 and compare them in a single figure, so that the contribution of meta-mappings can be shown. 
    We think this would be extremely misleading, since fig. 2 is meta-learning (viz. performing tasks from examples), while figure 3 is performing tasks zero-shot, without examples. We have however, moved figure 5. to the main text, which does include this comparison between performing a task zero-shot and from examples, as well as another baseline.

o How do you train the domain-specific encoder and decoder? Are they generalizable to a wide range of more complicated tasks like image classification? 
    The model is trained end-to-end. We expect that an appropriate convolutional architecture could be trained end-to-end in our system if given tasks related to image classification, or a pretrained model could be used as an encoder.

o It would be great to analyze the limitations of the proposed algorithm, especially for the case where a newly coming task belonging to an novel and unseen meta-task arrives. How insightful or predictable is the proposed zero-shot adaptation method in these cases?
    We show in fig. 3 and 4 that the model produces reasonable results even in this case, within the polynomial domain (because we did not have enough meta-mappings in the cards domain to hold one out). Analyzing the features of this generalization in detail seems somewhat beyond the scope of this paper -- indeed, many submissions to this conference are full papers that only perform such analysis on a simpler model.

o How do you obtain the lower-bound (solid line) and the upper-bound (dashed line) of the performance in the figures?
    We have added some clarification about this to the captions, but briefly:

    Polynomial tasks: the dashed chance line is the loss for outputting all zeros, which because of the way our polynomials are sampled is the mean for all polynomials. This is a relatively useful null, e.g. the difference between the dashed line and the model performance can be interpreted as percent variance explained. Optimal performance is zero loss, i.e. regressing every point perfectly.

    Cards tasks: the dashed chance line is the loss for choosing actions uniformly at random. The optimal performance is the score achievable by optimal knowledge of the game (that is, betting maximally on every hand that has a positive expected return, and not betting on hands that do not). The colored baselines are various more careful analyses, such as playing the most correlated known strategy, or the performance the model would exhibit if it did not perform its prior task representation.

o Will the dimension of Z influence the performance? Since data points, tasks, and meta-mappings contain different amount of information, investigating the effect of the dimension of Z is key for the robustness of the method.
    We generally found that too small a Z impaired performance, but once Z was large enough, making it larger generally did not substantially affect performance. This is in line with recent results on overparameterization in deep models.

We hope this helps to address your concerns, please let us know if further changes would be useful.

### 2019-11-11 writing/homoiconic_meta_mapping_main.tex
Responding to comments

@@
 Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}.
-The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
+The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also Section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}.
 However, humans can use our knowledge of a task to flexibly adapt when the task changes.
@@
 While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel.
-(We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) This adaptation can be cued in several ways, including examples of the mapping (after winning and losing at poker, try to lose at blackjack) or natural-language instructions (``try to lose at blackjack'').
+(We discuss the relationship between our work and prior work in Section \ref{sec_discussion}.) This adaptation can be cued in several ways, including examples of the mapping (after winning and losing at poker, try to lose at blackjack) or natural-language instructions (``try to lose at blackjack'').
 \par
@@
 That is, it can transform task representations using the same components it uses to transform basic data points.
-(See also appendix \ref{app_lesion_results_shared_z}.) \par
+(See also Appendix \ref{app_lesion_results_shared_z}.) \par
 Without training on meta-mappings, of course, the system will not be able to execute them well.
@@
 \caption{The HoMM architecture allows for transformations at different levels of abstraction.
-(a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on held-out probe inputs.
+(a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on probe inputs (used to encourage the system to generalize).
 However, our approach goes beyond basic meta-learning.
@@
 Input and output encoders/decoders are omitted for simplicity.
-See the text and appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
+See the text and Appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
 \end{figure}
@@
 Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs.
-These transformations are performed by a system with the following components (see fig.
+These transformations are performed by a system with the following components (see Fig.
 \ref{architecture_inference_fig}): $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- the meta network, which collapses a dataset of (input embedding, target embedding) pairs to produce a single function embedding.
@@
 \vspace{-0.5em}
-\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig.
+\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (Fig.
 \ref{architecture_inference_fig}a).
@@
 That is, the meta-learning training procedure optimizes the system for generalizing the function implied by the examples it sees, in order to respond appropriately to probe inputs.
-As in training a standard meta-learning model, these probes are held-out from the meta-network, but are still provided during training.
-Other examples are held-out entirely during training, and only used for evaluation, see appendix \ref{app_clarifying_holdouts} for some detailed description.
-See appendix \ref{app_model_details} for details on the architecture and hyper-parameters.
+As in training a standard meta-learning model, these probes are held-out from the meta-network, but the labels are still used to encourage the system to meta-learn to respond appropriately to new inputs.
+Other data points are held-out entirely during training, and only used for evaluation, see Appendix \ref{app_clarifying_holdouts} for some detailed description.
+See Appendix \ref{app_model_details} for further details on the architecture and hyper-parameters.
 \par
 \vspace{-0.25em}
-\paragraph{Meta-mapping:} The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see fig.
+\paragraph{Meta-mapping:} The fundamental insight of our paper is to show how basic tasks and meta-mappings can be treated homogenously, by allowing the network to transform its task representations like data (see Fig.
 \ref{architecture_inference_fig}b,c).
@@
 Allowing this might be useful in more complex applications.}.
-Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{game1,lose}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding (fig.
+Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{game1,lose}$ strategy, by stepping back down a level of abstraction and actually having it play the game via this embedding (Fig.
 \ref{architecture_inference_fig}c).
 This is how we evaluate meta-mapping performance -- evaluating the loss of transformed task embeddings on the respective target tasks.
+Note that this allows for zero-shot performance of the new task, because it simply requires transforming a prior task embedding.
 \par
@@
 
-%\subsection{Boolean functions}
-%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs.
-Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input.
-We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs.
-\par
-%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
-%
 \section{Learning multivariate polynomials} \label{sec_poly}
@@
 \includegraphics[width=\textwidth]{figures/poly/basic_results.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
+\caption{The polynomials domain, Section \ref{sec_poly}.}
 \label{poly_basic_results}
@@
 \includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
-\caption{The cards domain, section \ref{sec_cards}.}
+\caption{The cards domain, Section \ref{sec_cards}.}
 \label{cards_basic_results}
@@
 \caption{The HoMM system succeeds at basic meta-learning, which is a necessary prerequisite for meta-mappings.
-(\subref{poly_basic_results}) The polynomials domain, section \ref{sec_poly}.
+(\subref{poly_basic_results}) The polynomials domain, Section \ref{sec_poly}.
 The system successfully generalizes to held out polynomials.
 The solid line indicates optimal performance; the dashed line indicates untrained model performance.
-(\subref{cards_basic_results}) The card games domain, section \ref{sec_cards}.
+(\subref{cards_basic_results}) The card games domain, Section \ref{sec_cards}.
 The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out.
-The gray dashed line indicates chance performance, while the solid lines are optimal performance.
+The gray dashed line indicates chance performance (otuputting the mean across all polynomials, or playing randomly), while the solid lines are optimal performance.
 The orange dashed lines shows performance on held-out tasks of playing the strategy from the most correlated trained task.
 The system generally exceeds this difficult baseline, thus showing deeper generalization than just memorizing strategies and picking the closest.
-Error-bars are bootstrap 95\%-CIs, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
+Error-bars are bootstrap 95\%-CIs, numerical values for plots can be found in Appendix \ref{app_numerical_results}.}
 \vspace{-0.5em}
@@
 \includegraphics[width=\textwidth]{figures/poly/meta_results.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
+\caption{The polynomials domain, Section \ref{sec_poly}.}
 \label{poly_meta_map_results_examples}
@@
 \includegraphics[width=\textwidth]{figures/meta_mapping.png}
-\caption{The cards domain, section \ref{sec_cards}.}
+\caption{The cards domain, Section \ref{sec_cards}.}
 \label{cards_meta_map_results_examples}
 \end{subfigure}%
-\caption{The HoMM architecture performs well at meta-mappings.
+\caption{The HoMM architecture performs tasks zero-shot by meta-mappings.
 (\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and even to apply unseen meta-mappings.
@@
 This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
+Details of the architecture and training can be found in Appendix \ref{app_detailed_methods}.\par
 \vspace{-0.7em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig.
-\ref{poly_basic_results} (with good sample-efficiency, see supp.
-fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig.
+\ref{poly_basic_results} (with good sample-efficiency, see Supp.
+Fig.
 \ref{supp_poly_sweep_results}).
@@
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig.
+\paragraph{Zero-shot adaptation by meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (Fig.
 \ref{poly_meta_map_results_examples}).
@@
 We also trained the system to make meta-mappings, for example switching from trying to win a game to trying to lose.
-Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.
+Details of the architecture and training can be found in Appendix \ref{app_detailed_methods}.
 \par
 \vspace{-1em}
-\paragraph{Basic meta-learning:} First, we show that the system is able to play a held-out game from examples in fig.
+\paragraph{Basic meta-learning:} First, we show that the system is able to play a held-out game from examples in Fig.
 \ref{cards_basic_results}.
@@
 Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks.
-Furthermore, the task embeddings generated by the system are semantically organized, see appendix \ref{app_cards_tsne}.
+Furthermore, the task embeddings generated by the system are semantically organized, see Appendix \ref{app_cards_tsne}.
 \par
 \vspace{-0.7em}
-\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
+\paragraph{Zero-shot adaptation by meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior.
 For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training.
-In fig.
+In Fig.
 \ref{cards_meta_map_results_examples} we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it.
@@
 \caption{The HoMM system can perform meta-mappings from language cues rather than meta-mapping examples.
-Compare to fig.
+Compare to Fig.
 \ref{meta_map_results}, which shows the same results when using examples instead of language.
-(\subref{poly_meta_map_results_language}) In the polynomials domain, language cues still lead to good performance, even on held-out tasks or held-out meta-mappings, although examples perform slightly better (fig.
+(\subref{poly_meta_map_results_language}) In the polynomials domain, language cues still lead to good performance, even on held-out tasks or held-out meta-mappings, although examples perform slightly better (Fig.
 \ref{poly_meta_map_results_examples}).
@@
 \par
-This language-cued meta-mapping approach also yields good performance (fig.
+This language-cued meta-mapping approach also yields good performance (Fig.
 \ref{language_meta_map_results}).
 However, examples of the meta-mapping are slightly better, especially for meta-mappings not seen during training, presumably because examples provide a richer description.
-In Appendix \ref{app_why_meta_mapping} we show that using language to specify a meta-mapping performs better than using language to directly specify the target task, presumably by leveraging the richer task representation of the task embedding.
+In the next section we show that using language to specify a meta-mapping performs better than using language to directly specify the target task.
 \par
+
+\subsection{Why meta-map from tasks to tasks?} \label{why_meta_mapping}
+Why are meta-mappings between tasks useful?
+To answer this, we consider various ways of adapting to a new task in Figure \ref{fig_why_meta_mapping} (based on results from the cards domain, Section \ref{sec_cards}).
+The standard meta-learning approach would be to adapt from seeing examples of the new task, but this requires going out and collecting data, which may be expensive and does not allow zero-shot adaptation.
+Alternatively, the system could perform the new task via a meta-mapping from a prior learned task, where the meta-mapping is either induced from examples of the meta-mapping, or from language.
+Finally, the system could perform a new task from language alone, if it is trained to map instructions to tasks.
+This is the more typical zero-shot paradigm \citep[e.g.][]{Romera-Paredes2015}.
+\par
+To address this latter possibility, we trained a version of the model where we included training the language system to produce embeddings for the basic tasks (while simultaneously training the system on all the other objectives, such as performing the tasks from examples, in order to provide the strongest possible structuring of the system's knowledge for the strongest possible comparison).
+We compare this model's performance at held-out tasks to that of systems learning from examples of the new task directly, or from meta-mapping, see Fig.
+\ref{fig_why_meta_mapping}.
+\par
+These results demonstrate the advantage of meta-mapping.
+While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation.
+Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks.
+Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz.
+prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language).
+That is, meta-mapping allows zero-shot adaptation, like performing from language alone, but results in much better performance than language alone, by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par
+\begin{figure}
+\centering
+\includegraphics[width=0.66\textwidth]{figures/why_meta_mapping.png}
+\caption{Comparison of a variety of methods for performing one of the 10\% held-out tasks in the more difficult hold-out set in the cards domain.
+There are a number of ways the system could adapt to a new task: from seeing example of the new task, from hearing the new task described from language alone, or from leveraging its knowledge about prior tasks via meta-mappings (in this case, from the non-losers variations of the same games).
+The meta-mappings offer a happy medium between the other two alternatives -- they only require cached knowledge of prior tasks, rather than needing to collect experience on the task before a policy can be derived, but they outperform a system that simply tries to construct the task embedding from a description alone.
+Language alone is not nearly as rich a cue as knowledge of how a new task relates to prior tasks.}
+\label{fig_why_meta_mapping}
+\end{figure}
 
@@
 Other work has considered how similarity between tasks can be useful for generating representations for a new task \citep{Pal2019}, but without transforming task representations to do so.
-(Furthermore, similarity cannot specify as rich of functions as an input-output mapping.) To our knowledge none of the prior work has proposed using meta-mapping approaches to adapt to new tasks by transforming task representations, nor has the prior work proposed a parsimonious homoiconic model which can perform these mappings.
+(Furthermore, similarity is less specific than an input-output mapping, since it does not specify \emph{along which dimensions} two tasks are similar.) To our knowledge none of the prior work has proposed using meta-mapping approaches to adapt to new tasks by transforming task representations, nor has the prior work proposed a parsimonious homoiconic model which can perform these mappings.
 \par
@@
 It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}.
-We also connect to a different perspective on continual learning in appendix \ref{app_continual}.
+We also connect to a different perspective on continual learning in Appendix \ref{app_continual}.
 Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}.
@@
 However, the modularization of the architecture makes it easy to modify.
-(We compare some variations in appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
+(We compare some variations in Appendix \ref{app_lesion_results}.) For example, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}.
 Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}.
@@
 That is, we are able to achieve zero-shot performance on a novel task based on a held-out relationship between tasks.
-Furthermore, the meta-mapping approach yields better task performance than a zero-shot approach based on performing the task based on just a natural language description (supplementary fig.
-\ref{fig_why_meta_mapping}).
+Furthermore, the meta-mapping approach yields better task performance than a zero-shot approach based on performing the task based on just a natural language description.
 This is a step closer to human-level flexibility.

### 2019-11-11 writing/homoiconic_meta_mapping_appendix.tex
Iclr revision version

@@
 \appendix
-The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task.
-In section
+The supplemental material is organized as follows: In Section \ref{app_clarifying_meta_mapping} we clarify some definitional details. In Section 
 \ref{app_continual} we describe a continual-learning like perspective based on our approach.
-In section \ref{app_supp_figures} we provide supplemental figures.
-In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
-In section \ref{app_lesion_results} we provide some lesion studies.
-In section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses.
-In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper.
+In Section \ref{app_supp_figures} we provide supplemental figures.
+In Section \ref{app_cards_tsne} we show $t$-sne results for the cards domain.
+In Section \ref{app_lesion_results} we provide some lesion studies.
+In Section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses.
+In Section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper.
 \par
@@
 \par
-\subsection{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
-Why are meta-mappings between tasks useful?
-To answer this, we consider various ways of adapting to a new task in figure \ref{fig_why_meta_mapping} (based on results from the cards domain, section \ref{sec_cards}).
-The system could adapt from seeing examples of the new task, but this requires going out and collecting data, which may be expensive and does not allow zero-shot adaptation.
-Alternatively, the system could perform the new task via a meta-mapping from a prior learned task, where the meta-mapping is either induced from examples of the meta-mapping, or from language.
-Finally, the system could perform a new task from language alone, if it is trained to map instructions to tasks.
-\par
-To address this latter possibility, we trained a version of the model where we included training the language system to produce embeddings for the basic tasks (while simultaneously training the system on all the other objectives, such as performing the tasks from examples, in order to provide the strongest possible structuring of the system's knowledge for the strongest possible comparison).
-We compare this model's performance at held-out tasks to that of systems learning from examples of the new task directly, or from meta-mapping, see fig.
-\ref{fig_why_meta_mapping}.
-\par
-These results demonstrate the advantage of meta-mapping.
-While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation.
-Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks.
-Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz.
-prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language).
-That is, meta-mapping has the advantage of requiring no new data collection, like performing from language alone, but results in much better performance by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par
 \subsection{A definitional note}
@@
 \par
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figures/why_meta_mapping.png}
-\caption{Comparison of a variety of methods for performing one of the 10\% held-out tasks in the more difficult hold-out set in the cards domain.
-There are a number of ways the system could adapt to a new task: from seeing example of the new task, from hearing the new task described from language alone, or from leveraging its knowledge about prior tasks via meta-mappings (in this case, from the non-losers variations of the same games).
-The meta-mappings offer a happy medium between the other two alternatives -- they only require cached knowledge of prior tasks, rather than needing to collect experience on the task before a policy can be derived, but they outperform a system that simply tries to construct the task embedding from a description alone.
-Language alone is not nearly as rich a cue as knowledge of how a new task relates to prior tasks.}
-\label{fig_why_meta_mapping}
-\end{figure}
 \section{Continual learning} \label{app_continual}
@@
 We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters.
-The results are shown in fig.
+The results are shown in Fig.
 \ref{poly_continual_results}.
 The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp.
-fig.
+Fig.
 \ref{supp_poly_continual_results} for a more direct comparison).
@@
 \includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
-\caption{The polynomials domain, section \ref{sec_poly}.}
+\caption{The polynomials domain, Section \ref{sec_poly}.}
 \label{supp_poly_integration_results}
@@
 \includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
-\caption{The cards domain, section \ref{sec_cards}.}
+\caption{The cards domain, Section \ref{sec_cards}.}
 \label{supp_cards_integration_results}
@@
 We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network.
-In fig.
+In Fig.
 \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks.
 The embeddings show systematic grouping by game attributes.
-In fig.
+In Fig.
 \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type.
@@
 \caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks.
-(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)}
+(Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in Appendix \ref{meth_data_cards}.)}
 \label{fig_cards_tsne_basic}
@@
 There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}.
-In this section, we further show that training with a separate task encoding space worsens performance, see fig.
+In this section, we further show that training with a separate task encoding space worsens performance, see Fig.
 \ref{supp_lesion_shared_z_fig}.
-This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see fig.
+This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see Fig.
 \ref{supp_lesion_shared_z_learn_fig}.
@@
 \[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
-Note that there are three kinds of hold-out in the training of this system, see section \ref{app_clarifying_holdouts}. \par
+Note that there are three kinds of hold-out in the training of this system, see Section \ref{app_clarifying_holdouts}. \par
 \textbf{Language-cued meta-tasks:} The procedure is analogous to the meta-tasks from examples, except that the input to $\mathcal{H}$ is the embedding of the language input, rather than the output of $\mathcal{M}$.
@@
 \subsection{Source repositories}
-The full code for the experiments and analyses can be found on github:
-\begin{itemize}
-\item \url{https://github.com/lampinen/polynomials}
-    \begin{itemize}
-        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
-    \end{itemize}
-\item \url{https://github.com/lampinen/meta_cards} 
-\end{itemize}
+(Will be included in de-anonymized version.)
+%The full code for the experiments and analyses can be found on github:
+%\begin{itemize}
+%\item \url{https://github.com/lampinen/polynomials}
+%    \begin{itemize}
+%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
+%    \end{itemize}
+%\item \url{https://github.com/lampinen/meta_cards} 
+%\end{itemize}
 \section{Numerical results} \label{app_numerical_results}
@@
 \end{tabular}
-\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
+\caption{Table for basic meta-learning, Figure \ref{poly_basic_results}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
+\caption{Table for meta-mapping results from examples, Figure \ref{poly_meta_map_results_examples}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for meta-mapping results from language, figure \ref{poly_meta_map_results_language}}
+\caption{Table for meta-mapping results from language, Figure \ref{poly_meta_map_results_language}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for basic meta-learning, figure \ref{cards_basic_results}}
+\caption{Table for basic meta-learning, Figure \ref{cards_basic_results}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
+\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in Figure \ref{cards_basic_results}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for playing optimal rewards for basic meta-learning, solid lines in figure \ref{cards_basic_results}}
+\caption{Table for playing optimal rewards for basic meta-learning, solid lines in Figure \ref{cards_basic_results}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
+\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in Figure \ref{cards_basic_results}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for meta-mapping from examples, figure \ref{cards_meta_map_results_examples}}
+\caption{Table for meta-mapping from examples, Figure \ref{cards_meta_map_results_examples}}
 \end{table}
@@
 \end{tabular}
-\caption{Table for meta-mapping from language, figure \ref{cards_meta_map_results_language}}
+\caption{Table for meta-mapping from language, Figure \ref{cards_meta_map_results_language}}
 \end{table}
@@
 \end{tabular}
-\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in figure \ref{cards_meta_map_results_examples}}
+\caption{Table of rewards if system ignored meta-mapping, colored dashed lines in Figure \ref{cards_meta_map_results_examples}}
 \end{table}

### 2019-11-11 writing/iclr2020_submission/rebuttal.txt
Iclr revision version
Tweaks for rebuttal

@@
 * The presentation is in general not well-polished, and needs revision.
-    Are there specific points that would benefit from further clarification?
+    Are there specific points that would benefit from further clarification, beyond what you have mentioned above?
 
@@
 
-Our main contribution is to propose a framework and method for zero-shot task performance.
+Our main contribution is to propose a meta-mapping framework for zero-shot task performance, and parsimonious method for performing these meta-mappings.
 MAML as such is not a method of zero-shot task performance, it requires examples to learn from.
@@
 
-We hope that this clarifies
+We hope that this clarifies things, and will help to address your concerns. Please let us know if further changes would be useful.
 
@@
 Even the datasets constructed in that paper can be used as a benchmark to validate the proposed method in image classification.
+We agree that the approach proposed there is very interesting, and have added a brief discussion of it!
+However, it does not consider the types of systematic relationships between tasks to which our system applies.
+For example, switching from winning to losing one of card games results in exactly opposite strategies, while other meta-mappings denote other types of relationships (such as switching what suit is more valuable).
+Hierarchical clustering cannot capture these richly structure relationships (see e.g.
+McClelland, Sadeghi, and Saxe (2017), "A Critique of Pure Hierarchy: Uncovering Cross-Cutting Structure in a Natural Dataset"), and hierarchically clustered or similarity based datasets alone thus do not suffice.
+This is part of why we suggest the construction of new datasets in the future directions.
+
     o	Other basic meta-learning algorithms like MAML[3] and many others should still be compared and discussed, especially in the basic meta-learning setting in Figure 2.
-
-Our main contribution is to propose a framework and method for zero-shot task performance.
+Our main contribution is to propose a meta-mapping framework for zero-shot task performance, and parsimonious method for performing these meta-mappings.
 MAML as such is not a method of zero-shot task performance, it requires examples to learn from.
@@
 performing tasks from examples), while figure 3 is performing tasks zero-shot, without examples.
-We have however, moved figure 5.
+We have tried to edit the captions to clarify this.
+We have also moved figure 5.
 to the main text, which does include this comparison between performing a task zero-shot and from examples, as well as another baseline.

### 2019-11-11 writing/homoiconic_meta_mapping_main.tex
Iclr revision version
Tweaks for rebuttal

@@
 
-\PassOptionsToPackage{numbers}{natbib}
+%\PassOptionsToPackage{numbers}{natbib}
 
-\usepackage[final]{neurips_2019}
-%\usepackage{iclr2020_conference,times}
+%\usepackage[final]{neurips_2019}
+\usepackage{iclr2020_conference,times}
 
@@
 We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space.
-HoMM approaches can be applied to any type of machine learning task, including supervised learning and reinforcement learning.
+HoMM approaches can be applied to any type of machine learning task.
 We demonstrate the utility of this perspective by exhibiting zero-shot remapping of behavior to adapt to new tasks.
@@
 \par
-\subsubsection*{Acknowledgements}
-We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
+%\subsubsection*{Acknowledgements}
+%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
 

### 2019-11-11 writing/homoiconic_meta_mapping_appendix.tex
Other change back

@@
 \subsection{Source repositories}
-(Will be included in de-anonymized version.)
-%The full code for the experiments and analyses can be found on github:
-%\begin{itemize}
-%\item \url{https://github.com/lampinen/polynomials}
-%    \begin{itemize}
-%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
-%    \end{itemize}
-%\item \url{https://github.com/lampinen/meta_cards} 
-%\end{itemize}
+The full code for the experiments and analyses can be found on github:
+\begin{itemize}
+\item \url{https://github.com/lampinen/polynomials}
+    \begin{itemize}
+        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
+    \end{itemize}
+\item \url{https://github.com/lampinen/meta_cards} 
+\end{itemize}
 \section{Numerical results} \label{app_numerical_results}

### 2019-11-13 run_cards.py
Steps towards using library

@@ -1,0 +1,267 @@
+from itertools import permutations
+
+from copy import deepcopy
+
+import numpy as np
+import tensorflow as tf
+
+from HoMM import HoMM_model
+from HoMM.configs import default_run_config, default_architecture_config
+import simple_card_games 
+
+run_config = default_run_config.default_run_config
+run_config.update({
+    "output_dir": "results_for_humans_with_library/",
+
+    "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
+    "option_names": ["suits_rule", "losers", "black_valuable"],
+    "suits_rule": [True, False],
+    "losers": [True, False],
+    "black_valuable": [True, False],
+
+    "bets": [0, 1, 2],
+    "new_tasks": [{"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": False},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": False, "suits_rule": True},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": False},
+                  {"game": "straight_flush", "losers": True,
+                  "black_valuable": True, "suits_rule": True}], # will be removed
+                                                                # from base tasks
+
+    "init_learning_rate": 1e-4,
+    "init_meta_learning_rate": 5e-5,
+
+    "lr_decay": 0.85,
+    "language_lr_decay": 0.8,
+    "meta_lr_decay": 0.9,
+
+    "lr_decays_every": 100,
+    "min_learning_rate": 3e-8,
+    "min_language_learning_rate": 1e-8,
+    "min_meta_learning_rate": 3e-7,
+
+})
+
+architecture_config = default_architecture_config.default_architecture_config
+architecture_config.update({
+   "input_shape": [(4 + 2) * 2],  # one hot card value and suit * 2
+   "output_shape": [3],  # 3 possible bets
+
+   "outcome_shape": [3 + 1],  # one-hot bet + reward
+   "output_masking": True,
+
+    "IO_num_hidden": 64,
+    "optimizer": "RMSProp",
+})
+if False:  # enable for persistent reps
+    architecture_config.update({
+        "persistent_task_reps": True,
+        "combined_emb_guess_weight": "varied",
+        "emb_match_loss_weight": 0.2,
+    })
+    run_config.update({
+        "output_dir": "results_for_humans_with_library_persistent/",
+    })
+
+class cards_HoMM_model(HoMM_model.HoMM_model):
[…]

### 2019-11-13 simple_card_games.py

@@ -111,22 +111,18 @@ class card_game(object):
             else:
                 self.hand_to_win_prob[hand] = 1.0 
 
-
     def wins(self, hand):
         wp = self.hand_to_win_prob[hand]
         return np.random.rand() <= wp
 
-
     def deal(self):
         return self.hands[np.random.randint(self.num_hands)]
-
 
     def play(self, hand, bet):
         if self.wins(hand):
             return bet 
         else:
             return -bet
-
 
     def compute_expected_return(self, max_bet=2., policy=None, ties="win"):
         """If policy is None, computes the optimal expected return. If not,
@@ -153,11 +149,41 @@ class card_game(object):
         r /= len(self.hands)
         return r
 
+    def __str__(self):
+        return "game_%s_l_%i_bv_%i_sr_%i" % (self.game_type, self.losers,
+                                             self.black_valuable, self.suits_rule)
 
-def _stringify_game(t):
-    """Helper for printing, etc."""
-    return "game_%s_l_%i_bv_%i_sr_%i" % (t.game_type, t.losers,
-                                         t.black_valuable, t.suits_rule)
+
+def get_meta_pairings(base_train_tasks, base_eval_tasks, meta_class_train_tasks, meta_map_train_tasks):
+    """Gets which tasks map to which other tasks under the meta_tasks (i.e. the
+    part of the meta datasets which is precomputable)"""
+    all_meta_tasks = meta_class_train_tasks + meta_map_train_tasks
+    meta_pairings = {mt: {"train": [], "eval": []} for mt in all_meta_tasks}
+    for mt in all_meta_tasks:
+        if mt[:6] == "toggle":
+            to_toggle = mt[7:]
+            for task in base_train_tasks:
+                other = deepcopy(task)
+                other[to_toggle] = not other[to_toggle]
+                if other in base_train_tasks:
+                    meta_pairings[mt]["train"].append((str(task),
+                                                       str(other)))
+                elif other in base_eval_tasks:
+                    meta_pairings[mt]["eval"].append((str(task),
+                                                       str(other)))
+
+        elif mt[:2] == "is":
+            pos_class = mt[3:]
+            for task in base_train_tasks:
+                truth_val = (task["game"] == pos_class) or (pos_class in task and task[pos_class])
+                meta_pairings[mt]["train"].append((str(task),
+                                                  1*truth_val))
+            for task in base_eval_tasks:
[…]

### 2019-11-13 run_cards.py
Bug squashing

@@ -19,14 +19,16 @@ run_config.update({
     "losers": [True, False],
     "black_valuable": [True, False],
 
+    "softmax_beta": 5,
+
     "bets": [0, 1, 2],
-    "new_tasks": [{"game": "straight_flush", "losers": True,
+    "new_tasks": [{"game_type": "straight_flush", "losers": True,
                   "black_valuable": False, "suits_rule": False},
-                  {"game": "straight_flush", "losers": True,
+                  {"game_type": "straight_flush", "losers": True,
                   "black_valuable": False, "suits_rule": True},
-                  {"game": "straight_flush", "losers": True,
+                  {"game_type": "straight_flush", "losers": True,
                   "black_valuable": True, "suits_rule": False},
-                  {"game": "straight_flush", "losers": True,
+                  {"game_type": "straight_flush", "losers": True,
                   "black_valuable": True, "suits_rule": True}], # will be removed
                                                                 # from base tasks
 
@@ -73,12 +75,15 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
     def _pre_build_calls(self):
         run_config = self.run_config
 
-        # set up the base tasks
-        base_tasks = [{"game": g, "losers": l, "black_valuable": b,
+        self.bets = run_config["bets"]
+
+        # set up the base task defs
+        base_tasks = [{"game_type": g, "losers": l, "black_valuable": b,
                        "suits_rule": s} for g in run_config["game_types"] for l in run_config["losers"] for b in run_config["black_valuable"] for s in run_config["suits_rule"]]
 
         self.base_train_tasks = [t for t in base_tasks if t not in run_config["new_tasks"]]
         self.base_eval_tasks = run_config["new_tasks"]
+
 
         # set up the meta tasks
         self.meta_class_train_tasks = ["is_" + g for g in run_config["game_types"]] + ["is_" + o for o in run_config["option_names"]] 
@@ -93,6 +98,24 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
             base_eval_tasks=self.base_eval_tasks,
             meta_class_train_tasks=self.meta_class_train_tasks,
             meta_map_train_tasks=self.meta_map_train_tasks) 
+
+        # convert to games
+
+        self.base_train_tasks = [simple_card_games.game_from_def(t) for t in self.base_train_tasks]
+        self.base_eval_tasks = [simple_card_games.game_from_def(t) for t in self.base_eval_tasks]
+
[…]

### 2019-11-13 simple_card_games.py

@@ -1,5 +1,7 @@
 import numpy as np
 
+from copy import deepcopy
+
 
 class card_game(object):
     """Class for creating simple card games which have 4 card values and 2 
@@ -154,6 +156,19 @@ class card_game(object):
                                              self.black_valuable, self.suits_rule)
 
 
+def stringify_game_def(game_def):
+        return "game_%s_l_%i_bv_%i_sr_%i" % (game_def["game_type"], game_def["losers"],
+                                             game_def["black_valuable"], game_def["suits_rule"])
+
+
+def game_from_def(game_def):
+    g = card_game(game_type=game_def["game_type"],
+                  black_valuable=game_def["black_valuable"],
+                  suits_rule=game_def["suits_rule"],
+                  losers=game_def["losers"])
+    return g
+
+
 def get_meta_pairings(base_train_tasks, base_eval_tasks, meta_class_train_tasks, meta_map_train_tasks):
     """Gets which tasks map to which other tasks under the meta_tasks (i.e. the
     part of the meta datasets which is precomputable)"""
@@ -166,21 +181,21 @@ def get_meta_pairings(base_train_tasks, base_eval_tasks, meta_class_train_tasks,
                 other = deepcopy(task)
                 other[to_toggle] = not other[to_toggle]
                 if other in base_train_tasks:
-                    meta_pairings[mt]["train"].append((str(task),
-                                                       str(other)))
+                    meta_pairings[mt]["train"].append((stringify_game_def(task),
+                                                       stringify_game_def(other)))
                 elif other in base_eval_tasks:
-                    meta_pairings[mt]["eval"].append((str(task),
-                                                       str(other)))
+                    meta_pairings[mt]["eval"].append((stringify_game_def(task),
+                                                       stringify_game_def(other)))
 
         elif mt[:2] == "is":
             pos_class = mt[3:]
             for task in base_train_tasks:
-                truth_val = (task["game"] == pos_class) or (pos_class in task and task[pos_class])
-                meta_pairings[mt]["train"].append((str(task),
+                truth_val = (task["game_type"] == pos_class) or (pos_class in task and task[pos_class])
+                meta_pairings[mt]["train"].append((stringify_game_def(task),
                                                   1*truth_val))
             for task in base_eval_tasks:
-                truth_val = (task["game"] == pos_class) or (pos_class in task and task[pos_class])
-                meta_pairings[mt]["eval"].append((str(task),
[…]

### 2019-11-14 run_cards.py
Working?

@@ -104,6 +104,8 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
         self.base_train_tasks = [simple_card_games.game_from_def(t) for t in self.base_train_tasks]
         self.base_eval_tasks = [simple_card_games.game_from_def(t) for t in self.base_eval_tasks]
 
+        self.game_str_to_task = {str(t): t for t in self.base_train_tasks + self.base_eval_tasks}
+
 
     def fill_buffers(self, num_data_points=1024):
         """Add new "experiences" to memory buffers."""
@@ -197,13 +199,13 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
 
     def _pre_loss_calls(self):
         self.base_output_softmax = tf.nn.softmax(
-            self.run_config["softmax_beta"] * self.base_output)
+            self.run_config["softmax_beta"] * self.base_unmasked_output)
 
         self.base_fed_emb_output_softmax = tf.nn.softmax(
-            self.run_config["softmax_beta"] * self.base_fed_emb_output)
+            self.run_config["softmax_beta"] * self.base_fed_emb_unmasked_output)
 
         self.base_cached_emb_output_softmax = tf.nn.softmax(
-            self.run_config["softmax_beta"] * self.base_cached_emb_output)
+            self.run_config["softmax_beta"] * self.base_cached_emb_unmasked_output)
 
     def fill_buffers(self, num_data_points=1024):
         """Add new "experiences" to memory buffers."""
@@ -232,6 +234,8 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
     def reward_eval_helper(self, game, act_probs, encoded_hands=None, hands=None):
         if encoded_hands is not None:
             hands = self.decode_hands(encoded_hands)
+        if isinstance(game, str):
+            game = self.game_str_to_task[game]
         actions = [np.argmax(act_probs[i, :],
                              axis=-1) for i in range(len(act_probs))]
         bets = [self.bets[a] for a in actions]
@@ -248,7 +252,7 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
 
         if base_or_meta == "base":
             outcomes = feed_dict[self.base_target_ph]
-            if call_type == "standard": 
+            if call_type == "standard" or not self.architecture_config["persistent_task_reps"]: 
                 feed_dict[self.base_outcome_ph] = outcomes 
[…]

### 2019-11-14 run_cards.py
Bugfix

@@ -252,7 +252,7 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
 
         if base_or_meta == "base":
             outcomes = feed_dict[self.base_target_ph]
-            if call_type == "standard" or not self.architecture_config["persistent_task_reps"]: 
+            if call_type == "standard" or train_or_eval == "eval" or not self.architecture_config["persistent_task_reps"]: 
                 feed_dict[self.base_outcome_ph] = outcomes 
             targets, target_mask = self._outcomes_to_targets(outcomes)
             feed_dict[self.base_target_ph] = targets 

### 2019-11-14 run_cards.py
Bugfix + tweaks

@@ -44,6 +44,8 @@ run_config.update({
     "min_language_learning_rate": 1e-8,
     "min_meta_learning_rate": 3e-7,
 
+    "num_epochs": 40000,
+    "eval_every": 200,
 })
 
 architecture_config = default_architecture_config.default_architecture_config
@@ -56,12 +58,14 @@ architecture_config.update({
 
     "IO_num_hidden": 64,
     "optimizer": "RMSProp",
+
+    "meta_batch_size": 768,
 })
 if False:  # enable for persistent reps
     architecture_config.update({
         "persistent_task_reps": True,
         "combined_emb_guess_weight": "varied",
-        "emb_match_loss_weight": 0.2,
+        "emb_match_loss_weight": 0.5,
     })
     run_config.update({
         "output_dir": "results_for_humans_with_library_persistent/",

### 2019-11-14 run_cards.py
Tweaking for new library version

@@ -264,14 +264,16 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
 
         return feed_dict
 
-    def base_eval(self, task):
+    def base_eval(self, task, train_or_eval):
         feed_dict = self.build_feed_dict(task, call_type="base_cached_eval")
         fetches = [self.total_base_loss, self.base_output_softmax]
         res = self.sess.run(fetches, feed_dict=feed_dict)
         inputs = feed_dict[self.base_input_ph]
         rewards = self.reward_eval_helper(task, res[1], inputs)
         name = str(task)
-        return [name + "_loss", name + "_rewards"], [res[0], rewards] 
+        return ([name + "_loss:" + train_or_eval, 
+                 name + "_rewards:" + train_or_eval],
+                [res[0], rewards]) 
 
     def base_embedding_eval(self, embedding, task):
         feed_dict = self.build_feed_dict(task, fed_embedding=embedding, call_type="base_fed_eval")

### 2019-12-04 cards_persistent_analysis.Rmd
Some more analysis of what's going on, and starting to derive what selection criteria might be for model eval.

---
title: "Cards persistent analysis"
author: "Andrew Lampinen"
output: html_document
---

```{r}
library(tidyverse)
```

# data loading

```{r}
parent_dir = "."
subdirs = c("results_for_humans_with_library_2", "results_for_humans_with_library_3",
            #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4", 
            "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
            "results_for_humans_with_library_persistent_7", 
            "results_for_humans_with_library_persistent_8", 
            "results_for_humans_with_library_persistent_9"
            )
num_runs = 3
```

```{r}
read_config = function(config_file) { 
  config = read_delim(config_file, delim="\n") %>%
    separate(`key, value`, c("key", "value"), sep=",", extra="merge") %>%
    spread(key, value) %>%
    mutate_at(c("base_train_tasks", "base_eval_tasks", "meta_class_train_tasks", "meta_class_eval_tasks", "meta_map_train_tasks", "meta_map_eval_tasks"), function(x) {
      x = gsub("\\\"|[][]| |\'", "", x)
      return(str_split(x, ","))
    } )
}
```

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s/%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      print(filename)
      if (!file.exists(filename)) {
        print(paste("skipping ", filename, sep=""))
        next
      }
      if (grepl("config", file_type)) {
        this_d = read_config(filename)
      } else {
        this_d = read.csv(filename, check.names=F, header=T) 
        names(this_d) <- make.unique(names(this_d))

      }
      this_d = this_d %>%
        mutate(run = run_i,
               run_type = result_subdir)
      d = d %>%
        bind_rows(this_d)
    }

  }
  return(d)
}
```

```{r}
config_d = load_d(parent_dir, subdirs, num_runs, "run_config")
loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
```

# some manipulation

```{r}
loss_d = loss_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  mutate(meta = grepl("is|toggle", task)) %>%
  filter(!meta, grepl("rewards", task)) %>%
  mutate(task = sub("_rewards", "", task),
         train_or_eval = ifelse(grepl("straight_flush_l_1", task), "eval", "train"))

```

```{r}
meta_true_d = meta_true_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  separate(task, c("meta_task", "mapping_toe", "base_task_toe", "source", "target"), ":|->")

```

# basic plots
```{r}
theme_set(theme_bw())
```

```{r}
ggplot(loss_d,
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ meta)
```

```{r}
ggplot(meta_true_d %>% 
         filter(meta_task == "toggle_losers"),
       aes(x=epoch, y=loss, color=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run ~ run_type)
```

```{r}
ggplot(meta_true_d %>% 
         filter(meta_task == "toggle_losers",
                source == "game_straight_flush_l_0_bv_0_sr_0"),
       aes(x=epoch, y=loss, color=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run ~ run_type)
```

```{r}
ggplot(meta_true_d %>%
         filter(meta_task=="toggle_losers") %>%
         group_by(run_type, run, epoch, base_task_toe) %>%
         summarize(mean_loss=mean(loss)) %>%
         ungroup() %>%
         spread(base_task_toe, mean_loss),
       aes(x=example_is_train, y=example_is_eval, alpha=epoch)) +
  geom_point() +
  facet_grid(run ~ run_type)
```

```{r}
selected_meta_true_d = meta_true_d %>%
  filter(meta_task=="toggle_losers",
         base_task_toe == "example_is_train" | source == "game_straight_flush_l_0_bv_0_sr_0") %>%
  group_by(run_type, run, epoch, base_task_toe) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(base_task_toe, mean_loss) %>%
  group_by(run_type, run) %>%
  filter(example_is_train == max(example_is_train))
selected_meta_true_d %>%
  arrange(desc(example_is_train))

```

### 2019-12-04 run_cards.py
Some new runs

@@ -11,7 +11,7 @@ import simple_card_games
 
 run_config = default_run_config.default_run_config
 run_config.update({
-    "output_dir": "results_for_humans_with_library/",
+    "output_dir": "results_for_humans_with_library_4/",
 
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
@@ -19,7 +19,7 @@ run_config.update({
     "losers": [True, False],
     "black_valuable": [True, False],
 
-    "softmax_beta": 5,
+    "softmax_beta": 8,
 
     "bets": [0, 1, 2],
     "new_tasks": [{"game_type": "straight_flush", "losers": True,
@@ -32,20 +32,20 @@ run_config.update({
                   "black_valuable": True, "suits_rule": True}], # will be removed
                                                                 # from base tasks
 
-    "init_learning_rate": 1e-4,
-    "init_meta_learning_rate": 5e-5,
+    "init_learning_rate": 2e-4,
+    "init_meta_learning_rate": 1e-4,
 
     "lr_decay": 0.85,
     "language_lr_decay": 0.8,
     "meta_lr_decay": 0.9,
 
-    "lr_decays_every": 100,
+    "lr_decays_every": 200,
     "min_learning_rate": 3e-8,
     "min_language_learning_rate": 1e-8,
     "min_meta_learning_rate": 3e-7,
 
-    "num_epochs": 40000,
-    "eval_every": 200,
+    "num_epochs": 500000,
+    "eval_every": 100,
 })
 
 architecture_config = default_architecture_config.default_architecture_config
@@ -56,19 +56,19 @@ architecture_config.update({
    "outcome_shape": [3 + 1],  # one-hot bet + reward
    "output_masking": True,
 
-    "IO_num_hidden": 64,
+    "IO_num_hidden": 128,
     "optimizer": "RMSProp",
 
     "meta_batch_size": 768,
 })
-if False:  # enable for persistent reps
+if True:  # enable for persistent reps
     architecture_config.update({
         "persistent_task_reps": True,
         "combined_emb_guess_weight": "varied",
-        "emb_match_loss_weight": 0.5,
+        "emb_match_loss_weight": 1.,
     })
     run_config.update({
-        "output_dir": "results_for_humans_with_library_persistent/",
+        "output_dir": "results_for_humans_with_library_persistent_10/",
     })
 
 class cards_HoMM_model(HoMM_model.HoMM_model):

### 2019-12-05 writing/poster/HoMM_transferable_skills_poster.tex
Starting poster

\documentclass[final]{beamer}
\usepackage[size=a0]{beamerposter}
\mode<presentation>{\usetheme{lampinen}}
\usepackage{float}
\usepackage{url}           
%\usepackage{booktabs}      
\usepackage{amsfonts}      
%\usepackage{blkarray}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{nicefrac}      
%\usepackage{microtype}   
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage[numbers]{natbib}
\usetikzlibrary{matrix,backgrounds}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{decorations.pathreplacing,angles,quotes}

\tikzstyle{netnode} = [circle, draw, thick, inner sep=0pt, minimum size=0.5cm]
\tikzstyle{relunode} = [rectangle, draw, thick, inner sep=0pt, minimum size=0.5cm]

\tikzstyle{line} = [draw, line width=0.5pt, -latex']

\newcommand{\R}{\mathbb{R}}
\newcommand{\bb}[1]{{\bf\overline{#1}}}
\newcommand{\bh}[1]{{\bf\hat{#1}}}
\newcommand{\sg}[1]{{\color{red} #1}}
\newcommand{\eopt}[1]{\varepsilon^\text{opt}_{#1}}

\newcommand{\trainerr}{\mathcal{\varepsilon}_\text{train}}
\newcommand{\generr}{\mathcal{\varepsilon}_\text{test}}

\newcommand{\toptn}{{t}^\text{opt}_\text{neural}}
\newcommand{\eoptn}{\mathcal{\varepsilon}^\text{opt}_\text{neural}}
\newcommand{\eoptnn}{\mathcal{\varepsilon}^\text{opt}_\text{non-neural}}

\newcommand{\wa}{{\bf{W}^{21}}}
\newcommand{\wb}{{\bf{W}^{32}}}
\newcommand{\ddt}{\frac{d}{dt}}
\newcommand{\ovn}{\overline{N}}

\setlength{\parskip}{0.5em}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\title{Zero-Shot Task Adaptation by Homoiconic Meta-mapping (HoMM)}
\author{Andrew K. Lampinen \& James L. McClelland}
\institute{Department of Psychology, Stanford University}

\begin{document}

\begin{frame}[t]{}
\vspace{-1.5em}
\begin{columns}

\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Zero-shot adaptation}
\end{block}
\begin{block}{\huge Meta-mapping}
\end{block}
\end{column}
\begin{column}[t]{0.496\textwidth}
\begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
\end{block}
\end{column}
\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Conclusions}
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}

### 2019-12-05 writing/poster/HoMM_transferable_skills_poster.tex
Main schematic figure

@@
 \usepackage{xcolor}
-\usepackage{tikz}
 \usepackage{subcaption}
 \usepackage[numbers]{natbib}
-\usetikzlibrary{matrix,backgrounds}
-\usetikzlibrary{positioning}
+\usepackage{tikz}
+
 \usetikzlibrary{shapes,arrows}
-\usetikzlibrary{decorations.pathreplacing,angles,quotes}
 
-\tikzstyle{netnode} = [circle, draw, thick, inner sep=0pt, minimum size=0.5cm]
-\tikzstyle{relunode} = [rectangle, draw, thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{block} = [rectangle, draw, line width=2mm, align=center, rounded corners]
+\tikzstyle{boundingbox} = [line width=2mm, lightgray]
+\tikzstyle{dashblock} = [rectangle, draw, line width=2mm, align=center, dashed]
+\tikzstyle{conc} = [ellipse, draw, thick, dashed, align=center]
+\tikzstyle{netnode} = [circle, draw, line width=2mm, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{relunode} = [rectangle, draw, very thick, inner sep=0pt, minimum size=0.5cm]
+\tikzstyle{line} = [draw, line width=2mm, -latex']
+\tikzstyle{arrow} = [draw, ->, line width=2mm]
 
-\tikzstyle{line} = [draw, line width=0.5pt, -latex']
-
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\bb}[1]{{\bf\overline{#1}}}
-\newcommand{\bh}[1]{{\bf\hat{#1}}}
-\newcommand{\sg}[1]{{\color{red} #1}}
-\newcommand{\eopt}[1]{\varepsilon^\text{opt}_{#1}}
-
-\newcommand{\trainerr}{\mathcal{\varepsilon}_\text{train}}
-\newcommand{\generr}{\mathcal{\varepsilon}_\text{test}}
-
-\newcommand{\toptn}{{t}^\text{opt}_\text{neural}}
-\newcommand{\eoptn}{\mathcal{\varepsilon}^\text{opt}_\text{neural}}
-\newcommand{\eoptnn}{\mathcal{\varepsilon}^\text{opt}_\text{non-neural}}
-
-\newcommand{\wa}{{\bf{W}^{21}}}
-\newcommand{\wb}{{\bf{W}^{32}}}
-\newcommand{\ddt}{\frac{d}{dt}}
-\newcommand{\ovn}{\overline{N}}
+\definecolor{bpurp}{HTML}{984ea3}
+\definecolor{bblue}{HTML}{377eb8}
 
@@
 \begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}[scale=3, every node/.style={scale=1.2}]
+%% basic meta learning
+\begin{scope}[shift={(0.4, 0.4)}]
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\end{scope}
+\begin{scope}[shift={(0.2, 0.2)}]
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\end{scope}
+
+\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
+\node[lightgray] at (-1.2, 2.9) {(a) Basic meta-learning};
+\node at (-1.5, -4) (examples) {Examples};
+\node at (-1.5, -3.2) (D1) {
+\(\left\{
+\begin{matrix}
+(z^{ex}_{in,0}, z^{ex}_{targ,0})\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (1.5, -4) (probes) {Probes};
+\node at (1.5, -3.2) (D2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [block] at (-1.5, -1.95) (M) {\(\mathcal{M}\)};
+\path [arrow] ([yshift=-5]D1.north) to (M);
+
+\node at (-1, -1) (zfunc) {\(z^{func}\)};
+\path [arrow, out=90, in=-135] (M.north) to ([xshift=5,yshift=2]zfunc.south west);
+
+\node[block] at (0, -0.55) (H) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]zfunc.north) to (H.west);
+
+\node [block, dashed] at (1.5, -0.55) (F) {\(F_{z^{func}}\)};
+\path[arrow] (H.east) to (F.west);
+
+\path [arrow, dashed] (D2) to (F);
+
+\node at (1.5, 1) (outputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 1.75) (predictions) {Predictions};
+
+\path [arrow, dashed] (F) to ([yshift=3]outputs.south);
+
+\node at (-1.5, 1.75) (probetargs) {Probe targets};
+\node at (-1.5, 1) (D2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [align=center, text width=1.25 cm] at (0, 2.25) (dispatch) {\baselineskip=12pt Loss\par};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]outputs.west) to (dispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=-3.5]D2targs.east) to (dispatch.south);
+
+%% meta mapping
+\begin{scope}[shift={(6.4, 1.5)}]
+\draw[boundingbox, draw=bpurp, fill=white] (-3, -4.3) rectangle (2.6, 3.2);
+\node[bpurp] at (-1.6, 2.9) {(b) Meta-mapping};
+\node at (-1.5, -4) (metaexamples) {Examples};
+\node at (-1.5, -3.2) (metaD1) {
+\(\left\{
+\begin{matrix}
+(z^{func}_{in,0}, z^{func}_{targ,0})\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (1.5, -4) (metaprobes) {Probes};
+\node at (1.5, -3.2) (metaD2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{func,prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [block] at (-1.5, -1.95) (metaM) {\(\mathcal{M}\)};
+\path [arrow] ([yshift=-5]metaD1.north) to (metaM);
+
+\node at (-1, -1) (metazfunc) {\(z^{meta}\)};
+\path [arrow, out=90, in=-135] (metaM.north) to ([xshift=5,yshift=2]metazfunc.south west);
+
+\node[block] at (0, -0.55) (metaH) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]metazfunc.north) to (metaH.west);
+
+\node [block, dashed] at (1.5, -0.55) (metaF) {\(F_{z^{meta}}\)};
+\path[arrow] (metaH.east) to (metaF.west);
+
+\path [arrow, dashed] (metaD2) to (metaF);
+
+\node at (1.5, 1) (metaoutputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{func,pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 1.75) (metapredictions) {Predictions};
+
+\path [arrow, dashed] (metaF) to ([yshift=3]metaoutputs.south);
+
+\node at (-1.5, 1.75) (metaprobetargs) {Probe targets};
+\node at (-1.5, 1) (metaD2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{func,prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [align=center] at (0, 2.25) (metadispatch) {Loss (train)};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]metaoutputs.west) to (metadispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=1]metaD2targs.east) to (metadispatch.south);
+
+\end{scope}
+\path [arrow, line width=2mm, draw=bpurp, dotted, out=-40, in=-140] ([xshift=-1, yshift=3]zfunc.south) to ([xshift=17, yshift=2]metaD1.west);
+
+%% evaluating meta mapping
+\begin{scope}[shift={(12.1, 0)}]
+\draw[boundingbox, draw=bblue, fill=white] (-2.65, -4.3) rectangle (2.85, 3.2);
+\node[bblue] at (-0.85, 2.85) {(c) Zero-shot evaluation};
+
+\node at (1.5, -4) (metaevalprobes) {Probes};
+\node at (1.5, -3.2) (metaevalD2) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{in,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node at (-1, -1) (metaevalzfunc) {\(z^{func,pred}\)};
+
+\node[block] at (0, -0.55) (metaevalH) {\(\mathcal{H}\)};
+\path [arrow, out=45, in=180] ([yshift=-3]metaevalzfunc.north) to (metaevalH.west);
+
+\node [block, dashed] at (1.5, -0.55) (metaevalF) {\(F_{z^{func,pred}}\)};
+\path[arrow] (metaevalH.east) to (metaevalF.west);
+
+\path [arrow, dashed] (metaevalD2) to (metaevalF);
+
+\node at (1.5, 1) (metaevaloutputs) {
+%\(z^{pred}_{out}\)};
+\(\left\{
+\begin{matrix}
+z^{pred}_{out,0},\\
+$\vdots$
+\end{matrix}\right\}\)};
+\node at (1.5, 1.75) (metaevalpredictions) {Predictions};
+
+\path [arrow, dashed] (metaevalF) to ([yshift=3]metaevaloutputs.south);
+
+\node at (-1, 1.75) (metaevalprobetargs) {Probe targets};
+\node at (-1, 1) (metaevalD2targs) {
+%\(z^{prb}_{in}\)};
+\(\left\{
+\begin{matrix}
+z^{prb}_{targ,0}\\
+$\vdots$
+\end{matrix}\right\}\)};
+
+\node [align=center] at (0.3, 2.25) (metaevaldispatch) {Loss (eval)};
+
+\path [arrow, dashed, out=180, in=-90] ([xshift=3]metaevaloutputs.west) to (metaevaldispatch.south);
+
+\path [arrow, dashed, out=0, in=-90] ([xshift=-0.5]metaevalD2targs.east) to (metaevaldispatch.south);
+\end{scope}
+\path [arrow, line width=2mm, draw=bblue, dotted, out=-30, in=160] ([xshift=3,yshift=-3]metaoutputs.center) to ([xshift=2, yshift=-10]metaevalzfunc.north west);
+\end{tikzpicture}
+%\caption{The HoMM architecture allows for transformations at different levels of abstraction.
+(a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on probe inputs (used to encourage the system to generalize).
+However, our approach goes beyond basic meta-learning.
+The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (b).
+To evaluate meta-mapping performance, a probe embedding of a held-out function is transformed by the architecture to yield a predicted embedding for the transformed task.
+The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (c).
+Because the function embedding is predicted by a transformation rather than from examples, new tasks can be performed zero-shot.
+(\(M\) and \(H\) are learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\).
+Input and output encoders/decoders are omitted for simplicity.
+See the text and Appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
+\end{figure}
 \end{block}

### 2019-12-05 writing/poster/HoMM_transferable_skills_poster.tex
Some text

@@
 \begin{frame}[t]{}
-\vspace{-1.5em}
+\vspace{-1em}
 \begin{columns}
@@
 \begin{column}[t]{0.248\textwidth}
-\begin{block}{\huge Zero-shot adaptation}
+\begin{block}{\huge Intro: zero-shot adaptation}
+\Large
+\begin{itemize}
+\item Humans can adapt zero-shot to novel tasks, based on their relationship to prior tasks.
+\item For example, if asked to alter our behavior on a game we have learned (like trying to lose or achieve some other goal), we can perform well on our first try.
+\item We take inspiration from this to propose \emph{meta-mapping}, a novel function-transformation perspective on zero-shot task performance.
+\item We propose Homoiconic Meta-Mapping (HoMM) architectures as a parsimonious implementation of this framework.
+\item We demonstrate successful zero-shot adaptation to related but substantially different tasks, such as adapting to trying to lose a card game the system has been trained to win.
+\end{itemize}
 \end{block}
 \begin{block}{\huge Meta-mapping}
+\Large
+\begin{itemize}
+\item Consider a functional perspective. Basic tasks can be seen as functions mapping images to classes, or states to actions, or card hands to bets.
+\item We suggest it's then useful to think of transformations over functions, that is, functions which take other functions as input and/or output.
+\item We call these higher-level functions \emph{meta-mappings}. They are functions which take basic functions as input and produce other basic functions as output.
+\item For example, we could have a try-to-lose function which takes as input a function that tries to win money by betting, and outputs a function which tries to lose money by betting.
+\item We suggest that these transformations of functions are a useful way to think about human flexibility.
+\end{itemize}
 \end{block}

### 2019-12-05 writing/poster/HoMM_transferable_skills_poster.tex
Style tweaks and prior work

@@
 \begin{block}{\huge Intro: zero-shot adaptation}
-\Large
 \begin{itemize}
@@
 \begin{block}{\huge Meta-mapping}
-\Large
 \begin{itemize}
-\item Consider a functional perspective. Basic tasks can be seen as functions mapping images to classes, or states to actions, or card hands to bets.
+\item Consider a functional perspective. Basic tasks can be seen as functions mapping images to classes, or states to actions, or card hands to bets, etc.
 \item We suggest it's then useful to think of transformations over functions, that is, functions which take other functions as input and/or output.
@@
 \item For example, we could have a try-to-lose function which takes as input a function that tries to win money by betting, and outputs a function which tries to lose money by betting.
-\item We suggest that these transformations of functions are a useful way to think about human flexibility.
+\item We suggest that meta-mappings are a useful way to think about human-like zero-shot adaptation.
 \end{itemize}
@@
 \centering
+\normalsize
 \begin{tikzpicture}[scale=3, every node/.style={scale=1.2}]
@@
 \begin{column}[t]{0.248\textwidth}
+\begin{block}{\huge Why \& prior work}
+\begin{itemize}
+\item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
+\item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
+\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language alone.
+\item Meta-mapping thus offers a happy intermediate between meta-learning (which requires data on the new task), and zero-shot performance from language alone.
+\end{itemize}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{../figures/why_meta_mapping.png}
+\label{fig_why_meta_mapping}
+\end{figure}
+
+\end{block}
 \begin{block}{\huge Conclusions}

### 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
Tweaks and updates

@@
 \begin{block}{\huge Intro: zero-shot adaptation}
+\vspace{-0.6em}
 \begin{itemize}
@@
 \begin{block}{\huge Meta-mapping}
+\vspace{-0.6em}
 \begin{itemize}
@@
 \item We call these higher-level functions \emph{meta-mappings}. They are functions which take basic functions as input and produce other basic functions as output.
-\item For example, we could have a try-to-lose function which takes as input a function that tries to win money by betting, and outputs a function which tries to lose money by betting.
+\item For example, we could have a try-to-lose function which takes as input a function that tries to win money at poker, and outputs a function which tries to lose money at poker.
 \item We suggest that meta-mappings are a useful way to think about human-like zero-shot adaptation.
@@
 \end{block}
+\begin{block}{\huge Functional analogy}
+\vspace{-0.6em}
+\begin{itemize}
+\item Meta-mappings can be learned in the same way that other functions are learned -- using a deep network to approximate the function.
+\item We learn a meta-mapping from a dataset of example (input function, output function) tuples, analogously to learning a basic task from example tuples of (image, class), or (hand, bet, reward). 
+\end{itemize}
+\end{block}
 \end{column}
+
 \begin{column}[t]{0.496\textwidth}
 \begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
+\begin{columns}
+\begin{column}[t]{0.48\textwidth}
+\textbf{Basic tasks:}
+\begin{itemize}
+\item We embed inputs and outputs into a shared latent space $Z$. 
+\item We meta-learn to  
+\end{itemize}
+\end{column}
+\begin{column}[t]{0.48\textwidth}
+\textbf{Meta-mappings:}
+\end{column}
+\end{columns}
+
 \begin{figure}[H]
@@
 \normalsize
-\begin{tikzpicture}[scale=3, every node/.style={scale=1.2}]
+\begin{tikzpicture}[scale=2.5, every node/.style={scale=1}]
 %% basic meta learning

### 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
Basic task description

@@
 \usepackage{amsfonts}      
+\usepackage{bm}
 %\usepackage{blkarray}
@@
 \begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
+\vspace{-0.5em}
 \begin{columns}
 \begin{column}[t]{0.48\textwidth}
-\textbf{Basic tasks:}
+\textbf{Basic tasks (meta-learning):}
 \begin{itemize}
-\item We embed inputs and outputs into a shared latent space $Z$. 
-\item We meta-learn to  
+\item We embed inputs and outputs into a shared latent space \(\bm Z\). 
+\item We meta-learn a network \(\mathcal{M}\) to map a dataset of embedded example tuples \(\{(z^{ex}_{in}, z^{ex}_{out}), ...\}\) to an embedding for that task/function \(z^{func}\). 
+\item The function embedding \(z^{func}\) parameterizes a task-network \(F\), via a hyper network \(\mathcal{H}\).
+\item The task network \(F\) transforms embedded inputs to embedded outputs, which are decoded to output.
+\item The system is trained end-to-end.
 \end{itemize}
@@
 \begin{column}[t]{0.48\textwidth}
-\textbf{Meta-mappings:}
+\textbf{Meta-mappings (zero-shot task performance):}
 \end{column}

### 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
Further tweaks, experiment results, meta-mapping descriptioN

@@
 \item Meta-mappings can be learned in the same way that other functions are learned -- using a deep network to approximate the function.
-\item We learn a meta-mapping from a dataset of example (input function, output function) tuples, analogously to learning a basic task from example tuples of (image, class), or (hand, bet, reward). 
+\item We learn a meta-mapping from a dataset of example (input function, output function) tuples, analogously to learning a basic task from example tuples of (image, label), or (hand, bet, reward). 
 \end{itemize}
@@
 \begin{itemize}
-\item We embed inputs and outputs into a shared latent space \(\bm Z\). 
+\item We embed inputs and outputs into a shared latent space \(Z\). 
 \item We meta-learn a network \(\mathcal{M}\) to map a dataset of embedded example tuples \(\{(z^{ex}_{in}, z^{ex}_{out}), ...\}\) to an embedding for that task/function \(z^{func}\). 
 \item The function embedding \(z^{func}\) parameterizes a task-network \(F\), via a hyper network \(\mathcal{H}\).
-\item The task network \(F\) transforms embedded inputs to embedded outputs, which are decoded to output.
+\item The task network \(F\) transforms embedded inputs to results which are decoded to output.
 \item The system is trained end-to-end.
@@
 \textbf{Meta-mappings (zero-shot task performance):}
+\begin{itemize}
+\item We exploit the analogy above to use \emph{the same meta-learning system} for meta-mappings.
+\item We pass a dataset of example function mappings \(\{(z^{func}_{in}, z^{func}_{out}\}\) through \(\mathcal{M}\) to produce a meta-mapping embedding \(z^{meta}\). 
+\item We parameterize \(F\) as before, and can pass a new function embedding through \(F\) to guess an embedding for a transformed task \(z^{func,pred}\).
+\item We can use \(z^{func,pred}\) to perform a transformed task zero-shot (or train to match a target).
+\item Parsimonious, same networks as basic meta-learning.
+\end{itemize}
 \end{column}
@@
 \end{block}
+
+\begin{block}{\huge Experiments}
+\vspace{-0.5em}
+\begin{columns}
+\begin{column}[t]{0.48\textwidth}
+\textbf{Polynomial regression:}
+\begin{itemize}
+\item Basic tasks: regress polynomials (degree \(\leq 3\)) in 4 variables from examples. 
+\item Meta-mappings: transform polynomial by permuting variables, adding or multiplying constants, squaring. 
+\item Good zero-shot performance!
+\end{itemize}
+\begin{figure}[H]
+\includegraphics[width=0.7\textwidth]{../figures/poly/meta_results.png}
+\end{figure}
 \end{column}
+\begin{column}[t]{0.48\textwidth}
+\textbf{Simple card games:}
+\begin{itemize}
+\item Basic tasks: input is hand, make bet, get stochastic reward. A variety of games with different rules. 
+\item Meta-mappings: transform game by trying to lose, changing values of suits. 
+\item Good zero-shot performance!
+\end{itemize}
+\begin{figure}[H]
+\includegraphics[width=0.7\textwidth]{../figures/meta_mapping.png}
+\end{figure}
+\end{column}
+\end{columns}
+\end{block}
+\end{column}
+
 \begin{column}[t]{0.248\textwidth}

### 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
Some conclusions

@@
 \item Meta-mappings: transform game by trying to lose, changing values of suits. 
-\item Good zero-shot performance!
+\item Good performance in different hold-out conditions!
 \end{itemize}
@@
 \begin{block}{\huge Why \& prior work}
+\vspace{-0.6em}
 \begin{itemize}
 \item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
+\item Other prior work has considered using prior task similarity, but not transformation-based approaches.
 \item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
@@
 \begin{block}{\huge Conclusions}
+\vspace{-0.6em}
+\begin{itemize}
+\item We propose \emph{meta-mappings}, a new perspective on zero-shot task performance via transformation of prior tasks. 
+\item We propose homoiconic meta-mapping architectures as a parsimonious implementation that exploits the analogy between meta-mappings and basic tasks. 
+\item We demonstrate the success of our approach, and show it outperforms a zero-shot baseline based on language descriptions alone. 
+\item Check out our paper for additional studies, including:
+    \begin{itemize}
+    \Large
+    \item Cueing meta-mappings from language.
+    \item Lesions and baselines, like an unshared \(Z\) or a non-hyper-network based approach. 
+    \item Applications to continual learning.
+    \end{itemize}
+\end{itemize}
 \end{block}

### 2019-12-06 cards_persistent_analysis.Rmd
A note
Some tweaks and a non-productive selection technique

@@
 parent_dir = "."
-subdirs = c("results_for_humans_with_library_2", "results_for_humans_with_library_3",
+subdirs = c(#"results_for_humans_with_library_2", 
+            "results_for_humans_with_library_3", "results_for_humans_with_library_4",
             #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4",
             "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
-            "results_for_humans_with_library_persistent_7", 
-            "results_for_humans_with_library_persistent_8", 
-            "results_for_humans_with_library_persistent_9"
+            #"results_for_humans_with_library_persistent_7", 
+            #"results_for_humans_with_library_persistent_8", 
+            "results_for_humans_with_library_persistent_9",
+            "results_for_humans_with_library_persistent_10"
             )
-num_runs = 3
+num_runs = 2
 ```
@@
 
+This seems to be a good criteria for persistent reps, but interestingly not for non-persistent.
 ```{r}
@@
 ```
+
+This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other.
+
+```{r}
+selected_meta_true_d_3 = meta_true_d %>%
+  filter(meta_task=="toggle_losers",
+         !grepl("persistent", run_type)) %>%
+  mutate(source_type=case_when(
+    base_task_toe == "example_is_train" ~ "train",
+    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
+    T ~ "eval_other")) %>%
+  group_by(run_type, run, epoch, source_type) %>%
+  summarize(mean_loss=mean(loss)) %>%
+  ungroup() %>%
+  spread(source_type, mean_loss) %>%
+  mutate(train_and_other = train + eval_other) %>%
+  group_by(run_type, run) %>%
+  filter(train_and_other == max(train_and_other))
+selected_meta_true_d_3 %>%
+  arrange(desc(train_and_other))
+```

### 2019-12-06 cards_persistent_analysis.Rmd
Further tweak

@@
 
-This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other.
-
+This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other, but might work better with persistent
 ```{r}
 selected_meta_true_d_3 = meta_true_d %>%
-  filter(meta_task=="toggle_losers",
-         !grepl("persistent", run_type)) %>%
+  filter(meta_task=="toggle_losers") %>%
   mutate(source_type=case_when(

### 2019-12-06 cards_persistent_analysis.Rmd
Another approach

--- 2019-12-06 cards_persistent_analysis.Rmd
@@
 
-This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other.
-
+This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other, but might work better with persistent
 ```{r}
-selected_meta_true_d_3 = meta_true_d %>%
-  filter(meta_task=="toggle_losers",
-         !grepl("persistent", run_type)) %>%
+selected_meta_true_d_2 = meta_true_d %>%
+  filter(meta_task=="toggle_losers") %>%
   mutate(source_type=case_when(
@@
   filter(train_and_other == max(train_and_other))
-selected_meta_true_d_3 %>%
+selected_meta_true_d_2 %>%
   arrange(desc(train_and_other))
 ```
+
+Also somewhat promising:
+```{r}
+source_task_loss_d = loss_d %>%
+  filter(task == "game_straight_flush_l_0_bv_0_sr_0:train") %>%
+  select(epoch, run, run_type, loss) %>%
+  rename(source_task_base_loss = loss)
+
+selected_meta_true_d_3 = meta_true_d %>%
+  filter(meta_task=="toggle_losers") %>%
+  mutate(source_type=case_when(
+    base_task_toe == "example_is_train" ~ "train",
+    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
+    T ~ "eval_other")) %>%
+  group_by(run_type, run, epoch, source_type) %>%
+  summarize(mean_loss=mean(loss)) %>%
+  ungroup() %>%
+  spread(source_type, mean_loss) %>%
+  left_join(source_task_loss_d) %>%
+  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
+  group_by(run_type, run) %>%
+  filter(source_loss_and_other == max(source_loss_and_other))
+selected_meta_true_d_3 %>%
+  arrange(desc(source_loss_and_other))
+```

### 2019-12-07 writing/poster/HoMM_transferable_skills_poster.tex
Incorporating comments from Jay, tweaking, references

--- 2019-12-06 writing/poster/HoMM_transferable_skills_poster.tex
@@
 
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
-
 \title{Zero-Shot Task Adaptation by Homoiconic Meta-mapping (HoMM)}
@@
 \begin{block}{\huge Intro: zero-shot adaptation}
-\vspace{-0.6em}
+\vspace{-0.4em}
 \begin{itemize}
@@
 \begin{block}{\huge Meta-mapping}
-\vspace{-0.6em}
+\vspace{-0.4em}
 \begin{itemize}
@@
 \item We suggest it's then useful to think of transformations over functions, that is, functions which take other functions as input and/or output.
-\item We call these higher-level functions \emph{meta-mappings}. They are functions which take basic functions as input and produce other basic functions as output.
-\item For example, we could have a try-to-lose function which takes as input a function that tries to win money at poker, and outputs a function which tries to lose money at poker.
-\item We suggest that meta-mappings are a useful way to think about human-like zero-shot adaptation.
+\item We call these higher-level functions \emph{meta-mappings}. They are functions that transform basic tasks. 
+\item For example, we could have a try-to-lose meta-mapping which takes as input a function that tries to win money at a card game, and outputs a function which tries to lose money at that game.
+\item We suggest that meta-mappings are a useful perspective on human-like zero-shot adaptation.
 \end{itemize}
@@
 \begin{block}{\huge Functional analogy}
-\vspace{-0.6em}
+\vspace{-0.5em}
 \begin{itemize}
 \item Meta-mappings can be learned in the same way that other functions are learned -- using a deep network to approximate the function.
-\item We learn a meta-mapping from a dataset of example (input function, output function) tuples, analogously to learning a basic task from example tuples of (image, label), or (hand, bet, reward). 
+\item We can learn a meta-mapping from a dataset of example (input function, output function) tuples, analogously to learning a basic task from example tuples of (image, label), or (hand, bet, reward).
+\item We use this analogy to propose a homoiconic architecture for meta-mapping.
 \end{itemize}
+\vspace{0.2em}
 \end{block}
@@
 \begin{column}[t]{0.496\textwidth}
-\begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
+\begin{block}{\huge Homoiconic Meta-Mapping architectures}
 \vspace{-0.5em}
@@
 \begin{column}[t]{0.48\textwidth}
-\textbf{Basic tasks (meta-learning):}
+\textbf{Basic tasks (meta-learning, panel a):}
 \begin{itemize}
@@
 \begin{column}[t]{0.48\textwidth}
-\textbf{Meta-mappings (zero-shot task performance):}
+\textbf{Meta-mappings (zero-shot adaptation, b-c):}
 \begin{itemize}
-\item We exploit the analogy above to use \emph{the same meta-learning system} for meta-mappings.
+\item We exploit the analogy above to use \emph{the same meta-learning system} for meta-mappings (panel b).
 \item We pass a dataset of example function mappings \(\{(z^{func}_{in}, z^{func}_{out}\}\) through \(\mathcal{M}\) to produce a meta-mapping embedding \(z^{meta}\). 
 \item We parameterize \(F\) as before, and can pass a new function embedding through \(F\) to guess an embedding for a transformed task \(z^{func,pred}\).
-\item We can use \(z^{func,pred}\) to perform a transformed task zero-shot (or train to match a target).
-\item Parsimonious, same networks as basic meta-learning.
+\item \(z^{func,pred}\) can then be used to perform the transformed task zero-shot.
+\item This approach is parsimonious and homoiconic.
 \end{itemize}
@@
 \end{columns}
-
+\vspace{0.4em}
 \begin{figure}[H]
@@
 \end{figure}
+\vspace{-0.7em}
 \end{block}
@@
 \begin{itemize}
-\item Basic tasks: regress polynomials (degree \(\leq 3\)) in 4 variables from examples. 
-\item Meta-mappings: transform polynomial by permuting variables, adding or multiplying constants, squaring. 
-\item Good zero-shot performance!
+\item Basic tasks: regress polynomials (degree \(\leq 2\)) in 4 variables from examples. 
+\item Meta-mappings: transform polynomial by permuting inputs, adding or multiplying constants, or squaring. 
+\item Good 0-shot results, even with held-out mappings!
 \end{itemize}
@@
 \item Basic tasks: input is hand, make bet, get stochastic reward. A variety of games with different rules. 
-\item Meta-mappings: transform game by trying to lose, changing values of suits. 
-\item Good zero-shot performance!
+\item Meta-mappings: transform game by trying to lose, or changing values of suits. 
+\item Good performance, but depends on hold-outs!
 \end{itemize}
@@
 \begin{column}[t]{0.248\textwidth}
-\begin{block}{\huge Why \& prior work}
+\begin{block}{\huge Prior work and our contribution\vspace{0.2em}}
+\vspace{-0.6em}
 \begin{itemize}
-\item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
-\item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
-\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language alone.
-\item Meta-mapping thus offers a happy intermediate between meta-learning (which requires data on the new task), and zero-shot performance from language alone.
+\item Meta-learning \citep[e.g.][]{Vinyals2016, Finn2017a} allows performing new tasks from little data, but not zero-shot.
+\item Prior work has considered zero-shot task performance from language descriptions, see \citet{Xian2018}.
+\item Other prior work has considered using prior task similarity \citep[e.g.][]{Pal2019}, but has not used function-transformation approaches like ours.
+\item Transforming a task representation provides a richer and more explicit way to use prior task knowledge.
+\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language directly (see below).
 \end{itemize}
@@
 \end{block}
-\begin{block}{\huge Conclusions}
+\begin{block}{\huge Conclusions\vspace{0.2em}}
+\vspace{-0.6em}
+\begin{itemize}
+\item We propose \emph{meta-mappings}, a new perspective on zero-shot task performance via transformation of prior tasks. 
+\item We propose homoiconic meta-mapping architectures as a parsimonious implementation that exploits the analogy between meta-mappings and basic tasks. 
+\item We demonstrate the success of our approach, and show it outperforms a zero-shot language baseline.\\[0.4em] 
+\item Check out our paper for additional studies, including:
+    \begin{itemize}
+    \large
+    \item Details on language cues and comparisons.
+    \item Lesions and baselines, like separate networks for basic-tasks and meta-mapping, and a non-hyper-network approach. 
+    \item Applications to continual learning.
+    \end{itemize}
+\end{itemize}
+\end{block}
+
+\begin{block}{\huge References\vspace{0.2em}}
+\vspace{-0.1em}
+{
+\scriptsize
+\bibliographystyle{plainnat}
+\bibliography{../arrr.bib}
+}
 \end{block}

### 2020-01-07 run_cards.py
Doing eval properly

@@ -11,7 +11,7 @@ import simple_card_games
 
 run_config = default_run_config.default_run_config
 run_config.update({
-    "output_dir": "presentable_results/basic/",
+    "output_dir": "presentable_results/exact_eval/",
 
     "game_types": ["high_card","straight_flush",  "match", "pairs_and_high", "sum_under"],
     "option_names": ["suits_rule", "losers", "black_valuable"],
@@ -82,7 +82,7 @@ if False:  # enable for persistent reps
         "output_dir": run_config["output_dir"][:-1] + "_persistent/", 
     })
 
-if True:  # enable for language baseline
+if False:  # enable for language baseline
     run_config.update({
         "train_language_base": True,
         "train_base": False,
@@ -136,6 +136,8 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
         self.base_eval_tasks = [simple_card_games.game_from_def(t) for t in self.base_eval_tasks]
 
         self.game_str_to_task = {str(t): t for t in self.base_train_tasks + self.base_eval_tasks}
+
+        self.all_possible_hands = np.array([self.encode_hand(h) for h in self.base_train_tasks[0].hands], dtype=np.float32)
 
 
     def fill_buffers(self, num_data_points=1024):
@@ -274,8 +276,9 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
         actions = [np.argmax(act_probs[i, :],
                              axis=-1) for i in range(len(act_probs))]
         bets = [self.bets[a] for a in actions]
-        rs = [game.play(hands[i], self.bets[a]) for i, a in enumerate(actions)]
-        return np.mean(rs)
+        bet_dict = {h: b for (h, b) in zip(hands, bets)}
+        #rs = [game.play(hands[i], self.bets[a]) for i, a in enumerate(actions)]
+        return game.compute_expected_return(max_bet=1., policy=bet_dict, ties="nobody_wins") 
 
     def build_feed_dict(self, task, lr=None, fed_embedding=None,
                         call_type="base_standard_train"):
@@ -292,36 +295,39 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
             targets, target_mask = self._outcomes_to_targets(outcomes)
             feed_dict[self.base_target_ph] = targets 
             feed_dict[self.base_target_mask_ph] = target_mask
+            if train_or_eval == "eval" and call_type != "standard":  # eval on all possible hands
+                feed_dict[self.base_input_ph] = self.all_possible_hands 
 
         return feed_dict
[…]

### 2020-01-08 cards_persistent_analysis.Rmd
Analyzing new data, and making data for generating dissertation figure

@@
 ```{r}
-parent_dir = "."
-subdirs = c(#"results_for_humans_with_library_2", 
-            "results_for_humans_with_library_3", "results_for_humans_with_library_4",
-            #"results_for_humans_with_library_persistent",  "results_for_humans_with_library_persistent_2", "results_for_humans_with_library_persistent_3",  "results_for_humans_with_library_persistent_4",
-            "results_for_humans_with_library_persistent_5",  "results_for_humans_with_library_persistent_6",
-            #"results_for_humans_with_library_persistent_7", 
-            #"results_for_humans_with_library_persistent_8", 
-            "results_for_humans_with_library_persistent_9",
-            "results_for_humans_with_library_persistent_10"
-            )
-num_runs = 2
+parent_dir = "./presentable_results"
+subdirs = c("exact_eval")
+language_subdirs = c("exact_eval/language")
+
+num_runs = 5
 ```
@@
 load_d = function(results_dir, result_subdirs, num_runs, file_type) {
-  d = data.frame()
+  d = replicate(num_runs * length(result_subdirs), data.frame())
+  index = 1
   for (run_i in 0:(num_runs-1)) {
@@
                run_type = result_subdir)
-      d = d %>%
-        bind_rows(this_d)
+      d[[index]] = this_d
+      index = index + 1
     }
-
   }
+  d = bind_rows(d)
   return(d)
@@
 loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
+lang_d = load_d(parent_dir, language_subdirs, num_runs, "language_losses")
 meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
@@
   filter(!meta, grepl("rewards", task)) %>%
-  mutate(task = sub("_rewards", "", task),
+  mutate(task = sub("_expected_rewards", "", task),
          train_or_eval = ifelse(grepl("straight_flush_l_1", task), "eval", "train"))
+
+```
+
+```{r}
+lang_d = lang_d %>%
+  filter(epoch %% 100 == 0) %>%
+  gather(task, loss, -epoch, -run, -run_type) %>%
+  separate(task, c("task", "train_or_eval"), ":") %>%
+  mutate(task = sub("_expected_rewards", "", task))
 
@@
   facet_grid(run_type ~ meta)
+```
+```{r}
+ggplot(loss_d %>%
+         filter(task == "game_straight_flush_l_0_bv_0_sr_0:train"),
+       aes(x=epoch, y=loss, color=train_or_eval)) +
+  geom_line(stat="summary",
+            fun.y="mean") +
+  facet_grid(run_type ~ run)
 ```
@@
 selected_meta_true_d_3 = meta_true_d %>%
+  filter(epoch > 5000, epoch < 50000) %>%
   filter(meta_task=="toggle_losers") %>%
@@
 ```
+
+```{r}
+# window_size = 1000
+# 
+# sliding_window_selected_meta_true_d = meta_true_d %>%
+#   filter(epoch < 50000) %>%
+#   filter(meta_task=="toggle_losers") %>%
+#   mutate(source_type=case_when(
+#     base_task_toe == "example_is_train" ~ "train",
+#     source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
+#     T ~ "eval_other")) %>%
+#   group_by(run_type, run, epoch, source_type) %>%
+#   summarize(mean_loss=mean(loss)) %>%
+#   ungroup() %>%
+#   spread(source_type, mean_loss) %>%
+#   left_join(source_task_loss_d) %>%
+#   mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
+#   mutate(window = epoch %/% window_size) %>%
+#   group_by(run_type, run, window) %>%
+#   summarize(source_loss = mean(source_task_base_loss), eval_other = mean(eval_other), source_loss_and_other = mean(source_loss_and_other), eval_target = mean(eval_target)) %>%
+#   ungroup() %>%
+#   group_by(run_type, run) %>%
+#   filter(source_loss_and_other == max(source_loss_and_other))
+# sliding_window_selected_meta_true_d %>%
+#   arrange(desc(source_loss_and_other))
+```
+
+# language baselines
+
+```{r}
+ggplot(lang_d,
+       aes(x=epoch, y=loss, color=train_or_eval)) +
+  geom_line(stat="summary",
+            fun.y="mean") +
+  facet_grid(run_type ~ run)
+```
+
+Equivalent selection for the language baselines to that used above:
+```{r}
+selected_lang_d = lang_d %>%
+  filter(epoch > 5000,
+         epoch < 50000) %>%
+  mutate(task_type=case_when(
+    task == "game_straight_flush_l_0_bv_0_sr_0" ~ "source",
+    task == "game_straight_flush_l_1_bv_0_sr_0" ~ "eval_target",
+    train_or_eval == "eval" ~ "eval_other",
+    T ~ "train_other")) %>%
+  group_by(run_type, run, epoch, task_type) %>%
+  summarize(mean_loss=mean(loss)) %>%
+  ungroup() %>%
+  spread(task_type, mean_loss) %>%
+  mutate(source_loss_and_other = source + eval_other) %>%
+  group_by(run_type, run) %>%
+  filter(source_loss_and_other == max(source_loss_and_other))
+selected_lang_d %>%
+  arrange(desc(source_loss_and_other))
+```
+
+# data for figure
+
+```{r}
+diss_figure_data = bind_rows(
+  selected_lang_d %>%
+    ungroup() %>%
+    select(run, source, eval_target) %>%
+    mutate(result_type = "Language baseline"),
+  selected_meta_true_d_3 %>%
+    ungroup() %>%
+    rename(source=source_task_base_loss) %>%
+    select(run, source, eval_target) %>%
+    mutate(result_type = "HoMM")) %>%
+  gather(task, expected_reward, source, eval_target) %>%
+  mutate(expected_reward = expected_reward / max(expected_reward))  # different scalings
+```
+
+```{r}
+#write_csv()
+```

### 2020-01-08 cards_persistent_analysis.Rmd
Tweaks for dissertation data

@@
     mutate(result_type = "HoMM")) %>%
-  gather(task, expected_reward, source, eval_target) %>%
-  mutate(expected_reward = expected_reward / max(expected_reward))  # different scalings
+  gather(task, expected_reward, source, eval_target)
 ```
@@
 ```{r}
-#write_csv()
+write_csv(diss_figure_data, "~/Documents/grad/res/psych/cards/analysis/HoMM_data.csv")
 ```

### 2020-03-26 run_cards.py
Some control experiments

@@ -19,6 +19,8 @@ run_config.update({
     "losers": [True, False],
     "black_valuable": [True, False],
 
+    "metaclass_lesion": False,  # If True, don't train meta-classifications 
+
     "softmax_beta": 8,
 
     "bets": [0, 1, 2],
@@ -44,11 +46,11 @@ run_config.update({
     "min_language_learning_rate": 3e-8,
     "min_meta_learning_rate": 3e-8,
 
-    "num_epochs": 100000,
+    "num_epochs": 50000,
     "eval_every": 20,
 
-    "num_runs": 5,
-    "run_offset": 0
+    "num_runs": 1,
+    "run_offset": 4
 })
 
 architecture_config = default_architecture_config.default_architecture_config
@@ -82,6 +84,15 @@ if False:  # enable for persistent reps
         "output_dir": run_config["output_dir"][:-1] + "_persistent/", 
     })
 
+if False:  # enable for task-conditioned
+    architecture_config.update({
+        "task_conditioned_not_hyper": True,
+        "F_num_hidden_layers": 3,
+    })
+    run_config.update({
+        "output_dir": run_config["output_dir"] + "tcnh_more_complex/", 
+    })
+
 if False:  # enable for language baseline
     run_config.update({
         "train_language_base": True,
@@ -96,6 +107,14 @@ if False:  # enable for language baseline
     architecture_config.update({
         "max_sentence_len": 8,
     })
+
+if True:  # enable for meta-class lesion
+    run_config.update({
+        "metaclass_lesion": True,
+        "output_dir": run_config["output_dir"] + "metaclass_lesion/", 
+    })
+    
+
 
 
 class cards_HoMM_model(HoMM_model.HoMM_model):
@@ -117,7 +136,10 @@ class cards_HoMM_model(HoMM_model.HoMM_model):
 
 
         # set up the meta tasks
-        self.meta_class_train_tasks = ["is_" + g for g in run_config["game_types"]] + ["is_" + o for o in run_config["option_names"]] 
+        if run_config["metaclass_lesion"]: 
+            self.meta_class_train_tasks = []
+        else:
+            self.meta_class_train_tasks = ["is_" + g for g in run_config["game_types"]] + ["is_" + o for o in run_config["option_names"]] 
         self.meta_class_eval_tasks = [] 
 
         self.meta_map_train_tasks = ["toggle_" + o for o in run_config["option_names"]] 

### 2020-03-26 cards_model_analysis.Rmd
Language TCNH analysis

--- 2020-01-08 cards_persistent_analysis.Rmd
@@
 subdirs = c("exact_eval")
-language_subdirs = c("exact_eval/language")
+language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")
 
@@
   group_by(run_type, run) %>%
-  filter(source_loss_and_other == max(source_loss_and_other))
+  filter(source_loss_and_other == max(source_loss_and_other)) %>%
+  slice(1) # take first where multiple minima
 selected_lang_d %>%
@@
   selected_lang_d %>%
+    filter(run_type == "exact_eval/language") %>%
     ungroup() %>%
@@
     mutate(result_type = "Language baseline"),
+  selected_lang_d %>%
+    filter(run_type == "exact_eval/tcnh_more_complex/language") %>%
+    ungroup() %>%
+    select(run, source, eval_target) %>%
+    mutate(result_type = "Language baseline\n(task-conditioned)"),
   selected_meta_true_d_3 %>%

### 2020-03-30 cards_model_analysis.Rmd
Metaclass lesion

@@
 ---
-title: "Cards persistent analysis"
+title: "Cards model analysis"
 author: "Andrew Lampinen"
@@
 parent_dir = "./presentable_results"
-subdirs = c("exact_eval")
+subdirs = c("exact_eval", "exact_eval/metaclass_lesion")
 language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")
@@
   group_by(run_type, run) %>%
-  filter(source_loss_and_other == max(source_loss_and_other))
+  filter(source_loss_and_other == max(source_loss_and_other)) %>%
+  slice(1) # take first where multiple minima
 selected_meta_true_d_3 %>%
@@
     ungroup() %>%
+    filter(run_type == "exact_eval/metaclass_lesion") %>%
+    rename(source=source_task_base_loss) %>%
+    select(run, source, eval_target) %>%
+    mutate(result_type = "Meta-class lesion"),
+  selected_meta_true_d_3 %>%
+    ungroup() %>%
+    filter(run_type == "exact_eval") %>%
     rename(source=source_task_base_loss) %>%

### 2020-04-22 cards_model_analysis.Rmd
Basic meta-learning plot + CIs

@@
 ```
+
+## Basic meta-learning plot
+```{r}
+theme_set(theme_classic())
+```
+
+```{r}
+summarized_loss_d = loss_d %>%
+  filter(run_type == "exact_eval",
+         !meta) %>%
+  group_by(run, epoch, train_or_eval) %>%
+  summarize(loss = mean(loss, na.rm=T) / 0.53)
+```
+
+```{r}
+ggplot(summarized_loss_d,
+       aes(x=epoch, y=loss, color=train_or_eval)) +
+  geom_line(aes(group=interaction(run, train_or_eval)),
+            alpha=0.2) +
+  geom_line(stat="summary",
+            fun.y="mean",
+            size=1) +
+  scale_color_manual(breaks=c("train", "eval"), 
+                     labels=c("Trained\ngames", "Held-out\ngames"),
+                     values=c("#4d9221", "#c51b7d")) +
+  labs(y="Average meta-learning rewards\n(% of optimal)", x="Epoch") +
+  scale_y_continuous(breaks=c(0, 0.5, 1), labels=c("0%", "50%", "100%")) +
+  guides(color=guide_legend(title=NULL)) +
+  theme(legend.position=c(0.8, 0.25),
+        legend.key.size = unit(1.5, "lines"))
+
+ggsave("../metamapping_paper/figures/basic_meta_learning_cards.png", width=4, height=3)
+ggsave("../../psych/dissertation/3-human-adaptation/figures/basic_meta_learning_cards.png", width=5, height=3)
+```
+
+```{r}
+set.seed(0)  # reproducibility
+summarized_loss_d %>%
+  filter(epoch %in% c(0, 5000)) %>%
+  group_by(train_or_eval, epoch) %>%
+  do(results=mean_cl_boot(.$loss, na.rm=T)) %>%
+  mutate(mean=results$y,
+         CIlow=results$ymin,
+         CIhigh=results$ymax)
+```

### 2020-04-27 run_cards.py
Adding non-homoiconic option

@@ -84,6 +84,14 @@ if False:  # enable for persistent reps
         "output_dir": run_config["output_dir"][:-1] + "_persistent/", 
     })
 
+if False:  # enable for nonhomiconic, after ensuring HoMM is on correct branch 
+    architecture_config.update({
+        "nonhomoiconic": True,
+    })
+    run_config.update({
+        "output_dir": run_config["output_dir"] + "nonhomoiconic/",
+    })
+
 if False:  # enable for task-conditioned
     architecture_config.update({
         "task_conditioned_not_hyper": True,
@@ -108,7 +116,7 @@ if False:  # enable for language baseline
         "max_sentence_len": 8,
     })
 
-if True:  # enable for meta-class lesion
+if False:  # enable for meta-class lesion
     run_config.update({
         "metaclass_lesion": True,
         "output_dir": run_config["output_dir"] + "metaclass_lesion/", 

### 2020-04-28 cards_model_analysis.Rmd
nonhomoiconic analyses (part 1)

@@
 parent_dir = "./presentable_results"
-subdirs = c("exact_eval", "exact_eval/metaclass_lesion")
+subdirs = c("exact_eval", "exact_eval/metaclass_lesion", "exact_eval/nonhomoiconic")
 language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")
@@
     ungroup() %>%
+    filter(run_type == "exact_eval/nonhomoiconic") %>%
+    rename(source=source_task_base_loss) %>%
+    select(run, source, eval_target) %>%
+    mutate(result_type = "Nonhomoiconic"),
+  selected_meta_true_d_3 %>%
+    ungroup() %>%
     filter(run_type == "exact_eval") %>%

### 2020-11-18 cards_model_analysis.Rmd
README updates and as-yet-uncommited analyses

@@
 language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")
+language_meta_subdirs = c("exact_eval/language_meta", "exact_eval/language_meta_2", "exact_eval/language_meta_3", "exact_eval/language_meta_4")
 
@@
 meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
+lang_meta_true_d = load_d(parent_dir, language_meta_subdirs, num_runs, "language_meta_true_losses")
 ```
@@
 meta_true_d = meta_true_d %>%
+  filter(epoch %% 100 == 0) %>%
+  gather(task, loss, -epoch, -run, -run_type) %>%
+  separate(task, c("meta_task", "mapping_toe", "base_task_toe", "source", "target"), ":|->")
+
+```
+
+```{r}
+lang_meta_true_d = lang_meta_true_d %>%
   filter(epoch %% 100 == 0) %>%
@@
 ```
+
+# language meta
+
+```{r}
+ggplot(lang_meta_true_d %>% 
+         filter(meta_task == "toggle_losers"),
+       aes(x=epoch, y=loss, color=base_task_toe)) +
+  geom_line(stat="summary",
+            fun.y="mean") +
+  facet_grid(run_type ~ run)
+```
+
+```{r}
+ggplot(lang_meta_true_d %>% 
+         filter(meta_task == "toggle_losers",
+                source == "game_straight_flush_l_0_bv_0_sr_0"),
+       aes(x=epoch, y=loss, color=base_task_toe)) +
+  geom_line(stat="summary",
+            fun.y="mean") +
+  facet_grid(run_type ~ run)
+```
